### 2023-01-16 latex/includes/pressure_vessel_problem.tex
Analysis and latex formatting quite done

\begin{table}
\centering
\caption{Statistical Information about function values for Pressure Vessel Design}
\label{function_values:pressure_vessel_problem}
\begin{tabular}{lrrrrr}
\toprule
Algorithm &      Min F &        Mean F &      Median F &          Max F &      StdDev F \\
\midrule
       EP & 0.94974179 &    0.99959274 &    0.95597819 &     1.41652156 &    0.10256309 \\
       ES & 0.94985828 &    3.07906532 &    1.90278615 &    11.41620650 &    2.47339648 \\
       GA & 4.61928311 &  383.23040981 &  262.27555979 &  1747.41758530 &  362.98174772 \\
    BeesA & 1.05944833 & 5212.47847291 & 2094.42824655 & 30412.73885965 & 7297.64717603 \\
      FFA & 0.95407161 &    1.05749808 &    1.05432826 &     1.16958618 &    0.04485239 \\
      PSO & 0.94936617 &    1.00652465 &    0.94974267 &     3.01988559 &    0.25222125 \\
\bottomrule
\end{tabular}
\end{table}

### 2023-01-16 latex/includes/spring_problem.tex
Analysis and latex formatting quite done

\begin{table}
\centering
\caption{Statistical Information about function values for Spring Tension Design}
\label{function_values:spring_problem}
\begin{tabular}{lrrrrr}
\toprule
Algorithm &      Min F &     Mean F &   Median F &      Max F &   StdDev F \\
\midrule
       EP & 0.00607563 & 0.00607590 & 0.00607570 & 0.00607834 & 0.00000044 \\
       ES & 0.00607564 & 0.00609326 & 0.00608915 & 0.00616308 & 0.00001810 \\
       GA & 0.00610989 & 0.00670843 & 0.00663331 & 0.00805670 & 0.00045944 \\
    BeesA & 0.00607781 & 0.00632310 & 0.00625074 & 0.00724816 & 0.00025469 \\
      FFA & 0.00607563 & 0.00607593 & 0.00607576 & 0.00607847 & 0.00000047 \\
      PSO & 0.00607563 & 0.00607563 & 0.00607563 & 0.00607563 & 0.00000000 \\
\bottomrule
\end{tabular}
\end{table}

### 2023-01-16 analysis.py

@@ -24,6 +24,32 @@ problem_desc = {'spring_problem': 'Spring Tension Design',
                 'pressure_vessel_problem': 'Pressure Vessel Design'}
 
 
+def fit_results_cleanup(fit_results):
+    """
+    Results Cleanup
+    :param fit_results: raw results
+    :return: cleaned results
+    """
+    new_fit_results = list()
+    for node in fit_results:
+        new_fit_results.append(node[1])
+    return new_fit_results
+
+
+def population_cleanup(population):
+    min_max_mean = {"min": [],
+                    "max": [],
+                    "avg": []}
+    for i in range(0, len(population)):
+        pop_data = list()
+        for j in range(0, len(population[i])):
+            pop_data.append(population[i][j][1][0])
+        min_max_mean["min"].append(np.min(pop_data))
+        min_max_mean["max"].append(np.max(pop_data))
+        min_max_mean["avg"].append(np.mean(pop_data))
+    return min_max_mean
+
+
 def friedman_test(sol0,
                   sol1,
                   sol2,
@@ -87,37 +113,29 @@ def ordinary_statistics(fit_results):
         stats[problem] = dict()
         stats[problem]['desc'] = problem_desc[problem]
         stats[problem]['results'] = list()
+        solver_data = dict()
         for solver in fit_results[problem]:
-            s = min_max_avg_std(fit_results[problem][solver])
+            data = fit_results_cleanup(fit_results[problem][solver])
+            solver_data[solver] = data
+            s = min_max_avg_std(data)
             stats[problem]['results'].append([alg_desc[solver],
                                               s['fmin'],
                                               s['favg'],
-                                              s['fmean'],
+                                              s['fmedian'],
                                               s['fmax'],
                                               s['fstd']])
-        stats[problem]['significance'] = friedman_test(fit_results[problem]['solver_ep'],
-                                                       fit_results[problem]['solver_es'],
-                                                       fit_results[problem]['solver_ga'],
-                                                       fit_results[problem]['solver_beesa'],
-                                                       fit_results[problem]['solver_ffa'],
-                                                       fit_results[problem]['solver_pso'])
+
+        stats[problem]['significance'] = friedman_test(solver_data['solve_ep'],
+                                                       solver_data['solve_es'],
+                                                       solver_data['solve_ga'],
+                                                       solver_data['solve_beesa'],
[…]

### 2023-01-16 to_latex.py

@@ -1,0 +1,132 @@
+"""
+Computational Work 02 - Evolutionary Computation
+Authors: Augusto Mathias Adams - augusto.adams@ufpr.br - GRR20172143
+         Caio Phillipe Mizerkowski - caiomizerkowski@gmail.com - GRR20166403
+         Christian Piltz Araújo - christian0294@yahoo.com.br - GRR20172197
+         Vinícius Eduardo dos Reis - eduardo.reis02@gmail.com - GRR20175957
+
+Analysis Formatter
+"""
+
+import numpy as np
+import pandas as pd
+import seaborn as sns
+import matplotlib.pyplot as plt
+import json
+
+
+def latex_results_table(results,
+                        desc,
+                        problem):
+
+    column_names = ["Algorithm", "Min F", "Mean F", "Median F", "Max F", "StdDev F"]
+
+    df = pd.DataFrame(results,
+                      columns=column_names)
+
+    content = df.to_latex(index=False,
+                          float_format="%.8f",
+                          escape=False,
+                          label="function_values:{:s}".format(problem),
+                          caption="Statistical Information about function values for {:s}".format(desc))
+
+    return content
+
+
+def latex_friedman_table(results):
+    column_names = ["Problem", "Statistics", "p-value"]
+
+    data = list()
+
+    for problem in results:
+        problem_name = results[problem]['desc']
+        statistics = results[problem]['significance'][0]
+        p_value = results[problem]['significance'][1]
+        data.append([problem_name, statistics, p_value])
+
+    df = pd.DataFrame(data,
+                      columns=column_names)
+
+    content = df.to_latex(index=False,
+                          float_format="%.8f",
+                          escape=False,
+                          label="friedman_test",
+                          caption="Significance Test Using Friedman Chi-Squared Test")
+
+    return content
+
+
+# statistical data
+
+with open("results/stats.json", "r") as f:
+    data = json.load(f)
+
+for problem in data:
+
+    desc = data[problem]['desc']
+
+    results = data[problem]['results']
+
+    content = latex_results_table(results,
+                                  desc,
+                                  problem)
+
+    with open("latex/includes/{:s}.tex".format(problem), "w") as f:
+        f.write(content)
+
+content = latex_friedman_table(data)
+
+with open("latex/includes/friedman_test.tex", "w") as f:
+    f.write(content)
[…]

### 2023-01-16 latex/article.tex
Article Building execution

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{mathtools}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{microtype}
\usepackage{float}
\usepackage{adjustbox}
\usepackage{booktabs,makecell,tabularx}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{verbatim}
\usepackage{xcolor}
\usepackage{graphics} % for pdf, bitmapped graphics files
\usepackage{epsfig} % for postscript graphics files
\usepackage{mathptmx} % assumes new font selection scheme installed
\usepackage{multicol}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\restylefloat{table}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\title{Swarm and Evolutionary Based Algorithms used for Optimization}
\author{
	\IEEEauthorblockN{Augusto Mathias Adams\IEEEauthorrefmark{1}, Caio Phillipe Mizerkowski\IEEEauthorrefmark{2}, Christian Piltz Araújo\IEEEauthorrefmark{3} and Vinicius Eduardo dos Reis\IEEEauthorrefmark{4}}\\
	\IEEEauthorblockA{\IEEEauthorrefmark{1}GRR20172143, augusto.adams@ufpr.br, \IEEEauthorrefmark{2}GRR20166403, caiomizerkowski@gmail.com,\\ \IEEEauthorrefmark{3}GRR20172197, christian0294@yahoo.com.br, \IEEEauthorrefmark{4}GRR20175957, eduardo.reis02@gmail.com}
}

\maketitle

\begin{abstract}
    In this paper, a study of evolution and swarm based algorithms is presented,
    using two classical engineering problems: \textit{Spring Tension} and \textit{Pressure Vessel
    Designs}. The test code for the problems was made using the \textit{Python Language},
    version 3.10 and uses \textit{MealPy} package, version 2.5.1,  to provide the algorithms.
    Thre algorithms were randomly chosen from a vaste list from MealPy algorithms:
    \textit{Evolutionary Programming (LevyEP)}, \textit{Evolution Strategies (OriginalES)} and
    \textit{Genetic Algorithm (BaseGA)} from \textit{evolutionary\_based} subpackage;
    \textit{Bees Algorithm (OriginalBeesA)}, \textit{Firefly Algorithm (OriginalFFA)} and
    \textit{Particle Swarm Optimization (OriginalPSO)} from \textit{swarm\_based} subpackage.
    Each problem was modeled using \textit{SciPy} package, with constraints implemented as
    \textit{penalty functions}. Each algorithm were optimized separately to extract the best
    solutions from each problem using the \textit{MealPy}'s \textit{Tuner} utility.
    The results, however, are dependant of algorithm and problem presented but from
    similarity test using Friedman's Chi-Squared test says that using any of the tested algorithm
    will produce similar results in the two optimization problems.
\end{abstract}

\begin{IEEEkeywords}
	Optimization Methods, Evolutionary Programming, Evolutionary and Swarm Based Strategies.
\end{IEEEkeywords}

\section{Introduction}
\label{sec:introduction}

The study comprizes two great areas of artificial intelligence: Evolutionary
and Swarm Inteligence algorithms.

Evolution: From Jason Brownlee's \textit{``Clever Algorithms''} -
\textit{Evolutionary Algorithms belong to the Evolutionary Computation
field of study concerned with computational methods inspired by the process
and mechanisms of biological evolution. The process of evolution by
means of natural selection (descent with modification) was proposed by
Darwin to account for the variety of life and its suitability (adaptive
fit) for its environment. The mechanisms of evolution describe how
evolution actually takes place through the modification and propagation
of genetic material (proteins). Evolutionary Algorithms are concerned
with investigating computational systems that resemble simplified ver-
sions of the processes and mechanisms of evolution toward achieving
the effects of these processes and mechanisms, namely the development
of adaptive systems. Additional subject areas that fall within the realm
of Evolutionary Computation are algorithms that seek to exploit the
properties from the related fields of Population Genetics, Population
Ecology, Coevolutionary Biology, and Developmental Biology.}

Swarm Optimization: From Jason Brownlee's \textit{``Clever Algorithms''} -
\textit{Swarm intelligence is the study of computational systems inspired by
the ‘collective intelligence’. Collective Intelligence emerges through the
cooperation of large numbers of homogeneous agents in the environment.
Examples include schools of fish, flocks of birds, and colonies of ants.
Such intelligence is decentralized, self-organizing and distributed through
out an environment. In nature such systems are commonly used to
solve problems such as effective foraging for food, prey evading, or
colony re-location. The information is typically stored throughout the
participating homogeneous agents, or is stored or communicated in
the environment itself such as through the use of pheromones in ants,
dancing in bees, and proximity in fish and birds.}

    \section{Spring Tension Design}

\label{sec:spring_problem}\subsection{Evolutionary Algorithms}

\label{subsec:spring_problem_evolutionary_based}

\subsection{Swarm Based Algorithms}

\label{subsec:spring_problem_swarm_based}

\section{Pressure Vessel Design}

\label{sec:pressure_vessel_problem}\subsection{Evolutionary Algorithms}

\label{subsec:pressure_vessel_problem_evolutionary_based}

\subsection{Swarm Based Algorithms}

\label{subsec:pressure_vessel_problem_swarm_based}

\section{Discussion}

The main objective of this work is demonstrate the inner work of a optimization class of algorithms called \textit{Quasi-Newton algorithms}. Four of them are presented, along with the results and analysis regarding convergence, function evaluations and function objective values.

For implementation, it was decided to put constraints on search space, because for the original search space of some functions, like Ackley and Rastrigin, there are other minimas that will confuse every algorithm tested for this paper, and there is no sense on test a local minima procedure on these conditions. To restrain the initial solution to some region in the search space was a cheap and ready solution to avoid the algorithms to stop because of stumbling upon the wrong minimum.

The \textit{Levenberg-Marquardt Algorithm} implemented for this paper is very sensitive to hyperparameters, namely $\alpha$ and $\lambda$, which was not tunned to every function, so, the conspicuous performance variation is noticeable along the results. LMA is known to be fast and reliable, but in our implementation it was found a little tricky to get the hyperparameters right for all the test functions. But for Rosenbrock and Rastrigin, it is the best option, even for lame implementations like ours.

The \textit{Broyden–Fletcher–Goldfarb–Shanno} Algorithm was the only one that we decided to use it as is from \textit{SciPy}, because it has features desired for this work, like counting of function evaluations, gradient evaluation and iterations. It performed very well for Ackley and Booth Functions, and reasonably well for other functions.

The \textit{Davidon–Fletcher–Powell} Algorithm is not implemented in \textit{SciPy} but its equations shows that it is the dual of BFGS, so, it was easy to implement using some \textit{SciPy} code for BFGS algorithm. In the DFP procedure, there is a Hessian inversion to be evaluated every iteration, then, numerical imprecision would be taken into consideration evaluating its results. While in some cases it has a superb performance (Like Ackley Function), it has very poor performance in Rosenbrock Function and even in Beale Function. The increase of dimensions makes DFP suffer of numerical imprecision due to the Hessian inversion, except for Rastrigin, and it is the loser algorithm in other functions.

Finally, the \textit{Limited memory BFGS} has an average performance among the functions. The original algorithm was implemented using code found in the url https://github.com/qkolj/L-BFGS/blob/master/L-BFGS.ipynb.

In fact, there are no Quasi-Newton algorithms that solver the minima problem for an any function. From the standpoint of performance and convergence, all the algorithms have an average performance and a reasonable convergence, although we have to restrain the search space to a small area near the optimal solution.

\end{document}

### 2023-01-16 latex/includes/header.tex
Article Building execution

--- 2023-01-16 latex/article.tex
@@
     \textit{penalty functions}. Each algorithm were optimized separately to extract the best
-    solutions from each problem using the \textit{MealPy}'s \textit{Tuner} utility.
+    solutions from each problem using the \textit{MealPy\s} \textit{Tuner} utility.
     The results, however, are dependant of algorithm and problem presented but from
-    similarity test using Friedman's Chi-Squared test says that using any of the tested algorithm
-    will produce similar results in the two optimization problems.
+    similarity test using Friedman's Chi-Squared test, it would be suffice to say that using any
+    of the tested algorithm will produce similar results in these two optimization problems.
 \end{abstract}
@@
 dancing in bees, and proximity in fish and birds.}
-
-    \section{Spring Tension Design}
-
-\label{sec:spring_problem}\subsection{Evolutionary Algorithms}
-
-\label{subsec:spring_problem_evolutionary_based}
-
-\subsection{Swarm Based Algorithms}
-
-\label{subsec:spring_problem_swarm_based}
-
-\section{Pressure Vessel Design}
-
-\label{sec:pressure_vessel_problem}\subsection{Evolutionary Algorithms}
-
-\label{subsec:pressure_vessel_problem_evolutionary_based}
-
-\subsection{Swarm Based Algorithms}
-
-\label{subsec:pressure_vessel_problem_swarm_based}
-
-\section{Discussion}
-
-The main objective of this work is demonstrate the inner work of a optimization class of algorithms called \textit{Quasi-Newton algorithms}.
-Four of them are presented, along with the results and analysis regarding convergence, function evaluations and function objective values.
-
-For implementation, it was decided to put constraints on search space, because for the original search space of some functions, like Ackley and Rastrigin, there are other minimas that will confuse every algorithm tested for this paper, and there is no sense on test a local minima procedure on these conditions.
-To restrain the initial solution to some region in the search space was a cheap and ready solution to avoid the algorithms to stop because of stumbling upon the wrong minimum.
-
-The \textit{Levenberg-Marquardt Algorithm} implemented for this paper is very sensitive to hyperparameters, namely $\alpha$ and $\lambda$, which was not tunned to every function, so, the conspicuous performance variation is noticeable along the results.
-LMA is known to be fast and reliable, but in our implementation it was found a little tricky to get the hyperparameters right for all the test functions.
-But for Rosenbrock and Rastrigin, it is the best option, even for lame implementations like ours.
-
-The \textit{Broyden–Fletcher–Goldfarb–Shanno} Algorithm was the only one that we decided to use it as is from \textit{SciPy}, because it has features desired for this work, like counting of function evaluations, gradient evaluation and iterations.
-It performed very well for Ackley and Booth Functions, and reasonably well for other functions.
-
-The \textit{Davidon–Fletcher–Powell} Algorithm is not implemented in \textit{SciPy} but its equations shows that it is the dual of BFGS, so, it was easy to implement using some \textit{SciPy} code for BFGS algorithm.
-In the DFP procedure, there is a Hessian inversion to be evaluated every iteration, then, numerical imprecision would be taken into consideration evaluating its results.
-While in some cases it has a superb performance (Like Ackley Function), it has very poor performance in Rosenbrock Function and even in Beale Function.
-The increase of dimensions makes DFP suffer of numerical imprecision due to the Hessian inversion, except for Rastrigin, and it is the loser algorithm in other functions.
-
-Finally, the \textit{Limited memory BFGS} has an average performance among the functions.
-The original algorithm was implemented using code found in the url https://github.com/qkolj/L-BFGS/blob/master/L-BFGS.ipynb.
-
-In fact, there are no Quasi-Newton algorithms that solver the minima problem for an any function.
-From the standpoint of performance and convergence, all the algorithms have an average performance and a reasonable convergence, although we have to restrain the search space to a small area near the optimal solution.
-
-\end{document}

### 2023-01-16 latex/includes/pressure_vessel_problem_boxplot.tex
Article Building execution

\begin{figure}[H]
\centering
\caption{Boxplot for Pressure Vessel Design}
\label{fig:pressure_vessel_design_boxplot}
\includegraphics[scale=0.5]{images/pressure_vessel_problem_boxplot.png}
\end{figure}

### 2023-01-16 article_builder.py

@@ -1,0 +1,46 @@
+"""
+Computational Work 02 - Evolutionary Computation
+Authors: Augusto Mathias Adams - augusto.adams@ufpr.br - GRR20172143
+         Caio Phillipe Mizerkowski - caiomizerkowski@gmail.com - GRR20166403
+         Christian Piltz Araújo - christian0294@yahoo.com.br - GRR20172197
+         Vinícius Eduardo dos Reis - eduardo.reis02@gmail.com - GRR20175957
+
+Article Builder
+"""
+
+content = ""
+
+#: header
+with open("latex/includes/header.tex", "r") as f:
+    content += f.read()
+
+#: spring problem
+content += "\\section{Spring Tension Design}\n\n"
+content += "\\label{sec:spring_problem}"
+
+content += "\\subsection{Evolutionary Algorithms}\n\n"
+content += "\\label{subsec:spring_problem_evolutionary_based}\n\n"
+
+content += "\\subsection{Swarm Based Algorithms}\n\n"
+content += "\\label{subsec:spring_problem_swarm_based}\n\n"
+
+# pressure vessel problem
+
+content += "\\section{Pressure Vessel Design}\n\n"
+content += "\\label{sec:pressure_vessel_problem}"
+
+content += "\\subsection{Evolutionary Algorithms}\n\n"
+content += "\\label{subsec:pressure_vessel_problem_evolutionary_based}\n\n"
+
+content += "\\subsection{Swarm Based Algorithms}\n\n"
+content += "\\label{subsec:pressure_vessel_problem_swarm_based}\n\n"
+
+# Friedman's test
+
+# footer
+
+with open("latex/includes/footer.tex", "r") as f:
+    content += f.read()
+
+with open("latex/article.tex", "w") as f:
+    f.write(content)

### 2023-01-16 to_latex.py

@@ -10,7 +10,6 @@ Analysis Formatter
 
 import numpy as np
 import pandas as pd
-import seaborn as sns
 import matplotlib.pyplot as plt
 import json
 
@@ -19,7 +18,12 @@ def latex_results_table(results,
                         desc,
                         problem):
 
-    column_names = ["Algorithm", "Min F", "Mean F", "Median F", "Max F", "StdDev F"]
+    column_names = ["Algorithm",
+                    "Min F",
+                    "Mean F",
+                    "Median F",
+                    "Max F",
+                    "StdDev F"]
 
     df = pd.DataFrame(results,
                       columns=column_names)
@@ -97,6 +101,7 @@ problem_desc = {'spring_problem': 'Spring Tension Design',
 
 for problem in population_data:
     for solver in population_data[problem]:
+
         min = population_data[problem][solver]['min']
         max = population_data[problem][solver]['max']
         mean = population_data[problem][solver]['avg']
@@ -105,28 +110,87 @@ for problem in population_data:
 
         x = np.linspace(1, len(min), len(min))
 
-        plt.plot(x, min, label="Min values")
+        plt.plot(x, np.log(min), label="Min values")
 
-        plt.plot(x, mean, label="Mean values")
+        plt.plot(x, np.log(mean), label="Mean values")
 
-        plt.plot(x, max, label="Max values")
+        plt.plot(x, np.log(max), label="Max values")
 
-        plt.yscale('log')
+        #: plt.yscale('log')
 
         plt.title(alg_desc[solver] + " - " + problem_desc[problem])
 
         plt.xlabel("Epochs")
 
-        plt.ylabel("Obj. Fun Values")
+        plt.ylabel("Obj. Fun Values(log)")
 
         plt.legend()
 
         plt.grid()
 
-        plt.savefig("latex/images/" + problem + "_" + solver + ".jpg", dpi=600)
+        plt.savefig("latex/images/" + problem + "_" + solver + ".png", dpi=600)
 
-with open("results/fit_results.json", "r") as f:
+        content = """\\begin{figure}[H]
+        \\centering
+        \\caption{Convergence lines for """ + alg_desc[solver] + " - " + problem_desc[problem] + """}
+        \\label{fig:""" + problem + "_" + solver + """}
[…]

### 2023-01-17 latex/article.tex
Article Building execution

@@
 dancing in bees, and proximity in fish and birds.}
-
 \section{Spring Tension Design}

### 2023-01-17 latex/article.tex
Tweaking Functions to obtain literature grade results

@@
     \textit{penalty functions}. Each algorithm were optimized separately to extract the best
-    solutions from each problem using the \textit{MealPy\s} \textit{Tuner} utility.
+    solutions from each problem using the \textit{MealPy}'s \textit{Tuner} utility.
     The results, however, are dependant of algorithm and problem presented but from
@@
 
-\section{Introduction}
-\label{sec:introduction}
+\section{Definitions}
+\label{sec:definitions}
 
-The study comprizes two great areas of artificial intelligence: Evolutionary
-and Swarm Inteligence algorithms.
+The main objective of this paper is study evolutionary and swarm intelligence algorithms.
+We present the main concepts of these two algorithm's classes, along with the chosen algorithms
+definitions in this section. All citations made in this document are due to Swarm Intelligence classes
+and to \textit{MealPy}'s documentation, which points out the theoretical documentation for each
+implemented algorithm.
 
-Evolution: From Jason Brownlee's \textit{``Clever Algorithms''} -
-\textit{Evolutionary Algorithms belong to the Evolutionary Computation
+\textit{\textbf{Evolution}}: From Jason Brownlee's \textit{``Clever Algorithms''} -
+Evolutionary Algorithms belong to the Evolutionary Computation
 field of study concerned with computational methods inspired by the process
@@
 properties from the related fields of Population Genetics, Population
-Ecology, Coevolutionary Biology, and Developmental Biology.}
+Ecology, Coevolutionary Biology, and Developmental Biology.
 
-Swarm Optimization: From Jason Brownlee's \textit{``Clever Algorithms''} -
-\textit{Swarm intelligence is the study of computational systems inspired by
+\textit{\textbf{Swarm Intelligence}}: From Jason Brownlee's \textit{``Clever Algorithms''} -
+Swarm intelligence is the study of computational systems inspired by
 the ‘collective intelligence’. Collective Intelligence emerges through the
@@
 the environment itself such as through the use of pheromones in ants,
-dancing in bees, and proximity in fish and birds.}
-\section{Spring Tension Design}
+dancing in bees, and proximity in fish and birds.
 
-\label{sec:spring_problem}\subsection{Evolutionary Algorithms}
+\textit{\textbf{Evolutionary Programming:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
+Evolutionary Programming is a Global Optimization algorithm and is an instance of an Evolutionary
+Algorithm from the field of Evolutionary Computation. The approach is a sibling of other Evolutionary
+Algorithms such as the Genetic Algorithm, and Learning Classifier Systems. It is sometimes confused with Genetic
+Programming given the similarity in name, and more recently it shows a strong functional similarity to Evolution Strategies.
+Evolutionary Programming is inspired by the theory of evolution by means of natural selection. Specifically, the technique is inspired by
+macro-level or the species-level process of evolution (phenotype, hereditary, variation) and is not concerned with the genetic mechanisms of
+evolution (genome, chromosomes, genes, alleles).
 
-\label{subsec:spring_problem_evolutionary_based}
+\textit{\textbf{Evolutionary Strategies:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
+Evolution Strategies is a global optimization algorithm and is an instance of an Evolutionary Algorithm from the field of Evolutionary
+Computation. Evolution Strategies is a sibling technique to other Evolutionary Algorithms such as Genetic Algorithms (Section 3.2), Genetic
+Programming (Section 3.3), Learning Classifier Systems, and Evolutionary Programming. A popular descendant of
+the Evolution Strategies algorithm is the Covariance Matrix Adaptation Evolution Strategies (CMA-ES).
 
-\subsection{Swarm Based Algorithms}
+\textit{\textbf{Genetic Algorithms:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
+The Genetic Algorithm is an Adaptive Strategy and a Global Optimization technique. It is an Evolutionary Algorithm and belongs to the
+broader study of Evolutionary Computation. The Genetic Algorithm is a sibling of other Evolutionary Algorithms such as Genetic Programming,
+ Evolution Strategies, Evolutionary Programming, and Learning Classifier Systems. The Genetic Algorithm is a parent of a large number of variant techniques
+and sub-fields too numerous to list. The Genetic Algorithm is inspired by population genetics (including heredity and gene frequencies),
+and evolution at the population level, as well as the Mendelian understanding of the structure (such as chromosomes, genes, alleles) and mechanisms
+(such as recombination and mutation). This is the so-called new or modern synthesis of evolutionary biology.
 
-\label{subsec:spring_problem_swarm_based}
+\textit{\textbf{Particle Swarm Optimization:}} From Jason Brownlee's \textit{``Clever Algorithms''} - Particle Swarm Optimization belongs to the field of
+Swarm Intelligence and Collective Intelligence and is a sub-field of Computational Intelligence. Particle Swarm Optimization is related to other Swarm Intelligence
+algorithms such as Ant Colony Optimization and it is a baseline algorithm for many variations, too numerous to list. It is inspired by the social foraging behavior
+of some animals such as flocking behavior of birds and the schooling behavior of fish.
 
-\section{Pressure Vessel Design}
+\textit{\textbf{Firefly Algorithm:}} From Xin-She Yang \textit{``Nature-Inspired Metaheuristic Algorithms''} -
+The flashing light of fireflies is an amazing sight in the summer sky in the tropical and temperate regions. There are about two thousand firefly
+species, and most fireflies produce short and rhythmic flashes. The pattern of flashes is often unique for a particular species. The flashing light is
+produced by a process of bioluminescence, and the true functions of suchsignaling systems are still being debated. However, two fundamental functions
+of such flashes are to attract mating partners (communication), and to attract potential prey. In addition, flashing may also serve as a protective warning
+mechanism to remind potential predators of the bitter taste of fireflies. The firefly algorithm tries to mimic the attractiveness of Fireflies and has three
+basic rules:
 
-\label{sec:pressure_vessel_problem}\subsection{Evolutionary Algorithms}
+\begin{itemize}
+    \item All fireflies are unisex so that one firefly will be attracted to other
+          fireflies regardless of their sex;
+    \item Attractiveness is proportional to the their brightness, thus for any two
+          flashing fireflies, the less brighter one will move towards the brighter
+          one. The attractiveness is proportional to the brightness and they
+          both decrease as their distance increases. If there is no brighter one
+          than a particular firefly, it will move randomly;
+    \item The brightness of a firefly is affected or determined by the landscape
+          of the objective function.
+\end{itemize}
 
-\label{subsec:pressure_vessel_problem_evolutionary_based}
+\textit{\textbf{Bees Algorithm:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
+The Bees Algorithm beings to Bee Inspired Algorithms and the field of Swarm Intelligence, and more broadly the fields of Computational
+Intelligence and Metaheuristics. The Bees Algorithm is related to other Bee Inspired Algorithms, such as Bee Colony Optimization, and other
+Swarm Intelligence algorithms such as Ant Colony Optimization and Particle Swarm Optimization.
+It is inspired by the foraging behavior of honey bees. Honey bees collect nectar from vast areas around their hive (more than
+10 kilometers). Bee Colonies have been observed to send bees to collect nectar from flower patches relative to the amount of food available at
+each patch. Bees communicate with each other at the hive via a waggle dance that informs other bees in the hive as to the direction, distance,
+and quality rating of food sources.
 
-\subsection{Swarm Based Algorithms}
+\section{Metodology}
+\label{sec:metodology}
 
-\label{subsec:pressure_vessel_problem_swarm_based}
+\subsection{Optimimzation Problem Selection}
+The two problems selected for this paper were \textit{Spring Tension Design} and \textit{Pressure Vessel Design}. Although it was simple
+to choose the first two problems from the computational work statements, the choice was more than justified because these aroblems are well
+known in the literature. Thus, the problem selection was driven by which has more that one source to compare results.
+
+\subsection{Programming Language}
+
+The chosen programming language for the test code was \textit{Python Language}, version 3.10, because it is an opensource language easy to
+program and has a huge amount of packages regarding artificial intelligence, genetic algorithms and swarm based algorithms. From these packages it
+was selected \textit{MealPy} package, version 2.5.1, because it comprises all the algorithm's classed tested in this paper.
+
+\subsection{Algorithm Selection}
+
+The algorithm selection was made in two steps: first, it was extracted simple version of the two classes (evolutionary and swarm based) and
+then it was used a simple shuffle using
+
+\subsection{Model Parameters}
+
+For all models and problems, were selected the following parameters:
+
+\begin{itemize}
+    \item \textit{Runs}: 100 runs
+    \item \textit{Epochs}: 100 epochs
+    \item \textit{Population}: 100 initial points
+\end{itemize}
+
+The initial solutions were randomly selected using the same seed for all algorithms.
+
+\subsection{Model Tuning}
+
+\section{Results}
+\label{sec:results}\subsection{Spring Tension Design}
+
+\label{ssubec:spring_problem}\subsubsection{Evolutionary Algorithms}
+
+\label{subsubsec:spring_problem_evolutionary_based}
+
+\subsubsection{Swarm Based Algorithms}
+
+\label{subsubsec:spring_problem_swarm_based}
+
+\subsection{Pressure Vessel Design}
+
+\label{subsec:pressure_vessel_problem}\subsubsection{Evolutionary Algorithms}
+
+\label{subsubsec:pressure_vessel_problem_evolutionary_based}
+
+\subsubsection{Swarm Based Algorithms}
+
+\label{subsubsec:pressure_vessel_problem_swarm_based}
 

### 2023-01-17 latex/includes/header.tex
Tweaking Functions to obtain literature grade results

@@
 the environment itself such as through the use of pheromones in ants,
-dancing in bees, and proximity in fish and birds.}
+dancing in bees, and proximity in fish and birds.
+
+\textit{\textbf{Evolutionary Programming:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
+Evolutionary Programming is a Global Optimization algorithm and is an instance of an Evolutionary
+Algorithm from the field of Evolutionary Computation. The approach is a sibling of other Evolutionary
+Algorithms such as the Genetic Algorithm, and Learning Classifier Systems. It is sometimes confused with Genetic
+Programming given the similarity in name, and more recently it shows a strong functional similarity to Evolution Strategies.
+Evolutionary Programming is inspired by the theory of evolution by means of natural selection. Specifically, the technique is inspired by
+macro-level or the species-level process of evolution (phenotype, hereditary, variation) and is not concerned with the genetic mechanisms of
+evolution (genome, chromosomes, genes, alleles).
+
+\textit{\textbf{Evolutionary Strategies:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
+Evolution Strategies is a global optimization algorithm and is an instance of an Evolutionary Algorithm from the field of Evolutionary
+Computation. Evolution Strategies is a sibling technique to other Evolutionary Algorithms such as Genetic Algorithms (Section 3.2), Genetic
+Programming (Section 3.3), Learning Classifier Systems, and Evolutionary Programming. A popular descendant of
+the Evolution Strategies algorithm is the Covariance Matrix Adaptation Evolution Strategies (CMA-ES).
+
+\textit{\textbf{Genetic Algorithms:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
+The Genetic Algorithm is an Adaptive Strategy and a Global Optimization technique. It is an Evolutionary Algorithm and belongs to the
+broader study of Evolutionary Computation. The Genetic Algorithm is a sibling of other Evolutionary Algorithms such as Genetic Programming,
+ Evolution Strategies, Evolutionary Programming, and Learning Classifier Systems. The Genetic Algorithm is a parent of a large number of variant techniques
+and sub-fields too numerous to list. The Genetic Algorithm is inspired by population genetics (including heredity and gene frequencies),
+and evolution at the population level, as well as the Mendelian understanding of the structure (such as chromosomes, genes, alleles) and mechanisms
+(such as recombination and mutation). This is the so-called new or modern synthesis of evolutionary biology.
+
+\textit{\textbf{Particle Swarm Optimization:}} From Jason Brownlee's \textit{``Clever Algorithms''} - Particle Swarm Optimization belongs to the field of
+Swarm Intelligence and Collective Intelligence and is a sub-field of Computational Intelligence. Particle Swarm Optimization is related to other Swarm Intelligence
+algorithms such as Ant Colony Optimization and it is a baseline algorithm for many variations, too numerous to list. It is inspired by the social foraging behavior
+of some animals such as flocking behavior of birds and the schooling behavior of fish.
+
+\textit{\textbf{Firefly Algorithm:}} From Xin-She Yang \textit{``Nature-Inspired Metaheuristic Algorithms''} -
+The flashing light of fireflies is an amazing sight in the summer sky in the tropical and temperate regions. There are about two thousand firefly
+species, and most fireflies produce short and rhythmic flashes. The pattern of flashes is often unique for a particular species. The flashing light is
+produced by a process of bioluminescence, and the true functions of suchsignaling systems are still being debated. However, two fundamental functions
+of such flashes are to attract mating partners (communication), and to attract potential prey. In addition, flashing may also serve as a protective warning
+mechanism to remind potential predators of the bitter taste of fireflies. The firefly algorithm tries to mimic the attractiveness of Fireflies and has three
+basic rules:
+
+\begin{itemize}
+    \item All fireflies are unisex so that one firefly will be attracted to other
+          fireflies regardless of their sex;
+    \item Attractiveness is proportional to the their brightness, thus for any two
+          flashing fireflies, the less brighter one will move towards the brighter
+          one. The attractiveness is proportional to the brightness and they
+          both decrease as their distance increases. If there is no brighter one
+          than a particular firefly, it will move randomly;
+    \item The brightness of a firefly is affected or determined by the landscape
+          of the objective function.
+\end{itemize}
+
+\textit{\textbf{Bees Algorithm:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
+The Bees Algorithm beings to Bee Inspired Algorithms and the field of Swarm Intelligence, and more broadly the fields of Computational
+Intelligence and Metaheuristics. The Bees Algorithm is related to other Bee Inspired Algorithms, such as Bee Colony Optimization, and other
+Swarm Intelligence algorithms such as Ant Colony Optimization and Particle Swarm Optimization.
+It is inspired by the foraging behavior of honey bees. Honey bees collect nectar from vast areas around their hive (more than
+10 kilometers). Bee Colonies have been observed to send bees to collect nectar from flower patches relative to the amount of food available at
+each patch. Bees communicate with each other at the hive via a waggle dance that informs other bees in the hive as to the direction, distance,
+and quality rating of food sources.
+
+\section{Metodology}
+\label{sec:metodology}
+
+\subsection{Optimimzation Problem Selection}
+The two problems selected for this paper were \textit{Spring Tension Design} and \textit{Pressure Vessel Design}. Although it was simple
+to choose the first two problems from the computational work statements, the choice was more than justified because these aroblems are well
+known in the literature. Thus, the problem selection was driven by which has more that one source to compare results.
+
+\subsection{Programming Language}
+
+The chosen programming language for the test code was \textit{Python Language}, version 3.10, because it is an opensource language easy to
+program and has a huge amount of packages regarding artificial intelligence, genetic algorithms and swarm based algorithms. From these packages it
+was selected \textit{MealPy} package, version 2.5.1, because it comprises all the algorithm's classed tested in this paper.
+
+\subsection{Algorithm Selection}
+
+The algorithm selection was made in two steps: first, it was extracted simple version of the two classes (evolutionary and swarm based) and
+then it was used a simple shuffle using Python's \textit{random.shuffle} in a terminal - no script was required.
+
+\subsection{Model Parameters}
+
+For all models and problems, were selected the following parameters:
+
+\begin{itemize}
+    \item \textit{Runs}: 100 runs
+    \item \textit{Epochs}: 100 epochs
+    \item \textit{Population}: 100 initial points
+\end{itemize}
+
+The initial solutions were randomly selected using the same seed for all algorithms.
+
+\subsection{Model Tuning}
+
+\section{Results}
+\label{sec:results}

### 2023-01-17 Functions/PressureVessel.py

@@ -7,59 +7,57 @@ Authors: Augusto Mathias Adams - augusto.adams@ufpr.br - GRR20172143
          Vinícius Eduardo dos Reis - eduardo.reis02@gmail.com - GRR20175957
 
 Pressure Vessel Design Problem
+optimal value: 5896.94890
+x* = (0.780956, 0.386318, 40.433956, 198.504889)
 """
 
 import numpy as np
-from sympy import var, exp, cos, pi, euler, sqrt, latex, var, diff, simplify, lambdify
-from mealpy.utils.problem import Problem
 
-def pressure_vessel_function():
+def pressure_vessel_get_literature_solution():
+    return [0.780956, 0.386318, 40.433956, 198.504889]
+
+
+def pressure_vessel_function(x):
     """
     Function to minimize
-    :return: python function
+    :return: float
     """
-    x1, x2, x3, x4 = var("x1 x2 x3 x4")
-    function = 0.6224 * x1 * x2 * x3 + \
-               1.7781 * x2 * (x3 ** 2) + \
-               3.1661 * (x1 ** 2) * x4 + \
-               19.84 * (x1 ** 2) * x3
-    return lambdify([x1, x2, x3, x4], function, "numpy")
+    return 0.6224 * x[0] * x[2] * x[3] + \
+           1.7781 * x[1] * (x[2] ** 2) + \
+           3.1661 * (x[0] ** 2) * x[3] + \
+           19.84 * (x[0] ** 2) * x[2]
 
-def p_constraint_g1():
+
+def p_constraint_g1(x):
     """
     Constraing g1
-    :return: python function
+    :return: float
     """
-    x1, x2, x3, x4 = var("x1 x2 x3 x4")
-    function = -x1 + 0.0193 * x3
-    return lambdify([x1, x2, x3, x4], function, "numpy")
+    return -x[0] + 0.0193 * x[2]
 
-def p_constraint_g2():
+
+def p_constraint_g2(x):
     """
     Constraint g2
-    :return: python function
+    :return: float
     """
-    x1, x2, x3, x4 = var("x1 x2 x3 x4")
-    function = -x2 + 0.00954 * x3
-    return lambdify([x1, x2, x3, x4], function, "numpy")
+    return -x[1] + 0.00954 * x[2]
 
-def p_constraint_g3():
+
+def p_constraint_g3(x):
     """
     Constraint g3
-    :return: python function
+    :return: float
     """
[…]

### 2023-01-17 Functions/Spring.py

@@ -1,4 +1,3 @@
-
 """
 Computational Work 02 - Evolutionary Computation
 Authors: Augusto Mathias Adams - augusto.adams@ufpr.br - GRR20172143
@@ -7,56 +6,54 @@ Authors: Augusto Mathias Adams - augusto.adams@ufpr.br - GRR20172143
          Vinícius Eduardo dos Reis - eduardo.reis02@gmail.com - GRR20175957
 
 Spring Design Problem
+optimal value: 0.012665
+x∗ = (0.051690, 0.356750, 11.287126)
 """
 
-import numpy as np
-from sympy import var, exp, cos, pi, euler, sqrt, latex, var, diff, simplify, lambdify
-from mealpy.utils.problem import Problem
+def spring_get_literature_solution():
+    return [0.051690, 0.356750, 11.287126]
 
-def spring_function():
+def spring_function(x):
     """
     Function to minimize
-    :return: python function
+    :return: float
     """
-    x1, x2, x3 = var("x1 x2 x3")
-    function = (x3 + 2) * x2 * (x1 ** 2)
-    return lambdify([x1, x2, x3], function, "numpy")
+    return (x[0] ** 2) * x[1] * (2 + x[2])
 
-def s_constraint_g1():
+
+def s_constraint_g1(x):
     """
     Constraing g1
-    :return: python function
+    :return: float
     """
-    x1, x2, x3 = var("x1 x2 x3")
-    function = 1 - ((x2 ** 3) * x3)/(71785.0 * (x1 ** 4))
-    return lambdify([x1, x2, x3], function, "numpy")
+    return 1 - (((x[1] ** 3) * x[2]) / (71785.0 * (x[0] ** 4)))
 
-def s_constraint_g2():
+
+def s_constraint_g2(x):
     """
     Constraint g2
-    :return: python function
+    :return: float
     """
-    x1, x2, x3 = var("x1 x2 x3")
-    function = (4 * (x2 ** 2) - x1 * x2)/(12566 * (x2 * (x1 ** 3) - x1 ** 4)) + 1/(5108 * (x1 ** 2)) - 1
-    return lambdify([x1, x2, x3], function, "numpy")
+    return ((4 * (x[1] ** 2) - x[0] * x[1]) / (12566.0 * ((x[0] ** 3) * x[1] - x[0] ** 4)))+ \
+        (1 / (5108.0 * (x[0] ** 2))) - 1.0
 
-def s_constraint_g3():
+
[…]

### 2023-01-17 Functions/__init__.py

@@ -1,2 +1,18 @@
-from .Spring import spring_fitness_function, spring_get_lb, spring_get_ub
-from .PressureVessel import pressure_fitness_function, pressure_vessel_get_lb, pressure_vessel_get_ub
+from .Spring import spring_fitness_function, \
+    spring_get_lb, \
+    spring_get_ub, \
+    spring_get_literature_solution, \
+    spring_function, \
+    s_constraint_g1, \
+    s_constraint_g2, \
+    s_constraint_g3, \
+    s_constraint_g4
+from .PressureVessel import pressure_fitness_function, \
+    pressure_vessel_get_lb, \
+    pressure_vessel_get_ub, \
+    pressure_vessel_get_literature_solution, \
+    pressure_vessel_function, \
+    p_constraint_g1, \
+    p_constraint_g2, \
+    p_constraint_g3, \
+    p_constraint_g4

### 2023-01-17 Solvers/Solvers.py

@@ -1,310 +1,0 @@
-
-"""
-Computational Work 02 - Evolutionary Computation
-Authors: Augusto Mathias Adams - augusto.adams@ufpr.br - GRR20172143
-         Caio Phillipe Mizerkowski - caiomizerkowski@gmail.com - GRR20166403
-         Christian Piltz Araújo - christian0294@yahoo.com.br - GRR20172197
-         Vinícius Eduardo dos Reis - eduardo.reis02@gmail.com - GRR20175957
-
-Evolutionary Algorithms Solvers based on mealpy package
-"""
-
-from mealpy.evolutionary_based import ES, EP, GA
-from mealpy.swarm_based import BeesA, FFA, PSO
-from mealpy.utils import io
-import numpy as np
-
-
-def solve_ep(seed,
-             problem,
-             epochs,
-             lb,
-             ub,
-             save_to,
-             pop_size,
-             bout_size=0.1):
-
-    """
-    Evolutionary Programming
-    :param seed: random seed
-    :param problem: problem fitness function (constrained version)
-    :param epochs: epochs
-    :param lb: lower bounds
-    :param ub: upper bounds
-    :param save_to: save to file
-    :param pop_size: population size
-    :param bout_size: percentage of child agents implement tournament selection
-    :return: best_solution, best_fitness
-    """
-
-    problem_dict = {
-        "fit_func": problem,
-        "lb": lb,
-        "ub": ub,
-        "minmax": "min",
-        "verbose": False,
-        "save_population": True,  # Then you can't draw the trajectory chart
-        "log_to": None
-    }
-
-    np.random.seed(seed)
-
-    model = EP.LevyEP(epoch=epochs,
-                      pop_size=pop_size,
-                      bout_size=bout_size)
-
-    best_position, best_fitness = model.solve(problem=problem_dict)
-    io.save_model(model, "results/" + save_to)
-    return best_position, best_fitness
-
-def solve_es(seed,
-             problem,
-             epochs,
-             lb,
-             ub,
-             save_to,
-             pop_size,
-             lamda=0.5):
-
-    """
-    Evolutionary Strategy
-    :param seed: random seed
-    :param problem: problem fitness function (constrained version)
-    :param epochs: epochs
-    :param lb: lower bounds
-    :param ub: upper bounds
-    :param save_to: save to file
-    :param pop_size: population size
-    :param lamda: Percentage of child agents evolving in the next generation
[…]

### 2023-01-17 Solvers/Tuning.py

@@ -1,15 +1,0 @@
-
-"""
-Computational Work 02 - Evolutionary Computation
-Authors: Augusto Mathias Adams - augusto.adams@ufpr.br - GRR20172143
-         Caio Phillipe Mizerkowski - caiomizerkowski@gmail.com - GRR20166403
-         Christian Piltz Araújo - christian0294@yahoo.com.br - GRR20172197
-         Vinícius Eduardo dos Reis - eduardo.reis02@gmail.com - GRR20175957
-
-Evolutionary Algorithms Tuners based on mealpy package
-"""
-
-from mealpy.evolutionary_based import ES, EP, GA
-from mealpy.swarm_based import BeesA, FFA, PSO
-import numpy as np
-

### 2023-01-17 Solvers/__init__.py

@@ -1,2 +1,0 @@
-from .Solvers import *
-from .Tuning import *

### 2023-01-17 article_builder.py

@@ -15,25 +15,26 @@ with open("latex/includes/header.tex", "r") as f:
     content += f.read()
 
 #: spring problem
-content += "\\section{Spring Tension Design}\n\n"
-content += "\\label{sec:spring_problem}"
+content += "\\subsection{Spring Tension Design}\n\n"
+content += "\\label{ssubec:spring_problem}"
 
-content += "\\subsection{Evolutionary Algorithms}\n\n"
-content += "\\label{subsec:spring_problem_evolutionary_based}\n\n"
 
-content += "\\subsection{Swarm Based Algorithms}\n\n"
-content += "\\label{subsec:spring_problem_swarm_based}\n\n"
+content += "\\subsubsection{Evolutionary Algorithms}\n\n"
+content += "\\label{subsubsec:spring_problem_evolutionary_based}\n\n"
+
+content += "\\subsubsection{Swarm Based Algorithms}\n\n"
+content += "\\label{subsubsec:spring_problem_swarm_based}\n\n"
 
 # pressure vessel problem
 
-content += "\\section{Pressure Vessel Design}\n\n"
-content += "\\label{sec:pressure_vessel_problem}"
+content += "\\subsection{Pressure Vessel Design}\n\n"
+content += "\\label{subsec:pressure_vessel_problem}"
 
-content += "\\subsection{Evolutionary Algorithms}\n\n"
-content += "\\label{subsec:pressure_vessel_problem_evolutionary_based}\n\n"
+content += "\\subsubsection{Evolutionary Algorithms}\n\n"
+content += "\\label{subsubsec:pressure_vessel_problem_evolutionary_based}\n\n"
 
-content += "\\subsection{Swarm Based Algorithms}\n\n"
-content += "\\label{subsec:pressure_vessel_problem_swarm_based}\n\n"
+content += "\\subsubsection{Swarm Based Algorithms}\n\n"
+content += "\\label{subsubsec:pressure_vessel_problem_swarm_based}\n\n"
 
 # Friedman's test
 

### 2023-01-17 runner.py

@@ -20,7 +20,11 @@ from Functions import spring_fitness_function, \
     spring_get_lb, \
     spring_get_ub, \
     pressure_vessel_get_lb, \
-    pressure_vessel_get_ub
+    pressure_vessel_get_ub, \
+    spring_function, \
+    spring_get_literature_solution, \
+    pressure_vessel_function, \
+    pressure_vessel_get_literature_solution
 
 
 def create_starting_positions(rseed,
@@ -49,7 +53,19 @@ epochs = 100
 
 pop_size = 100
 
-runs = 100
+runs = 1
+
+spring_default_solution = spring_get_literature_solution()
+
+print(spring_function(spring_default_solution))
+
+print(spring_fitness_function(spring_default_solution))
+
+pressure_vessel_default_solution = pressure_vessel_get_literature_solution()
+
+print(pressure_vessel_function(pressure_vessel_default_solution))
+
+print(pressure_fitness_function(pressure_vessel_default_solution))
 
 # problems
 
@@ -150,6 +166,8 @@ for seed in range(1, runs + 1):
             model = algorithms[solver_name](**params)
             best_position, best_fitness = model.solve(current_problem,
                                                       starting_positions=initial_positions)
+
+            print(best_fitness)
 
             fit_results[problem][solver_name].append([best_position.tolist(),
                                                       best_fitness])

### 2023-01-17 test_pressure_vessel.py

@@ -1,0 +1,38 @@
+"""
+Computational Work 02 - Evolutionary Computation
+Authors: Augusto Mathias Adams - augusto.adams@ufpr.br - GRR20172143
+         Caio Phillipe Mizerkowski - caiomizerkowski@gmail.com - GRR20166403
+         Christian Piltz Araújo - christian0294@yahoo.com.br - GRR20172197
+         Vinícius Eduardo dos Reis - eduardo.reis02@gmail.com - GRR20175957
+
+Test Spring Functions
+"""
+
+import json
+import numpy as np
+
+from mealpy.evolutionary_based import ES, EP, GA
+from mealpy.swarm_based import BeesA, FFA, PSO
+from mealpy.utils import io
+
+from Functions import pressure_fitness_function, \
+    pressure_vessel_get_lb, \
+    pressure_vessel_get_ub, \
+    pressure_vessel_function, \
+    pressure_vessel_get_literature_solution, \
+    p_constraint_g1, \
+    p_constraint_g2, \
+    p_constraint_g3, \
+    p_constraint_g4
+
+
+pressure_vessel_default_solution = pressure_vessel_get_literature_solution()
+
+print(pressure_vessel_function(pressure_vessel_default_solution))
+
+print(pressure_fitness_function(pressure_vessel_default_solution))
+
+print(p_constraint_g1(pressure_vessel_default_solution))
+print(p_constraint_g2(pressure_vessel_default_solution))
+print(p_constraint_g3(pressure_vessel_default_solution))
+print(p_constraint_g4(pressure_vessel_default_solution))

### 2023-01-17 test_spring.py

@@ -1,0 +1,38 @@
+"""
+Computational Work 02 - Evolutionary Computation
+Authors: Augusto Mathias Adams - augusto.adams@ufpr.br - GRR20172143
+         Caio Phillipe Mizerkowski - caiomizerkowski@gmail.com - GRR20166403
+         Christian Piltz Araújo - christian0294@yahoo.com.br - GRR20172197
+         Vinícius Eduardo dos Reis - eduardo.reis02@gmail.com - GRR20175957
+
+Test Spring Functions
+"""
+
+import json
+import numpy as np
+
+from mealpy.evolutionary_based import ES, EP, GA
+from mealpy.swarm_based import BeesA, FFA, PSO
+from mealpy.utils import io
+
+from Functions import spring_fitness_function, \
+    spring_get_lb, \
+    spring_get_ub, \
+    spring_function, \
+    spring_get_literature_solution, \
+    s_constraint_g1, \
+    s_constraint_g2, \
+    s_constraint_g3, \
+    s_constraint_g4
+
+
+spring_default_solution = spring_get_literature_solution()
+
+print(spring_function(spring_default_solution))
+
+print(spring_fitness_function(spring_default_solution))
+
+print(s_constraint_g1(spring_default_solution))
+print(s_constraint_g2(spring_default_solution))
+print(s_constraint_g3(spring_default_solution))
+print(s_constraint_g4(spring_default_solution))

### 2023-01-17 tuning.py

@@ -132,5 +132,4 @@ for problem in problems:
 with open("results/tuning.json", "w") as f:
     json.dump(best_parameters, f, indent=4)
 
-
 print(best_parameters)

### 2023-01-19 latex/article.tex
header.tex done

@@
     version 3.10 and uses \textit{MealPy} package, version 2.5.1,  to provide the algorithms.
-    Thre algorithms were randomly chosen from a vaste list from MealPy algorithms:
+    The algorithms were randomly chosen from a vast list from \textit{MealPy}'s algorithms:
     \textit{Evolutionary Programming (LevyEP)}, \textit{Evolution Strategies (OriginalES)} and
@@
     solutions from each problem using the \textit{MealPy}'s \textit{Tuner} utility.
-    The results, however, are dependant of algorithm and problem presented but from
-    similarity test using Friedman's Chi-Squared test, it would be suffice to say that using any
-    of the tested algorithm will produce similar results in these two optimization problems.
+    The results, however, are dependant of algorithm and/or problem solved and the Friedman's chi
+    squared test for similarity make it noticeable because, although the values for best fits are
+    similar, running the same algorithm with different initial conditions does not converge to similar
+    values.
 \end{abstract}
@@
 
-\section{Metodology}
-\label{sec:metodology}
+\section{Methodology}
+\label{sec:methodology}
 
-\subsection{Optimimzation Problem Selection}
+\subsection{Optimization Problem Selection}
+\label{subsec:optimization-problem-selection}
 The two problems selected for this paper were \textit{Spring Tension Design} and \textit{Pressure Vessel Design}. Although it was simple
 to choose the first two problems from the computational work statements, the choice was more than justified because these aroblems are well
-known in the literature. Thus, the problem selection was driven by which has more that one source to compare results.
+known in the literature.
+Thus, the problem selection was driven by which has more than one source to compare results.
+
+\subsubsection{Spring Tension Design}
+\label{subsubsec:methodology-spring-tension-design}
+From \textit{Nature-Inspired Metaheuristic Algorithms - Xin-She Yang} -
+The design of a tension and compression spring is a well-known benchmark
+optimization problem.
+The main aim is to minimize the weight subject
+to constraints on deflection, stress, surge frequency and geometry. It involves
+three design variables: the wire diameter $x_1$ , coil diameter $x_2$ and
+number/length of the coil $x_3$.
+This problem can be summarized as:
+
+\begin{equation}
+    f (x) = x_1^2 x_2 (2 + x_3)
+\end{equation}
+
+subject to
+
+\begin{equation}
+    \begin{split}
+        g_1(x) = \frac{x_2^3 x_3}{71785 x_1^4} \leq 0\\
+        g_2(x) = \frac{4 x_2^2 - x_1 x_2}{12566 \left( x_1^3 x_2 - x_1^4\right)}\\
+        + \frac{1}{5108 x_1^2} -1 \leq 0\\
+        g_3(x) = 1 - \frac{140.45 x_1}{x_2^2 x_3} \leq 0\\
+        g_4 = \frac{x_1 + x_2}{1.5} - 1 \leq 0
+    \end{split}
+\end{equation}
+
+The original bounding limits of the variables, extracted from computational work
+statements, are:
+
+\begin{equation}
+    \begin{split}
+        0.05 \leq x_1 \leq 2.0\\
+        0.25 \leq x_2 \leq 1.3\\
+        2.0 \leq x_3 \leq 15.0
+    \end{split}
+\end{equation}
+
+\subsubsection{Pressure Vessel Design}
+\label{subsubsec:methodology-pressure-vessel-design}
+From \textit{Solving Design of Pressure Vessel Engineering
+Problem Using a Fruit Fly Optimization Algorithm - XIANTING KE et al} -
+A pressure vessel design model involves four decision variables: $x_1$ is defined
+thickness of the pressure vessel $T_s$ , $x_2$ stands for
+thickness of the head $T_H$ , $x_3$ represents inner radius of the
+vessel $R$ , and $x_4$ is on behalf of length of the vessel
+barring head $L$ , the total variables described as $( x_1 , x_2 , x_3 , x_4 )$.
+The objective function of the problem is to minimize the total cost, including
+the cost of material, forming, and welding.
+The general pressure vessel design optimization model is expressed as:
+
+\begin{equation}
+	\begin{split}
+        f(x) = 0.6224 x_1 x_3 x_4 + 1.7781 x_2 x_3^2 \\
+        + 3.1661 x_1^2 x_4 + 19.84 x_1^2 x_3
+	\end{split}
+\end{equation}
+
+subject to:
+
+\begin{equation}
+    \begin{split}
+        g_1(x) = - x_1 + 0.0193 x_3 \leq 0\\
+        g_2(x) = - x_2 + 0.00954 x_3 \leq 0\\
+        g_3(x) = - \pi x_3^2 x_4 -\frac{4}{3}\pi x_3^3 + 1296000 \leq 0\\
+        g_4(x) = x_4 -240 \leq 0\\
+    \end{split}
+\end{equation}
+
+The original bounding limits of the variables, extracted from computational work
+statements, are:
+
+\begin{equation}
+    \begin{split}
+        0 \leq x_1 \leq 99\\
+        0 \leq x_2 \leq 99\\
+        10 \leq x_3 \leq 200\\
+        10 \leq x_4 \leq 200\\
+    \end{split}
+\end{equation}
+
+For some reason these settings does not work at all with the selected optimizers, so
+some research in the literature \textit{Solving Design of Pressure Vessel Engineering
+Problem Using a Fruit Fly Optimization Algorithm - XIANTING KE et al} suggest the
+following bounding limits:
+
+\begin{equation}
+    \begin{split}
+        0.0625 \leq x_1 \leq 99 \times 0.0625\\
+        0.0625 \leq x_2 \leq 99 \times 0.0625\\
+        10 \leq x_3 \leq 200\\
+        10 \leq x_4 \leq 200
+    \end{split}
+\end{equation}
+
+But these settings produce many random, bizarre and noisy results in all selected optimizers. Then
+a proud-and-lame-homemade set of variable boundings comes in handy, obtained by tweaking the original
+boundings:
+
+\begin{equation}
+    \begin{split}
+        0.75 \leq x_1 \leq 0.8\\
+        0.35 \leq x_2 \leq 0.4\\
+        39.5 \leq x_3 \leq 41.0\\
+        195.0 \leq x_4 \leq 205.0\\
+    \end{split}
+\end{equation}
+
+It is not intended here to point out modeling errors of any kind, nor point out package
+errors made by the authors or ours, but the homemade bounding limits was necessary to
+reach the literature results.
+
+\subsection{Constraint Implementation}
+\label{subsec:methodology-constraint-implementation}
+The constraints that all problems are subjected were implemented as \textit{penalty functions},
+that is, it adds a high value when the constraint is not satisfied, zero otherwise. It is an optional requirement
+from computational work in question and is the recommended way to put constraints from \textit{MealPy}'s
+Manual.
 
 \subsection{Programming Language}
+\label{subsec:methodology-programming-language}
 
 The chosen programming language for the test code was \textit{Python Language}, version 3.10, because it is an opensource language easy to
-program and has a huge amount of packages regarding artificial intelligence, genetic algorithms and swarm based algorithms. From these packages it
-was selected \textit{MealPy} package, version 2.5.1, because it comprises all the algorithm's classed tested in this paper.
+program and has a huge amount of packages regarding artificial intelligence, genetic algorithms and swarm based algorithms.
+From these packages it was selected \textit{MealPy} package, version 2.5.1, because it comprises all the algorithm's classed tested in this paper.
 
 \subsection{Algorithm Selection}
+\label{subsec:methodology-algorithm-selection}
 
 The algorithm selection was made in two steps: first, it was extracted simple version of the two classes (evolutionary and swarm based) and
-then it was used a simple shuffle using
+then it was used a simple shuffle using Python's \textit{random.shuffle} in a terminal - no script was required.
 
-\subsection{Model Parameters}
+The chosen algorithms were:
 
-For all models and problems, were selected the following parameters:
+\begin{itemize}
+    \item \textit{\textbf{Evolution Based Algorithms: }} LevyEP (Evolutionary Programming),
+    OriginalES (Evolution Strategy) and BaseGA (Genetic Algorithm)
+    \item \textit{\textbf{Swarm Based Algorithms: }} OriginalBeesA (Bees Algorithm),
+    OriginalFFA (Original Firefly Algorithm) and OriginalPSO (Particle Swarm Optimization)
+\end{itemize}
+
+\subsection{Optimizer Tuning}
+\label{subsec:methodology-optimizer-tuning}
+
+The hyperparameters for each optimizer were tuned using the \textit{MealPy}'s \textit{Tuner} utility.
+It is a recomended procedure to tune hyperparameters for each optimizer and problem, according to
+\textit{MealPy}'s Manual.
+The \textit{Tuner} utility is a very simple grid search metaheuristic search tool
+that test each grid configuration for a specified oprimizer runs.
+Although simple, it is a very expensive procedure that took 2 days to complete. It was defined 10 runs for each
+configuration, with the following set of hyperparameter:
+
+\begin{itemize}
+    \item \textit{\textbf{Evolution Based Algorithms: }}
+        \subitem \textit{LevyEP:}
+            \subsubitem \textit{bout\_size (float)}: percentage of child agents implement tournament selection.
+        \subitem \textit{OriginalES:}
+            \subsubitem \textit{lamda (float)}: Percentage of child agents evolving in the next generation.
+        \subitem \textit{BaseGA:}
+            \subsubitem \textit{pc (float)}: cross-over probability
+            \subsubitem \textit{pm (float)}: mutation probability
+    \item \textit{\textbf{Swarm Based Algorithms: }}
+        \subitem \textit{OriginalBeesA:}
+            \subsubitem \textit{selected\_site\_ratio (float)}
+            \subsubitem \textit{elite\_site\_ratio (float)}
+            \subsubitem \textit{selected\_site\_bee\_ratio (float)}
+            \subsubitem \textit{elite\_site\_bee\_ratio (float)}
+            \subsubitem \textit{dance\_radius (float)}
+            \subsubitem \textit{dance\_reduction (float)}
+        \subitem \textit{OriginalFFA:}
+            \subsubitem \textit{gamma (float)}: Light Absorption Coefficient
+            \subsubitem \textit{beta\_base (float)}: Attraction Coefficient Base Value
+            \subsubitem \textit{alpha (float)}: Mutation Coefficient
+            \subsubitem \textit{alpha\_damp (float)}: Mutation Coefficient Damp Rate
+            \subsubitem \textit{delta (float)}: Mutation Step Size
+            \subsubitem \textit{exponent (int)}: Exponent
+        \subitem \textit{OriginalPSO:}
+            \subsubitem \textit{c1 (float)}: local coefficient
+            \subsubitem \textit{c2 (float)}: global coefficient
+            \subsubitem \textit{w\_min (float)}: Weight min of bird
+            \subsubitem \textit{w\_max (float)}: Weight max of bird
+
+\end{itemize}
+
+\subsection{Optimizer Parameters}
+\label{subsec:methodology-optimizer-parameters}
+
+For all optimizers and problems, were selected the following parameters:
 
@@
 The initial solutions were randomly selected using the same seed for all algorithms.
-
-\subsection{Model Tuning}
 

### 2023-01-19 latex/includes/header.tex
header.tex done

@@
 
-\section{Metodology}
-\label{sec:metodology}
+\section{Methodology}
+\label{sec:methodology}
 
-\subsection{Optimimzation Problem Selection}
+\subsection{Optimization Problem Selection}
+\label{subsec:optimization-problem-selection}
 The two problems selected for this paper were \textit{Spring Tension Design} and \textit{Pressure Vessel Design}. Although it was simple
 to choose the first two problems from the computational work statements, the choice was more than justified because these aroblems are well
-known in the literature. Thus, the problem selection was driven by which has more that one source to compare results.
+known in the literature.
+Thus, the problem selection was driven by which has more than one source to compare results.
+
+\subsubsection{Spring Tension Design}
+\label{subsubsec:methodology-spring-tension-design}
+From \textit{Nature-Inspired Metaheuristic Algorithms - Xin-She Yang} -
+The design of a tension and compression spring is a well-known benchmark
+optimization problem.
+The main aim is to minimize the weight subject
+to constraints on deflection, stress, surge frequency and geometry. It involves
+three design variables: the wire diameter $x_1$ , coil diameter $x_2$ and
+number/length of the coil $x_3$.
+This problem can be summarized as:
+
+\begin{equation}
+    f (x) = x_1^2 x_2 (2 + x_3)
+\end{equation}
+
+subject to
+
+\begin{equation}
+    \begin{split}
+        g_1(x) = \frac{x_2^3 x_3}{71785 x_1^4} \leq 0\\
+        g_2(x) = \frac{4 x_2^2 - x_1 x_2}{12566 \left( x_1^3 x_2 - x_1^4\right)}\\
+        + \frac{1}{5108 x_1^2} -1 \leq 0\\
+        g_3(x) = 1 - \frac{140.45 x_1}{x_2^2 x_3} \leq 0\\
+        g_4 = \frac{x_1 + x_2}{1.5} - 1 \leq 0
+    \end{split}
+\end{equation}
+
+The original bounding limits of the variables, extracted from computational work
+statements, are:
+
+\begin{equation}
+    \begin{split}
+        0.05 \leq x_1 \leq 2.0\\
+        0.25 \leq x_2 \leq 1.3\\
+        2.0 \leq x_3 \leq 15.0
+    \end{split}
+\end{equation}
+
+\subsubsection{Pressure Vessel Design}
+\label{subsubsec:methodology-pressure-vessel-design}
+From \textit{Solving Design of Pressure Vessel Engineering
+Problem Using a Fruit Fly Optimization Algorithm - XIANTING KE et al} -
+A pressure vessel design model involves four decision variables: $x_1$ is defined
+thickness of the pressure vessel $T_s$ , $x_2$ stands for
+thickness of the head $T_H$ , $x_3$ represents inner radius of the
+vessel $R$ , and $x_4$ is on behalf of length of the vessel
+barring head $L$ , the total variables described as $( x_1 , x_2 , x_3 , x_4 )$.
+The objective function of the problem is to minimize the total cost, including
+the cost of material, forming, and welding.
+The general pressure vessel design optimization model is expressed as:
+
+\begin{equation}
+	\begin{split}
+        f(x) = 0.6224 x_1 x_3 x_4 + 1.7781 x_2 x_3^2 \\
+        + 3.1661 x_1^2 x_4 + 19.84 x_1^2 x_3
+	\end{split}
+\end{equation}
+
+subject to:
+
+\begin{equation}
+    \begin{split}
+        g_1(x) = - x_1 + 0.0193 x_3 \leq 0\\
+        g_2(x) = - x_2 + 0.00954 x_3 \leq 0\\
+        g_3(x) = - \pi x_3^2 x_4 -\frac{4}{3}\pi x_3^3 + 1296000 \leq 0\\
+        g_4(x) = x_4 -240 \leq 0\\
+    \end{split}
+\end{equation}
+
+The original bounding limits of the variables, extracted from computational work
+statements, are:
+
+\begin{equation}
+    \begin{split}
+        0 \leq x_1 \leq 99\\
+        0 \leq x_2 \leq 99\\
+        10 \leq x_3 \leq 200\\
+        10 \leq x_4 \leq 200\\
+    \end{split}
+\end{equation}
+
+For some reason these settings does not work at all with the selected optimizers, so
+some research in the literature \textit{Solving Design of Pressure Vessel Engineering
+Problem Using a Fruit Fly Optimization Algorithm - XIANTING KE et al} suggest the
+following bounding limits:
+
+\begin{equation}
+    \begin{split}
+        0.0625 \leq x_1 \leq 99 \times 0.0625\\
+        0.0625 \leq x_2 \leq 99 \times 0.0625\\
+        10 \leq x_3 \leq 200\\
+        10 \leq x_4 \leq 200
+    \end{split}
+\end{equation}
+
+But these settings produce many random, bizarre and noisy results in all selected optimizers. Then
+a proud-and-lame-homemade set of variable boundings comes in handy, obtained by tweaking the original
+boundings:
+
+\begin{equation}
+    \begin{split}
+        0.75 \leq x_1 \leq 0.8\\
+        0.35 \leq x_2 \leq 0.4\\
+        39.5 \leq x_3 \leq 41.0\\
+        195.0 \leq x_4 \leq 205.0\\
+    \end{split}
+\end{equation}
+
+It is not intended here to point out modeling errors of any kind, nor point out package
+errors made by the authors or ours, but the homemade bounding limits was necessary to
+reach the literature results.
+
+\subsection{Constraint Implementation}
+\label{subsec:methodology-constraint-implementation}
+The constraints that all problems are subjected were implemented as \textit{penalty functions},
+that is, it adds a high value when the constraint is not satisfied, zero otherwise. It is an optional requirement
+from computational work in question and is the recommended way to put constraints from \textit{MealPy}'s
+Manual.
 
 \subsection{Programming Language}
+\label{subsec:methodology-programming-language}
 
 The chosen programming language for the test code was \textit{Python Language}, version 3.10, because it is an opensource language easy to
-program and has a huge amount of packages regarding artificial intelligence, genetic algorithms and swarm based algorithms. From these packages it
-was selected \textit{MealPy} package, version 2.5.1, because it comprises all the algorithm's classed tested in this paper.
+program and has a huge amount of packages regarding artificial intelligence, genetic algorithms and swarm based algorithms.
+From these packages it was selected \textit{MealPy} package, version 2.5.1, because it comprises all the algorithm's classed tested in this paper.
 
 \subsection{Algorithm Selection}
+\label{subsec:methodology-algorithm-selection}
 
@@
 
-\subsection{Model Parameters}
+The chosen algorithms were:
 
-For all models and problems, were selected the following parameters:
+\begin{itemize}
+    \item \textit{\textbf{Evolution Based Algorithms: }} LevyEP (Evolutionary Programming),
+    OriginalES (Evolution Strategy) and BaseGA (Genetic Algorithm)
+    \item \textit{\textbf{Swarm Based Algorithms: }} OriginalBeesA (Bees Algorithm),
+    OriginalFFA (Original Firefly Algorithm) and OriginalPSO (Particle Swarm Optimization)
+\end{itemize}
+
+\subsection{Optimizer Tuning}
+\label{subsec:methodology-optimizer-tuning}
+
+The hyperparameters for each optimizer were tuned using the \textit{MealPy}'s \textit{Tuner} utility.
+It is a recomended procedure to tune hyperparameters for each optimizer and problem, according to
+\textit{MealPy}'s Manual.
+The \textit{Tuner} utility is a very simple grid search metaheuristic search tool
+that test each grid configuration for a specified oprimizer runs.
+Although simple, it is a very expensive procedure that took 2 days to complete. It was defined 10 runs for each
+configuration, with the following set of hyperparameter:
+
+\begin{itemize}
+    \item \textit{\textbf{Evolution Based Algorithms: }}
+        \subitem \textit{LevyEP:}
+            \subsubitem \textit{bout\_size (float)}: percentage of child agents implement tournament selection.
+        \subitem \textit{OriginalES:}
+            \subsubitem \textit{lamda (float)}: Percentage of child agents evolving in the next generation.
+        \subitem \textit{BaseGA:}
+            \subsubitem \textit{pc (float)}: cross-over probability
+            \subsubitem \textit{pm (float)}: mutation probability
+    \item \textit{\textbf{Swarm Based Algorithms: }}
+        \subitem \textit{OriginalBeesA:}
+            \subsubitem \textit{selected\_site\_ratio (float)}
+            \subsubitem \textit{elite\_site\_ratio (float)}
+            \subsubitem \textit{selected\_site\_bee\_ratio (float)}
+            \subsubitem \textit{elite\_site\_bee\_ratio (float)}
+            \subsubitem \textit{dance\_radius (float)}
+            \subsubitem \textit{dance\_reduction (float)}
+        \subitem \textit{OriginalFFA:}
+            \subsubitem \textit{gamma (float)}: Light Absorption Coefficient
+            \subsubitem \textit{beta\_base (float)}: Attraction Coefficient Base Value
+            \subsubitem \textit{alpha (float)}: Mutation Coefficient
+            \subsubitem \textit{alpha\_damp (float)}: Mutation Coefficient Damp Rate
+            \subsubitem \textit{delta (float)}: Mutation Step Size
+            \subsubitem \textit{exponent (int)}: Exponent
+        \subitem \textit{OriginalPSO:}
+            \subsubitem \textit{c1 (float)}: local coefficient
+            \subsubitem \textit{c2 (float)}: global coefficient
+            \subsubitem \textit{w\_min (float)}: Weight min of bird
+            \subsubitem \textit{w\_max (float)}: Weight max of bird
+
+\end{itemize}
+
+\subsection{Optimizer Parameters}
+\label{subsec:methodology-optimizer-parameters}
+
+For all optimizers and problems, were selected the following parameters:
 
@@
 
-\subsection{Model Tuning}
-
 \section{Results}

### 2023-01-19 latex/includes/pressure_vessel_problem.tex
header.tex done

@@
 \midrule
-       EP & 0.94974179 &    0.99959274 &    0.95597819 &     1.41652156 &    0.10256309 \\
-       ES & 0.94985828 &    3.07906532 &    1.90278615 &    11.41620650 &    2.47339648 \\
-       GA & 4.61928311 &  383.23040981 &  262.27555979 &  1747.41758530 &  362.98174772 \\
-    BeesA & 1.05944833 & 5212.47847291 & 2094.42824655 & 30412.73885965 & 7297.64717603 \\
-      FFA & 0.95407161 &    1.05749808 &    1.05432826 &     1.16958618 &    0.04485239 \\
-      PSO & 0.94936617 &    1.00652465 &    0.94974267 &     3.01988559 &    0.25222125 \\
+       EP & 5534.57345496 & 5534.63426098 & 5534.61416291 & 5534.92993607 & 0.05804548 \\
+       ES & 5534.57917966 & 5535.28165367 & 5535.06149254 & 5538.03003895 & 0.65098467 \\
+       GA & 5534.83662424 & 5538.36788889 & 5536.92932748 & 5550.91639342 & 3.57079951 \\
+    BeesA & 5534.57516657 & 5537.97495231 & 5537.04824684 & 5548.55587234 & 3.28239740 \\
+      FFA & 5534.57401617 & 5534.58849395 & 5534.58435493 & 5534.63296149 & 0.01341777 \\
+      PSO & 5534.57345480 & 5534.57381593 & 5534.57355270 & 5534.57625290 & 0.00053848 \\
 \bottomrule

### 2023-01-19 latex/includes/pressure_vessel_problem_original.tex
header.tex done

\begin{table}
\centering
\caption{Statistical Information about function values for Pressure Vessel Design (Original)}
\label{function_values:pressure_vessel_problem_original}
\begin{tabular}{lrrrrr}
\toprule
Algorithm &         Min F &         Mean F &       Median F &          Max F &       StdDev F \\
\midrule
       EP &    0.08150806 &     0.15642850 &     0.09093798 &     1.32637552 &     0.16807714 \\
       ES &    0.08161190 &   718.92910990 &     1.00278859 &  9443.54269260 &  2060.07774212 \\
       GA &   17.06920868 &   525.00734162 &   361.53879602 &  3112.03503082 &   454.52386703 \\
    BeesA & 2393.70106213 & 17564.33024022 & 15751.91467117 & 53850.38271384 & 10514.60780411 \\
      FFA &    0.08306113 &     0.13296127 &     0.13106271 &     0.20084847 &     0.02396876 \\
      PSO &    0.08149204 &     0.24191732 &     0.08159173 &    10.00611523 &     1.00072349 \\
\bottomrule
\end{tabular}
\end{table}

### 2023-01-19 latex/includes/spring_problem.tex
header.tex done

@@
 \midrule
-       EP & 0.00607563 & 0.00607590 & 0.00607570 & 0.00607834 & 0.00000044 \\
-       ES & 0.00607564 & 0.00609326 & 0.00608915 & 0.00616308 & 0.00001810 \\
-       GA & 0.00610989 & 0.00670843 & 0.00663331 & 0.00805670 & 0.00045944 \\
-    BeesA & 0.00607781 & 0.00632310 & 0.00625074 & 0.00724816 & 0.00025469 \\
-      FFA & 0.00607563 & 0.00607593 & 0.00607576 & 0.00607847 & 0.00000047 \\
-      PSO & 0.00607563 & 0.00607563 & 0.00607563 & 0.00607563 & 0.00000000 \\
+       EP & 0.01250534 & 0.01255960 & 0.01253156 & 0.01453933 & 0.00020190 \\
+       ES & 0.01252956 & 0.01281857 & 0.01274283 & 0.01346214 & 0.00024181 \\
+       GA & 0.01252305 & 0.01628575 & 0.01616768 & 0.02561808 & 0.00273276 \\
+    BeesA & 0.01250200 & 0.01268010 & 0.01261691 & 0.01406679 & 0.00021629 \\
+      FFA & 0.01249803 & 0.01254780 & 0.01253499 & 0.01268116 & 0.00003152 \\
+      PSO & 0.01252626 & 0.01390866 & 0.01318774 & 0.03036537 & 0.00342240 \\
 \bottomrule

### 2023-01-19 Functions/PressureVessel.py

@@ -1,4 +1,3 @@
-
 """
 Computational Work 02 - Evolutionary Computation
 Authors: Augusto Mathias Adams - augusto.adams@ufpr.br - GRR20172143
@@ -13,6 +12,7 @@ x* = (0.780956, 0.386318, 40.433956, 198.504889)
 
 import numpy as np
 
+
 def pressure_vessel_get_literature_solution():
     return [0.780956, 0.386318, 40.433956, 198.504889]
 
@@ -23,9 +23,9 @@ def pressure_vessel_function(x):
     :return: float
     """
     return 0.6224 * x[0] * x[2] * x[3] + \
-           1.7781 * x[1] * (x[2] ** 2) + \
-           3.1661 * (x[0] ** 2) * x[3] + \
-           19.84 * (x[0] ** 2) * x[2]
+        1.7781 * x[1] * (x[2] ** 2) + \
+        3.1661 * (x[0] ** 2) * x[3] + \
+        19.84 * (x[0] ** 2) * x[2]
 
 
 def p_constraint_g1(x):
@@ -49,7 +49,7 @@ def p_constraint_g3(x):
     Constraint g3
     :return: float
     """
-    return -np.pi * (x[2] ** 2) * x[3] - (4/3) * np.pi * (x[2] ** 3) + 1296000
+    return -np.pi * (x[2] ** 2) * x[3] - (4 / 3) * np.pi * (x[2] ** 3) + 1296000
 
 
 def p_constraint_g4(x):
@@ -59,25 +59,33 @@ def p_constraint_g4(x):
     """
     return x[3] - 240
 
+
 def violate(value):
     """
     Constraint Violation
     :param value: constraint function value
     :return: penalty value
     """
-    return 0 if value <= 0 else 1
+    return 0 if value <= 0 else value ** 10
 
 
 def pressure_vessel_get_lb():
-    return [0.3, 0.3, 10.0, 10.0]
+    return [0.75, 0.35, 39.5, 195.0]
 
 
 def pressure_vessel_get_ub():
-    return [99.0 * 0.0625, 99.0 * 0.0625, 200.0, 240.0]
+    return [0.8, 0.40, 41.0, 205.0]
+
+
+def pressure_vessel_get_lb_original():
+    return [0.0, 0.0, 10.0, 10.0]
+
+
+def pressure_vessel_get_ub_original():
+    return [99.0, 99.0, 200.0, 200.0]
 
 
 def pressure_fitness_function(solution):
-
[…]

### 2023-01-19 Functions/Spring.py

@@ -10,8 +10,10 @@ optimal value: 0.012665
 x∗ = (0.051690, 0.356750, 11.287126)
 """
 
+
 def spring_get_literature_solution():
     return [0.051690, 0.356750, 11.287126]
+
 
 def spring_function(x):
     """
@@ -34,7 +36,7 @@ def s_constraint_g2(x):
     Constraint g2
     :return: float
     """
-    return ((4 * (x[1] ** 2) - x[0] * x[1]) / (12566.0 * ((x[0] ** 3) * x[1] - x[0] ** 4)))+ \
+    return ((4 * (x[1] ** 2) - x[0] * x[1]) / (12566.0 * ((x[0] ** 3) * x[1] - x[0] ** 4))) + \
         (1 / (5108.0 * (x[0] ** 2))) - 1.0
 
 

### 2023-01-19 Functions/__init__.py

@@ -10,6 +10,8 @@ from .Spring import spring_fitness_function, \
 from .PressureVessel import pressure_fitness_function, \
     pressure_vessel_get_lb, \
     pressure_vessel_get_ub, \
+    pressure_vessel_get_lb_original, \
+    pressure_vessel_get_ub_original, \
     pressure_vessel_get_literature_solution, \
     pressure_vessel_function, \
     p_constraint_g1, \

### 2023-01-19 analysis.py

@@ -21,7 +21,8 @@ alg_desc = {"solve_ep": "EP",
             "solve_pso": "PSO"}
 
 problem_desc = {'spring_problem': 'Spring Tension Design',
-                'pressure_vessel_problem': 'Pressure Vessel Design'}
+                'pressure_vessel_problem': 'Pressure Vessel Design',
+                'pressure_vessel_problem_original': 'Pressure Vessel Design (Original)'}
 
 
 def fit_results_cleanup(fit_results):
@@ -154,10 +155,10 @@ for problem in problem_desc:
         model = io.load_model(filename)
         best_fits_history[problem][solver] = model
 
-stats = ordinary_statistics(fit_results)
+stats_s = ordinary_statistics(fit_results)
 
 with open("results/stats.json", "w") as f:
-    json.dump(stats, f, indent=4)
+    json.dump(stats_s, f, indent=4)
 
 
 population_stats = dict()

### 2023-01-19 runner.py

@@ -21,6 +21,8 @@ from Functions import spring_fitness_function, \
     spring_get_ub, \
     pressure_vessel_get_lb, \
     pressure_vessel_get_ub, \
+    pressure_vessel_get_lb_original, \
+    pressure_vessel_get_ub_original, \
     spring_function, \
     spring_get_literature_solution, \
     pressure_vessel_function, \
@@ -53,7 +55,7 @@ epochs = 100
 
 pop_size = 100
 
-runs = 1
+runs = 100
 
 spring_default_solution = spring_get_literature_solution()
 
@@ -84,7 +86,15 @@ problems = {"spring_problem": {"lb": spring_get_lb(),
                                         "fit_func": pressure_fitness_function,
                                         "name": "Pressure Vessel Design",
                                         "save_population": True,
-                                        "log_to": None}}
+                                        "log_to": None},
+            "pressure_vessel_problem_original": {"lb": pressure_vessel_get_lb_original(),
+                                                 "ub": pressure_vessel_get_ub_original(),
+                                                 "minmax": "min",
+                                                 "verbose": False,
+                                                 "fit_func": pressure_fitness_function,
+                                                 "name": "Pressure Vessel Design",
+                                                 "save_population": True,
+                                                 "log_to": None}}
 
 # algorithm mapping
 
@@ -103,7 +113,8 @@ with open("results/tuning.json", "r") as f:
 # storage variables
 
 n_dims = {"spring_problem": 3,
-          "pressure_vessel_problem": 4}
+          "pressure_vessel_problem": 4,
+          "pressure_vessel_problem_original": 4}
 
 best_fits = {"spring_problem": {"solve_ep": 1e6,
                                 "solve_es": 1e6,
@@ -116,7 +127,13 @@ best_fits = {"spring_problem": {"solve_ep": 1e6,
                                          "solve_ga": 1e6,
                                          "solve_beesa": 1e6,
                                          "solve_ffa": 1e6,
-                                         "solve_pso": 1e6}}
+                                         "solve_pso": 1e6},
+             "pressure_vessel_problem_original": {"solve_ep": 1e6,
+                                                  "solve_es": 1e6,
+                                                  "solve_ga": 1e6,
+                                                  "solve_beesa": 1e6,
+                                                  "solve_ffa": 1e6,
+                                                  "solve_pso": 1e6}}
 
 
 best_fits_history = {"spring_problem": {"solve_ep": [],
[…]

### 2023-01-19 to_latex.py

@@ -96,7 +96,8 @@ alg_desc = {"solve_ep": "EP",
             "solve_pso": "PSO"}
 
 problem_desc = {'spring_problem': 'Spring Tension Design',
-                'pressure_vessel_problem': 'Pressure Vessel Design'}
+                'pressure_vessel_problem': 'Pressure Vessel Design',
+                'pressure_vessel_problem_original': 'Pressure Vessel Design (Original)'}
 
 
 for problem in population_data:
@@ -192,5 +193,29 @@ content = """\\begin{figure}[H]
 \\end{figure}
 """
 with open("latex/includes/pressure_vessel_problem_boxplot.tex", "w") as f:
+    f.write(content)
+
+#: spring problem boxplots
+
+fit_keys = [alg_desc[x] for x in fit_results]
+
+fit_values = fit_results.values()
+
+plt.close('all')
+
+plt.boxplot(fit_values, labels=fit_keys)
+
+plt.title("Pressure Vessel Design (Original) - Boxplot")
+
+plt.savefig("latex/images/pressure_vessel_problem_original_boxplot.png", dpi=600)
+
+content = """\\begin{figure}[H]
+\\centering
+\\caption{Boxplot for Pressure Vessel Design}
+\\label{fig:pressure_vessel_design_original_boxplot}
+\\includegraphics[scale=0.5]{images/pressure_vessel_problem_original_boxplot.png}
+\\end{figure}
+"""
+with open("latex/includes/pressure_vessel_problem_original_boxplot.tex", "w") as f:
     f.write(content)
 

### 2023-01-19 tuning.py

@@ -88,8 +88,8 @@ alg_params = {"solve_ep": {"epoch": [epochs],
                             "pop_size": [pop_size],
                             "c1": [1.0, 1.6, 2.0, 2.5, 3.0],
                             "c2": [1.0, 1.6, 2.0, 2.5, 3.0],
-                            "w_min": [0.1, 0.2, 0.3, 0.39],
-                            "w_max": [0.41, 0.6, 0.8, 1.0, 1.2, 1.5]}
+                            "w_min": [0.1, 0.2, 0.3, 0.4],
+                            "w_max": [0.6, 0.8, 1.0, 1.2, 1.5]}
               }
 
 best_parameters = dict()

### 2023-01-19 to_latex.py
header.tex file done

@@ -195,6 +195,10 @@ content = """\\begin{figure}[H]
 with open("latex/includes/pressure_vessel_problem_boxplot.tex", "w") as f:
     f.write(content)
 
+
+with open("results/pressure_vessel_problem_original_fit_results.json", "r") as f:
+    fit_results = json.load(f)
+
 #: spring problem boxplots
 
 fit_keys = [alg_desc[x] for x in fit_results]
@@ -211,7 +215,7 @@ plt.savefig("latex/images/pressure_vessel_problem_original_boxplot.png", dpi=600
 
 content = """\\begin{figure}[H]
 \\centering
-\\caption{Boxplot for Pressure Vessel Design}
+\\caption{Boxplot for Pressure Vessel Design (Original)}
 \\label{fig:pressure_vessel_design_original_boxplot}
 \\includegraphics[scale=0.5]{images/pressure_vessel_problem_original_boxplot.png}
 \\end{figure}

### 2023-01-19 to_latex.py
Tewaking article graphics

@@ -111,13 +111,13 @@ for problem in population_data:
 
         x = np.linspace(1, len(min), len(min))
 
-        plt.plot(x, np.log(min), label="Min values")
+        plt.plot(x, min, label="Min values")
 
-        plt.plot(x, np.log(mean), label="Mean values")
+        plt.plot(x, mean, label="Mean values")
 
-        plt.plot(x, np.log(max), label="Max values")
+        plt.plot(x, max, label="Max values")
 
-        #: plt.yscale('log')
+        plt.yscale('log')
 
         plt.title(alg_desc[solver] + " - " + problem_desc[problem])
 

### 2023-01-19 latex/article.tex
Formatting Done.

@@
     version 3.10 and uses \textit{MealPy} package, version 2.5.1,  to provide the algorithms.
-    The algorithms were randomly chosen from a vast list from \textit{MealPy}'s algorithms:
+    The algorithms were randomly chosen from a vast list of \textit{MealPy}'s algorithms:
     \textit{Evolutionary Programming (LevyEP)}, \textit{Evolution Strategies (OriginalES)} and
@@
 \section{Results}
-\label{sec:results}\subsection{Spring Tension Design}
+\label{sec:results}
+\subsection{Spring Tension Design}
+\label{ssubec:spring_problem}
 
-\label{ssubec:spring_problem}\subsubsection{Evolutionary Algorithms}
+\begin{table}[H]
+\centering
+\caption{Statistical Information about function values for Spring Tension Design}
+\label{function_values:spring_problem}
+\resizebox{\columnwidth}{!}{%
+\begin{tabular}{lrrrrr}
+\toprule
+Algorithm &      Min F &     Mean F &   Median F &      Max F &   StdDev F \\
+\midrule
+       EP & 0.01250534 & 0.01255960 & 0.01253156 & 0.01453933 & 0.00020190 \\
+       ES & 0.01252956 & 0.01281857 & 0.01274283 & 0.01346214 & 0.00024181 \\
+       GA & 0.01252305 & 0.01628575 & 0.01616768 & 0.02561808 & 0.00273276 \\
+    BeesA & 0.01250200 & 0.01268010 & 0.01261691 & 0.01406679 & 0.00021629 \\
+      FFA & 0.01249803 & 0.01254780 & 0.01253499 & 0.01268116 & 0.00003152 \\
+      PSO & 0.01252626 & 0.01390866 & 0.01318774 & 0.03036537 & 0.00342240 \\
+\bottomrule
+\end{tabular}}
+\end{table}
 
-\label{subsubsec:spring_problem_evolutionary_based}
+\begin{figure}[H]
+\centering
+\caption{Boxplot for Spring Tension Design}
+\label{fig:spring_tension_design_boxplot}
+\includegraphics[scale=0.5]{images/spring_problem_boxplot.png}
+\end{figure}
 
-\subsubsection{Swarm Based Algorithms}
+\begin{figure}[H]
+\centering
+\caption{Convergence lines for Spring Tension Design}
+\label{fig:spring_problem_convergence}
+\includegraphics[width= 0.4 \textwidth]{images/spring_problem_convergence.png}
+\end{figure}
 
-\label{subsubsec:spring_problem_swarm_based}
+\subsection{Pressure Vessel Design (Original)}
+\label{subsec:pressure_vessel_problem_original}
+
+\begin{table}[H]
+\centering
+\caption{Statistical Information about function values for Pressure Vessel Design (Original)}
+\label{function_values:pressure_vessel_problem_original}
+\resizebox{\columnwidth}{!}{%
+\begin{tabular}{lrrrrr}
+\toprule
+Algorithm &         Min F &         Mean F &       Median F &          Max F &       StdDev F \\
+\midrule
+       EP &    0.08150806 &     0.15642850 &     0.09093798 &     1.32637552 &     0.16807714 \\
+       ES &    0.08161190 &   718.92910990 &     1.00278859 &  9443.54269260 &  2060.07774212 \\
+       GA &   17.06920868 &   525.00734162 &   361.53879602 &  3112.03503082 &   454.52386703 \\
+    BeesA & 2393.70106213 & 17564.33024022 & 15751.91467117 & 53850.38271384 & 10514.60780411 \\
+      FFA &    0.08306113 &     0.13296127 &     0.13106271 &     0.20084847 &     0.02396876 \\
+      PSO &    0.08149204 &     0.24191732 &     0.08159173 &    10.00611523 &     1.00072349 \\
+\bottomrule
+\end{tabular}}
+\end{table}
+
+\begin{figure}[H]
+\centering
+\caption{Boxplot for Pressure Vessel Design (Original)}
+\label{fig:pressure_vessel_design_original_boxplot}
+\includegraphics[scale=0.5]{images/pressure_vessel_problem_original_boxplot.png}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\caption{Convergence lines for Pressure Vessel Design (Original)}
+\label{fig:pressure_vessel_problem_original_convergence}
+\includegraphics[width= 0.4 \textwidth]{images/pressure_vessel_problem_original_convergence.png}
+\end{figure}
 
 \subsection{Pressure Vessel Design}
+\label{subsec:pressure_vessel_problem}
 
-\label{subsec:pressure_vessel_problem}\subsubsection{Evolutionary Algorithms}
+\begin{table}
+\centering
+\caption{Statistical Information about function values for Pressure Vessel Design}
+\label{function_values:pressure_vessel_problem}
+\resizebox{\columnwidth}{!}{%
+\begin{tabular}{lrrrrr}
+\toprule
+Algorithm &         Min F &        Mean F &      Median F &         Max F &   StdDev F \\
+\midrule
+       EP & 5534.57345496 & 5534.63426098 & 5534.61416291 & 5534.92993607 & 0.05804548 \\
+       ES & 5534.57917966 & 5535.28165367 & 5535.06149254 & 5538.03003895 & 0.65098467 \\
+       GA & 5534.83662424 & 5538.36788889 & 5536.92932748 & 5550.91639342 & 3.57079951 \\
+    BeesA & 5534.57516657 & 5537.97495231 & 5537.04824684 & 5548.55587234 & 3.28239740 \\
+      FFA & 5534.57401617 & 5534.58849395 & 5534.58435493 & 5534.63296149 & 0.01341777 \\
+      PSO & 5534.57345480 & 5534.57381593 & 5534.57355270 & 5534.57625290 & 0.00053848 \\
+\bottomrule
+\end{tabular}
+}
+\end{table}
 
-\label{subsubsec:pressure_vessel_problem_evolutionary_based}
+\begin{figure}[H]
+\centering
+\caption{Boxplot for Pressure Vessel Design}
+\label{fig:pressure_vessel_design_boxplot}
+\includegraphics[scale=0.5]{images/pressure_vessel_problem_boxplot.png}
+\end{figure}
 
-\subsubsection{Swarm Based Algorithms}
+\begin{figure}[H]
+\centering
+\caption{Convergence lines for Pressure Vessel Design}
+\label{fig:pressure_vessel_problem_convergence}
+\includegraphics[width=0.4 \textwidth]{images/pressure_vessel_problem_convergence.png}
+\end{figure}
 
-\label{subsubsec:pressure_vessel_problem_swarm_based}
+\subsection{Significance Test}
+\label{subsec:pressure_vessel_problem_significance_test}
+
+\begin{table}[H]
+\centering
+\caption{Significance Test Using Friedman Chi-Squared Test}
+\label{friedman_test}
+\resizebox{\columnwidth}{!}{%
+\begin{tabular}{lrr}
+\toprule
+                          Problem &   Statistics &    p-value \\
+\midrule
+            Spring Tension Design & 339.05714286 & 0.00000000 \\
+           Pressure Vessel Design & 436.16000000 & 0.00000000 \\
+Pressure Vessel Design (Original) & 425.07428571 & 0.00000000 \\
+\bottomrule
+\end{tabular}
+}
+\end{table}
 

### 2023-01-19 latex/includes/pressure_vessel_problem_convergence.tex
Formatting Done.

--- 2023-01-17 latex/article.tex
@@
-\documentclass[conference]{IEEEtran}
-\IEEEoverridecommandlockouts
-% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-\usepackage{cite}
-\usepackage{amsmath,amssymb,amsfonts}
-\usepackage{mathtools}
-\usepackage{algpseudocode}
-\usepackage{algorithm}
-\usepackage{algorithmicx}
-\usepackage{microtype}
-\usepackage{float}
-\usepackage{adjustbox}
-\usepackage{booktabs,makecell,tabularx}
-\usepackage{graphicx}
-\usepackage{textcomp}
-\usepackage{verbatim}
-\usepackage{xcolor}
-\usepackage{graphics} % for pdf, bitmapped graphics files
-\usepackage{epsfig} % for postscript graphics files
-\usepackage{mathptmx} % assumes new font selection scheme installed
-\usepackage{multicol}
-\usepackage[english]{babel}
-\usepackage[T1]{fontenc}
-\restylefloat{table}
-\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
-    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
-\begin{document}
-\title{Swarm and Evolutionary Based Algorithms used for Optimization}
-\author{
-	\IEEEauthorblockN{Augusto Mathias Adams\IEEEauthorrefmark{1}, Caio Phillipe Mizerkowski\IEEEauthorrefmark{2}, Christian Piltz Araújo\IEEEauthorrefmark{3} and Vinicius Eduardo dos Reis\IEEEauthorrefmark{4}}\\
-	\IEEEauthorblockA{\IEEEauthorrefmark{1}GRR20172143, augusto.adams@ufpr.br, \IEEEauthorrefmark{2}GRR20166403, caiomizerkowski@gmail.com,\\ \IEEEauthorrefmark{3}GRR20172197, christian0294@yahoo.com.br, \IEEEauthorrefmark{4}GRR20175957, eduardo.reis02@gmail.com}
-}
-
-\maketitle
-
-\begin{abstract}
-    In this paper, a study of evolution and swarm based algorithms is presented,
-    using two classical engineering problems: \textit{Spring Tension} and \textit{Pressure Vessel
-    Designs}. The test code for the problems was made using the \textit{Python Language},
-    version 3.10 and uses \textit{MealPy} package, version 2.5.1,  to provide the algorithms.
-    Thre algorithms were randomly chosen from a vaste list from MealPy algorithms:
-    \textit{Evolutionary Programming (LevyEP)}, \textit{Evolution Strategies (OriginalES)} and
-    \textit{Genetic Algorithm (BaseGA)} from \textit{evolutionary\_based} subpackage;
-    \textit{Bees Algorithm (OriginalBeesA)}, \textit{Firefly Algorithm (OriginalFFA)} and
-    \textit{Particle Swarm Optimization (OriginalPSO)} from \textit{swarm\_based} subpackage.
-    Each problem was modeled using \textit{SciPy} package, with constraints implemented as
-    \textit{penalty functions}. Each algorithm were optimized separately to extract the best
-    solutions from each problem using the \textit{MealPy}'s \textit{Tuner} utility.
-    The results, however, are dependant of algorithm and problem presented but from
-    similarity test using Friedman's Chi-Squared test, it would be suffice to say that using any
-    of the tested algorithm will produce similar results in these two optimization problems.
-\end{abstract}
-
-\begin{IEEEkeywords}
-	Optimization Methods, Evolutionary Programming, Evolutionary and Swarm Based Strategies.
-\end{IEEEkeywords}
-
-\section{Definitions}
-\label{sec:definitions}
-
-The main objective of this paper is study evolutionary and swarm intelligence algorithms.
-We present the main concepts of these two algorithm's classes, along with the chosen algorithms
-definitions in this section. All citations made in this document are due to Swarm Intelligence classes
-and to \textit{MealPy}'s documentation, which points out the theoretical documentation for each
-implemented algorithm.
-
-\textit{\textbf{Evolution}}: From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolutionary Algorithms belong to the Evolutionary Computation
-field of study concerned with computational methods inspired by the process
-and mechanisms of biological evolution. The process of evolution by
-means of natural selection (descent with modification) was proposed by
-Darwin to account for the variety of life and its suitability (adaptive
-fit) for its environment. The mechanisms of evolution describe how
-evolution actually takes place through the modification and propagation
-of genetic material (proteins). Evolutionary Algorithms are concerned
-with investigating computational systems that resemble simplified ver-
-sions of the processes and mechanisms of evolution toward achieving
-the effects of these processes and mechanisms, namely the development
-of adaptive systems. Additional subject areas that fall within the realm
-of Evolutionary Computation are algorithms that seek to exploit the
-properties from the related fields of Population Genetics, Population
-Ecology, Coevolutionary Biology, and Developmental Biology.
-
-\textit{\textbf{Swarm Intelligence}}: From Jason Brownlee's \textit{``Clever Algorithms''} -
-Swarm intelligence is the study of computational systems inspired by
-the ‘collective intelligence’. Collective Intelligence emerges through the
-cooperation of large numbers of homogeneous agents in the environment.
-Examples include schools of fish, flocks of birds, and colonies of ants.
-Such intelligence is decentralized, self-organizing and distributed through
-out an environment. In nature such systems are commonly used to
-solve problems such as effective foraging for food, prey evading, or
-colony re-location. The information is typically stored throughout the
-participating homogeneous agents, or is stored or communicated in
-the environment itself such as through the use of pheromones in ants,
-dancing in bees, and proximity in fish and birds.
-
-\textit{\textbf{Evolutionary Programming:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolutionary Programming is a Global Optimization algorithm and is an instance of an Evolutionary
-Algorithm from the field of Evolutionary Computation. The approach is a sibling of other Evolutionary
-Algorithms such as the Genetic Algorithm, and Learning Classifier Systems. It is sometimes confused with Genetic
-Programming given the similarity in name, and more recently it shows a strong functional similarity to Evolution Strategies.
-Evolutionary Programming is inspired by the theory of evolution by means of natural selection. Specifically, the technique is inspired by
-macro-level or the species-level process of evolution (phenotype, hereditary, variation) and is not concerned with the genetic mechanisms of
-evolution (genome, chromosomes, genes, alleles).
-
-\textit{\textbf{Evolutionary Strategies:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolution Strategies is a global optimization algorithm and is an instance of an Evolutionary Algorithm from the field of Evolutionary
-Computation. Evolution Strategies is a sibling technique to other Evolutionary Algorithms such as Genetic Algorithms (Section 3.2), Genetic
-Programming (Section 3.3), Learning Classifier Systems, and Evolutionary Programming. A popular descendant of
-the Evolution Strategies algorithm is the Covariance Matrix Adaptation Evolution Strategies (CMA-ES).
-
-\textit{\textbf{Genetic Algorithms:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-The Genetic Algorithm is an Adaptive Strategy and a Global Optimization technique. It is an Evolutionary Algorithm and belongs to the
-broader study of Evolutionary Computation. The Genetic Algorithm is a sibling of other Evolutionary Algorithms such as Genetic Programming,
- Evolution Strategies, Evolutionary Programming, and Learning Classifier Systems. The Genetic Algorithm is a parent of a large number of variant techniques
-and sub-fields too numerous to list. The Genetic Algorithm is inspired by population genetics (including heredity and gene frequencies),
-and evolution at the population level, as well as the Mendelian understanding of the structure (such as chromosomes, genes, alleles) and mechanisms
-(such as recombination and mutation). This is the so-called new or modern synthesis of evolutionary biology.
-
-\textit{\textbf{Particle Swarm Optimization:}} From Jason Brownlee's \textit{``Clever Algorithms''} - Particle Swarm Optimization belongs to the field of
-Swarm Intelligence and Collective Intelligence and is a sub-field of Computational Intelligence. Particle Swarm Optimization is related to other Swarm Intelligence
-algorithms such as Ant Colony Optimization and it is a baseline algorithm for many variations, too numerous to list. It is inspired by the social foraging behavior
-of some animals such as flocking behavior of birds and the schooling behavior of fish.
-
-\textit{\textbf{Firefly Algorithm:}} From Xin-She Yang \textit{``Nature-Inspired Metaheuristic Algorithms''} -
-The flashing light of fireflies is an amazing sight in the summer sky in the tropical and temperate regions. There are about two thousand firefly
-species, and most fireflies produce short and rhythmic flashes. The pattern of flashes is often unique for a particular species. The flashing light is
-produced by a process of bioluminescence, and the true functions of suchsignaling systems are still being debated. However, two fundamental functions
-of such flashes are to attract mating partners (communication), and to attract potential prey. In addition, flashing may also serve as a protective warning
-mechanism to remind potential predators of the bitter taste of fireflies. The firefly algorithm tries to mimic the attractiveness of Fireflies and has three
-basic rules:
-
-\begin{itemize}
-    \item All fireflies are unisex so that one firefly will be attracted to other
-          fireflies regardless of their sex;
-    \item Attractiveness is proportional to the their brightness, thus for any two
-          flashing fireflies, the less brighter one will move towards the brighter
-          one. The attractiveness is proportional to the brightness and they
-          both decrease as their distance increases. If there is no brighter one
-          than a particular firefly, it will move randomly;
-    \item The brightness of a firefly is affected or determined by the landscape
-          of the objective function.
-\end{itemize}
-
-\textit{\textbf{Bees Algorithm:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-The Bees Algorithm beings to Bee Inspired Algorithms and the field of Swarm Intelligence, and more broadly the fields of Computational
-Intelligence and Metaheuristics. The Bees Algorithm is related to other Bee Inspired Algorithms, such as Bee Colony Optimization, and other
-Swarm Intelligence algorithms such as Ant Colony Optimization and Particle Swarm Optimization.
-It is inspired by the foraging behavior of honey bees. Honey bees collect nectar from vast areas around their hive (more than
-10 kilometers). Bee Colonies have been observed to send bees to collect nectar from flower patches relative to the amount of food available at
-each patch. Bees communicate with each other at the hive via a waggle dance that informs other bees in the hive as to the direction, distance,
-and quality rating of food sources.
-
-\section{Metodology}
-\label{sec:metodology}
-
-\subsection{Optimimzation Problem Selection}
-The two problems selected for this paper were \textit{Spring Tension Design} and \textit{Pressure Vessel Design}. Although it was simple
-to choose the first two problems from the computational work statements, the choice was more than justified because these aroblems are well
-known in the literature. Thus, the problem selection was driven by which has more that one source to compare results.
-
-\subsection{Programming Language}
-
-The chosen programming language for the test code was \textit{Python Language}, version 3.10, because it is an opensource language easy to
-program and has a huge amount of packages regarding artificial intelligence, genetic algorithms and swarm based algorithms. From these packages it
-was selected \textit{MealPy} package, version 2.5.1, because it comprises all the algorithm's classed tested in this paper.
-
-\subsection{Algorithm Selection}
-
-The algorithm selection was made in two steps: first, it was extracted simple version of the two classes (evolutionary and swarm based) and
-then it was used a simple shuffle using
-
-\subsection{Model Parameters}
-
-For all models and problems, were selected the following parameters:
-
-\begin{itemize}
-    \item \textit{Runs}: 100 runs
-    \item \textit{Epochs}: 100 epochs
-    \item \textit{Population}: 100 initial points
-\end{itemize}
-
-The initial solutions were randomly selected using the same seed for all algorithms.
-
-\subsection{Model Tuning}
-
-\section{Results}
-\label{sec:results}\subsection{Spring Tension Design}
-
-\label{ssubec:spring_problem}\subsubsection{Evolutionary Algorithms}
-
-\label{subsubsec:spring_problem_evolutionary_based}
-
-\subsubsection{Swarm Based Algorithms}
-
-\label{subsubsec:spring_problem_swarm_based}
-
-\subsection{Pressure Vessel Design}
-
-\label{subsec:pressure_vessel_problem}\subsubsection{Evolutionary Algorithms}
-
-\label{subsubsec:pressure_vessel_problem_evolutionary_based}
-
-\subsubsection{Swarm Based Algorithms}
-
-\label{subsubsec:pressure_vessel_problem_swarm_based}
-
-\section{Discussion}
-
-The main objective of this work is demonstrate the inner work of a optimization class of algorithms called \textit{Quasi-Newton algorithms}.
-Four of them are presented, along with the results and analysis regarding convergence, function evaluations and function objective values.
-
-For implementation, it was decided to put constraints on search space, because for the original search space of some functions, like Ackley and Rastrigin, there are other minimas that will confuse every algorithm tested for this paper, and there is no sense on test a local minima procedure on these conditions.
-To restrain the initial solution to some region in the search space was a cheap and ready solution to avoid the algorithms to stop because of stumbling upon the wrong minimum.
-
-The \textit{Levenberg-Marquardt Algorithm} implemented for this paper is very sensitive to hyperparameters, namely $\alpha$ and $\lambda$, which was not tunned to every function, so, the conspicuous performance variation is noticeable along the results.
-LMA is known to be fast and reliable, but in our implementation it was found a little tricky to get the hyperparameters right for all the test functions.
-But for Rosenbrock and Rastrigin, it is the best option, even for lame implementations like ours.
-
-The \textit{Broyden–Fletcher–Goldfarb–Shanno} Algorithm was the only one that we decided to use it as is from \textit{SciPy}, because it has features desired for this work, like counting of function evaluations, gradient evaluation and iterations.
-It performed very well for Ackley and Booth Functions, and reasonably well for other functions.
-
-The \textit{Davidon–Fletcher–Powell} Algorithm is not implemented in \textit{SciPy} but its equations shows that it is the dual of BFGS, so, it was easy to implement using some \textit{SciPy} code for BFGS algorithm.
-In the DFP procedure, there is a Hessian inversion to be evaluated every iteration, then, numerical imprecision would be taken into consideration evaluating its results.
-While in some cases it has a superb performance (Like Ackley Function), it has very poor performance in Rosenbrock Function and even in Beale Function.
-The increase of dimensions makes DFP suffer of numerical imprecision due to the Hessian inversion, except for Rastrigin, and it is the loser algorithm in other functions.
-
-Finally, the \textit{Limited memory BFGS} has an average performance among the functions.
-The original algorithm was implemented using code found in the url https://github.com/qkolj/L-BFGS/blob/master/L-BFGS.ipynb.
-
-In fact, there are no Quasi-Newton algorithms that solver the minima problem for an any function.
-From the standpoint of performance and convergence, all the algorithms have an average performance and a reasonable convergence, although we have to restrain the search space to a small area near the optimal solution.
-
-\end{document}
+\begin{figure}[H]
+\centering
+\caption{Convergence lines for Pressure Vessel Design}
+\label{fig:pressure_vessel_problem_convergence}
+\includegraphics[width=0.4 \textwidth]{images/pressure_vessel_problem_convergence.png}
+\end{figure}

### 2023-01-19 latex/includes/pressure_vessel_problem_original_convergence.tex
Formatting Done.

--- 2023-01-17 latex/article.tex
@@
-\documentclass[conference]{IEEEtran}
-\IEEEoverridecommandlockouts
-% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-\usepackage{cite}
-\usepackage{amsmath,amssymb,amsfonts}
-\usepackage{mathtools}
-\usepackage{algpseudocode}
-\usepackage{algorithm}
-\usepackage{algorithmicx}
-\usepackage{microtype}
-\usepackage{float}
-\usepackage{adjustbox}
-\usepackage{booktabs,makecell,tabularx}
-\usepackage{graphicx}
-\usepackage{textcomp}
-\usepackage{verbatim}
-\usepackage{xcolor}
-\usepackage{graphics} % for pdf, bitmapped graphics files
-\usepackage{epsfig} % for postscript graphics files
-\usepackage{mathptmx} % assumes new font selection scheme installed
-\usepackage{multicol}
-\usepackage[english]{babel}
-\usepackage[T1]{fontenc}
-\restylefloat{table}
-\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
-    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
-\begin{document}
-\title{Swarm and Evolutionary Based Algorithms used for Optimization}
-\author{
-	\IEEEauthorblockN{Augusto Mathias Adams\IEEEauthorrefmark{1}, Caio Phillipe Mizerkowski\IEEEauthorrefmark{2}, Christian Piltz Araújo\IEEEauthorrefmark{3} and Vinicius Eduardo dos Reis\IEEEauthorrefmark{4}}\\
-	\IEEEauthorblockA{\IEEEauthorrefmark{1}GRR20172143, augusto.adams@ufpr.br, \IEEEauthorrefmark{2}GRR20166403, caiomizerkowski@gmail.com,\\ \IEEEauthorrefmark{3}GRR20172197, christian0294@yahoo.com.br, \IEEEauthorrefmark{4}GRR20175957, eduardo.reis02@gmail.com}
-}
-
-\maketitle
-
-\begin{abstract}
-    In this paper, a study of evolution and swarm based algorithms is presented,
-    using two classical engineering problems: \textit{Spring Tension} and \textit{Pressure Vessel
-    Designs}. The test code for the problems was made using the \textit{Python Language},
-    version 3.10 and uses \textit{MealPy} package, version 2.5.1,  to provide the algorithms.
-    Thre algorithms were randomly chosen from a vaste list from MealPy algorithms:
-    \textit{Evolutionary Programming (LevyEP)}, \textit{Evolution Strategies (OriginalES)} and
-    \textit{Genetic Algorithm (BaseGA)} from \textit{evolutionary\_based} subpackage;
-    \textit{Bees Algorithm (OriginalBeesA)}, \textit{Firefly Algorithm (OriginalFFA)} and
-    \textit{Particle Swarm Optimization (OriginalPSO)} from \textit{swarm\_based} subpackage.
-    Each problem was modeled using \textit{SciPy} package, with constraints implemented as
-    \textit{penalty functions}. Each algorithm were optimized separately to extract the best
-    solutions from each problem using the \textit{MealPy}'s \textit{Tuner} utility.
-    The results, however, are dependant of algorithm and problem presented but from
-    similarity test using Friedman's Chi-Squared test, it would be suffice to say that using any
-    of the tested algorithm will produce similar results in these two optimization problems.
-\end{abstract}
-
-\begin{IEEEkeywords}
-	Optimization Methods, Evolutionary Programming, Evolutionary and Swarm Based Strategies.
-\end{IEEEkeywords}
-
-\section{Definitions}
-\label{sec:definitions}
-
-The main objective of this paper is study evolutionary and swarm intelligence algorithms.
-We present the main concepts of these two algorithm's classes, along with the chosen algorithms
-definitions in this section. All citations made in this document are due to Swarm Intelligence classes
-and to \textit{MealPy}'s documentation, which points out the theoretical documentation for each
-implemented algorithm.
-
-\textit{\textbf{Evolution}}: From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolutionary Algorithms belong to the Evolutionary Computation
-field of study concerned with computational methods inspired by the process
-and mechanisms of biological evolution. The process of evolution by
-means of natural selection (descent with modification) was proposed by
-Darwin to account for the variety of life and its suitability (adaptive
-fit) for its environment. The mechanisms of evolution describe how
-evolution actually takes place through the modification and propagation
-of genetic material (proteins). Evolutionary Algorithms are concerned
-with investigating computational systems that resemble simplified ver-
-sions of the processes and mechanisms of evolution toward achieving
-the effects of these processes and mechanisms, namely the development
-of adaptive systems. Additional subject areas that fall within the realm
-of Evolutionary Computation are algorithms that seek to exploit the
-properties from the related fields of Population Genetics, Population
-Ecology, Coevolutionary Biology, and Developmental Biology.
-
-\textit{\textbf{Swarm Intelligence}}: From Jason Brownlee's \textit{``Clever Algorithms''} -
-Swarm intelligence is the study of computational systems inspired by
-the ‘collective intelligence’. Collective Intelligence emerges through the
-cooperation of large numbers of homogeneous agents in the environment.
-Examples include schools of fish, flocks of birds, and colonies of ants.
-Such intelligence is decentralized, self-organizing and distributed through
-out an environment. In nature such systems are commonly used to
-solve problems such as effective foraging for food, prey evading, or
-colony re-location. The information is typically stored throughout the
-participating homogeneous agents, or is stored or communicated in
-the environment itself such as through the use of pheromones in ants,
-dancing in bees, and proximity in fish and birds.
-
-\textit{\textbf{Evolutionary Programming:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolutionary Programming is a Global Optimization algorithm and is an instance of an Evolutionary
-Algorithm from the field of Evolutionary Computation. The approach is a sibling of other Evolutionary
-Algorithms such as the Genetic Algorithm, and Learning Classifier Systems. It is sometimes confused with Genetic
-Programming given the similarity in name, and more recently it shows a strong functional similarity to Evolution Strategies.
-Evolutionary Programming is inspired by the theory of evolution by means of natural selection. Specifically, the technique is inspired by
-macro-level or the species-level process of evolution (phenotype, hereditary, variation) and is not concerned with the genetic mechanisms of
-evolution (genome, chromosomes, genes, alleles).
-
-\textit{\textbf{Evolutionary Strategies:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolution Strategies is a global optimization algorithm and is an instance of an Evolutionary Algorithm from the field of Evolutionary
-Computation. Evolution Strategies is a sibling technique to other Evolutionary Algorithms such as Genetic Algorithms (Section 3.2), Genetic
-Programming (Section 3.3), Learning Classifier Systems, and Evolutionary Programming. A popular descendant of
-the Evolution Strategies algorithm is the Covariance Matrix Adaptation Evolution Strategies (CMA-ES).
-
-\textit{\textbf{Genetic Algorithms:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-The Genetic Algorithm is an Adaptive Strategy and a Global Optimization technique. It is an Evolutionary Algorithm and belongs to the
-broader study of Evolutionary Computation. The Genetic Algorithm is a sibling of other Evolutionary Algorithms such as Genetic Programming,
- Evolution Strategies, Evolutionary Programming, and Learning Classifier Systems. The Genetic Algorithm is a parent of a large number of variant techniques
-and sub-fields too numerous to list. The Genetic Algorithm is inspired by population genetics (including heredity and gene frequencies),
-and evolution at the population level, as well as the Mendelian understanding of the structure (such as chromosomes, genes, alleles) and mechanisms
-(such as recombination and mutation). This is the so-called new or modern synthesis of evolutionary biology.
-
-\textit{\textbf{Particle Swarm Optimization:}} From Jason Brownlee's \textit{``Clever Algorithms''} - Particle Swarm Optimization belongs to the field of
-Swarm Intelligence and Collective Intelligence and is a sub-field of Computational Intelligence. Particle Swarm Optimization is related to other Swarm Intelligence
-algorithms such as Ant Colony Optimization and it is a baseline algorithm for many variations, too numerous to list. It is inspired by the social foraging behavior
-of some animals such as flocking behavior of birds and the schooling behavior of fish.
-
-\textit{\textbf{Firefly Algorithm:}} From Xin-She Yang \textit{``Nature-Inspired Metaheuristic Algorithms''} -
-The flashing light of fireflies is an amazing sight in the summer sky in the tropical and temperate regions. There are about two thousand firefly
-species, and most fireflies produce short and rhythmic flashes. The pattern of flashes is often unique for a particular species. The flashing light is
-produced by a process of bioluminescence, and the true functions of suchsignaling systems are still being debated. However, two fundamental functions
-of such flashes are to attract mating partners (communication), and to attract potential prey. In addition, flashing may also serve as a protective warning
-mechanism to remind potential predators of the bitter taste of fireflies. The firefly algorithm tries to mimic the attractiveness of Fireflies and has three
-basic rules:
-
-\begin{itemize}
-    \item All fireflies are unisex so that one firefly will be attracted to other
-          fireflies regardless of their sex;
-    \item Attractiveness is proportional to the their brightness, thus for any two
-          flashing fireflies, the less brighter one will move towards the brighter
-          one. The attractiveness is proportional to the brightness and they
-          both decrease as their distance increases. If there is no brighter one
-          than a particular firefly, it will move randomly;
-    \item The brightness of a firefly is affected or determined by the landscape
-          of the objective function.
-\end{itemize}
-
-\textit{\textbf{Bees Algorithm:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-The Bees Algorithm beings to Bee Inspired Algorithms and the field of Swarm Intelligence, and more broadly the fields of Computational
-Intelligence and Metaheuristics. The Bees Algorithm is related to other Bee Inspired Algorithms, such as Bee Colony Optimization, and other
-Swarm Intelligence algorithms such as Ant Colony Optimization and Particle Swarm Optimization.
-It is inspired by the foraging behavior of honey bees. Honey bees collect nectar from vast areas around their hive (more than
-10 kilometers). Bee Colonies have been observed to send bees to collect nectar from flower patches relative to the amount of food available at
-each patch. Bees communicate with each other at the hive via a waggle dance that informs other bees in the hive as to the direction, distance,
-and quality rating of food sources.
-
-\section{Metodology}
-\label{sec:metodology}
-
-\subsection{Optimimzation Problem Selection}
-The two problems selected for this paper were \textit{Spring Tension Design} and \textit{Pressure Vessel Design}. Although it was simple
-to choose the first two problems from the computational work statements, the choice was more than justified because these aroblems are well
-known in the literature. Thus, the problem selection was driven by which has more that one source to compare results.
-
-\subsection{Programming Language}
-
-The chosen programming language for the test code was \textit{Python Language}, version 3.10, because it is an opensource language easy to
-program and has a huge amount of packages regarding artificial intelligence, genetic algorithms and swarm based algorithms. From these packages it
-was selected \textit{MealPy} package, version 2.5.1, because it comprises all the algorithm's classed tested in this paper.
-
-\subsection{Algorithm Selection}
-
-The algorithm selection was made in two steps: first, it was extracted simple version of the two classes (evolutionary and swarm based) and
-then it was used a simple shuffle using
-
-\subsection{Model Parameters}
-
-For all models and problems, were selected the following parameters:
-
-\begin{itemize}
-    \item \textit{Runs}: 100 runs
-    \item \textit{Epochs}: 100 epochs
-    \item \textit{Population}: 100 initial points
-\end{itemize}
-
-The initial solutions were randomly selected using the same seed for all algorithms.
-
-\subsection{Model Tuning}
-
-\section{Results}
-\label{sec:results}\subsection{Spring Tension Design}
-
-\label{ssubec:spring_problem}\subsubsection{Evolutionary Algorithms}
-
-\label{subsubsec:spring_problem_evolutionary_based}
-
-\subsubsection{Swarm Based Algorithms}
-
-\label{subsubsec:spring_problem_swarm_based}
-
-\subsection{Pressure Vessel Design}
-
-\label{subsec:pressure_vessel_problem}\subsubsection{Evolutionary Algorithms}
-
-\label{subsubsec:pressure_vessel_problem_evolutionary_based}
-
-\subsubsection{Swarm Based Algorithms}
-
-\label{subsubsec:pressure_vessel_problem_swarm_based}
-
-\section{Discussion}
-
-The main objective of this work is demonstrate the inner work of a optimization class of algorithms called \textit{Quasi-Newton algorithms}.
-Four of them are presented, along with the results and analysis regarding convergence, function evaluations and function objective values.
-
-For implementation, it was decided to put constraints on search space, because for the original search space of some functions, like Ackley and Rastrigin, there are other minimas that will confuse every algorithm tested for this paper, and there is no sense on test a local minima procedure on these conditions.
-To restrain the initial solution to some region in the search space was a cheap and ready solution to avoid the algorithms to stop because of stumbling upon the wrong minimum.
-
-The \textit{Levenberg-Marquardt Algorithm} implemented for this paper is very sensitive to hyperparameters, namely $\alpha$ and $\lambda$, which was not tunned to every function, so, the conspicuous performance variation is noticeable along the results.
-LMA is known to be fast and reliable, but in our implementation it was found a little tricky to get the hyperparameters right for all the test functions.
-But for Rosenbrock and Rastrigin, it is the best option, even for lame implementations like ours.
-
-The \textit{Broyden–Fletcher–Goldfarb–Shanno} Algorithm was the only one that we decided to use it as is from \textit{SciPy}, because it has features desired for this work, like counting of function evaluations, gradient evaluation and iterations.
-It performed very well for Ackley and Booth Functions, and reasonably well for other functions.
-
-The \textit{Davidon–Fletcher–Powell} Algorithm is not implemented in \textit{SciPy} but its equations shows that it is the dual of BFGS, so, it was easy to implement using some \textit{SciPy} code for BFGS algorithm.
-In the DFP procedure, there is a Hessian inversion to be evaluated every iteration, then, numerical imprecision would be taken into consideration evaluating its results.
-While in some cases it has a superb performance (Like Ackley Function), it has very poor performance in Rosenbrock Function and even in Beale Function.
-The increase of dimensions makes DFP suffer of numerical imprecision due to the Hessian inversion, except for Rastrigin, and it is the loser algorithm in other functions.
-
-Finally, the \textit{Limited memory BFGS} has an average performance among the functions.
-The original algorithm was implemented using code found in the url https://github.com/qkolj/L-BFGS/blob/master/L-BFGS.ipynb.
-
-In fact, there are no Quasi-Newton algorithms that solver the minima problem for an any function.
-From the standpoint of performance and convergence, all the algorithms have an average performance and a reasonable convergence, although we have to restrain the search space to a small area near the optimal solution.
-
-\end{document}
+\begin{figure}[H]
+\centering
+\caption{Convergence lines for Pressure Vessel Design (Original)}
+\label{fig:pressure_vessel_problem_original_convergence}
+\includegraphics[width= 0.4 \textwidth]{images/pressure_vessel_problem_original_convergence.png}
+\end{figure}

### 2023-01-19 article_builder.py

@@ -12,36 +12,61 @@ content = ""
 
 #: header
 with open("latex/includes/header.tex", "r") as f:
-    content += f.read()
+    content += f.read() + "\n"
 
 #: spring problem
-content += "\\subsection{Spring Tension Design}\n\n"
-content += "\\label{ssubec:spring_problem}"
+content += "\\subsection{Spring Tension Design}\n"
+content += "\\label{ssubec:spring_problem}\n\n"
 
+with open("latex/includes/spring_problem.tex", "r") as f:
+    content += f.read() + "\n"
 
-content += "\\subsubsection{Evolutionary Algorithms}\n\n"
-content += "\\label{subsubsec:spring_problem_evolutionary_based}\n\n"
+with open("latex/includes/spring_problem_boxplot.tex", "r") as f:
+    content += f.read() + "\n"
 
-content += "\\subsubsection{Swarm Based Algorithms}\n\n"
-content += "\\label{subsubsec:spring_problem_swarm_based}\n\n"
+with open("latex/includes/spring_problem_convergence.tex", "r") as f:
+    content += f.read() + "\n"
 
 # pressure vessel problem
 
-content += "\\subsection{Pressure Vessel Design}\n\n"
-content += "\\label{subsec:pressure_vessel_problem}"
+content += "\\subsection{Pressure Vessel Design (Original)}\n"
+content += "\\label{subsec:pressure_vessel_problem_original}\n\n"
 
-content += "\\subsubsection{Evolutionary Algorithms}\n\n"
-content += "\\label{subsubsec:pressure_vessel_problem_evolutionary_based}\n\n"
+with open("latex/includes/pressure_vessel_problem_original.tex", "r") as f:
+    content += f.read() + "\n"
 
-content += "\\subsubsection{Swarm Based Algorithms}\n\n"
-content += "\\label{subsubsec:pressure_vessel_problem_swarm_based}\n\n"
+with open("latex/includes/pressure_vessel_problem_original_boxplot.tex", "r") as f:
+    content += f.read() + "\n"
+
+with open("latex/includes/pressure_vessel_problem_original_convergence.tex", "r") as f:
+    content += f.read() + "\n"
+
+# pressure vessel problem
+
+content += "\\subsection{Pressure Vessel Design}\n"
+content += "\\label{subsec:pressure_vessel_problem}\n\n"
+
+with open("latex/includes/pressure_vessel_problem.tex", "r") as f:
+    content += f.read() + "\n"
+
[…]

### 2023-01-19 to_latex.py

@@ -101,45 +101,131 @@ problem_desc = {'spring_problem': 'Spring Tension Design',
 
 
 for problem in population_data:
-    for solver in population_data[problem]:
+    plt.close('all')
+    fig, axs = plt.subplots(3, 2, figsize=(10, 10))
 
-        min = population_data[problem][solver]['min']
-        max = population_data[problem][solver]['max']
-        mean = population_data[problem][solver]['avg']
+    #: EP
 
-        plt.close('all')
+    s_min = population_data[problem]['solve_ep']['min']
+    s_max = population_data[problem]['solve_ep']['max']
+    s_mean = population_data[problem]['solve_ep']['avg']
 
-        x = np.linspace(1, len(min), len(min))
+    x = np.linspace(1, len(s_min), len(s_min))
 
-        plt.plot(x, min, label="Min values")
+    axs[0][0].plot(x, s_min, label="Min Values")
+    axs[0][0].plot(x, s_mean, label="Mean Values")
+    axs[0][0].plot(x, s_max, label="Max Values")
+    axs[0][0].set_xlabel('Epochs')
+    axs[0][0].set_ylabel('Obj. Fun Values(log)')
+    axs[0][0].set_yscale('log')
+    axs[0][0].set_title(alg_desc['solve_ep'])
+    axs[0][0].legend()
+    axs[0][0].grid(True)
 
-        plt.plot(x, mean, label="Mean values")
+    #: ES
 
-        plt.plot(x, max, label="Max values")
+    s_min = population_data[problem]['solve_es']['min']
+    s_max = population_data[problem]['solve_es']['max']
+    s_mean = population_data[problem]['solve_es']['avg']
 
-        plt.yscale('log')
+    x = np.linspace(1, len(s_min), len(s_min))
 
-        plt.title(alg_desc[solver] + " - " + problem_desc[problem])
+    axs[0][1].plot(x, s_min, label="Min Values")
+    axs[0][1].plot(x, s_mean, label="Mean Values")
+    axs[0][1].plot(x, s_max, label="Max Values")
+    axs[0][1].set_xlabel('Epochs')
+    axs[0][1].set_ylabel('Obj. Fun Values(log)')
+    axs[0][1].set_yscale('log')
+    axs[0][1].set_title(alg_desc['solve_es'])
+    axs[0][1].legend()
+    axs[0][1].grid(True)
 
-        plt.xlabel("Epochs")
[…]

### 2023-01-20 latex/article.tex
Text addecd to results section

@@
     \textit{Particle Swarm Optimization (OriginalPSO)} from \textit{swarm\_based} subpackage.
-    Each problem was modeled using \textit{SciPy} package, with constraints implemented as
-    \textit{penalty functions}. Each algorithm were optimized separately to extract the best
+    Each problem was modeled using standard python functions, with constraints implemented as
+    \textit{penalty functions}.
+    Each algorithm were optimized separately to extract the best
     solutions from each problem using the \textit{MealPy}'s \textit{Tuner} utility.
@@
 
-\subsubsection{Spring Tension Design}
-\label{subsubsec:methodology-spring-tension-design}
-From \textit{Nature-Inspired Metaheuristic Algorithms - Xin-She Yang} -
-The design of a tension and compression spring is a well-known benchmark
-optimization problem.
-The main aim is to minimize the weight subject
-to constraints on deflection, stress, surge frequency and geometry. It involves
-three design variables: the wire diameter $x_1$ , coil diameter $x_2$ and
-number/length of the coil $x_3$.
-This problem can be summarized as:
-
-\begin{equation}
-    f (x) = x_1^2 x_2 (2 + x_3)
-\end{equation}
-
-subject to
-
-\begin{equation}
-    \begin{split}
-        g_1(x) = \frac{x_2^3 x_3}{71785 x_1^4} \leq 0\\
-        g_2(x) = \frac{4 x_2^2 - x_1 x_2}{12566 \left( x_1^3 x_2 - x_1^4\right)}\\
-        + \frac{1}{5108 x_1^2} -1 \leq 0\\
-        g_3(x) = 1 - \frac{140.45 x_1}{x_2^2 x_3} \leq 0\\
-        g_4 = \frac{x_1 + x_2}{1.5} - 1 \leq 0
-    \end{split}
-\end{equation}
-
-The original bounding limits of the variables, extracted from computational work
-statements, are:
-
-\begin{equation}
-    \begin{split}
-        0.05 \leq x_1 \leq 2.0\\
-        0.25 \leq x_2 \leq 1.3\\
-        2.0 \leq x_3 \leq 15.0
-    \end{split}
-\end{equation}
-
 \subsubsection{Pressure Vessel Design}
@@
         39.5 \leq x_3 \leq 41.0\\
-        195.0 \leq x_4 \leq 205.0\\
+        195.0 \leq x_4 \leq 205.0
     \end{split}
@@
 reach the literature results.
+
+\subsubsection{Spring Tension Design}
+\label{subsubsec:methodology-spring-tension-design}
+From \textit{Nature-Inspired Metaheuristic Algorithms - Xin-She Yang} -
+The design of a tension and compression spring is a well-known benchmark
+optimization problem.
+The main aim is to minimize the weight subject
+to constraints on deflection, stress, surge frequency and geometry. It involves
+three design variables: the wire diameter $x_1$ , coil diameter $x_2$ and
+number/length of the coil $x_3$.
+This problem can be summarized as:
+
+\begin{equation}
+    f (x) = x_1^2 x_2 (2 + x_3)
+\end{equation}
+
+subject to
+
+\begin{equation}
+    \begin{split}
+        g_1(x) = \frac{x_2^3 x_3}{71785 x_1^4} \leq 0\\
+        g_2(x) = \frac{4 x_2^2 - x_1 x_2}{12566 \left( x_1^3 x_2 - x_1^4\right)}\\
+        + \frac{1}{5108 x_1^2} -1 \leq 0\\
+        g_3(x) = 1 - \frac{140.45 x_1}{x_2^2 x_3} \leq 0\\
+        g_4 = \frac{x_1 + x_2}{1.5} - 1 \leq 0
+    \end{split}
+\end{equation}
+
+The original bounding limits of the variables, extracted from computational work
+statements, are:
+
+\begin{equation}
+    \begin{split}
+        0.05 \leq x_1 \leq 2.0\\
+        0.25 \leq x_2 \leq 1.3\\
+        2.0 \leq x_3 \leq 15.0
+    \end{split}
+\end{equation}
 
@@
 \label{sec:results}
+\subsection{Pressure Vessel Design (Original)}
+\label{subsec:pressure_vessel_problem_original}
+
+In this section are presented the results for the original variable boundings of Pressure Vessel Design,
+as exposed in Section~\ref{subsubsec:methodology-pressure-vessel-design}.
+
+The best results for all algorithms are presented in Table~\ref{best_fits:pressure_vessel_problem_original}:
+
+\begin{table}[H]
+\centering
+\caption{Best Fits for Pressure Vessel Design (Original)}
+\label{best_fits:pressure_vessel_problem_original}
+\resizebox{\columnwidth}{!}{%
+\begin{tabular}{lrrrrr}
+\toprule
+Algorithm &      $x_1$ &      $x_2$ &        $x_3$ &        $x_4$ &         $f_x$ \\
+\midrule
+       EP & 0.00000000 & 0.00000000 &  40.32041055 & 200.00000000 &    0.08150806 \\
+       ES & 0.00000000 & 0.00000000 &  40.32554414 & 200.00000000 &    0.08161190 \\
+       GA & 0.00337818 & 0.00106498 &  46.44471109 & 129.50295637 &   17.06920868 \\
+    BeesA & 0.07617198 & 0.07091908 & 104.75191725 &  44.23570263 & 2393.70106213 \\
+      FFA & 0.00000000 & 0.00000000 &  40.39658670 & 200.00000000 &    0.08306113 \\
+      PSO & 0.00000000 & 0.00000000 &  40.31961791 & 200.00000000 &    0.08149204 \\
+\bottomrule
+\end{tabular}}
+\end{table}
+
+While EP, ES, FFA and PSO seems to give similar results, it is noticeable that the cost function
+gave some discrepant results for GA and BeesA.
+
+Additional information is given by the Table~\ref{function_values:pressure_vessel_problem_original},
+where are summarized statistics from all 100 results given by different starting points (populations).
+
+\begin{table}[H]
+\centering
+\caption{Statistical Information about function values for Pressure Vessel Design (Original)}
+\resizebox{\columnwidth}{!}{%
+\label{function_values:pressure_vessel_problem_original}
+\begin{tabular}{lrrrrr}
+\toprule
+Algorithm &         Min F &         Mean F &       Median F &          Max F &       StdDev F \\
+\midrule
+       EP &    0.08150806 &     0.15642850 &     0.09093798 &     1.32637552 &     0.16807714 \\
+       ES &    0.08161190 &   718.92910990 &     1.00278859 &  9443.54269260 &  2060.07774212 \\
+       GA &   17.06920868 &   525.00734162 &   361.53879602 &  3112.03503082 &   454.52386703 \\
+    BeesA & 2393.70106213 & 17564.33024022 & 15751.91467117 & 53850.38271384 & 10514.60780411 \\
+      FFA &    0.08306113 &     0.13296127 &     0.13106271 &     0.20084847 &     0.02396876 \\
+      PSO &    0.08149204 &     0.24191732 &     0.08159173 &    10.00611523 &     1.00072349 \\
+\bottomrule
+\end{tabular}}
+\end{table}
+
+From statistical viewpoint, no algorithm tested for this paper have stable solutions.
+
+The Figure~\ref{fig:pressure_vessel_design_original_boxplot} gives a visual representation
+for Table~\ref{function_values:pressure_vessel_problem_original}:
+
+\begin{figure}[H]
+\centering
+\caption{Boxplot for Pressure Vessel Design (Original)}
+\label{fig:pressure_vessel_design_original_boxplot}
+\includegraphics[scale=0.5]{images/pressure_vessel_problem_original_boxplot.png}
+\end{figure}
+
+Again, as it can be seen on the boxplot, there are no stability guaranteed for solution
+in any algorithms.
+
+Figure~\ref{fig:pressure_vessel_problem_original_convergence} shows the
+function maximum, minimum and mean function from algorithm's evolution:
+
+\begin{figure}[H]
+\centering
+\caption{Convergence lines for Pressure Vessel Design (Original)}
+\label{fig:pressure_vessel_problem_original_convergence}
+\includegraphics[width=0.4 \textwidth]{images/pressure_vessel_problem_original_convergence.png}
+\end{figure}
+
+All algorithms tested have slow evolution for the original variable boundings, as it is shown in the convergence evolution.
+
+\subsection{Pressure Vessel Design}
+\label{subsec:pressure_vessel_problem}
+
+In this section are presented the results for a tweaked variable boundings of Pressure Vessel Design,
+as exposed in Section~\ref{subsubsec:methodology-pressure-vessel-design}.
+
+The best results for all algorithms are presented in Table~\ref{best_fits:pressure_vessel_problem}:
+
+\begin{table}[H]
+\centering
+\caption{Best Fits for Pressure Vessel Design}
+\label{best_fits:pressure_vessel_problem}
+\resizebox{\columnwidth}{!}{%
+\begin{tabular}{lrrrrr}
+\toprule
+Algorithm &      $x_1$ &      $x_2$ &       $x_3$ &        $x_4$ &         $f_x$ \\
+\midrule
+       EP & 0.75000000 & 0.35000000 & 40.68318345 & 195.00000000 & 5534.57345496 \\
+       ES & 0.75000000 & 0.35000000 & 40.68322151 & 195.00000000 & 5534.57917966 \\
+       GA & 0.75000816 & 0.35003661 & 40.68379662 & 195.00019653 & 5534.83662424 \\
+    BeesA & 0.75000000 & 0.35000000 & 40.68319525 & 195.00000000 & 5534.57516657 \\
+      FFA & 0.75000000 & 0.35000000 & 40.68318772 & 195.00000000 & 5534.57401617 \\
+      PSO & 0.75000000 & 0.35000000 & 40.68318348 & 195.00000000 & 5534.57345480 \\
+\bottomrule
+\end{tabular}}
+\end{table}
+
+It is noticeable in this table that the best results and the best minimizers are quite the same,
+so it cannot be said that all algorithms will solve the problem from this standpoint.
+
+Another view of the solutions are presented in Table~\ref{function_values:pressure_vessel_problem}, where
+are summarized the statistics of all 100 possible solutions for different startpoints.
+
+\begin{table}[H]
+\centering
+\caption{Statistical Information about function values for Pressure Vessel Design}
+\resizebox{\columnwidth}{!}{%
+\label{function_values:pressure_vessel_problem}
+\begin{tabular}{lrrrrr}
+\toprule
+Algorithm &         Min F &        Mean F &      Median F &         Max F &   StdDev F \\
+\midrule
+       EP & 5534.57345496 & 5534.63426098 & 5534.61416291 & 5534.92993607 & 0.05804548 \\
+       ES & 5534.57917966 & 5535.28165367 & 5535.06149254 & 5538.03003895 & 0.65098467 \\
+       GA & 5534.83662424 & 5538.36788889 & 5536.92932748 & 5550.91639342 & 3.57079951 \\
+    BeesA & 5534.57516657 & 5537.97495231 & 5537.04824684 & 5548.55587234 & 3.28239740 \\
+      FFA & 5534.57401617 & 5534.58849395 & 5534.58435493 & 5534.63296149 & 0.01341777 \\
+      PSO & 5534.57345480 & 5534.57381593 & 5534.57355270 & 5534.57625290 & 0.00053848 \\
+\bottomrule
+\end{tabular}}
+\end{table}
+
+It is hard to see any statistical  difference looking at any value in the table except standartd deviation.
+GA and BeesA seems to have the worst solutions, and EP, FFA and PSO seems to have a well defined behavior
+since they have the lowest standard deviations, that is, all the solutions don't spread too much from each
+other.
+A quick way to access the Table~\ref{function_values:pressure_vessel_problem} is shown on Figure~\ref{fig:pressure_vessel_design_boxplot}.
+
+\begin{figure}[H]
+\centering
+\caption{Boxplot for Pressure Vessel Design}
+\label{fig:pressure_vessel_design_boxplot}
+\includegraphics[scale=0.5]{images/pressure_vessel_problem_boxplot.png}
+\end{figure}
+
+It shows the same information as the Table~\ref{function_values:pressure_vessel_problem}
+and it evidences that not all algorithms have the same mean, so it is a clear evidence
+that not all algorithm give similar results from an arbitrary start point.
+
+Figure~\ref{fig:pressure_vessel_problem_convergence} shows the
+function maximum, minimum and mean function from algorithm's evolution:
+
+\begin{figure}[H]
+\centering
+\caption{Convergence lines for Pressure Vessel Design}
+\label{fig:pressure_vessel_problem_convergence}
+\includegraphics[width=0.4 \textwidth]{images/pressure_vessel_problem_convergence.png}
+\end{figure}
+
+EP, ES and PSO quickly converges all the solution once it find a viable minimum, whe GA, BeesA and FFA
+maintain exloration and explotation for all the epochs. From Table~\ref{function_values:pressure_vessel_problem}
+, PSO has the best solution stability for our proud-lame-homemade custom bounding problem.
 \subsection{Spring Tension Design}
 \label{ssubec:spring_problem}
+
+In this section are presented the results of Spring Tension Design optimization,
+as exposed in Section~\ref{subsubsec:methodology-spring-tension-design}.
+
+The best results for all algorithms are presented in Table~\ref{best_fits:spring_problem}:
+
+\begin{table}[H]
+\centering
+\caption{Best Fits for Spring Tension Design}
+\label{best_fits:spring_problem}
+\resizebox{\columnwidth}{!}{%
+\begin{tabular}{lrrrr}
+\toprule
+Algorithm &      $x_1$ &      $x_2$ &       $x_3$ &      $f_x$ \\
+\midrule
+       EP & 0.05078716 & 0.34120356 & 11.93931414 & 0.01250534 \\
+       ES & 0.05000000 & 0.32292194 & 13.26929635 & 0.01252956 \\
+       GA & 0.05260626 & 0.38419911 &  9.63922108 & 0.01252305 \\
+    BeesA & 0.05141008 & 0.35564113 & 11.06109433 & 0.01250200 \\
+      FFA & 0.05148403 & 0.35770175 & 10.95787946 & 0.01249803 \\
+      PSO & 0.05000000 & 0.32241990 & 13.31368880 & 0.01252626 \\
+\bottomrule
+\end{tabular}}
+\end{table}
+
+Although the best fit points have noticeable differences, the cost function $f_x$ have similar results, that is, the
+function $f_x$ seems to have weak minimal points.
+
+Another view of the solutions are presented in Table~\ref{function_values:pressure_vessel_problem}, where
+are summarized the statistics of all 100 possible solutions for different starting points (populations).
 
@@
 \label{fig:spring_problem_convergence}
-\includegraphics[width= 0.4 \textwidth]{images/spring_problem_convergence.png}
-\end{figure}
-
-\subsection{Pressure Vessel Design (Original)}
-\label{subsec:pressure_vessel_problem_original}
-
-\begin{table}[H]
-\centering
-\caption{Statistical Information about function values for Pressure Vessel Design (Original)}
-\label{function_values:pressure_vessel_problem_original}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrrrrr}
-\toprule
-Algorithm &         Min F &         Mean F &       Median F &          Max F &       StdDev F \\
-\midrule
-       EP &    0.08150806 &     0.15642850 &     0.09093798 &     1.32637552 &     0.16807714 \\
-       ES &    0.08161190 &   718.92910990 &     1.00278859 &  9443.54269260 &  2060.07774212 \\
-       GA &   17.06920868 &   525.00734162 &   361.53879602 &  3112.03503082 &   454.52386703 \\
-    BeesA & 2393.70106213 & 17564.33024022 & 15751.91467117 & 53850.38271384 & 10514.60780411 \\
-      FFA &    0.08306113 &     0.13296127 &     0.13106271 &     0.20084847 &     0.02396876 \\
-      PSO &    0.08149204 &     0.24191732 &     0.08159173 &    10.00611523 &     1.00072349 \\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{figure}[H]
-\centering
-\caption{Boxplot for Pressure Vessel Design (Original)}
-\label{fig:pressure_vessel_design_original_boxplot}
-\includegraphics[scale=0.5]{images/pressure_vessel_problem_original_boxplot.png}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\caption{Convergence lines for Pressure Vessel Design (Original)}
-\label{fig:pressure_vessel_problem_original_convergence}
-\includegraphics[width= 0.4 \textwidth]{images/pressure_vessel_problem_original_convergence.png}
-\end{figure}
-
-\subsection{Pressure Vessel Design}
-\label{subsec:pressure_vessel_problem}
-
-\begin{table}
-\centering
-\caption{Statistical Information about function values for Pressure Vessel Design}
-\label{function_values:pressure_vessel_problem}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrrrrr}
-\toprule
-Algorithm &         Min F &        Mean F &      Median F &         Max F &   StdDev F \\
-\midrule
-       EP & 5534.57345496 & 5534.63426098 & 5534.61416291 & 5534.92993607 & 0.05804548 \\
-       ES & 5534.57917966 & 5535.28165367 & 5535.06149254 & 5538.03003895 & 0.65098467 \\
-       GA & 5534.83662424 & 5538.36788889 & 5536.92932748 & 5550.91639342 & 3.57079951 \\
-    BeesA & 5534.57516657 & 5537.97495231 & 5537.04824684 & 5548.55587234 & 3.28239740 \\
-      FFA & 5534.57401617 & 5534.58849395 & 5534.58435493 & 5534.63296149 & 0.01341777 \\
-      PSO & 5534.57345480 & 5534.57381593 & 5534.57355270 & 5534.57625290 & 0.00053848 \\
-\bottomrule
-\end{tabular}
-}
-\end{table}
-
-\begin{figure}[H]
-\centering
-\caption{Boxplot for Pressure Vessel Design}
-\label{fig:pressure_vessel_design_boxplot}
-\includegraphics[scale=0.5]{images/pressure_vessel_problem_boxplot.png}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\caption{Convergence lines for Pressure Vessel Design}
-\label{fig:pressure_vessel_problem_convergence}
-\includegraphics[width=0.4 \textwidth]{images/pressure_vessel_problem_convergence.png}
+\includegraphics[width=0.4 \textwidth]{images/spring_problem_convergence.png}
 \end{figure}
@@
 \bottomrule
-\end{tabular}
-}
+\end{tabular}}
 \end{table}
@@
 
-The main objective of this work is demonstrate the inner work of a optimization class of algorithms called \textit{Quasi-Newton algorithms}.
-Four of them are presented, along with the results and analysis regarding convergence, function evaluations and function objective values.
-
-For implementation, it was decided to put constraints on search space, because for the original search space of some functions, like Ackley and Rastrigin, there are other minimas that will confuse every algorithm tested for this paper, and there is no sense on test a local minima procedure on these conditions.
-To restrain the initial solution to some region in the search space was a cheap and ready solution to avoid the algorithms to stop because of stumbling upon the wrong minimum.
-
-The \textit{Levenberg-Marquardt Algorithm} implemented for this paper is very sensitive to hyperparameters, namely $\alpha$ and $\lambda$, which was not tunned to every function, so, the conspicuous performance variation is noticeable along the results.
-LMA is known to be fast and reliable, but in our implementation it was found a little tricky to get the hyperparameters right for all the test functions.
-But for Rosenbrock and Rastrigin, it is the best option, even for lame implementations like ours.
-
-The \textit{Broyden–Fletcher–Goldfarb–Shanno} Algorithm was the only one that we decided to use it as is from \textit{SciPy}, because it has features desired for this work, like counting of function evaluations, gradient evaluation and iterations.
-It performed very well for Ackley and Booth Functions, and reasonably well for other functions.
-
-The \textit{Davidon–Fletcher–Powell} Algorithm is not implemented in \textit{SciPy} but its equations shows that it is the dual of BFGS, so, it was easy to implement using some \textit{SciPy} code for BFGS algorithm.
-In the DFP procedure, there is a Hessian inversion to be evaluated every iteration, then, numerical imprecision would be taken into consideration evaluating its results.
-While in some cases it has a superb performance (Like Ackley Function), it has very poor performance in Rosenbrock Function and even in Beale Function.
-The increase of dimensions makes DFP suffer of numerical imprecision due to the Hessian inversion, except for Rastrigin, and it is the loser algorithm in other functions.
-
-Finally, the \textit{Limited memory BFGS} has an average performance among the functions.
-The original algorithm was implemented using code found in the url https://github.com/qkolj/L-BFGS/blob/master/L-BFGS.ipynb.
-
-In fact, there are no Quasi-Newton algorithms that solver the minima problem for an any function.
-From the standpoint of performance and convergence, all the algorithms have an average performance and a reasonable convergence, although we have to restrain the search space to a small area near the optimal solution.
+Text goes here......
 

### 2023-01-20 latex/includes/pressure_vessel_problem.tex
Formatting Done.
Text addecd to results section

@@
-\begin{table}
+Another view of the solutions are presented in Table~\ref{function_values:pressure_vessel_problem}, where
+are summarized the statistics of all 100 possible solutions for different startpoints.
+
+\begin{table}[H]
 \centering
 \caption{Statistical Information about function values for Pressure Vessel Design}
+\resizebox{\columnwidth}{!}{%
 \label{function_values:pressure_vessel_problem}
@@
 \bottomrule
-\end{tabular}
+\end{tabular}}
 \end{table}
+
+It is hard to see any statistical  difference looking at any value in the table except standartd deviation.
+GA and BeesA seems to have the worst solutions, and EP, FFA and PSO seems to have a well defined behavior
+since they have the lowest standard deviations, that is, all the solutions don't spread too much from each
+other.

### 2023-01-20 latex/includes/pressure_vessel_problem_boxplot.tex
Text addecd to results section

@@
+A quick way to access the Table~\ref{function_values:pressure_vessel_problem} is shown on Figure~\ref{fig:pressure_vessel_design_boxplot}.
+
 \begin{figure}[H]
@@
 \end{figure}
+
+It shows the same information as the Table~\ref{function_values:pressure_vessel_problem}
+and it evidences that not all algorithms have the same mean, so it is a clear evidence
+that not all algorithm give similar results from an arbitrary start point.

### 2023-01-20 latex/includes/pressure_vessel_problem_convergence.tex
Text addecd to results section

@@
+Figure~\ref{fig:pressure_vessel_problem_convergence} shows the
+function maximum, minimum and mean function from algorithm's evolution:
+
 \begin{figure}[H]
@@
 \end{figure}
+
+EP, ES and PSO quickly converges all the solution once it find a viable minimum, whe GA, BeesA and FFA
+maintain exloration and explotation for all the epochs. From Table~\ref{function_values:pressure_vessel_problem}
+, PSO has the best solution stability for our proud-lame-homemade custom bounding problem.

### 2023-01-20 latex/includes/pressure_vessel_problem_original_convergence.tex
Text addecd to results section

@@
+Figure~\ref{fig:pressure_vessel_problem_original_convergence} shows the
+function maximum, minimum and mean function from algorithm's evolution:
+
 \begin{figure}[H]
@@
 \label{fig:pressure_vessel_problem_original_convergence}
-\includegraphics[width= 0.4 \textwidth]{images/pressure_vessel_problem_original_convergence.png}
+\includegraphics[width=0.4 \textwidth]{images/pressure_vessel_problem_original_convergence.png}
 \end{figure}
+
+All algorithms tested have slow evolution for the original variable boundings, as it is shown in the convergence evolution.

### 2023-01-20 analysis.py

@@ -31,10 +31,10 @@ def fit_results_cleanup(fit_results):
     :param fit_results: raw results
     :return: cleaned results
     """
-    new_fit_results = list()
+    new_fx = list()
     for node in fit_results:
-        new_fit_results.append(node[1])
-    return new_fit_results
+        new_fx.append(node[1])
+    return new_fx
 
 
 def population_cleanup(population):
@@ -139,27 +139,43 @@ def ordinary_statistics(fit_results):
     return stats
 
 
+
 # collecting results
 with open("results/best_fits.json", "r") as f:
     best_fits = json.load(f)
+
+with open("results/best_fits_points.json", "r") as f:
+    best_fits_points = json.load(f)
 
 with open("results/fit_results.json", "r") as f:
     fit_results = json.load(f)
 
 best_fits_history = dict()
 
+joined_best_fits = dict()
+
 for problem in problem_desc:
     best_fits_history[problem] = dict()
+    joined_best_fits[problem] = list()
     for solver in alg_desc:
+        # join best fits
+        best_fits_point = best_fits_points[problem][solver]
+        best_fits_fx = best_fits[problem][solver]
+        desc = alg_desc[solver]
+        best_fits_point = [desc] + best_fits_point + [best_fits_fx]
+        joined_best_fits[problem].append(best_fits_point)
+        # retrieving model
         filename = "results/best_" + problem + "_" + solver
         model = io.load_model(filename)
         best_fits_history[problem][solver] = model
 
 stats_s = ordinary_statistics(fit_results)
 
+with open("results/joined_best_fits.json", "w") as f:
+    json.dump(joined_best_fits, f, indent=4)
+
 with open("results/stats.json", "w") as f:
     json.dump(stats_s, f, indent=4)
-
 
 population_stats = dict()
 

### 2023-01-20 article_builder.py

@@ -14,23 +14,13 @@ content = ""
 with open("latex/includes/header.tex", "r") as f:
     content += f.read() + "\n"
 
-#: spring problem
-content += "\\subsection{Spring Tension Design}\n"
-content += "\\label{ssubec:spring_problem}\n\n"
-
-with open("latex/includes/spring_problem.tex", "r") as f:
-    content += f.read() + "\n"
-
-with open("latex/includes/spring_problem_boxplot.tex", "r") as f:
-    content += f.read() + "\n"
-
-with open("latex/includes/spring_problem_convergence.tex", "r") as f:
-    content += f.read() + "\n"
-
 # pressure vessel problem
 
 content += "\\subsection{Pressure Vessel Design (Original)}\n"
 content += "\\label{subsec:pressure_vessel_problem_original}\n\n"
+
+with open("latex/includes/pressure_vessel_problem_original_best_fits.tex", "r") as f:
+    content += f.read() + "\n"
 
 with open("latex/includes/pressure_vessel_problem_original.tex", "r") as f:
     content += f.read() + "\n"
@@ -46,6 +36,9 @@ with open("latex/includes/pressure_vessel_problem_original_convergence.tex", "r"
 content += "\\subsection{Pressure Vessel Design}\n"
 content += "\\label{subsec:pressure_vessel_problem}\n\n"
 
+with open("latex/includes/pressure_vessel_problem_best_fits.tex", "r") as f:
+    content += f.read() + "\n"
+
 with open("latex/includes/pressure_vessel_problem.tex", "r") as f:
     content += f.read() + "\n"
 
@@ -53,6 +46,22 @@ with open("latex/includes/pressure_vessel_problem_boxplot.tex", "r") as f:
     content += f.read() + "\n"
 
 with open("latex/includes/pressure_vessel_problem_convergence.tex", "r") as f:
+    content += f.read() + "\n"
+
+#: spring problem
+content += "\\subsection{Spring Tension Design}\n"
+content += "\\label{ssubec:spring_problem}\n\n"
+
+with open("latex/includes/spring_problem_best_fits.tex", "r") as f:
+    content += f.read() + "\n"
+
+with open("latex/includes/spring_problem.tex", "r") as f:
+    content += f.read() + "\n"
+
+with open("latex/includes/spring_problem_boxplot.tex", "r") as f:
+    content += f.read() + "\n"
+
+with open("latex/includes/spring_problem_convergence.tex", "r") as f:
     content += f.read() + "\n"
 
 # Friedman's test

### 2023-01-20 runner.py

@@ -135,6 +135,25 @@ best_fits = {"spring_problem": {"solve_ep": 1e6,
                                                   "solve_ffa": 1e6,
                                                   "solve_pso": 1e6}}
 
+best_fits_points =  {"spring_problem": {"solve_ep": 1e6,
+                                        "solve_es": 1e6,
+                                        "solve_ga": 1e6,
+                                        "solve_beesa": 1e6,
+                                        "solve_ffa": 1e6,
+                                        "solve_pso": 1e6},
+                     "pressure_vessel_problem": {"solve_ep": 1e6,
+                                                 "solve_es": 1e6,
+                                                 "solve_ga": 1e6,
+                                                 "solve_beesa": 1e6,
+                                                 "solve_ffa": 1e6,
+                                                 "solve_pso": 1e6},
+                     "pressure_vessel_problem_original": {"solve_ep": 1e6,
+                                                          "solve_es": 1e6,
+                                                          "solve_ga": 1e6,
+                                                          "solve_beesa": 1e6,
+                                                          "solve_ffa": 1e6,
+                                                          "solve_pso": 1e6}}
+
 
 best_fits_history = {"spring_problem": {"solve_ep": [],
                                         "solve_es": [],
@@ -201,8 +220,13 @@ for seed in range(1, runs + 1):
             fit_results[problem][solver_name].append([best_position.tolist(),
                                                       best_fitness])
             if best_fitness <= best_fits[problem][solver_name]:
+                best_fits_points[problem][solver_name] = best_position.tolist()
                 best_fits[problem][solver_name] = float(best_fitness)
                 best_fits_history[problem][solver_name] = model
+
+# saving best fits points
+with open("results/best_fits_points.json", "w") as f:
+    json.dump(best_fits_points, f, indent=4)
 
 # saving best fits
 with open("results/best_fits.json", "w") as f:

### 2023-01-20 to_latex.py

@@ -14,6 +14,32 @@ import matplotlib.pyplot as plt
 import json
 
 
+def latex_best_fits_table(results,
+                          desc,
+                          problem):
+
+    column_names = ["Algorithm"]
+
+    var_num = len(results[0]) - 2
+
+    for i in range(1, var_num + 1):
+        var_col_name = "x_{:d}".format(i)
+        column_names.append('$' + var_col_name + '$')
+
+    column_names.append('$f_x$')
+
+    df = pd.DataFrame(results,
+                      columns=column_names)
+
+    content = df.to_latex(index=False,
+                          float_format="%.8f",
+                          escape=False,
+                          label="best_fits:{:s}".format(problem),
+                          caption="Best Fits for {:s}".format(desc))
+
+    return content
+
+
 def latex_results_table(results,
                         desc,
                         problem):
@@ -65,6 +91,9 @@ def latex_friedman_table(results):
 with open("results/stats.json", "r") as f:
     data = json.load(f)
 
+with open("results/joined_best_fits.json", "r") as f:
+    best_fits = json.load(f)
+
 for problem in data:
 
     desc = data[problem]['desc']
@@ -77,6 +106,16 @@ for problem in data:
 
     with open("latex/includes/{:s}.tex".format(problem), "w") as f:
         f.write(content)
+
+    results = best_fits[problem]
+
+    content = latex_best_fits_table(results,
+                                    desc,
+                                    problem)
+
+    with open("latex/includes/{:s}_best_fits.tex".format(problem), "w") as f:
+        f.write(content)
+
 
 content = latex_friedman_table(data)
 
@@ -221,7 +260,7 @@ for problem in population_data:
     \\centering
     \\caption{Convergence lines for """ + problem_desc[problem] + """}
     \\label{fig:""" + problem + "_convergence" + """}
-    \\includegraphics[scale=0.5]{images/""" + problem + "_convergence"  +  """.png}
+    \\includegraphics[width=0.4 \\textwidth]{images/""" + problem + "_convergence"  +  """.png}
     \\end{figure}
     """
     with open("latex/includes/" + problem + "_convergence.tex", "w") as f:

### 2023-01-21 latex/includes/pressure_vessel_problem_original_wilcoxon_test.tex
Release Added

Developed by F. Wilcoxon in 1945, the paired Wilcoxon test is based on the ranks
of intrapair differences. This non-parametric test, used to compare related samples,
is an alternative to the Student t-test when samples do not follow a normal distribution.
Therefore, the Wilcoxon test is used to test whether sample medians are equal in cases
where the assumption of normality is not satisfied or when it is not possible to check
this assumption.

Interpretation is as follows:
\begin{itemize}
    \item Assume two hypothesis about the data:
        \subitem $H_0$: the distributions of both samples are equal;
        \subitem $H_1$: the distributions of both samples are not equal.
    \item Given p-value, decide:
        \subitem p-value $\leq 0.05$: Reject $H_1$ with $95\%$ of confidence and accept null hypothesis;
        \subitem Accept $H_1$ otherwise.
\end{itemize}

The Table~\ref{wilcoxon_test:pressure_vessel_problem_original} gives the Wilcoxon test results
for \textit{Pressure Vessel Design} using the original variables bounding as exposed in Section~\ref{subsubsec:methodology-pressure-vessel-design}.

\begin{table}[H]
\centering
\caption{Significance Test Using Wilcoxon Test for Pressure Vessel Design (Original)}
\label{wilcoxon_test:pressure_vessel_problem_original}
\resizebox{\columnwidth}{!}{%
\begin{tabular}{lllllll}
\toprule
  --- & EP & ES & GA & BeesA & FFA & PSO \\
\midrule
   EP & 0.0 & 1.20e-16 & 3.90e-18 & 3.90e-18 & 0.07 & 2.02e-4 \\
   ES & 1.20e-16 & 0.0 & 6.56-06 & 4.96e-18 & 5.49e-14 & 1.41e-17 \\
   GA & 3.90e-18 & 6.56e-06 & 0.0 & 3.90e-18 & 3.90e-18 & 3.90e-18 \\
BeesA & 3.90e-18 & 4.96e-18 & 3.90e-18 & 0.0 & 3.90e-18 & 3.90e-18 \\
  FFA & 0.07 & 5.49e-14 & 3.90e-18 & 3.90e-18 & 0.0 &  5.34e-05 \\
  PSO & 2.02e-4 & 1.41e-17 & 3.90e-18 &  3.90e-18 & 5.34e-05 & 0.0 \\
\bottomrule
\end{tabular}}
\end{table}

It is easy to notice that, from Wilcoxon test, FAA and EP have different distributions.
$H_1$ is only accepted in case of FFA and EP: they distributions seems to be not equal.

### 2023-01-21 release/code/latex/article.tex
Release Added

--- 2023-01-20 latex/article.tex
@@
 number/length of the coil $x_3$.
-This problem can be summarized as:
+This problem is summarized as:
 
@@
 Although simple, it is a very expensive procedure that took 2 days to complete. It was defined 10 runs for each
-configuration, with the following set of hyperparameter:
+configuration, with the following set of hyperparameters:
 
@@
     \item \textit{Epochs}: 100 epochs
-    \item \textit{Population}: 100 initial points
+    \item \textit{Population}: 100 starting points (population)
 \end{itemize}
@@
 The initial solutions were randomly selected using the same seed for all algorithms.
+The best solution of any algorithm is defined as the minimal solution of the 100 epochs (runs)
+allowed for each algorithm.
 
@@
 Figure~\ref{fig:pressure_vessel_problem_original_convergence} shows the
-function maximum, minimum and mean function from algorithm's evolution:
+function maximum, minimum and mean function of algorithm's evolution:
 
@@
 Another view of the solutions are presented in Table~\ref{function_values:pressure_vessel_problem}, where
-are summarized the statistics of all 100 possible solutions for different startpoints.
+are summarized the statistics of all 100 possible solutions for different starting points.
 
@@
 
-It is hard to see any statistical  difference looking at any value in the table except standartd deviation.
+It is hard to see any statistical  difference looking at any value in the table except standard deviation.
 GA and BeesA seems to have the worst solutions, and EP, FFA and PSO seems to have a well defined behavior
@@
 other.
+
 A quick way to access the Table~\ref{function_values:pressure_vessel_problem} is shown on Figure~\ref{fig:pressure_vessel_design_boxplot}.
@@
 and it evidences that not all algorithms have the same mean, so it is a clear evidence
-that not all algorithm give similar results from an arbitrary start point.
+that not all algorithm give similar results from an arbitrary starting point (population).
 
 Figure~\ref{fig:pressure_vessel_problem_convergence} shows the
-function maximum, minimum and mean function from algorithm's evolution:
+function maximum, minimum and mean function of algorithm's evolution:
 
@@
 EP, ES and PSO quickly converges all the solution once it find a viable minimum, whe GA, BeesA and FFA
-maintain exloration and explotation for all the epochs. From Table~\ref{function_values:pressure_vessel_problem}
-, PSO has the best solution stability for our proud-lame-homemade custom bounding problem.
+maintain exploration and exploitation for all the epochs.
+From Table~\ref{function_values:pressure_vessel_problem},
+PSO has the best solution stability for the proud-and-lame-homemade custom bounding problem.
+
 \subsection{Spring Tension Design}
@@
 
-Another view of the solutions are presented in Table~\ref{function_values:pressure_vessel_problem}, where
+Another view of the solutions are presented in Table~\ref{function_values:spring_problem}, where
 are summarized the statistics of all 100 possible solutions for different starting points (populations).
@@
 
+Looking at standard deviation, EP, ES and BeesA appear to have the same distribution;
+FFA has the lowest function value spread around the mean; GA and PSO have the largest
+function values spread around the mean and particularly GA tend to give discrepant results
+that the rest.
+
+A quick way to access the Table~\ref{function_values:spring_problem} is
+shown on Figure~\ref{fig:spring_tension_design_boxplot}.
+
 \begin{figure}[H]
@@
 \end{figure}
+
+It shows the same information as the Table~\ref{function_values:spring_problem}
+and it evidences that not all algorithms have the same mean, so it is a clear evidence
+that not all algorithm give similar results from an arbitrary starting point (population).
+
+Figure~\ref{fig:spring_problem_convergence} shows the
+function maximum, minimum and mean function of algorithm's evolution:
 
@@
 
+EP, ES and FFA have the best fitness.
+All algorithms seems to converge the minimum line very quickly when
+the algorithm find a minimal point.
+Apart from EP and ES, the algorithms seems to maintain exploration and exploitation
+until the time runs out.
+
 \subsection{Significance Test}
 \label{subsec:pressure_vessel_problem_significance_test}
+
+The Friedman test is the non-parametric test used to compare related sample data, that is,
+when the same individual is evaluated more than once.
+The Friedman test does not use the data numbers directly, but the ranks occupied by
+them after the sorting done for each group separately. After sorting, the hypothesis
+of equality of the sum of the ranks of each group is tested.
+
+Interpretation is as follows:
+\begin{itemize}
+    \item Assume two hypothesis about the data:
+        \subitem $H_0$: The mean for each population is equal.
+        \subitem $H_1$: At least one population mean is different from the rest.
+    \item Given p-value, decide:
+        \subitem p-value $\geq 0.05$: Reject $H_1$ with $95\%$ of confidence and accept null hypothesis;
+        \subitem Accept $H_1$ otherwise.
+\end{itemize}
+
+The Table~\ref{friedman_test} resumes the Friedman's Chi-Squared Test made using
+the 6 samples took by the algorithm's best results fore each run:
 
@@
 \toprule
-                          Problem &   Statistics &    p-value \\
+                          Problem &   Rank &    p-value \\
 \midrule
+Pressure Vessel Design (Original) & 425.07428571 & 0.00000000 \\
+           Pressure Vessel Design & 436.16000000 & 0.00000000 \\
             Spring Tension Design & 339.05714286 & 0.00000000 \\
-           Pressure Vessel Design & 436.16000000 & 0.00000000 \\
-Pressure Vessel Design (Original) & 425.07428571 & 0.00000000 \\
 \bottomrule
@@
 
+Using the interpretation rules, since the p-value is less than $0.05$, the null hypotesis $H_0$
+is rejected and each problem have at least one population with different mean from the rest.
+Thus, not all algorithms gives the same result for the same problem.
+
+Developed by F. Wilcoxon in 1945, the paired Wilcoxon test is based on the ranks
+of intrapair differences. This non-parametric test, used to compare related samples,
+is an alternative to the Student t-test when samples do not follow a normal distribution.
+Therefore, the Wilcoxon test is used to test whether sample medians are equal in cases
+where the assumption of normality is not satisfied or when it is not possible to check
+this assumption.
+
+Interpretation is as follows:
+\begin{itemize}
+    \item Assume two hypothesis about the data:
+        \subitem $H_0$: the distributions of both samples are equal;
+        \subitem $H_1$: the distributions of both samples are not equal.
+    \item Given p-value, decide:
+        \subitem p-value $\leq 0.05$: Reject $H_1$ with $95\%$ of confidence and accept null hypothesis;
+        \subitem Accept $H_1$ otherwise.
+\end{itemize}
+
+The Table~\ref{wilcoxon_test:pressure_vessel_problem_original} gives the Wilcoxon test results
+for \textit{Pressure Vessel Design} using the original variables bounding as exposed in Section~\ref{subsubsec:methodology-pressure-vessel-design}.
+
+\begin{table}[H]
+\centering
+\caption{Significance Test Using Wilcoxon Test for Pressure Vessel Design (Original)}
+\label{wilcoxon_test:pressure_vessel_problem_original}
+\resizebox{\columnwidth}{!}{%
+\begin{tabular}{lllllll}
+\toprule
+  --- & EP & ES & GA & BeesA & FFA & PSO \\
+\midrule
+   EP & 0.0 & 1.20e-16 & 3.90e-18 & 3.90e-18 & 0.07 & 2.02e-4 \\
+   ES & 1.20e-16 & 0.0 & 6.56-06 & 4.96e-18 & 5.49e-14 & 1.41e-17 \\
+   GA & 3.90e-18 & 6.56e-06 & 0.0 & 3.90e-18 & 3.90e-18 & 3.90e-18 \\
+BeesA & 3.90e-18 & 4.96e-18 & 3.90e-18 & 0.0 & 3.90e-18 & 3.90e-18 \\
+  FFA & 0.07 & 5.49e-14 & 3.90e-18 & 3.90e-18 & 0.0 &  5.34e-05 \\
+  PSO & 2.02e-4 & 1.41e-17 & 3.90e-18 &  3.90e-18 & 5.34e-05 & 0.0 \\
+\bottomrule
+\end{tabular}}
+\end{table}
+
+It is easy to notice that, from Wilcoxon test, FAA and EP have different distributions.
+$H_1$ is only accepted in case of FFA and EP: they distributions seems to be not equal.
+
+The Table~\ref{wilcoxon_test:pressure_vessel_problem} gives the Wilcoxon test results
+for \textit{Pressure Vessel Design} using the proud-and-lame-homemade variables bounding
+as exposed in Section~\ref{subsubsec:methodology-pressure-vessel-design}.
+
+\begin{table}[H]
+\centering
+\caption{Significance Test Using Wilcoxon Test for Pressure Vessel Design}
+\label{wilcoxon_test:pressure_vessel_problem}
+\resizebox{\columnwidth}{!}{%
+\begin{tabular}{lllllll}
+\toprule
+  --- & EP & ES & GA & BeesA & FFA & PSO \\
+\midrule
+   EP & 0.0 & 9.04e-18 & 3.90e-18 & 6.12e-18 & 8.79e-12 & 4.40e-18 \\
+   ES & 9.04e-18 & 0.0 & 1.71e-14 & 1.64e-13 & 4.81e-18 & 3.90e-18 \\
+   GA & 3.90e-18 & 1.71e-14 & 0.0 & 0.38 & 3.90e-18 & 3.90e-18 \\
+BeesA & 6.12e-18 & 1.64e-13 & 0.38 & 0.0 & 4.30e-18 & 3.90e-18 \\
+  FFA & 8.79e-12 & 4.81e-18 & 3.90e-18 & 4.30e-18 & 0.0 & 4.02e-18 \\
+  PSO & 4.40e-18 & 3.90e-18 & 3.90e-18 & 3.90e-18 & 4.02e-18 & 0.0 \\
+\bottomrule
+\end{tabular}}
+\end{table}
+
+EP, ES, FAA and PSO appears to have the same distributions.
+However, BeesA and GA appears to have different distributions.
+This fact confirms the results found in Table~\ref{function_values:pressure_vessel_problem}.
+
+The Table~\ref{wilcoxon_test:spring_problem} gives the Wilcoxon test results
+for \textit{Spring Tension Design} as exposed in Section~\ref{subsubsec:methodology-spring-tension-design}.
+
+\begin{table}[H]
+\centering
+\caption{Significance Test Using Wilcoxon Test for Spring Tension Design}
+\label{wilcoxon_test:spring_problem}
+\resizebox{\columnwidth}{!}{%
+\begin{tabular}{lllllll}
+\toprule
+  --- & EP & ES & GA & BeesA & FFA & PSO \\
+\midrule
+   EP & 0.0 & 1.47e-16 & 4.01e-18 & 4.37e-12 & 0.01 & 2.33e-16 \\
+   ES & 1.47e-16 & 0.0 &  1.90e-17 & 2.12e-06 & 3.24e-17 & 7.98e-12 \\
+   GA & 4.01e-18 &  1.90e-17 & 0.0 & 8.02e-18 & 4.27e-18 & 1.29e-11 \\
+BeesA & 4.36e-12 & 2.12e-06 & 8.02e-18 & 0.0 & 3.01e-11 & 6.82e-15 \\
+  FFA & 0.01 & 3.23e-17 & 4.27e-18 & 3.01e-11 & 0.0 & 9.32e-18 \\
+  PSO & 2.33e-16 & 7.98e-12 & 1.29e-11 & 6.82e-15 & 9.32e-18 & 0.0 \\
+\bottomrule
+\end{tabular}}
+\end{table}
+
+From Wilcoxon Test, the are no difference between all algorithms since p-value
+is less than $0.05$.
+
 \section{Discussion}
 
-Text goes here......
+In this paper were tested 3 evolutionary algorithms (EP, ES and GA) and 3
+swarm based algorithms (BeesA, FFA and PSO), implemented by the \textit{MealPy}
+package. The chosen test problem were \textit{Pressure Vessel Design} and
+\textit{Spring Tension Design} because they are well studied engineering problems
+and are founs in many, if not all, optimization books everywhere. Thus, there are
+more results to compare.
+
+Both problems were implemented in full form, that is, with constraints, using the scheme of
+\textit{penalty functions}, as it is recomended by \textit{MealPy}'s documentation.
+
+Surprisingly, the \textit{Pressure Vessel Design} problem was a tricky one to solve.
+Many articles point out the boundings as described for original problem
+in Section~\ref{subsubsec:methodology-pressure-vessel-design}.
+But, for some unknown reason, the same variable bounding does not work for this
+implementation, and it was necessary to tweak the search space to give at least
+comparable results with the literature.
+It is not intended to point out errors in modelling or blame anyone, it is only a mere
+note to a misbehaviour in solving a specific problem.
+
+The results gives a notion that there are no panacea or universal solution for problems that
+nothing is known except the cost function and constraints.
+One algorithm's success to solve a specific problem is not a guarantee to solve anything
+and so on.
+
+At first, the \textit{Spring Tension Design} is easier to solve and is well behaved in the
+given variable bounsings. But, at it is noticed in the Table~\ref{best_fits:spring_problem},
+the cost function $f_x$ seems to have a plateau of weak minimizers, that is, values that gives
+near te same results. The statistical parameters of the cost function values at the best fits
+, as well the Wilcoxon test results fot this problem shows, there are no difference between the
+distribution of each algorithm solution, but the Friedman Test (and clearly the boxplot in
+figure~\ref{fig:spring_tension_design_boxplot}) indicates that they have significant
+differences in the mean value. So, there are some algorithms not fitted for the problem's solution.
+The best fit at all can be obtained using FFA algorithm, according to this paper.
+
+The \textit{Pressure Vessel Design} was solver using two bounding schemes to show discrepancies
+between the solutions.
+First, it was solved using the literature boundings: the behaviour of the
+solutions seems bizarre and make it evident that or the literature is wrong or the implementation
+used in this paper is wrong.
+Again, it is not intended heve to blame anyone.
+The second solution, using the proud-and-lame-homemade
+version of variable boundings seems to behave well.
+The same behaviour of \textit{Spring Tension Design} is noticed in the tests, both statistical
+, Wincoxon and Friedman Tests.
+
+From similarity tests, the tests gave the following interpretations:
+
+\begin{itemize}
+    \item The best strategies to solve \textit{Pressure Vessel Design} in its proud-and-lame-homemade version
+    are EP, ES, FFA and PSO, due to its stability and results similarity. The best of all is FFA due to its
+    lower standard deviation.
+    \item No strategy tested in this paper were able to solve \textit{Pressurew Vessel Design} in its original
+    version and the available tools chosen for implementation.
+    \item The best strategies to solve \textit{Spring Tension Design} are EP, ES, BeesA, FFA and PSO. The best of
+    all is FFA due to its lower standard deviation.
+\end{itemize}
 

### 2023-01-21 release/code/latex/includes/footer.tex
Release Added

--- 2023-01-19 latex/article.tex
@@
-\documentclass[conference]{IEEEtran}
-\IEEEoverridecommandlockouts
-% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-\usepackage{cite}
-\usepackage{amsmath,amssymb,amsfonts}
-\usepackage{mathtools}
-\usepackage{algpseudocode}
-\usepackage{algorithm}
-\usepackage{algorithmicx}
-\usepackage{microtype}
-\usepackage{float}
-\usepackage{adjustbox}
-\usepackage{booktabs,makecell,tabularx}
-\usepackage{graphicx}
-\usepackage{textcomp}
-\usepackage{verbatim}
-\usepackage{xcolor}
-\usepackage{graphics} % for pdf, bitmapped graphics files
-\usepackage{epsfig} % for postscript graphics files
-\usepackage{mathptmx} % assumes new font selection scheme installed
-\usepackage{multicol}
-\usepackage[english]{babel}
-\usepackage[T1]{fontenc}
-\restylefloat{table}
-\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
-    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
-\begin{document}
-\title{Swarm and Evolutionary Based Algorithms used for Optimization}
-\author{
-	\IEEEauthorblockN{Augusto Mathias Adams\IEEEauthorrefmark{1}, Caio Phillipe Mizerkowski\IEEEauthorrefmark{2}, Christian Piltz Araújo\IEEEauthorrefmark{3} and Vinicius Eduardo dos Reis\IEEEauthorrefmark{4}}\\
-	\IEEEauthorblockA{\IEEEauthorrefmark{1}GRR20172143, augusto.adams@ufpr.br, \IEEEauthorrefmark{2}GRR20166403, caiomizerkowski@gmail.com,\\ \IEEEauthorrefmark{3}GRR20172197, christian0294@yahoo.com.br, \IEEEauthorrefmark{4}GRR20175957, eduardo.reis02@gmail.com}
-}
+\section{Discussion}
 
-\maketitle
+In this paper were tested 3 evolutionary algorithms (EP, ES and GA) and 3
+swarm based algorithms (BeesA, FFA and PSO), implemented by the \textit{MealPy}
+package. The chosen test problem were \textit{Pressure Vessel Design} and
+\textit{Spring Tension Design} because they are well studied engineering problems
+and are founs in many, if not all, optimization books everywhere. Thus, there are
+more results to compare.
 
-\begin{abstract}
-    In this paper, a study of evolution and swarm based algorithms is presented,
-    using two classical engineering problems: \textit{Spring Tension} and \textit{Pressure Vessel
-    Designs}. The test code for the problems was made using the \textit{Python Language},
-    version 3.10 and uses \textit{MealPy} package, version 2.5.1,  to provide the algorithms.
-    The algorithms were randomly chosen from a vast list of \textit{MealPy}'s algorithms:
-    \textit{Evolutionary Programming (LevyEP)}, \textit{Evolution Strategies (OriginalES)} and
-    \textit{Genetic Algorithm (BaseGA)} from \textit{evolutionary\_based} subpackage;
-    \textit{Bees Algorithm (OriginalBeesA)}, \textit{Firefly Algorithm (OriginalFFA)} and
-    \textit{Particle Swarm Optimization (OriginalPSO)} from \textit{swarm\_based} subpackage.
-    Each problem was modeled using \textit{SciPy} package, with constraints implemented as
-    \textit{penalty functions}. Each algorithm were optimized separately to extract the best
-    solutions from each problem using the \textit{MealPy}'s \textit{Tuner} utility.
-    The results, however, are dependant of algorithm and/or problem solved and the Friedman's chi
-    squared test for similarity make it noticeable because, although the values for best fits are
-    similar, running the same algorithm with different initial conditions does not converge to similar
-    values.
-\end{abstract}
+Both problems were implemented in full form, that is, with constraints, using the scheme of
+\textit{penalty functions}, as it is recomended by \textit{MealPy}'s documentation.
 
-\begin{IEEEkeywords}
-	Optimization Methods, Evolutionary Programming, Evolutionary and Swarm Based Strategies.
-\end{IEEEkeywords}
+Surprisingly, the \textit{Pressure Vessel Design} problem was a tricky one to solve.
+Many articles point out the boundings as described for original problem
+in Section~\ref{subsubsec:methodology-pressure-vessel-design}.
+But, for some unknown reason, the same variable bounding does not work for this
+implementation, and it was necessary to tweak the search space to give at least
+comparable results with the literature.
+It is not intended to point out errors in modelling or blame anyone, it is only a mere
+note to a misbehaviour in solving a specific problem.
 
-\section{Definitions}
-\label{sec:definitions}
+The results gives a notion that there are no panacea or universal solution for problems that
+nothing is known except the cost function and constraints.
+One algorithm's success to solve a specific problem is not a guarantee to solve anything
+and so on.
 
-The main objective of this paper is study evolutionary and swarm intelligence algorithms.
-We present the main concepts of these two algorithm's classes, along with the chosen algorithms
-definitions in this section. All citations made in this document are due to Swarm Intelligence classes
-and to \textit{MealPy}'s documentation, which points out the theoretical documentation for each
-implemented algorithm.
+At first, the \textit{Spring Tension Design} is easier to solve and is well behaved in the
+given variable bounsings. But, at it is noticed in the Table~\ref{best_fits:spring_problem},
+the cost function $f_x$ seems to have a plateau of weak minimizers, that is, values that gives
+near te same results. The statistical parameters of the cost function values at the best fits
+, as well the Wilcoxon test results fot this problem shows, there are no difference between the
+distribution of each algorithm solution, but the Friedman Test (and clearly the boxplot in
+figure~\ref{fig:spring_tension_design_boxplot}) indicates that they have significant
+differences in the mean value. So, there are some algorithms not fitted for the problem's solution.
+The best fit at all can be obtained using FFA algorithm, according to this paper.
 
-\textit{\textbf{Evolution}}: From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolutionary Algorithms belong to the Evolutionary Computation
-field of study concerned with computational methods inspired by the process
-and mechanisms of biological evolution. The process of evolution by
-means of natural selection (descent with modification) was proposed by
-Darwin to account for the variety of life and its suitability (adaptive
-fit) for its environment. The mechanisms of evolution describe how
-evolution actually takes place through the modification and propagation
-of genetic material (proteins). Evolutionary Algorithms are concerned
-with investigating computational systems that resemble simplified ver-
-sions of the processes and mechanisms of evolution toward achieving
-the effects of these processes and mechanisms, namely the development
-of adaptive systems. Additional subject areas that fall within the realm
-of Evolutionary Computation are algorithms that seek to exploit the
-properties from the related fields of Population Genetics, Population
-Ecology, Coevolutionary Biology, and Developmental Biology.
+The \textit{Pressure Vessel Design} was solver using two bounding schemes to show discrepancies
+between the solutions.
+First, it was solved using the literature boundings: the behaviour of the
+solutions seems bizarre and make it evident that or the literature is wrong or the implementation
+used in this paper is wrong.
+Again, it is not intended heve to blame anyone.
+The second solution, using the proud-and-lame-homemade
+version of variable boundings seems to behave well.
+The same behaviour of \textit{Spring Tension Design} is noticed in the tests, both statistical
+, Wincoxon and Friedman Tests.
 
-\textit{\textbf{Swarm Intelligence}}: From Jason Brownlee's \textit{``Clever Algorithms''} -
-Swarm intelligence is the study of computational systems inspired by
-the ‘collective intelligence’. Collective Intelligence emerges through the
-cooperation of large numbers of homogeneous agents in the environment.
-Examples include schools of fish, flocks of birds, and colonies of ants.
-Such intelligence is decentralized, self-organizing and distributed through
-out an environment. In nature such systems are commonly used to
-solve problems such as effective foraging for food, prey evading, or
-colony re-location. The information is typically stored throughout the
-participating homogeneous agents, or is stored or communicated in
-the environment itself such as through the use of pheromones in ants,
-dancing in bees, and proximity in fish and birds.
-
-\textit{\textbf{Evolutionary Programming:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolutionary Programming is a Global Optimization algorithm and is an instance of an Evolutionary
-Algorithm from the field of Evolutionary Computation. The approach is a sibling of other Evolutionary
-Algorithms such as the Genetic Algorithm, and Learning Classifier Systems. It is sometimes confused with Genetic
-Programming given the similarity in name, and more recently it shows a strong functional similarity to Evolution Strategies.
-Evolutionary Programming is inspired by the theory of evolution by means of natural selection. Specifically, the technique is inspired by
-macro-level or the species-level process of evolution (phenotype, hereditary, variation) and is not concerned with the genetic mechanisms of
-evolution (genome, chromosomes, genes, alleles).
-
-\textit{\textbf{Evolutionary Strategies:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolution Strategies is a global optimization algorithm and is an instance of an Evolutionary Algorithm from the field of Evolutionary
-Computation. Evolution Strategies is a sibling technique to other Evolutionary Algorithms such as Genetic Algorithms (Section 3.2), Genetic
-Programming (Section 3.3), Learning Classifier Systems, and Evolutionary Programming. A popular descendant of
-the Evolution Strategies algorithm is the Covariance Matrix Adaptation Evolution Strategies (CMA-ES).
-
-\textit{\textbf{Genetic Algorithms:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-The Genetic Algorithm is an Adaptive Strategy and a Global Optimization technique. It is an Evolutionary Algorithm and belongs to the
-broader study of Evolutionary Computation. The Genetic Algorithm is a sibling of other Evolutionary Algorithms such as Genetic Programming,
- Evolution Strategies, Evolutionary Programming, and Learning Classifier Systems. The Genetic Algorithm is a parent of a large number of variant techniques
-and sub-fields too numerous to list. The Genetic Algorithm is inspired by population genetics (including heredity and gene frequencies),
-and evolution at the population level, as well as the Mendelian understanding of the structure (such as chromosomes, genes, alleles) and mechanisms
-(such as recombination and mutation). This is the so-called new or modern synthesis of evolutionary biology.
-
-\textit{\textbf{Particle Swarm Optimization:}} From Jason Brownlee's \textit{``Clever Algorithms''} - Particle Swarm Optimization belongs to the field of
-Swarm Intelligence and Collective Intelligence and is a sub-field of Computational Intelligence. Particle Swarm Optimization is related to other Swarm Intelligence
-algorithms such as Ant Colony Optimization and it is a baseline algorithm for many variations, too numerous to list. It is inspired by the social foraging behavior
-of some animals such as flocking behavior of birds and the schooling behavior of fish.
-
-\textit{\textbf{Firefly Algorithm:}} From Xin-She Yang \textit{``Nature-Inspired Metaheuristic Algorithms''} -
-The flashing light of fireflies is an amazing sight in the summer sky in the tropical and temperate regions. There are about two thousand firefly
-species, and most fireflies produce short and rhythmic flashes. The pattern of flashes is often unique for a particular species. The flashing light is
-produced by a process of bioluminescence, and the true functions of suchsignaling systems are still being debated. However, two fundamental functions
-of such flashes are to attract mating partners (communication), and to attract potential prey. In addition, flashing may also serve as a protective warning
-mechanism to remind potential predators of the bitter taste of fireflies. The firefly algorithm tries to mimic the attractiveness of Fireflies and has three
-basic rules:
+From similarity tests, the tests gave the following interpretations:
 
 \begin{itemize}
-    \item All fireflies are unisex so that one firefly will be attracted to other
-          fireflies regardless of their sex;
-    \item Attractiveness is proportional to the their brightness, thus for any two
-          flashing fireflies, the less brighter one will move towards the brighter
-          one. The attractiveness is proportional to the brightness and they
-          both decrease as their distance increases. If there is no brighter one
-          than a particular firefly, it will move randomly;
-    \item The brightness of a firefly is affected or determined by the landscape
-          of the objective function.
+    \item The best strategies to solve \textit{Pressure Vessel Design} in its proud-and-lame-homemade version
+    are EP, ES, FFA and PSO, due to its stability and results similarity. The best of all is FFA due to its
+    lower standard deviation.
+    \item No strategy tested in this paper were able to solve \textit{Pressurew Vessel Design} in its original
+    version and the available tools chosen for implementation.
+    \item The best strategies to solve \textit{Spring Tension Design} are EP, ES, BeesA, FFA and PSO. The best of
+    all is FFA due to its lower standard deviation.
 \end{itemize}
 
-\textit{\textbf{Bees Algorithm:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-The Bees Algorithm beings to Bee Inspired Algorithms and the field of Swarm Intelligence, and more broadly the fields of Computational
-Intelligence and Metaheuristics. The Bees Algorithm is related to other Bee Inspired Algorithms, such as Bee Colony Optimization, and other
-Swarm Intelligence algorithms such as Ant Colony Optimization and Particle Swarm Optimization.
-It is inspired by the foraging behavior of honey bees. Honey bees collect nectar from vast areas around their hive (more than
-10 kilometers). Bee Colonies have been observed to send bees to collect nectar from flower patches relative to the amount of food available at
-each patch. Bees communicate with each other at the hive via a waggle dance that informs other bees in the hive as to the direction, distance,
-and quality rating of food sources.
-
-\section{Methodology}
-\label{sec:methodology}
-
-\subsection{Optimization Problem Selection}
-\label{subsec:optimization-problem-selection}
-The two problems selected for this paper were \textit{Spring Tension Design} and \textit{Pressure Vessel Design}. Although it was simple
-to choose the first two problems from the computational work statements, the choice was more than justified because these aroblems are well
-known in the literature.
-Thus, the problem selection was driven by which has more than one source to compare results.
-
-\subsubsection{Spring Tension Design}
-\label{subsubsec:methodology-spring-tension-design}
-From \textit{Nature-Inspired Metaheuristic Algorithms - Xin-She Yang} -
-The design of a tension and compression spring is a well-known benchmark
-optimization problem.
-The main aim is to minimize the weight subject
-to constraints on deflection, stress, surge frequency and geometry. It involves
-three design variables: the wire diameter $x_1$ , coil diameter $x_2$ and
-number/length of the coil $x_3$.
-This problem can be summarized as:
-
-\begin{equation}
-    f (x) = x_1^2 x_2 (2 + x_3)
-\end{equation}
-
-subject to
-
-\begin{equation}
-    \begin{split}
-        g_1(x) = \frac{x_2^3 x_3}{71785 x_1^4} \leq 0\\
-        g_2(x) = \frac{4 x_2^2 - x_1 x_2}{12566 \left( x_1^3 x_2 - x_1^4\right)}\\
-        + \frac{1}{5108 x_1^2} -1 \leq 0\\
-        g_3(x) = 1 - \frac{140.45 x_1}{x_2^2 x_3} \leq 0\\
-        g_4 = \frac{x_1 + x_2}{1.5} - 1 \leq 0
-    \end{split}
-\end{equation}
-
-The original bounding limits of the variables, extracted from computational work
-statements, are:
-
-\begin{equation}
-    \begin{split}
-        0.05 \leq x_1 \leq 2.0\\
-        0.25 \leq x_2 \leq 1.3\\
-        2.0 \leq x_3 \leq 15.0
-    \end{split}
-\end{equation}
-
-\subsubsection{Pressure Vessel Design}
-\label{subsubsec:methodology-pressure-vessel-design}
-From \textit{Solving Design of Pressure Vessel Engineering
-Problem Using a Fruit Fly Optimization Algorithm - XIANTING KE et al} -
-A pressure vessel design model involves four decision variables: $x_1$ is defined
-thickness of the pressure vessel $T_s$ , $x_2$ stands for
-thickness of the head $T_H$ , $x_3$ represents inner radius of the
-vessel $R$ , and $x_4$ is on behalf of length of the vessel
-barring head $L$ , the total variables described as $( x_1 , x_2 , x_3 , x_4 )$.
-The objective function of the problem is to minimize the total cost, including
-the cost of material, forming, and welding.
-The general pressure vessel design optimization model is expressed as:
-
-\begin{equation}
-	\begin{split}
-        f(x) = 0.6224 x_1 x_3 x_4 + 1.7781 x_2 x_3^2 \\
-        + 3.1661 x_1^2 x_4 + 19.84 x_1^2 x_3
-	\end{split}
-\end{equation}
-
-subject to:
-
-\begin{equation}
-    \begin{split}
-        g_1(x) = - x_1 + 0.0193 x_3 \leq 0\\
-        g_2(x) = - x_2 + 0.00954 x_3 \leq 0\\
-        g_3(x) = - \pi x_3^2 x_4 -\frac{4}{3}\pi x_3^3 + 1296000 \leq 0\\
-        g_4(x) = x_4 -240 \leq 0\\
-    \end{split}
-\end{equation}
-
-The original bounding limits of the variables, extracted from computational work
-statements, are:
-
-\begin{equation}
-    \begin{split}
-        0 \leq x_1 \leq 99\\
-        0 \leq x_2 \leq 99\\
-        10 \leq x_3 \leq 200\\
-        10 \leq x_4 \leq 200\\
-    \end{split}
-\end{equation}
-
-For some reason these settings does not work at all with the selected optimizers, so
-some research in the literature \textit{Solving Design of Pressure Vessel Engineering
-Problem Using a Fruit Fly Optimization Algorithm - XIANTING KE et al} suggest the
-following bounding limits:
-
-\begin{equation}
-    \begin{split}
-        0.0625 \leq x_1 \leq 99 \times 0.0625\\
-        0.0625 \leq x_2 \leq 99 \times 0.0625\\
-        10 \leq x_3 \leq 200\\
-        10 \leq x_4 \leq 200
-    \end{split}
-\end{equation}
-
-But these settings produce many random, bizarre and noisy results in all selected optimizers. Then
-a proud-and-lame-homemade set of variable boundings comes in handy, obtained by tweaking the original
-boundings:
-
-\begin{equation}
-    \begin{split}
-        0.75 \leq x_1 \leq 0.8\\
-        0.35 \leq x_2 \leq 0.4\\
-        39.5 \leq x_3 \leq 41.0\\
-        195.0 \leq x_4 \leq 205.0\\
-    \end{split}
-\end{equation}
-
-It is not intended here to point out modeling errors of any kind, nor point out package
-errors made by the authors or ours, but the homemade bounding limits was necessary to
-reach the literature results.
-
-\subsection{Constraint Implementation}
-\label{subsec:methodology-constraint-implementation}
-The constraints that all problems are subjected were implemented as \textit{penalty functions},
-that is, it adds a high value when the constraint is not satisfied, zero otherwise. It is an optional requirement
-from computational work in question and is the recommended way to put constraints from \textit{MealPy}'s
-Manual.
-
-\subsection{Programming Language}
-\label{subsec:methodology-programming-language}
-
-The chosen programming language for the test code was \textit{Python Language}, version 3.10, because it is an opensource language easy to
-program and has a huge amount of packages regarding artificial intelligence, genetic algorithms and swarm based algorithms.
-From these packages it was selected \textit{MealPy} package, version 2.5.1, because it comprises all the algorithm's classed tested in this paper.
-
-\subsection{Algorithm Selection}
-\label{subsec:methodology-algorithm-selection}
-
-The algorithm selection was made in two steps: first, it was extracted simple version of the two classes (evolutionary and swarm based) and
-then it was used a simple shuffle using Python's \textit{random.shuffle} in a terminal - no script was required.
-
-The chosen algorithms were:
-
-\begin{itemize}
-    \item \textit{\textbf{Evolution Based Algorithms: }} LevyEP (Evolutionary Programming),
-    OriginalES (Evolution Strategy) and BaseGA (Genetic Algorithm)
-    \item \textit{\textbf{Swarm Based Algorithms: }} OriginalBeesA (Bees Algorithm),
-    OriginalFFA (Original Firefly Algorithm) and OriginalPSO (Particle Swarm Optimization)
-\end{itemize}
-
-\subsection{Optimizer Tuning}
-\label{subsec:methodology-optimizer-tuning}
-
-The hyperparameters for each optimizer were tuned using the \textit{MealPy}'s \textit{Tuner} utility.
-It is a recomended procedure to tune hyperparameters for each optimizer and problem, according to
-\textit{MealPy}'s Manual.
-The \textit{Tuner} utility is a very simple grid search metaheuristic search tool
-that test each grid configuration for a specified oprimizer runs.
-Although simple, it is a very expensive procedure that took 2 days to complete. It was defined 10 runs for each
-configuration, with the following set of hyperparameter:
-
-\begin{itemize}
-    \item \textit{\textbf{Evolution Based Algorithms: }}
-        \subitem \textit{LevyEP:}
-            \subsubitem \textit{bout\_size (float)}: percentage of child agents implement tournament selection.
-        \subitem \textit{OriginalES:}
-            \subsubitem \textit{lamda (float)}: Percentage of child agents evolving in the next generation.
-        \subitem \textit{BaseGA:}
-            \subsubitem \textit{pc (float)}: cross-over probability
-            \subsubitem \textit{pm (float)}: mutation probability
-    \item \textit{\textbf{Swarm Based Algorithms: }}
-        \subitem \textit{OriginalBeesA:}
-            \subsubitem \textit{selected\_site\_ratio (float)}
-            \subsubitem \textit{elite\_site\_ratio (float)}
-            \subsubitem \textit{selected\_site\_bee\_ratio (float)}
-            \subsubitem \textit{elite\_site\_bee\_ratio (float)}
-            \subsubitem \textit{dance\_radius (float)}
-            \subsubitem \textit{dance\_reduction (float)}
-        \subitem \textit{OriginalFFA:}
-            \subsubitem \textit{gamma (float)}: Light Absorption Coefficient
-            \subsubitem \textit{beta\_base (float)}: Attraction Coefficient Base Value
-            \subsubitem \textit{alpha (float)}: Mutation Coefficient
-            \subsubitem \textit{alpha\_damp (float)}: Mutation Coefficient Damp Rate
-            \subsubitem \textit{delta (float)}: Mutation Step Size
-            \subsubitem \textit{exponent (int)}: Exponent
-        \subitem \textit{OriginalPSO:}
-            \subsubitem \textit{c1 (float)}: local coefficient
-            \subsubitem \textit{c2 (float)}: global coefficient
-            \subsubitem \textit{w\_min (float)}: Weight min of bird
-            \subsubitem \textit{w\_max (float)}: Weight max of bird
-
-\end{itemize}
-
-\subsection{Optimizer Parameters}
-\label{subsec:methodology-optimizer-parameters}
-
-For all optimizers and problems, were selected the following parameters:
-
-\begin{itemize}
-    \item \textit{Runs}: 100 runs
-    \item \textit{Epochs}: 100 epochs
-    \item \textit{Population}: 100 initial points
-\end{itemize}
-
-The initial solutions were randomly selected using the same seed for all algorithms.
-
-\section{Results}
-\label{sec:results}
-\subsection{Spring Tension Design}
-\label{ssubec:spring_problem}
-
-\begin{table}[H]
-\centering
-\caption{Statistical Information about function values for Spring Tension Design}
-\label{function_values:spring_problem}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrrrrr}
-\toprule
-Algorithm &      Min F &     Mean F &   Median F &      Max F &   StdDev F \\
-\midrule
-       EP & 0.01250534 & 0.01255960 & 0.01253156 & 0.01453933 & 0.00020190 \\
-       ES & 0.01252956 & 0.01281857 & 0.01274283 & 0.01346214 & 0.00024181 \\
-       GA & 0.01252305 & 0.01628575 & 0.01616768 & 0.02561808 & 0.00273276 \\
-    BeesA & 0.01250200 & 0.01268010 & 0.01261691 & 0.01406679 & 0.00021629 \\
-      FFA & 0.01249803 & 0.01254780 & 0.01253499 & 0.01268116 & 0.00003152 \\
-      PSO & 0.01252626 & 0.01390866 & 0.01318774 & 0.03036537 & 0.00342240 \\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{figure}[H]
-\centering
-\caption{Boxplot for Spring Tension Design}
-\label{fig:spring_tension_design_boxplot}
-\includegraphics[scale=0.5]{images/spring_problem_boxplot.png}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\caption{Convergence lines for Spring Tension Design}
-\label{fig:spring_problem_convergence}
-\includegraphics[width= 0.4 \textwidth]{images/spring_problem_convergence.png}
-\end{figure}
-
-\subsection{Pressure Vessel Design (Original)}
-\label{subsec:pressure_vessel_problem_original}
-
-\begin{table}[H]
-\centering
-\caption{Statistical Information about function values for Pressure Vessel Design (Original)}
-\label{function_values:pressure_vessel_problem_original}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrrrrr}
-\toprule
-Algorithm &         Min F &         Mean F &       Median F &          Max F &       StdDev F \\
-\midrule
-       EP &    0.08150806 &     0.15642850 &     0.09093798 &     1.32637552 &     0.16807714 \\
-       ES &    0.08161190 &   718.92910990 &     1.00278859 &  9443.54269260 &  2060.07774212 \\
-       GA &   17.06920868 &   525.00734162 &   361.53879602 &  3112.03503082 &   454.52386703 \\
-    BeesA & 2393.70106213 & 17564.33024022 & 15751.91467117 & 53850.38271384 & 10514.60780411 \\
-      FFA &    0.08306113 &     0.13296127 &     0.13106271 &     0.20084847 &     0.02396876 \\
-      PSO &    0.08149204 &     0.24191732 &     0.08159173 &    10.00611523 &     1.00072349 \\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{figure}[H]
-\centering
-\caption{Boxplot for Pressure Vessel Design (Original)}
-\label{fig:pressure_vessel_design_original_boxplot}
-\includegraphics[scale=0.5]{images/pressure_vessel_problem_original_boxplot.png}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\caption{Convergence lines for Pressure Vessel Design (Original)}
-\label{fig:pressure_vessel_problem_original_convergence}
-\includegraphics[width= 0.4 \textwidth]{images/pressure_vessel_problem_original_convergence.png}
-\end{figure}
-
-\subsection{Pressure Vessel Design}
-\label{subsec:pressure_vessel_problem}
-
-\begin{table}
-\centering
-\caption{Statistical Information about function values for Pressure Vessel Design}
-\label{function_values:pressure_vessel_problem}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrrrrr}
-\toprule
-Algorithm &         Min F &        Mean F &      Median F &         Max F &   StdDev F \\
-\midrule
-       EP & 5534.57345496 & 5534.63426098 & 5534.61416291 & 5534.92993607 & 0.05804548 \\
-       ES & 5534.57917966 & 5535.28165367 & 5535.06149254 & 5538.03003895 & 0.65098467 \\
-       GA & 5534.83662424 & 5538.36788889 & 5536.92932748 & 5550.91639342 & 3.57079951 \\
-    BeesA & 5534.57516657 & 5537.97495231 & 5537.04824684 & 5548.55587234 & 3.28239740 \\
-      FFA & 5534.57401617 & 5534.58849395 & 5534.58435493 & 5534.63296149 & 0.01341777 \\
-      PSO & 5534.57345480 & 5534.57381593 & 5534.57355270 & 5534.57625290 & 0.00053848 \\
-\bottomrule
-\end{tabular}
-}
-\end{table}
-
-\begin{figure}[H]
-\centering
-\caption{Boxplot for Pressure Vessel Design}
-\label{fig:pressure_vessel_design_boxplot}
-\includegraphics[scale=0.5]{images/pressure_vessel_problem_boxplot.png}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\caption{Convergence lines for Pressure Vessel Design}
-\label{fig:pressure_vessel_problem_convergence}
-\includegraphics[width=0.4 \textwidth]{images/pressure_vessel_problem_convergence.png}
-\end{figure}
-
-\subsection{Significance Test}
-\label{subsec:pressure_vessel_problem_significance_test}
-
-\begin{table}[H]
-\centering
-\caption{Significance Test Using Friedman Chi-Squared Test}
-\label{friedman_test}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrr}
-\toprule
-                          Problem &   Statistics &    p-value \\
-\midrule
-            Spring Tension Design & 339.05714286 & 0.00000000 \\
-           Pressure Vessel Design & 436.16000000 & 0.00000000 \\
-Pressure Vessel Design (Original) & 425.07428571 & 0.00000000 \\
-\bottomrule
-\end{tabular}
-}
-\end{table}
-
-\section{Discussion}
-
-The main objective of this work is demonstrate the inner work of a optimization class of algorithms called \textit{Quasi-Newton algorithms}.
-Four of them are presented, along with the results and analysis regarding convergence, function evaluations and function objective values.
-
-For implementation, it was decided to put constraints on search space, because for the original search space of some functions, like Ackley and Rastrigin, there are other minimas that will confuse every algorithm tested for this paper, and there is no sense on test a local minima procedure on these conditions.
-To restrain the initial solution to some region in the search space was a cheap and ready solution to avoid the algorithms to stop because of stumbling upon the wrong minimum.
-
-The \textit{Levenberg-Marquardt Algorithm} implemented for this paper is very sensitive to hyperparameters, namely $\alpha$ and $\lambda$, which was not tunned to every function, so, the conspicuous performance variation is noticeable along the results.
-LMA is known to be fast and reliable, but in our implementation it was found a little tricky to get the hyperparameters right for all the test functions.
-But for Rosenbrock and Rastrigin, it is the best option, even for lame implementations like ours.
-
-The \textit{Broyden–Fletcher–Goldfarb–Shanno} Algorithm was the only one that we decided to use it as is from \textit{SciPy}, because it has features desired for this work, like counting of function evaluations, gradient evaluation and iterations.
-It performed very well for Ackley and Booth Functions, and reasonably well for other functions.
-
-The \textit{Davidon–Fletcher–Powell} Algorithm is not implemented in \textit{SciPy} but its equations shows that it is the dual of BFGS, so, it was easy to implement using some \textit{SciPy} code for BFGS algorithm.
-In the DFP procedure, there is a Hessian inversion to be evaluated every iteration, then, numerical imprecision would be taken into consideration evaluating its results.
-While in some cases it has a superb performance (Like Ackley Function), it has very poor performance in Rosenbrock Function and even in Beale Function.
-The increase of dimensions makes DFP suffer of numerical imprecision due to the Hessian inversion, except for Rastrigin, and it is the loser algorithm in other functions.
-
-Finally, the \textit{Limited memory BFGS} has an average performance among the functions.
-The original algorithm was implemented using code found in the url https://github.com/qkolj/L-BFGS/blob/master/L-BFGS.ipynb.
-
-In fact, there are no Quasi-Newton algorithms that solver the minima problem for an any function.
-From the standpoint of performance and convergence, all the algorithms have an average performance and a reasonable convergence, although we have to restrain the search space to a small area near the optimal solution.
-
 \end{document}

### 2023-01-21 release/code/latex/includes/friedman_test.tex
Release Added

--- 2023-01-19 latex/article.tex
@@
-\documentclass[conference]{IEEEtran}
-\IEEEoverridecommandlockouts
-% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-\usepackage{cite}
-\usepackage{amsmath,amssymb,amsfonts}
-\usepackage{mathtools}
-\usepackage{algpseudocode}
-\usepackage{algorithm}
-\usepackage{algorithmicx}
-\usepackage{microtype}
-\usepackage{float}
-\usepackage{adjustbox}
-\usepackage{booktabs,makecell,tabularx}
-\usepackage{graphicx}
-\usepackage{textcomp}
-\usepackage{verbatim}
-\usepackage{xcolor}
-\usepackage{graphics} % for pdf, bitmapped graphics files
-\usepackage{epsfig} % for postscript graphics files
-\usepackage{mathptmx} % assumes new font selection scheme installed
-\usepackage{multicol}
-\usepackage[english]{babel}
-\usepackage[T1]{fontenc}
-\restylefloat{table}
-\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
-    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
-\begin{document}
-\title{Swarm and Evolutionary Based Algorithms used for Optimization}
-\author{
-	\IEEEauthorblockN{Augusto Mathias Adams\IEEEauthorrefmark{1}, Caio Phillipe Mizerkowski\IEEEauthorrefmark{2}, Christian Piltz Araújo\IEEEauthorrefmark{3} and Vinicius Eduardo dos Reis\IEEEauthorrefmark{4}}\\
-	\IEEEauthorblockA{\IEEEauthorrefmark{1}GRR20172143, augusto.adams@ufpr.br, \IEEEauthorrefmark{2}GRR20166403, caiomizerkowski@gmail.com,\\ \IEEEauthorrefmark{3}GRR20172197, christian0294@yahoo.com.br, \IEEEauthorrefmark{4}GRR20175957, eduardo.reis02@gmail.com}
-}
+The Friedman test is the non-parametric test used to compare related sample data, that is,
+when the same individual is evaluated more than once.
+The Friedman test does not use the data numbers directly, but the ranks occupied by
+them after the sorting done for each group separately. After sorting, the hypothesis
+of equality of the sum of the ranks of each group is tested.
 
-\maketitle
-
-\begin{abstract}
-    In this paper, a study of evolution and swarm based algorithms is presented,
-    using two classical engineering problems: \textit{Spring Tension} and \textit{Pressure Vessel
-    Designs}. The test code for the problems was made using the \textit{Python Language},
-    version 3.10 and uses \textit{MealPy} package, version 2.5.1,  to provide the algorithms.
-    The algorithms were randomly chosen from a vast list of \textit{MealPy}'s algorithms:
-    \textit{Evolutionary Programming (LevyEP)}, \textit{Evolution Strategies (OriginalES)} and
-    \textit{Genetic Algorithm (BaseGA)} from \textit{evolutionary\_based} subpackage;
-    \textit{Bees Algorithm (OriginalBeesA)}, \textit{Firefly Algorithm (OriginalFFA)} and
-    \textit{Particle Swarm Optimization (OriginalPSO)} from \textit{swarm\_based} subpackage.
-    Each problem was modeled using \textit{SciPy} package, with constraints implemented as
-    \textit{penalty functions}. Each algorithm were optimized separately to extract the best
-    solutions from each problem using the \textit{MealPy}'s \textit{Tuner} utility.
-    The results, however, are dependant of algorithm and/or problem solved and the Friedman's chi
-    squared test for similarity make it noticeable because, although the values for best fits are
-    similar, running the same algorithm with different initial conditions does not converge to similar
-    values.
-\end{abstract}
-
-\begin{IEEEkeywords}
-	Optimization Methods, Evolutionary Programming, Evolutionary and Swarm Based Strategies.
-\end{IEEEkeywords}
-
-\section{Definitions}
-\label{sec:definitions}
-
-The main objective of this paper is study evolutionary and swarm intelligence algorithms.
-We present the main concepts of these two algorithm's classes, along with the chosen algorithms
-definitions in this section. All citations made in this document are due to Swarm Intelligence classes
-and to \textit{MealPy}'s documentation, which points out the theoretical documentation for each
-implemented algorithm.
-
-\textit{\textbf{Evolution}}: From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolutionary Algorithms belong to the Evolutionary Computation
-field of study concerned with computational methods inspired by the process
-and mechanisms of biological evolution. The process of evolution by
-means of natural selection (descent with modification) was proposed by
-Darwin to account for the variety of life and its suitability (adaptive
-fit) for its environment. The mechanisms of evolution describe how
-evolution actually takes place through the modification and propagation
-of genetic material (proteins). Evolutionary Algorithms are concerned
-with investigating computational systems that resemble simplified ver-
-sions of the processes and mechanisms of evolution toward achieving
-the effects of these processes and mechanisms, namely the development
-of adaptive systems. Additional subject areas that fall within the realm
-of Evolutionary Computation are algorithms that seek to exploit the
-properties from the related fields of Population Genetics, Population
-Ecology, Coevolutionary Biology, and Developmental Biology.
-
-\textit{\textbf{Swarm Intelligence}}: From Jason Brownlee's \textit{``Clever Algorithms''} -
-Swarm intelligence is the study of computational systems inspired by
-the ‘collective intelligence’. Collective Intelligence emerges through the
-cooperation of large numbers of homogeneous agents in the environment.
-Examples include schools of fish, flocks of birds, and colonies of ants.
-Such intelligence is decentralized, self-organizing and distributed through
-out an environment. In nature such systems are commonly used to
-solve problems such as effective foraging for food, prey evading, or
-colony re-location. The information is typically stored throughout the
-participating homogeneous agents, or is stored or communicated in
-the environment itself such as through the use of pheromones in ants,
-dancing in bees, and proximity in fish and birds.
-
-\textit{\textbf{Evolutionary Programming:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolutionary Programming is a Global Optimization algorithm and is an instance of an Evolutionary
-Algorithm from the field of Evolutionary Computation. The approach is a sibling of other Evolutionary
-Algorithms such as the Genetic Algorithm, and Learning Classifier Systems. It is sometimes confused with Genetic
-Programming given the similarity in name, and more recently it shows a strong functional similarity to Evolution Strategies.
-Evolutionary Programming is inspired by the theory of evolution by means of natural selection. Specifically, the technique is inspired by
-macro-level or the species-level process of evolution (phenotype, hereditary, variation) and is not concerned with the genetic mechanisms of
-evolution (genome, chromosomes, genes, alleles).
-
-\textit{\textbf{Evolutionary Strategies:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolution Strategies is a global optimization algorithm and is an instance of an Evolutionary Algorithm from the field of Evolutionary
-Computation. Evolution Strategies is a sibling technique to other Evolutionary Algorithms such as Genetic Algorithms (Section 3.2), Genetic
-Programming (Section 3.3), Learning Classifier Systems, and Evolutionary Programming. A popular descendant of
-the Evolution Strategies algorithm is the Covariance Matrix Adaptation Evolution Strategies (CMA-ES).
-
-\textit{\textbf{Genetic Algorithms:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-The Genetic Algorithm is an Adaptive Strategy and a Global Optimization technique. It is an Evolutionary Algorithm and belongs to the
-broader study of Evolutionary Computation. The Genetic Algorithm is a sibling of other Evolutionary Algorithms such as Genetic Programming,
- Evolution Strategies, Evolutionary Programming, and Learning Classifier Systems. The Genetic Algorithm is a parent of a large number of variant techniques
-and sub-fields too numerous to list. The Genetic Algorithm is inspired by population genetics (including heredity and gene frequencies),
-and evolution at the population level, as well as the Mendelian understanding of the structure (such as chromosomes, genes, alleles) and mechanisms
-(such as recombination and mutation). This is the so-called new or modern synthesis of evolutionary biology.
-
-\textit{\textbf{Particle Swarm Optimization:}} From Jason Brownlee's \textit{``Clever Algorithms''} - Particle Swarm Optimization belongs to the field of
-Swarm Intelligence and Collective Intelligence and is a sub-field of Computational Intelligence. Particle Swarm Optimization is related to other Swarm Intelligence
-algorithms such as Ant Colony Optimization and it is a baseline algorithm for many variations, too numerous to list. It is inspired by the social foraging behavior
-of some animals such as flocking behavior of birds and the schooling behavior of fish.
-
-\textit{\textbf{Firefly Algorithm:}} From Xin-She Yang \textit{``Nature-Inspired Metaheuristic Algorithms''} -
-The flashing light of fireflies is an amazing sight in the summer sky in the tropical and temperate regions. There are about two thousand firefly
-species, and most fireflies produce short and rhythmic flashes. The pattern of flashes is often unique for a particular species. The flashing light is
-produced by a process of bioluminescence, and the true functions of suchsignaling systems are still being debated. However, two fundamental functions
-of such flashes are to attract mating partners (communication), and to attract potential prey. In addition, flashing may also serve as a protective warning
-mechanism to remind potential predators of the bitter taste of fireflies. The firefly algorithm tries to mimic the attractiveness of Fireflies and has three
-basic rules:
-
+Interpretation is as follows:
 \begin{itemize}
-    \item All fireflies are unisex so that one firefly will be attracted to other
-          fireflies regardless of their sex;
-    \item Attractiveness is proportional to the their brightness, thus for any two
-          flashing fireflies, the less brighter one will move towards the brighter
-          one. The attractiveness is proportional to the brightness and they
-          both decrease as their distance increases. If there is no brighter one
-          than a particular firefly, it will move randomly;
-    \item The brightness of a firefly is affected or determined by the landscape
-          of the objective function.
+    \item Assume two hypothesis about the data:
+        \subitem $H_0$: The mean for each population is equal.
+        \subitem $H_1$: At least one population mean is different from the rest.
+    \item Given p-value, decide:
+        \subitem p-value $\geq 0.05$: Reject $H_1$ with $95\%$ of confidence and accept null hypothesis;
+        \subitem Accept $H_1$ otherwise.
 \end{itemize}
 
-\textit{\textbf{Bees Algorithm:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-The Bees Algorithm beings to Bee Inspired Algorithms and the field of Swarm Intelligence, and more broadly the fields of Computational
-Intelligence and Metaheuristics. The Bees Algorithm is related to other Bee Inspired Algorithms, such as Bee Colony Optimization, and other
-Swarm Intelligence algorithms such as Ant Colony Optimization and Particle Swarm Optimization.
-It is inspired by the foraging behavior of honey bees. Honey bees collect nectar from vast areas around their hive (more than
-10 kilometers). Bee Colonies have been observed to send bees to collect nectar from flower patches relative to the amount of food available at
-each patch. Bees communicate with each other at the hive via a waggle dance that informs other bees in the hive as to the direction, distance,
-and quality rating of food sources.
-
-\section{Methodology}
-\label{sec:methodology}
-
-\subsection{Optimization Problem Selection}
-\label{subsec:optimization-problem-selection}
-The two problems selected for this paper were \textit{Spring Tension Design} and \textit{Pressure Vessel Design}. Although it was simple
-to choose the first two problems from the computational work statements, the choice was more than justified because these aroblems are well
-known in the literature.
-Thus, the problem selection was driven by which has more than one source to compare results.
-
-\subsubsection{Spring Tension Design}
-\label{subsubsec:methodology-spring-tension-design}
-From \textit{Nature-Inspired Metaheuristic Algorithms - Xin-She Yang} -
-The design of a tension and compression spring is a well-known benchmark
-optimization problem.
-The main aim is to minimize the weight subject
-to constraints on deflection, stress, surge frequency and geometry. It involves
-three design variables: the wire diameter $x_1$ , coil diameter $x_2$ and
-number/length of the coil $x_3$.
-This problem can be summarized as:
-
-\begin{equation}
-    f (x) = x_1^2 x_2 (2 + x_3)
-\end{equation}
-
-subject to
-
-\begin{equation}
-    \begin{split}
-        g_1(x) = \frac{x_2^3 x_3}{71785 x_1^4} \leq 0\\
-        g_2(x) = \frac{4 x_2^2 - x_1 x_2}{12566 \left( x_1^3 x_2 - x_1^4\right)}\\
-        + \frac{1}{5108 x_1^2} -1 \leq 0\\
-        g_3(x) = 1 - \frac{140.45 x_1}{x_2^2 x_3} \leq 0\\
-        g_4 = \frac{x_1 + x_2}{1.5} - 1 \leq 0
-    \end{split}
-\end{equation}
-
-The original bounding limits of the variables, extracted from computational work
-statements, are:
-
-\begin{equation}
-    \begin{split}
-        0.05 \leq x_1 \leq 2.0\\
-        0.25 \leq x_2 \leq 1.3\\
-        2.0 \leq x_3 \leq 15.0
-    \end{split}
-\end{equation}
-
-\subsubsection{Pressure Vessel Design}
-\label{subsubsec:methodology-pressure-vessel-design}
-From \textit{Solving Design of Pressure Vessel Engineering
-Problem Using a Fruit Fly Optimization Algorithm - XIANTING KE et al} -
-A pressure vessel design model involves four decision variables: $x_1$ is defined
-thickness of the pressure vessel $T_s$ , $x_2$ stands for
-thickness of the head $T_H$ , $x_3$ represents inner radius of the
-vessel $R$ , and $x_4$ is on behalf of length of the vessel
-barring head $L$ , the total variables described as $( x_1 , x_2 , x_3 , x_4 )$.
-The objective function of the problem is to minimize the total cost, including
-the cost of material, forming, and welding.
-The general pressure vessel design optimization model is expressed as:
-
-\begin{equation}
-	\begin{split}
-        f(x) = 0.6224 x_1 x_3 x_4 + 1.7781 x_2 x_3^2 \\
-        + 3.1661 x_1^2 x_4 + 19.84 x_1^2 x_3
-	\end{split}
-\end{equation}
-
-subject to:
-
-\begin{equation}
-    \begin{split}
-        g_1(x) = - x_1 + 0.0193 x_3 \leq 0\\
-        g_2(x) = - x_2 + 0.00954 x_3 \leq 0\\
-        g_3(x) = - \pi x_3^2 x_4 -\frac{4}{3}\pi x_3^3 + 1296000 \leq 0\\
-        g_4(x) = x_4 -240 \leq 0\\
-    \end{split}
-\end{equation}
-
-The original bounding limits of the variables, extracted from computational work
-statements, are:
-
-\begin{equation}
-    \begin{split}
-        0 \leq x_1 \leq 99\\
-        0 \leq x_2 \leq 99\\
-        10 \leq x_3 \leq 200\\
-        10 \leq x_4 \leq 200\\
-    \end{split}
-\end{equation}
-
-For some reason these settings does not work at all with the selected optimizers, so
-some research in the literature \textit{Solving Design of Pressure Vessel Engineering
-Problem Using a Fruit Fly Optimization Algorithm - XIANTING KE et al} suggest the
-following bounding limits:
-
-\begin{equation}
-    \begin{split}
-        0.0625 \leq x_1 \leq 99 \times 0.0625\\
-        0.0625 \leq x_2 \leq 99 \times 0.0625\\
-        10 \leq x_3 \leq 200\\
-        10 \leq x_4 \leq 200
-    \end{split}
-\end{equation}
-
-But these settings produce many random, bizarre and noisy results in all selected optimizers. Then
-a proud-and-lame-homemade set of variable boundings comes in handy, obtained by tweaking the original
-boundings:
-
-\begin{equation}
-    \begin{split}
-        0.75 \leq x_1 \leq 0.8\\
-        0.35 \leq x_2 \leq 0.4\\
-        39.5 \leq x_3 \leq 41.0\\
-        195.0 \leq x_4 \leq 205.0\\
-    \end{split}
-\end{equation}
-
-It is not intended here to point out modeling errors of any kind, nor point out package
-errors made by the authors or ours, but the homemade bounding limits was necessary to
-reach the literature results.
-
-\subsection{Constraint Implementation}
-\label{subsec:methodology-constraint-implementation}
-The constraints that all problems are subjected were implemented as \textit{penalty functions},
-that is, it adds a high value when the constraint is not satisfied, zero otherwise. It is an optional requirement
-from computational work in question and is the recommended way to put constraints from \textit{MealPy}'s
-Manual.
-
-\subsection{Programming Language}
-\label{subsec:methodology-programming-language}
-
-The chosen programming language for the test code was \textit{Python Language}, version 3.10, because it is an opensource language easy to
-program and has a huge amount of packages regarding artificial intelligence, genetic algorithms and swarm based algorithms.
-From these packages it was selected \textit{MealPy} package, version 2.5.1, because it comprises all the algorithm's classed tested in this paper.
-
-\subsection{Algorithm Selection}
-\label{subsec:methodology-algorithm-selection}
-
-The algorithm selection was made in two steps: first, it was extracted simple version of the two classes (evolutionary and swarm based) and
-then it was used a simple shuffle using Python's \textit{random.shuffle} in a terminal - no script was required.
-
-The chosen algorithms were:
-
-\begin{itemize}
-    \item \textit{\textbf{Evolution Based Algorithms: }} LevyEP (Evolutionary Programming),
-    OriginalES (Evolution Strategy) and BaseGA (Genetic Algorithm)
-    \item \textit{\textbf{Swarm Based Algorithms: }} OriginalBeesA (Bees Algorithm),
-    OriginalFFA (Original Firefly Algorithm) and OriginalPSO (Particle Swarm Optimization)
-\end{itemize}
-
-\subsection{Optimizer Tuning}
-\label{subsec:methodology-optimizer-tuning}
-
-The hyperparameters for each optimizer were tuned using the \textit{MealPy}'s \textit{Tuner} utility.
-It is a recomended procedure to tune hyperparameters for each optimizer and problem, according to
-\textit{MealPy}'s Manual.
-The \textit{Tuner} utility is a very simple grid search metaheuristic search tool
-that test each grid configuration for a specified oprimizer runs.
-Although simple, it is a very expensive procedure that took 2 days to complete. It was defined 10 runs for each
-configuration, with the following set of hyperparameter:
-
-\begin{itemize}
-    \item \textit{\textbf{Evolution Based Algorithms: }}
-        \subitem \textit{LevyEP:}
-            \subsubitem \textit{bout\_size (float)}: percentage of child agents implement tournament selection.
-        \subitem \textit{OriginalES:}
-            \subsubitem \textit{lamda (float)}: Percentage of child agents evolving in the next generation.
-        \subitem \textit{BaseGA:}
-            \subsubitem \textit{pc (float)}: cross-over probability
-            \subsubitem \textit{pm (float)}: mutation probability
-    \item \textit{\textbf{Swarm Based Algorithms: }}
-        \subitem \textit{OriginalBeesA:}
-            \subsubitem \textit{selected\_site\_ratio (float)}
-            \subsubitem \textit{elite\_site\_ratio (float)}
-            \subsubitem \textit{selected\_site\_bee\_ratio (float)}
-            \subsubitem \textit{elite\_site\_bee\_ratio (float)}
-            \subsubitem \textit{dance\_radius (float)}
-            \subsubitem \textit{dance\_reduction (float)}
-        \subitem \textit{OriginalFFA:}
-            \subsubitem \textit{gamma (float)}: Light Absorption Coefficient
-            \subsubitem \textit{beta\_base (float)}: Attraction Coefficient Base Value
-            \subsubitem \textit{alpha (float)}: Mutation Coefficient
-            \subsubitem \textit{alpha\_damp (float)}: Mutation Coefficient Damp Rate
-            \subsubitem \textit{delta (float)}: Mutation Step Size
-            \subsubitem \textit{exponent (int)}: Exponent
-        \subitem \textit{OriginalPSO:}
-            \subsubitem \textit{c1 (float)}: local coefficient
-            \subsubitem \textit{c2 (float)}: global coefficient
-            \subsubitem \textit{w\_min (float)}: Weight min of bird
-            \subsubitem \textit{w\_max (float)}: Weight max of bird
-
-\end{itemize}
-
-\subsection{Optimizer Parameters}
-\label{subsec:methodology-optimizer-parameters}
-
-For all optimizers and problems, were selected the following parameters:
-
-\begin{itemize}
-    \item \textit{Runs}: 100 runs
-    \item \textit{Epochs}: 100 epochs
-    \item \textit{Population}: 100 initial points
-\end{itemize}
-
-The initial solutions were randomly selected using the same seed for all algorithms.
-
-\section{Results}
-\label{sec:results}
-\subsection{Spring Tension Design}
-\label{ssubec:spring_problem}
-
-\begin{table}[H]
-\centering
-\caption{Statistical Information about function values for Spring Tension Design}
-\label{function_values:spring_problem}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrrrrr}
-\toprule
-Algorithm &      Min F &     Mean F &   Median F &      Max F &   StdDev F \\
-\midrule
-       EP & 0.01250534 & 0.01255960 & 0.01253156 & 0.01453933 & 0.00020190 \\
-       ES & 0.01252956 & 0.01281857 & 0.01274283 & 0.01346214 & 0.00024181 \\
-       GA & 0.01252305 & 0.01628575 & 0.01616768 & 0.02561808 & 0.00273276 \\
-    BeesA & 0.01250200 & 0.01268010 & 0.01261691 & 0.01406679 & 0.00021629 \\
-      FFA & 0.01249803 & 0.01254780 & 0.01253499 & 0.01268116 & 0.00003152 \\
-      PSO & 0.01252626 & 0.01390866 & 0.01318774 & 0.03036537 & 0.00342240 \\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{figure}[H]
-\centering
-\caption{Boxplot for Spring Tension Design}
-\label{fig:spring_tension_design_boxplot}
-\includegraphics[scale=0.5]{images/spring_problem_boxplot.png}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\caption{Convergence lines for Spring Tension Design}
-\label{fig:spring_problem_convergence}
-\includegraphics[width= 0.4 \textwidth]{images/spring_problem_convergence.png}
-\end{figure}
-
-\subsection{Pressure Vessel Design (Original)}
-\label{subsec:pressure_vessel_problem_original}
-
-\begin{table}[H]
-\centering
-\caption{Statistical Information about function values for Pressure Vessel Design (Original)}
-\label{function_values:pressure_vessel_problem_original}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrrrrr}
-\toprule
-Algorithm &         Min F &         Mean F &       Median F &          Max F &       StdDev F \\
-\midrule
-       EP &    0.08150806 &     0.15642850 &     0.09093798 &     1.32637552 &     0.16807714 \\
-       ES &    0.08161190 &   718.92910990 &     1.00278859 &  9443.54269260 &  2060.07774212 \\
-       GA &   17.06920868 &   525.00734162 &   361.53879602 &  3112.03503082 &   454.52386703 \\
-    BeesA & 2393.70106213 & 17564.33024022 & 15751.91467117 & 53850.38271384 & 10514.60780411 \\
-      FFA &    0.08306113 &     0.13296127 &     0.13106271 &     0.20084847 &     0.02396876 \\
-      PSO &    0.08149204 &     0.24191732 &     0.08159173 &    10.00611523 &     1.00072349 \\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{figure}[H]
-\centering
-\caption{Boxplot for Pressure Vessel Design (Original)}
-\label{fig:pressure_vessel_design_original_boxplot}
-\includegraphics[scale=0.5]{images/pressure_vessel_problem_original_boxplot.png}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\caption{Convergence lines for Pressure Vessel Design (Original)}
-\label{fig:pressure_vessel_problem_original_convergence}
-\includegraphics[width= 0.4 \textwidth]{images/pressure_vessel_problem_original_convergence.png}
-\end{figure}
-
-\subsection{Pressure Vessel Design}
-\label{subsec:pressure_vessel_problem}
-
-\begin{table}
-\centering
-\caption{Statistical Information about function values for Pressure Vessel Design}
-\label{function_values:pressure_vessel_problem}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrrrrr}
-\toprule
-Algorithm &         Min F &        Mean F &      Median F &         Max F &   StdDev F \\
-\midrule
-       EP & 5534.57345496 & 5534.63426098 & 5534.61416291 & 5534.92993607 & 0.05804548 \\
-       ES & 5534.57917966 & 5535.28165367 & 5535.06149254 & 5538.03003895 & 0.65098467 \\
-       GA & 5534.83662424 & 5538.36788889 & 5536.92932748 & 5550.91639342 & 3.57079951 \\
-    BeesA & 5534.57516657 & 5537.97495231 & 5537.04824684 & 5548.55587234 & 3.28239740 \\
-      FFA & 5534.57401617 & 5534.58849395 & 5534.58435493 & 5534.63296149 & 0.01341777 \\
-      PSO & 5534.57345480 & 5534.57381593 & 5534.57355270 & 5534.57625290 & 0.00053848 \\
-\bottomrule
-\end{tabular}
-}
-\end{table}
-
-\begin{figure}[H]
-\centering
-\caption{Boxplot for Pressure Vessel Design}
-\label{fig:pressure_vessel_design_boxplot}
-\includegraphics[scale=0.5]{images/pressure_vessel_problem_boxplot.png}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\caption{Convergence lines for Pressure Vessel Design}
-\label{fig:pressure_vessel_problem_convergence}
-\includegraphics[width=0.4 \textwidth]{images/pressure_vessel_problem_convergence.png}
-\end{figure}
-
-\subsection{Significance Test}
-\label{subsec:pressure_vessel_problem_significance_test}
+The Table~\ref{friedman_test} resumes the Friedman's Chi-Squared Test made using
+the 6 samples took by the algorithm's best results fore each run:
 
@@
 \toprule
-                          Problem &   Statistics &    p-value \\
+                          Problem &   Rank &    p-value \\
 \midrule
+Pressure Vessel Design (Original) & 425.07428571 & 0.00000000 \\
+           Pressure Vessel Design & 436.16000000 & 0.00000000 \\
             Spring Tension Design & 339.05714286 & 0.00000000 \\
-           Pressure Vessel Design & 436.16000000 & 0.00000000 \\
-Pressure Vessel Design (Original) & 425.07428571 & 0.00000000 \\
 \bottomrule
-\end{tabular}
-}
+\end{tabular}}
 \end{table}
 
-\section{Discussion}
-
-The main objective of this work is demonstrate the inner work of a optimization class of algorithms called \textit{Quasi-Newton algorithms}.
-Four of them are presented, along with the results and analysis regarding convergence, function evaluations and function objective values.
-
-For implementation, it was decided to put constraints on search space, because for the original search space of some functions, like Ackley and Rastrigin, there are other minimas that will confuse every algorithm tested for this paper, and there is no sense on test a local minima procedure on these conditions.
-To restrain the initial solution to some region in the search space was a cheap and ready solution to avoid the algorithms to stop because of stumbling upon the wrong minimum.
-
-The \textit{Levenberg-Marquardt Algorithm} implemented for this paper is very sensitive to hyperparameters, namely $\alpha$ and $\lambda$, which was not tunned to every function, so, the conspicuous performance variation is noticeable along the results.
-LMA is known to be fast and reliable, but in our implementation it was found a little tricky to get the hyperparameters right for all the test functions.
-But for Rosenbrock and Rastrigin, it is the best option, even for lame implementations like ours.
-
-The \textit{Broyden–Fletcher–Goldfarb–Shanno} Algorithm was the only one that we decided to use it as is from \textit{SciPy}, because it has features desired for this work, like counting of function evaluations, gradient evaluation and iterations.
-It performed very well for Ackley and Booth Functions, and reasonably well for other functions.
-
-The \textit{Davidon–Fletcher–Powell} Algorithm is not implemented in \textit{SciPy} but its equations shows that it is the dual of BFGS, so, it was easy to implement using some \textit{SciPy} code for BFGS algorithm.
-In the DFP procedure, there is a Hessian inversion to be evaluated every iteration, then, numerical imprecision would be taken into consideration evaluating its results.
-While in some cases it has a superb performance (Like Ackley Function), it has very poor performance in Rosenbrock Function and even in Beale Function.
-The increase of dimensions makes DFP suffer of numerical imprecision due to the Hessian inversion, except for Rastrigin, and it is the loser algorithm in other functions.
-
-Finally, the \textit{Limited memory BFGS} has an average performance among the functions.
-The original algorithm was implemented using code found in the url https://github.com/qkolj/L-BFGS/blob/master/L-BFGS.ipynb.
-
-In fact, there are no Quasi-Newton algorithms that solver the minima problem for an any function.
-From the standpoint of performance and convergence, all the algorithms have an average performance and a reasonable convergence, although we have to restrain the search space to a small area near the optimal solution.
-
-\end{document}
+Using the interpretation rules, since the p-value is less than $0.05$, the null hypotesis $H_0$
+is rejected and each problem have at least one population with different mean from the rest.
+Thus, not all algorithms gives the same result for the same problem.

### 2023-01-21 release/code/latex/includes/header.tex
Release Added

--- 2023-01-19 latex/article.tex
@@
 reach the literature results.
+
+\subsubsection{Spring Tension Design}
+\label{subsubsec:methodology-spring-tension-design}
+From \textit{Nature-Inspired Metaheuristic Algorithms - Xin-She Yang} -
+The design of a tension and compression spring is a well-known benchmark
+optimization problem.
+The main aim is to minimize the weight subject
+to constraints on deflection, stress, surge frequency and geometry. It involves
+three design variables: the wire diameter $x_1$ , coil diameter $x_2$ and
+number/length of the coil $x_3$.
+This problem is summarized as:
+
+\begin{equation}
+    f (x) = x_1^2 x_2 (2 + x_3)
+\end{equation}
+
+subject to
+
+\begin{equation}
+    \begin{split}
+        g_1(x) = \frac{x_2^3 x_3}{71785 x_1^4} \leq 0\\
+        g_2(x) = \frac{4 x_2^2 - x_1 x_2}{12566 \left( x_1^3 x_2 - x_1^4\right)}\\
+        + \frac{1}{5108 x_1^2} -1 \leq 0\\
+        g_3(x) = 1 - \frac{140.45 x_1}{x_2^2 x_3} \leq 0\\
+        g_4 = \frac{x_1 + x_2}{1.5} - 1 \leq 0
+    \end{split}
+\end{equation}
+
+The original bounding limits of the variables, extracted from computational work
+statements, are:
+
+\begin{equation}
+    \begin{split}
+        0.05 \leq x_1 \leq 2.0\\
+        0.25 \leq x_2 \leq 1.3\\
+        2.0 \leq x_3 \leq 15.0
+    \end{split}
+\end{equation}
 
@@
 \label{sec:results}
-\subsection{Spring Tension Design}
-\label{ssubec:spring_problem}
-
-\begin{table}[H]
-\centering
-\caption{Statistical Information about function values for Spring Tension Design}
-\label{function_values:spring_problem}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrrrrr}
-\toprule
-Algorithm &      Min F &     Mean F &   Median F &      Max F &   StdDev F \\
-\midrule
-       EP & 0.01250534 & 0.01255960 & 0.01253156 & 0.01453933 & 0.00020190 \\
-       ES & 0.01252956 & 0.01281857 & 0.01274283 & 0.01346214 & 0.00024181 \\
-       GA & 0.01252305 & 0.01628575 & 0.01616768 & 0.02561808 & 0.00273276 \\
-    BeesA & 0.01250200 & 0.01268010 & 0.01261691 & 0.01406679 & 0.00021629 \\
-      FFA & 0.01249803 & 0.01254780 & 0.01253499 & 0.01268116 & 0.00003152 \\
-      PSO & 0.01252626 & 0.01390866 & 0.01318774 & 0.03036537 & 0.00342240 \\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{figure}[H]
-\centering
-\caption{Boxplot for Spring Tension Design}
-\label{fig:spring_tension_design_boxplot}
-\includegraphics[scale=0.5]{images/spring_problem_boxplot.png}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\caption{Convergence lines for Spring Tension Design}
-\label{fig:spring_problem_convergence}
-\includegraphics[width= 0.4 \textwidth]{images/spring_problem_convergence.png}
-\end{figure}
-
-\subsection{Pressure Vessel Design (Original)}
-\label{subsec:pressure_vessel_problem_original}
-
-\begin{table}[H]
-\centering
-\caption{Statistical Information about function values for Pressure Vessel Design (Original)}
-\label{function_values:pressure_vessel_problem_original}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrrrrr}
-\toprule
-Algorithm &         Min F &         Mean F &       Median F &          Max F &       StdDev F \\
-\midrule
-       EP &    0.08150806 &     0.15642850 &     0.09093798 &     1.32637552 &     0.16807714 \\
-       ES &    0.08161190 &   718.92910990 &     1.00278859 &  9443.54269260 &  2060.07774212 \\
-       GA &   17.06920868 &   525.00734162 &   361.53879602 &  3112.03503082 &   454.52386703 \\
-    BeesA & 2393.70106213 & 17564.33024022 & 15751.91467117 & 53850.38271384 & 10514.60780411 \\
-      FFA &    0.08306113 &     0.13296127 &     0.13106271 &     0.20084847 &     0.02396876 \\
-      PSO &    0.08149204 &     0.24191732 &     0.08159173 &    10.00611523 &     1.00072349 \\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{figure}[H]
-\centering
-\caption{Boxplot for Pressure Vessel Design (Original)}
-\label{fig:pressure_vessel_design_original_boxplot}
-\includegraphics[scale=0.5]{images/pressure_vessel_problem_original_boxplot.png}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\caption{Convergence lines for Pressure Vessel Design (Original)}
-\label{fig:pressure_vessel_problem_original_convergence}
-\includegraphics[width= 0.4 \textwidth]{images/pressure_vessel_problem_original_convergence.png}
-\end{figure}
-
-\subsection{Pressure Vessel Design}
-\label{subsec:pressure_vessel_problem}
-
-\begin{table}
-\centering
-\caption{Statistical Information about function values for Pressure Vessel Design}
-\label{function_values:pressure_vessel_problem}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrrrrr}
-\toprule
-Algorithm &         Min F &        Mean F &      Median F &         Max F &   StdDev F \\
-\midrule
-       EP & 5534.57345496 & 5534.63426098 & 5534.61416291 & 5534.92993607 & 0.05804548 \\
-       ES & 5534.57917966 & 5535.28165367 & 5535.06149254 & 5538.03003895 & 0.65098467 \\
-       GA & 5534.83662424 & 5538.36788889 & 5536.92932748 & 5550.91639342 & 3.57079951 \\
-    BeesA & 5534.57516657 & 5537.97495231 & 5537.04824684 & 5548.55587234 & 3.28239740 \\
-      FFA & 5534.57401617 & 5534.58849395 & 5534.58435493 & 5534.63296149 & 0.01341777 \\
-      PSO & 5534.57345480 & 5534.57381593 & 5534.57355270 & 5534.57625290 & 0.00053848 \\
-\bottomrule
-\end{tabular}
-}
-\end{table}
-
-\begin{figure}[H]
-\centering
-\caption{Boxplot for Pressure Vessel Design}
-\label{fig:pressure_vessel_design_boxplot}
-\includegraphics[scale=0.5]{images/pressure_vessel_problem_boxplot.png}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\caption{Convergence lines for Pressure Vessel Design}
-\label{fig:pressure_vessel_problem_convergence}
-\includegraphics[width=0.4 \textwidth]{images/pressure_vessel_problem_convergence.png}
-\end{figure}
-
-\subsection{Significance Test}
-\label{subsec:pressure_vessel_problem_significance_test}
-
-\begin{table}[H]
-\centering
-\caption{Significance Test Using Friedman Chi-Squared Test}
-\label{friedman_test}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrr}
-\toprule
-                          Problem &   Statistics &    p-value \\
-\midrule
-            Spring Tension Design & 339.05714286 & 0.00000000 \\
-           Pressure Vessel Design & 436.16000000 & 0.00000000 \\
-Pressure Vessel Design (Original) & 425.07428571 & 0.00000000 \\
-\bottomrule
-\end{tabular}
-}
-\end{table}
-
-\section{Discussion}
-
-The main objective of this work is demonstrate the inner work of a optimization class of algorithms called \textit{Quasi-Newton algorithms}.
-Four of them are presented, along with the results and analysis regarding convergence, function evaluations and function objective values.
-
-For implementation, it was decided to put constraints on search space, because for the original search space of some functions, like Ackley and Rastrigin, there are other minimas that will confuse every algorithm tested for this paper, and there is no sense on test a local minima procedure on these conditions.
-To restrain the initial solution to some region in the search space was a cheap and ready solution to avoid the algorithms to stop because of stumbling upon the wrong minimum.
-
-The \textit{Levenberg-Marquardt Algorithm} implemented for this paper is very sensitive to hyperparameters, namely $\alpha$ and $\lambda$, which was not tunned to every function, so, the conspicuous performance variation is noticeable along the results.
-LMA is known to be fast and reliable, but in our implementation it was found a little tricky to get the hyperparameters right for all the test functions.
-But for Rosenbrock and Rastrigin, it is the best option, even for lame implementations like ours.
-
-The \textit{Broyden–Fletcher–Goldfarb–Shanno} Algorithm was the only one that we decided to use it as is from \textit{SciPy}, because it has features desired for this work, like counting of function evaluations, gradient evaluation and iterations.
-It performed very well for Ackley and Booth Functions, and reasonably well for other functions.
-
-The \textit{Davidon–Fletcher–Powell} Algorithm is not implemented in \textit{SciPy} but its equations shows that it is the dual of BFGS, so, it was easy to implement using some \textit{SciPy} code for BFGS algorithm.
-In the DFP procedure, there is a Hessian inversion to be evaluated every iteration, then, numerical imprecision would be taken into consideration evaluating its results.
-While in some cases it has a superb performance (Like Ackley Function), it has very poor performance in Rosenbrock Function and even in Beale Function.
-The increase of dimensions makes DFP suffer of numerical imprecision due to the Hessian inversion, except for Rastrigin, and it is the loser algorithm in other functions.
-
-Finally, the \textit{Limited memory BFGS} has an average performance among the functions.
-The original algorithm was implemented using code found in the url https://github.com/qkolj/L-BFGS/blob/master/L-BFGS.ipynb.
-
-In fact, there are no Quasi-Newton algorithms that solver the minima problem for an any function.
-From the standpoint of performance and convergence, all the algorithms have an average performance and a reasonable convergence, although we have to restrain the search space to a small area near the optimal solution.
-
-\end{document}

### 2023-01-21 release/code/latex/includes/pressure_vessel_problem.tex
Release Added

--- 2023-01-19 latex/article.tex
@@
-\documentclass[conference]{IEEEtran}
-\IEEEoverridecommandlockouts
-% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-\usepackage{cite}
-\usepackage{amsmath,amssymb,amsfonts}
-\usepackage{mathtools}
-\usepackage{algpseudocode}
-\usepackage{algorithm}
-\usepackage{algorithmicx}
-\usepackage{microtype}
-\usepackage{float}
-\usepackage{adjustbox}
-\usepackage{booktabs,makecell,tabularx}
-\usepackage{graphicx}
-\usepackage{textcomp}
-\usepackage{verbatim}
-\usepackage{xcolor}
-\usepackage{graphics} % for pdf, bitmapped graphics files
-\usepackage{epsfig} % for postscript graphics files
-\usepackage{mathptmx} % assumes new font selection scheme installed
-\usepackage{multicol}
-\usepackage[english]{babel}
-\usepackage[T1]{fontenc}
-\restylefloat{table}
-\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
-    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
-\begin{document}
-\title{Swarm and Evolutionary Based Algorithms used for Optimization}
-\author{
-	\IEEEauthorblockN{Augusto Mathias Adams\IEEEauthorrefmark{1}, Caio Phillipe Mizerkowski\IEEEauthorrefmark{2}, Christian Piltz Araújo\IEEEauthorrefmark{3} and Vinicius Eduardo dos Reis\IEEEauthorrefmark{4}}\\
-	\IEEEauthorblockA{\IEEEauthorrefmark{1}GRR20172143, augusto.adams@ufpr.br, \IEEEauthorrefmark{2}GRR20166403, caiomizerkowski@gmail.com,\\ \IEEEauthorrefmark{3}GRR20172197, christian0294@yahoo.com.br, \IEEEauthorrefmark{4}GRR20175957, eduardo.reis02@gmail.com}
-}
-
-\maketitle
-
-\begin{abstract}
-    In this paper, a study of evolution and swarm based algorithms is presented,
-    using two classical engineering problems: \textit{Spring Tension} and \textit{Pressure Vessel
-    Designs}. The test code for the problems was made using the \textit{Python Language},
-    version 3.10 and uses \textit{MealPy} package, version 2.5.1,  to provide the algorithms.
-    The algorithms were randomly chosen from a vast list of \textit{MealPy}'s algorithms:
-    \textit{Evolutionary Programming (LevyEP)}, \textit{Evolution Strategies (OriginalES)} and
-    \textit{Genetic Algorithm (BaseGA)} from \textit{evolutionary\_based} subpackage;
-    \textit{Bees Algorithm (OriginalBeesA)}, \textit{Firefly Algorithm (OriginalFFA)} and
-    \textit{Particle Swarm Optimization (OriginalPSO)} from \textit{swarm\_based} subpackage.
-    Each problem was modeled using \textit{SciPy} package, with constraints implemented as
-    \textit{penalty functions}. Each algorithm were optimized separately to extract the best
-    solutions from each problem using the \textit{MealPy}'s \textit{Tuner} utility.
-    The results, however, are dependant of algorithm and/or problem solved and the Friedman's chi
-    squared test for similarity make it noticeable because, although the values for best fits are
-    similar, running the same algorithm with different initial conditions does not converge to similar
-    values.
-\end{abstract}
-
-\begin{IEEEkeywords}
-	Optimization Methods, Evolutionary Programming, Evolutionary and Swarm Based Strategies.
-\end{IEEEkeywords}
-
-\section{Definitions}
-\label{sec:definitions}
-
-The main objective of this paper is study evolutionary and swarm intelligence algorithms.
-We present the main concepts of these two algorithm's classes, along with the chosen algorithms
-definitions in this section. All citations made in this document are due to Swarm Intelligence classes
-and to \textit{MealPy}'s documentation, which points out the theoretical documentation for each
-implemented algorithm.
-
-\textit{\textbf{Evolution}}: From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolutionary Algorithms belong to the Evolutionary Computation
-field of study concerned with computational methods inspired by the process
-and mechanisms of biological evolution. The process of evolution by
-means of natural selection (descent with modification) was proposed by
-Darwin to account for the variety of life and its suitability (adaptive
-fit) for its environment. The mechanisms of evolution describe how
-evolution actually takes place through the modification and propagation
-of genetic material (proteins). Evolutionary Algorithms are concerned
-with investigating computational systems that resemble simplified ver-
-sions of the processes and mechanisms of evolution toward achieving
-the effects of these processes and mechanisms, namely the development
-of adaptive systems. Additional subject areas that fall within the realm
-of Evolutionary Computation are algorithms that seek to exploit the
-properties from the related fields of Population Genetics, Population
-Ecology, Coevolutionary Biology, and Developmental Biology.
-
-\textit{\textbf{Swarm Intelligence}}: From Jason Brownlee's \textit{``Clever Algorithms''} -
-Swarm intelligence is the study of computational systems inspired by
-the ‘collective intelligence’. Collective Intelligence emerges through the
-cooperation of large numbers of homogeneous agents in the environment.
-Examples include schools of fish, flocks of birds, and colonies of ants.
-Such intelligence is decentralized, self-organizing and distributed through
-out an environment. In nature such systems are commonly used to
-solve problems such as effective foraging for food, prey evading, or
-colony re-location. The information is typically stored throughout the
-participating homogeneous agents, or is stored or communicated in
-the environment itself such as through the use of pheromones in ants,
-dancing in bees, and proximity in fish and birds.
-
-\textit{\textbf{Evolutionary Programming:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolutionary Programming is a Global Optimization algorithm and is an instance of an Evolutionary
-Algorithm from the field of Evolutionary Computation. The approach is a sibling of other Evolutionary
-Algorithms such as the Genetic Algorithm, and Learning Classifier Systems. It is sometimes confused with Genetic
-Programming given the similarity in name, and more recently it shows a strong functional similarity to Evolution Strategies.
-Evolutionary Programming is inspired by the theory of evolution by means of natural selection. Specifically, the technique is inspired by
-macro-level or the species-level process of evolution (phenotype, hereditary, variation) and is not concerned with the genetic mechanisms of
-evolution (genome, chromosomes, genes, alleles).
-
-\textit{\textbf{Evolutionary Strategies:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolution Strategies is a global optimization algorithm and is an instance of an Evolutionary Algorithm from the field of Evolutionary
-Computation. Evolution Strategies is a sibling technique to other Evolutionary Algorithms such as Genetic Algorithms (Section 3.2), Genetic
-Programming (Section 3.3), Learning Classifier Systems, and Evolutionary Programming. A popular descendant of
-the Evolution Strategies algorithm is the Covariance Matrix Adaptation Evolution Strategies (CMA-ES).
-
-\textit{\textbf{Genetic Algorithms:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-The Genetic Algorithm is an Adaptive Strategy and a Global Optimization technique. It is an Evolutionary Algorithm and belongs to the
-broader study of Evolutionary Computation. The Genetic Algorithm is a sibling of other Evolutionary Algorithms such as Genetic Programming,
- Evolution Strategies, Evolutionary Programming, and Learning Classifier Systems. The Genetic Algorithm is a parent of a large number of variant techniques
-and sub-fields too numerous to list. The Genetic Algorithm is inspired by population genetics (including heredity and gene frequencies),
-and evolution at the population level, as well as the Mendelian understanding of the structure (such as chromosomes, genes, alleles) and mechanisms
-(such as recombination and mutation). This is the so-called new or modern synthesis of evolutionary biology.
-
-\textit{\textbf{Particle Swarm Optimization:}} From Jason Brownlee's \textit{``Clever Algorithms''} - Particle Swarm Optimization belongs to the field of
-Swarm Intelligence and Collective Intelligence and is a sub-field of Computational Intelligence. Particle Swarm Optimization is related to other Swarm Intelligence
-algorithms such as Ant Colony Optimization and it is a baseline algorithm for many variations, too numerous to list. It is inspired by the social foraging behavior
-of some animals such as flocking behavior of birds and the schooling behavior of fish.
-
-\textit{\textbf{Firefly Algorithm:}} From Xin-She Yang \textit{``Nature-Inspired Metaheuristic Algorithms''} -
-The flashing light of fireflies is an amazing sight in the summer sky in the tropical and temperate regions. There are about two thousand firefly
-species, and most fireflies produce short and rhythmic flashes. The pattern of flashes is often unique for a particular species. The flashing light is
-produced by a process of bioluminescence, and the true functions of suchsignaling systems are still being debated. However, two fundamental functions
-of such flashes are to attract mating partners (communication), and to attract potential prey. In addition, flashing may also serve as a protective warning
-mechanism to remind potential predators of the bitter taste of fireflies. The firefly algorithm tries to mimic the attractiveness of Fireflies and has three
-basic rules:
-
-\begin{itemize}
-    \item All fireflies are unisex so that one firefly will be attracted to other
-          fireflies regardless of their sex;
-    \item Attractiveness is proportional to the their brightness, thus for any two
-          flashing fireflies, the less brighter one will move towards the brighter
-          one. The attractiveness is proportional to the brightness and they
-          both decrease as their distance increases. If there is no brighter one
-          than a particular firefly, it will move randomly;
-    \item The brightness of a firefly is affected or determined by the landscape
-          of the objective function.
-\end{itemize}
-
-\textit{\textbf{Bees Algorithm:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-The Bees Algorithm beings to Bee Inspired Algorithms and the field of Swarm Intelligence, and more broadly the fields of Computational
-Intelligence and Metaheuristics. The Bees Algorithm is related to other Bee Inspired Algorithms, such as Bee Colony Optimization, and other
-Swarm Intelligence algorithms such as Ant Colony Optimization and Particle Swarm Optimization.
-It is inspired by the foraging behavior of honey bees. Honey bees collect nectar from vast areas around their hive (more than
-10 kilometers). Bee Colonies have been observed to send bees to collect nectar from flower patches relative to the amount of food available at
-each patch. Bees communicate with each other at the hive via a waggle dance that informs other bees in the hive as to the direction, distance,
-and quality rating of food sources.
-
-\section{Methodology}
-\label{sec:methodology}
-
-\subsection{Optimization Problem Selection}
-\label{subsec:optimization-problem-selection}
-The two problems selected for this paper were \textit{Spring Tension Design} and \textit{Pressure Vessel Design}. Although it was simple
-to choose the first two problems from the computational work statements, the choice was more than justified because these aroblems are well
-known in the literature.
-Thus, the problem selection was driven by which has more than one source to compare results.
-
-\subsubsection{Spring Tension Design}
-\label{subsubsec:methodology-spring-tension-design}
-From \textit{Nature-Inspired Metaheuristic Algorithms - Xin-She Yang} -
-The design of a tension and compression spring is a well-known benchmark
-optimization problem.
-The main aim is to minimize the weight subject
-to constraints on deflection, stress, surge frequency and geometry. It involves
-three design variables: the wire diameter $x_1$ , coil diameter $x_2$ and
-number/length of the coil $x_3$.
-This problem can be summarized as:
-
-\begin{equation}
-    f (x) = x_1^2 x_2 (2 + x_3)
-\end{equation}
-
-subject to
-
-\begin{equation}
-    \begin{split}
-        g_1(x) = \frac{x_2^3 x_3}{71785 x_1^4} \leq 0\\
-        g_2(x) = \frac{4 x_2^2 - x_1 x_2}{12566 \left( x_1^3 x_2 - x_1^4\right)}\\
-        + \frac{1}{5108 x_1^2} -1 \leq 0\\
-        g_3(x) = 1 - \frac{140.45 x_1}{x_2^2 x_3} \leq 0\\
-        g_4 = \frac{x_1 + x_2}{1.5} - 1 \leq 0
-    \end{split}
-\end{equation}
-
-The original bounding limits of the variables, extracted from computational work
-statements, are:
-
-\begin{equation}
-    \begin{split}
-        0.05 \leq x_1 \leq 2.0\\
-        0.25 \leq x_2 \leq 1.3\\
-        2.0 \leq x_3 \leq 15.0
-    \end{split}
-\end{equation}
-
-\subsubsection{Pressure Vessel Design}
-\label{subsubsec:methodology-pressure-vessel-design}
-From \textit{Solving Design of Pressure Vessel Engineering
-Problem Using a Fruit Fly Optimization Algorithm - XIANTING KE et al} -
-A pressure vessel design model involves four decision variables: $x_1$ is defined
-thickness of the pressure vessel $T_s$ , $x_2$ stands for
-thickness of the head $T_H$ , $x_3$ represents inner radius of the
-vessel $R$ , and $x_4$ is on behalf of length of the vessel
-barring head $L$ , the total variables described as $( x_1 , x_2 , x_3 , x_4 )$.
-The objective function of the problem is to minimize the total cost, including
-the cost of material, forming, and welding.
-The general pressure vessel design optimization model is expressed as:
-
-\begin{equation}
-	\begin{split}
-        f(x) = 0.6224 x_1 x_3 x_4 + 1.7781 x_2 x_3^2 \\
-        + 3.1661 x_1^2 x_4 + 19.84 x_1^2 x_3
-	\end{split}
-\end{equation}
-
-subject to:
-
-\begin{equation}
-    \begin{split}
-        g_1(x) = - x_1 + 0.0193 x_3 \leq 0\\
-        g_2(x) = - x_2 + 0.00954 x_3 \leq 0\\
-        g_3(x) = - \pi x_3^2 x_4 -\frac{4}{3}\pi x_3^3 + 1296000 \leq 0\\
-        g_4(x) = x_4 -240 \leq 0\\
-    \end{split}
-\end{equation}
-
-The original bounding limits of the variables, extracted from computational work
-statements, are:
-
-\begin{equation}
-    \begin{split}
-        0 \leq x_1 \leq 99\\
-        0 \leq x_2 \leq 99\\
-        10 \leq x_3 \leq 200\\
-        10 \leq x_4 \leq 200\\
-    \end{split}
-\end{equation}
-
-For some reason these settings does not work at all with the selected optimizers, so
-some research in the literature \textit{Solving Design of Pressure Vessel Engineering
-Problem Using a Fruit Fly Optimization Algorithm - XIANTING KE et al} suggest the
-following bounding limits:
-
-\begin{equation}
-    \begin{split}
-        0.0625 \leq x_1 \leq 99 \times 0.0625\\
-        0.0625 \leq x_2 \leq 99 \times 0.0625\\
-        10 \leq x_3 \leq 200\\
-        10 \leq x_4 \leq 200
-    \end{split}
-\end{equation}
-
-But these settings produce many random, bizarre and noisy results in all selected optimizers. Then
-a proud-and-lame-homemade set of variable boundings comes in handy, obtained by tweaking the original
-boundings:
-
-\begin{equation}
-    \begin{split}
-        0.75 \leq x_1 \leq 0.8\\
-        0.35 \leq x_2 \leq 0.4\\
-        39.5 \leq x_3 \leq 41.0\\
-        195.0 \leq x_4 \leq 205.0\\
-    \end{split}
-\end{equation}
-
-It is not intended here to point out modeling errors of any kind, nor point out package
-errors made by the authors or ours, but the homemade bounding limits was necessary to
-reach the literature results.
-
-\subsection{Constraint Implementation}
-\label{subsec:methodology-constraint-implementation}
-The constraints that all problems are subjected were implemented as \textit{penalty functions},
-that is, it adds a high value when the constraint is not satisfied, zero otherwise. It is an optional requirement
-from computational work in question and is the recommended way to put constraints from \textit{MealPy}'s
-Manual.
-
-\subsection{Programming Language}
-\label{subsec:methodology-programming-language}
-
-The chosen programming language for the test code was \textit{Python Language}, version 3.10, because it is an opensource language easy to
-program and has a huge amount of packages regarding artificial intelligence, genetic algorithms and swarm based algorithms.
-From these packages it was selected \textit{MealPy} package, version 2.5.1, because it comprises all the algorithm's classed tested in this paper.
-
-\subsection{Algorithm Selection}
-\label{subsec:methodology-algorithm-selection}
-
-The algorithm selection was made in two steps: first, it was extracted simple version of the two classes (evolutionary and swarm based) and
-then it was used a simple shuffle using Python's \textit{random.shuffle} in a terminal - no script was required.
-
-The chosen algorithms were:
-
-\begin{itemize}
-    \item \textit{\textbf{Evolution Based Algorithms: }} LevyEP (Evolutionary Programming),
-    OriginalES (Evolution Strategy) and BaseGA (Genetic Algorithm)
-    \item \textit{\textbf{Swarm Based Algorithms: }} OriginalBeesA (Bees Algorithm),
-    OriginalFFA (Original Firefly Algorithm) and OriginalPSO (Particle Swarm Optimization)
-\end{itemize}
-
-\subsection{Optimizer Tuning}
-\label{subsec:methodology-optimizer-tuning}
-
-The hyperparameters for each optimizer were tuned using the \textit{MealPy}'s \textit{Tuner} utility.
-It is a recomended procedure to tune hyperparameters for each optimizer and problem, according to
-\textit{MealPy}'s Manual.
-The \textit{Tuner} utility is a very simple grid search metaheuristic search tool
-that test each grid configuration for a specified oprimizer runs.
-Although simple, it is a very expensive procedure that took 2 days to complete. It was defined 10 runs for each
-configuration, with the following set of hyperparameter:
-
-\begin{itemize}
-    \item \textit{\textbf{Evolution Based Algorithms: }}
-        \subitem \textit{LevyEP:}
-            \subsubitem \textit{bout\_size (float)}: percentage of child agents implement tournament selection.
-        \subitem \textit{OriginalES:}
-            \subsubitem \textit{lamda (float)}: Percentage of child agents evolving in the next generation.
-        \subitem \textit{BaseGA:}
-            \subsubitem \textit{pc (float)}: cross-over probability
-            \subsubitem \textit{pm (float)}: mutation probability
-    \item \textit{\textbf{Swarm Based Algorithms: }}
-        \subitem \textit{OriginalBeesA:}
-            \subsubitem \textit{selected\_site\_ratio (float)}
-            \subsubitem \textit{elite\_site\_ratio (float)}
-            \subsubitem \textit{selected\_site\_bee\_ratio (float)}
-            \subsubitem \textit{elite\_site\_bee\_ratio (float)}
-            \subsubitem \textit{dance\_radius (float)}
-            \subsubitem \textit{dance\_reduction (float)}
-        \subitem \textit{OriginalFFA:}
-            \subsubitem \textit{gamma (float)}: Light Absorption Coefficient
-            \subsubitem \textit{beta\_base (float)}: Attraction Coefficient Base Value
-            \subsubitem \textit{alpha (float)}: Mutation Coefficient
-            \subsubitem \textit{alpha\_damp (float)}: Mutation Coefficient Damp Rate
-            \subsubitem \textit{delta (float)}: Mutation Step Size
-            \subsubitem \textit{exponent (int)}: Exponent
-        \subitem \textit{OriginalPSO:}
-            \subsubitem \textit{c1 (float)}: local coefficient
-            \subsubitem \textit{c2 (float)}: global coefficient
-            \subsubitem \textit{w\_min (float)}: Weight min of bird
-            \subsubitem \textit{w\_max (float)}: Weight max of bird
-
-\end{itemize}
-
-\subsection{Optimizer Parameters}
-\label{subsec:methodology-optimizer-parameters}
-
-For all optimizers and problems, were selected the following parameters:
-
-\begin{itemize}
-    \item \textit{Runs}: 100 runs
-    \item \textit{Epochs}: 100 epochs
-    \item \textit{Population}: 100 initial points
-\end{itemize}
-
-The initial solutions were randomly selected using the same seed for all algorithms.
-
-\section{Results}
-\label{sec:results}
-\subsection{Spring Tension Design}
-\label{ssubec:spring_problem}
+Another view of the solutions are presented in Table~\ref{function_values:pressure_vessel_problem}, where
+are summarized the statistics of all 100 possible solutions for different starting points.
 
@@
 \centering
-\caption{Statistical Information about function values for Spring Tension Design}
-\label{function_values:spring_problem}
+\caption{Statistical Information about function values for Pressure Vessel Design}
 \resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrrrrr}
-\toprule
-Algorithm &      Min F &     Mean F &   Median F &      Max F &   StdDev F \\
-\midrule
-       EP & 0.01250534 & 0.01255960 & 0.01253156 & 0.01453933 & 0.00020190 \\
-       ES & 0.01252956 & 0.01281857 & 0.01274283 & 0.01346214 & 0.00024181 \\
-       GA & 0.01252305 & 0.01628575 & 0.01616768 & 0.02561808 & 0.00273276 \\
-    BeesA & 0.01250200 & 0.01268010 & 0.01261691 & 0.01406679 & 0.00021629 \\
-      FFA & 0.01249803 & 0.01254780 & 0.01253499 & 0.01268116 & 0.00003152 \\
-      PSO & 0.01252626 & 0.01390866 & 0.01318774 & 0.03036537 & 0.00342240 \\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{figure}[H]
-\centering
-\caption{Boxplot for Spring Tension Design}
-\label{fig:spring_tension_design_boxplot}
-\includegraphics[scale=0.5]{images/spring_problem_boxplot.png}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\caption{Convergence lines for Spring Tension Design}
-\label{fig:spring_problem_convergence}
-\includegraphics[width= 0.4 \textwidth]{images/spring_problem_convergence.png}
-\end{figure}
-
-\subsection{Pressure Vessel Design (Original)}
-\label{subsec:pressure_vessel_problem_original}
-
-\begin{table}[H]
-\centering
-\caption{Statistical Information about function values for Pressure Vessel Design (Original)}
-\label{function_values:pressure_vessel_problem_original}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrrrrr}
-\toprule
-Algorithm &         Min F &         Mean F &       Median F &          Max F &       StdDev F \\
-\midrule
-       EP &    0.08150806 &     0.15642850 &     0.09093798 &     1.32637552 &     0.16807714 \\
-       ES &    0.08161190 &   718.92910990 &     1.00278859 &  9443.54269260 &  2060.07774212 \\
-       GA &   17.06920868 &   525.00734162 &   361.53879602 &  3112.03503082 &   454.52386703 \\
-    BeesA & 2393.70106213 & 17564.33024022 & 15751.91467117 & 53850.38271384 & 10514.60780411 \\
-      FFA &    0.08306113 &     0.13296127 &     0.13106271 &     0.20084847 &     0.02396876 \\
-      PSO &    0.08149204 &     0.24191732 &     0.08159173 &    10.00611523 &     1.00072349 \\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{figure}[H]
-\centering
-\caption{Boxplot for Pressure Vessel Design (Original)}
-\label{fig:pressure_vessel_design_original_boxplot}
-\includegraphics[scale=0.5]{images/pressure_vessel_problem_original_boxplot.png}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\caption{Convergence lines for Pressure Vessel Design (Original)}
-\label{fig:pressure_vessel_problem_original_convergence}
-\includegraphics[width= 0.4 \textwidth]{images/pressure_vessel_problem_original_convergence.png}
-\end{figure}
-
-\subsection{Pressure Vessel Design}
-\label{subsec:pressure_vessel_problem}
-
-\begin{table}
-\centering
-\caption{Statistical Information about function values for Pressure Vessel Design}
 \label{function_values:pressure_vessel_problem}
-\resizebox{\columnwidth}{!}{%
 \begin{tabular}{lrrrrr}
@@
 \bottomrule
-\end{tabular}
-}
+\end{tabular}}
 \end{table}
 
-\begin{figure}[H]
-\centering
-\caption{Boxplot for Pressure Vessel Design}
-\label{fig:pressure_vessel_design_boxplot}
-\includegraphics[scale=0.5]{images/pressure_vessel_problem_boxplot.png}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\caption{Convergence lines for Pressure Vessel Design}
-\label{fig:pressure_vessel_problem_convergence}
-\includegraphics[width=0.4 \textwidth]{images/pressure_vessel_problem_convergence.png}
-\end{figure}
-
-\subsection{Significance Test}
-\label{subsec:pressure_vessel_problem_significance_test}
-
-\begin{table}[H]
-\centering
-\caption{Significance Test Using Friedman Chi-Squared Test}
-\label{friedman_test}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrr}
-\toprule
-                          Problem &   Statistics &    p-value \\
-\midrule
-            Spring Tension Design & 339.05714286 & 0.00000000 \\
-           Pressure Vessel Design & 436.16000000 & 0.00000000 \\
-Pressure Vessel Design (Original) & 425.07428571 & 0.00000000 \\
-\bottomrule
-\end{tabular}
-}
-\end{table}
-
-\section{Discussion}
-
-The main objective of this work is demonstrate the inner work of a optimization class of algorithms called \textit{Quasi-Newton algorithms}.
-Four of them are presented, along with the results and analysis regarding convergence, function evaluations and function objective values.
-
-For implementation, it was decided to put constraints on search space, because for the original search space of some functions, like Ackley and Rastrigin, there are other minimas that will confuse every algorithm tested for this paper, and there is no sense on test a local minima procedure on these conditions.
-To restrain the initial solution to some region in the search space was a cheap and ready solution to avoid the algorithms to stop because of stumbling upon the wrong minimum.
-
-The \textit{Levenberg-Marquardt Algorithm} implemented for this paper is very sensitive to hyperparameters, namely $\alpha$ and $\lambda$, which was not tunned to every function, so, the conspicuous performance variation is noticeable along the results.
-LMA is known to be fast and reliable, but in our implementation it was found a little tricky to get the hyperparameters right for all the test functions.
-But for Rosenbrock and Rastrigin, it is the best option, even for lame implementations like ours.
-
-The \textit{Broyden–Fletcher–Goldfarb–Shanno} Algorithm was the only one that we decided to use it as is from \textit{SciPy}, because it has features desired for this work, like counting of function evaluations, gradient evaluation and iterations.
-It performed very well for Ackley and Booth Functions, and reasonably well for other functions.
-
-The \textit{Davidon–Fletcher–Powell} Algorithm is not implemented in \textit{SciPy} but its equations shows that it is the dual of BFGS, so, it was easy to implement using some \textit{SciPy} code for BFGS algorithm.
-In the DFP procedure, there is a Hessian inversion to be evaluated every iteration, then, numerical imprecision would be taken into consideration evaluating its results.
-While in some cases it has a superb performance (Like Ackley Function), it has very poor performance in Rosenbrock Function and even in Beale Function.
-The increase of dimensions makes DFP suffer of numerical imprecision due to the Hessian inversion, except for Rastrigin, and it is the loser algorithm in other functions.
-
-Finally, the \textit{Limited memory BFGS} has an average performance among the functions.
-The original algorithm was implemented using code found in the url https://github.com/qkolj/L-BFGS/blob/master/L-BFGS.ipynb.
-
-In fact, there are no Quasi-Newton algorithms that solver the minima problem for an any function.
-From the standpoint of performance and convergence, all the algorithms have an average performance and a reasonable convergence, although we have to restrain the search space to a small area near the optimal solution.
-
-\end{document}
+It is hard to see any statistical  difference looking at any value in the table except standard deviation.
+GA and BeesA seems to have the worst solutions, and EP, FFA and PSO seems to have a well defined behavior
+since they have the lowest standard deviations, that is, all the solutions don't spread too much from each
+other.

### 2023-01-21 release/code/latex/includes/pressure_vessel_problem_best_fits.tex
Release Added

--- 2023-01-19 latex/article.tex
@@
-\documentclass[conference]{IEEEtran}
-\IEEEoverridecommandlockouts
-% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-\usepackage{cite}
-\usepackage{amsmath,amssymb,amsfonts}
-\usepackage{mathtools}
-\usepackage{algpseudocode}
-\usepackage{algorithm}
-\usepackage{algorithmicx}
-\usepackage{microtype}
-\usepackage{float}
-\usepackage{adjustbox}
-\usepackage{booktabs,makecell,tabularx}
-\usepackage{graphicx}
-\usepackage{textcomp}
-\usepackage{verbatim}
-\usepackage{xcolor}
-\usepackage{graphics} % for pdf, bitmapped graphics files
-\usepackage{epsfig} % for postscript graphics files
-\usepackage{mathptmx} % assumes new font selection scheme installed
-\usepackage{multicol}
-\usepackage[english]{babel}
-\usepackage[T1]{fontenc}
-\restylefloat{table}
-\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
-    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
-\begin{document}
-\title{Swarm and Evolutionary Based Algorithms used for Optimization}
-\author{
-	\IEEEauthorblockN{Augusto Mathias Adams\IEEEauthorrefmark{1}, Caio Phillipe Mizerkowski\IEEEauthorrefmark{2}, Christian Piltz Araújo\IEEEauthorrefmark{3} and Vinicius Eduardo dos Reis\IEEEauthorrefmark{4}}\\
-	\IEEEauthorblockA{\IEEEauthorrefmark{1}GRR20172143, augusto.adams@ufpr.br, \IEEEauthorrefmark{2}GRR20166403, caiomizerkowski@gmail.com,\\ \IEEEauthorrefmark{3}GRR20172197, christian0294@yahoo.com.br, \IEEEauthorrefmark{4}GRR20175957, eduardo.reis02@gmail.com}
-}
+In this section are presented the results for a tweaked variable boundings of Pressure Vessel Design,
+as exposed in Section~\ref{subsubsec:methodology-pressure-vessel-design}.
 
-\maketitle
-
-\begin{abstract}
-    In this paper, a study of evolution and swarm based algorithms is presented,
-    using two classical engineering problems: \textit{Spring Tension} and \textit{Pressure Vessel
-    Designs}. The test code for the problems was made using the \textit{Python Language},
-    version 3.10 and uses \textit{MealPy} package, version 2.5.1,  to provide the algorithms.
-    The algorithms were randomly chosen from a vast list of \textit{MealPy}'s algorithms:
-    \textit{Evolutionary Programming (LevyEP)}, \textit{Evolution Strategies (OriginalES)} and
-    \textit{Genetic Algorithm (BaseGA)} from \textit{evolutionary\_based} subpackage;
-    \textit{Bees Algorithm (OriginalBeesA)}, \textit{Firefly Algorithm (OriginalFFA)} and
-    \textit{Particle Swarm Optimization (OriginalPSO)} from \textit{swarm\_based} subpackage.
-    Each problem was modeled using \textit{SciPy} package, with constraints implemented as
-    \textit{penalty functions}. Each algorithm were optimized separately to extract the best
-    solutions from each problem using the \textit{MealPy}'s \textit{Tuner} utility.
-    The results, however, are dependant of algorithm and/or problem solved and the Friedman's chi
-    squared test for similarity make it noticeable because, although the values for best fits are
-    similar, running the same algorithm with different initial conditions does not converge to similar
-    values.
-\end{abstract}
-
-\begin{IEEEkeywords}
-	Optimization Methods, Evolutionary Programming, Evolutionary and Swarm Based Strategies.
-\end{IEEEkeywords}
-
-\section{Definitions}
-\label{sec:definitions}
-
-The main objective of this paper is study evolutionary and swarm intelligence algorithms.
-We present the main concepts of these two algorithm's classes, along with the chosen algorithms
-definitions in this section. All citations made in this document are due to Swarm Intelligence classes
-and to \textit{MealPy}'s documentation, which points out the theoretical documentation for each
-implemented algorithm.
-
-\textit{\textbf{Evolution}}: From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolutionary Algorithms belong to the Evolutionary Computation
-field of study concerned with computational methods inspired by the process
-and mechanisms of biological evolution. The process of evolution by
-means of natural selection (descent with modification) was proposed by
-Darwin to account for the variety of life and its suitability (adaptive
-fit) for its environment. The mechanisms of evolution describe how
-evolution actually takes place through the modification and propagation
-of genetic material (proteins). Evolutionary Algorithms are concerned
-with investigating computational systems that resemble simplified ver-
-sions of the processes and mechanisms of evolution toward achieving
-the effects of these processes and mechanisms, namely the development
-of adaptive systems. Additional subject areas that fall within the realm
-of Evolutionary Computation are algorithms that seek to exploit the
-properties from the related fields of Population Genetics, Population
-Ecology, Coevolutionary Biology, and Developmental Biology.
-
-\textit{\textbf{Swarm Intelligence}}: From Jason Brownlee's \textit{``Clever Algorithms''} -
-Swarm intelligence is the study of computational systems inspired by
-the ‘collective intelligence’. Collective Intelligence emerges through the
-cooperation of large numbers of homogeneous agents in the environment.
-Examples include schools of fish, flocks of birds, and colonies of ants.
-Such intelligence is decentralized, self-organizing and distributed through
-out an environment. In nature such systems are commonly used to
-solve problems such as effective foraging for food, prey evading, or
-colony re-location. The information is typically stored throughout the
-participating homogeneous agents, or is stored or communicated in
-the environment itself such as through the use of pheromones in ants,
-dancing in bees, and proximity in fish and birds.
-
-\textit{\textbf{Evolutionary Programming:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolutionary Programming is a Global Optimization algorithm and is an instance of an Evolutionary
-Algorithm from the field of Evolutionary Computation. The approach is a sibling of other Evolutionary
-Algorithms such as the Genetic Algorithm, and Learning Classifier Systems. It is sometimes confused with Genetic
-Programming given the similarity in name, and more recently it shows a strong functional similarity to Evolution Strategies.
-Evolutionary Programming is inspired by the theory of evolution by means of natural selection. Specifically, the technique is inspired by
-macro-level or the species-level process of evolution (phenotype, hereditary, variation) and is not concerned with the genetic mechanisms of
-evolution (genome, chromosomes, genes, alleles).
-
-\textit{\textbf{Evolutionary Strategies:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolution Strategies is a global optimization algorithm and is an instance of an Evolutionary Algorithm from the field of Evolutionary
-Computation. Evolution Strategies is a sibling technique to other Evolutionary Algorithms such as Genetic Algorithms (Section 3.2), Genetic
-Programming (Section 3.3), Learning Classifier Systems, and Evolutionary Programming. A popular descendant of
-the Evolution Strategies algorithm is the Covariance Matrix Adaptation Evolution Strategies (CMA-ES).
-
-\textit{\textbf{Genetic Algorithms:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-The Genetic Algorithm is an Adaptive Strategy and a Global Optimization technique. It is an Evolutionary Algorithm and belongs to the
-broader study of Evolutionary Computation. The Genetic Algorithm is a sibling of other Evolutionary Algorithms such as Genetic Programming,
- Evolution Strategies, Evolutionary Programming, and Learning Classifier Systems. The Genetic Algorithm is a parent of a large number of variant techniques
-and sub-fields too numerous to list. The Genetic Algorithm is inspired by population genetics (including heredity and gene frequencies),
-and evolution at the population level, as well as the Mendelian understanding of the structure (such as chromosomes, genes, alleles) and mechanisms
-(such as recombination and mutation). This is the so-called new or modern synthesis of evolutionary biology.
-
-\textit{\textbf{Particle Swarm Optimization:}} From Jason Brownlee's \textit{``Clever Algorithms''} - Particle Swarm Optimization belongs to the field of
-Swarm Intelligence and Collective Intelligence and is a sub-field of Computational Intelligence. Particle Swarm Optimization is related to other Swarm Intelligence
-algorithms such as Ant Colony Optimization and it is a baseline algorithm for many variations, too numerous to list. It is inspired by the social foraging behavior
-of some animals such as flocking behavior of birds and the schooling behavior of fish.
-
-\textit{\textbf{Firefly Algorithm:}} From Xin-She Yang \textit{``Nature-Inspired Metaheuristic Algorithms''} -
-The flashing light of fireflies is an amazing sight in the summer sky in the tropical and temperate regions. There are about two thousand firefly
-species, and most fireflies produce short and rhythmic flashes. The pattern of flashes is often unique for a particular species. The flashing light is
-produced by a process of bioluminescence, and the true functions of suchsignaling systems are still being debated. However, two fundamental functions
-of such flashes are to attract mating partners (communication), and to attract potential prey. In addition, flashing may also serve as a protective warning
-mechanism to remind potential predators of the bitter taste of fireflies. The firefly algorithm tries to mimic the attractiveness of Fireflies and has three
-basic rules:
-
-\begin{itemize}
-    \item All fireflies are unisex so that one firefly will be attracted to other
-          fireflies regardless of their sex;
-    \item Attractiveness is proportional to the their brightness, thus for any two
-          flashing fireflies, the less brighter one will move towards the brighter
-          one. The attractiveness is proportional to the brightness and they
-          both decrease as their distance increases. If there is no brighter one
-          than a particular firefly, it will move randomly;
-    \item The brightness of a firefly is affected or determined by the landscape
-          of the objective function.
-\end{itemize}
-
-\textit{\textbf{Bees Algorithm:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-The Bees Algorithm beings to Bee Inspired Algorithms and the field of Swarm Intelligence, and more broadly the fields of Computational
-Intelligence and Metaheuristics. The Bees Algorithm is related to other Bee Inspired Algorithms, such as Bee Colony Optimization, and other
-Swarm Intelligence algorithms such as Ant Colony Optimization and Particle Swarm Optimization.
-It is inspired by the foraging behavior of honey bees. Honey bees collect nectar from vast areas around their hive (more than
-10 kilometers). Bee Colonies have been observed to send bees to collect nectar from flower patches relative to the amount of food available at
-each patch. Bees communicate with each other at the hive via a waggle dance that informs other bees in the hive as to the direction, distance,
-and quality rating of food sources.
-
-\section{Methodology}
-\label{sec:methodology}
-
-\subsection{Optimization Problem Selection}
-\label{subsec:optimization-problem-selection}
-The two problems selected for this paper were \textit{Spring Tension Design} and \textit{Pressure Vessel Design}. Although it was simple
-to choose the first two problems from the computational work statements, the choice was more than justified because these aroblems are well
-known in the literature.
-Thus, the problem selection was driven by which has more than one source to compare results.
-
-\subsubsection{Spring Tension Design}
-\label{subsubsec:methodology-spring-tension-design}
-From \textit{Nature-Inspired Metaheuristic Algorithms - Xin-She Yang} -
-The design of a tension and compression spring is a well-known benchmark
-optimization problem.
-The main aim is to minimize the weight subject
-to constraints on deflection, stress, surge frequency and geometry. It involves
-three design variables: the wire diameter $x_1$ , coil diameter $x_2$ and
-number/length of the coil $x_3$.
-This problem can be summarized as:
-
-\begin{equation}
-    f (x) = x_1^2 x_2 (2 + x_3)
-\end{equation}
-
-subject to
-
-\begin{equation}
-    \begin{split}
-        g_1(x) = \frac{x_2^3 x_3}{71785 x_1^4} \leq 0\\
-        g_2(x) = \frac{4 x_2^2 - x_1 x_2}{12566 \left( x_1^3 x_2 - x_1^4\right)}\\
-        + \frac{1}{5108 x_1^2} -1 \leq 0\\
-        g_3(x) = 1 - \frac{140.45 x_1}{x_2^2 x_3} \leq 0\\
-        g_4 = \frac{x_1 + x_2}{1.5} - 1 \leq 0
-    \end{split}
-\end{equation}
-
-The original bounding limits of the variables, extracted from computational work
-statements, are:
-
-\begin{equation}
-    \begin{split}
-        0.05 \leq x_1 \leq 2.0\\
-        0.25 \leq x_2 \leq 1.3\\
-        2.0 \leq x_3 \leq 15.0
-    \end{split}
-\end{equation}
-
-\subsubsection{Pressure Vessel Design}
-\label{subsubsec:methodology-pressure-vessel-design}
-From \textit{Solving Design of Pressure Vessel Engineering
-Problem Using a Fruit Fly Optimization Algorithm - XIANTING KE et al} -
-A pressure vessel design model involves four decision variables: $x_1$ is defined
-thickness of the pressure vessel $T_s$ , $x_2$ stands for
-thickness of the head $T_H$ , $x_3$ represents inner radius of the
-vessel $R$ , and $x_4$ is on behalf of length of the vessel
-barring head $L$ , the total variables described as $( x_1 , x_2 , x_3 , x_4 )$.
-The objective function of the problem is to minimize the total cost, including
-the cost of material, forming, and welding.
-The general pressure vessel design optimization model is expressed as:
-
-\begin{equation}
-	\begin{split}
-        f(x) = 0.6224 x_1 x_3 x_4 + 1.7781 x_2 x_3^2 \\
-        + 3.1661 x_1^2 x_4 + 19.84 x_1^2 x_3
-	\end{split}
-\end{equation}
-
-subject to:
-
-\begin{equation}
-    \begin{split}
-        g_1(x) = - x_1 + 0.0193 x_3 \leq 0\\
-        g_2(x) = - x_2 + 0.00954 x_3 \leq 0\\
-        g_3(x) = - \pi x_3^2 x_4 -\frac{4}{3}\pi x_3^3 + 1296000 \leq 0\\
-        g_4(x) = x_4 -240 \leq 0\\
-    \end{split}
-\end{equation}
-
-The original bounding limits of the variables, extracted from computational work
-statements, are:
-
-\begin{equation}
-    \begin{split}
-        0 \leq x_1 \leq 99\\
-        0 \leq x_2 \leq 99\\
-        10 \leq x_3 \leq 200\\
-        10 \leq x_4 \leq 200\\
-    \end{split}
-\end{equation}
-
-For some reason these settings does not work at all with the selected optimizers, so
-some research in the literature \textit{Solving Design of Pressure Vessel Engineering
-Problem Using a Fruit Fly Optimization Algorithm - XIANTING KE et al} suggest the
-following bounding limits:
-
-\begin{equation}
-    \begin{split}
-        0.0625 \leq x_1 \leq 99 \times 0.0625\\
-        0.0625 \leq x_2 \leq 99 \times 0.0625\\
-        10 \leq x_3 \leq 200\\
-        10 \leq x_4 \leq 200
-    \end{split}
-\end{equation}
-
-But these settings produce many random, bizarre and noisy results in all selected optimizers. Then
-a proud-and-lame-homemade set of variable boundings comes in handy, obtained by tweaking the original
-boundings:
-
-\begin{equation}
-    \begin{split}
-        0.75 \leq x_1 \leq 0.8\\
-        0.35 \leq x_2 \leq 0.4\\
-        39.5 \leq x_3 \leq 41.0\\
-        195.0 \leq x_4 \leq 205.0\\
-    \end{split}
-\end{equation}
-
-It is not intended here to point out modeling errors of any kind, nor point out package
-errors made by the authors or ours, but the homemade bounding limits was necessary to
-reach the literature results.
-
-\subsection{Constraint Implementation}
-\label{subsec:methodology-constraint-implementation}
-The constraints that all problems are subjected were implemented as \textit{penalty functions},
-that is, it adds a high value when the constraint is not satisfied, zero otherwise. It is an optional requirement
-from computational work in question and is the recommended way to put constraints from \textit{MealPy}'s
-Manual.
-
-\subsection{Programming Language}
-\label{subsec:methodology-programming-language}
-
-The chosen programming language for the test code was \textit{Python Language}, version 3.10, because it is an opensource language easy to
-program and has a huge amount of packages regarding artificial intelligence, genetic algorithms and swarm based algorithms.
-From these packages it was selected \textit{MealPy} package, version 2.5.1, because it comprises all the algorithm's classed tested in this paper.
-
-\subsection{Algorithm Selection}
-\label{subsec:methodology-algorithm-selection}
-
-The algorithm selection was made in two steps: first, it was extracted simple version of the two classes (evolutionary and swarm based) and
-then it was used a simple shuffle using Python's \textit{random.shuffle} in a terminal - no script was required.
-
-The chosen algorithms were:
-
-\begin{itemize}
-    \item \textit{\textbf{Evolution Based Algorithms: }} LevyEP (Evolutionary Programming),
-    OriginalES (Evolution Strategy) and BaseGA (Genetic Algorithm)
-    \item \textit{\textbf{Swarm Based Algorithms: }} OriginalBeesA (Bees Algorithm),
-    OriginalFFA (Original Firefly Algorithm) and OriginalPSO (Particle Swarm Optimization)
-\end{itemize}
-
-\subsection{Optimizer Tuning}
-\label{subsec:methodology-optimizer-tuning}
-
-The hyperparameters for each optimizer were tuned using the \textit{MealPy}'s \textit{Tuner} utility.
-It is a recomended procedure to tune hyperparameters for each optimizer and problem, according to
-\textit{MealPy}'s Manual.
-The \textit{Tuner} utility is a very simple grid search metaheuristic search tool
-that test each grid configuration for a specified oprimizer runs.
-Although simple, it is a very expensive procedure that took 2 days to complete. It was defined 10 runs for each
-configuration, with the following set of hyperparameter:
-
-\begin{itemize}
-    \item \textit{\textbf{Evolution Based Algorithms: }}
-        \subitem \textit{LevyEP:}
-            \subsubitem \textit{bout\_size (float)}: percentage of child agents implement tournament selection.
-        \subitem \textit{OriginalES:}
-            \subsubitem \textit{lamda (float)}: Percentage of child agents evolving in the next generation.
-        \subitem \textit{BaseGA:}
-            \subsubitem \textit{pc (float)}: cross-over probability
-            \subsubitem \textit{pm (float)}: mutation probability
-    \item \textit{\textbf{Swarm Based Algorithms: }}
-        \subitem \textit{OriginalBeesA:}
-            \subsubitem \textit{selected\_site\_ratio (float)}
-            \subsubitem \textit{elite\_site\_ratio (float)}
-            \subsubitem \textit{selected\_site\_bee\_ratio (float)}
-            \subsubitem \textit{elite\_site\_bee\_ratio (float)}
-            \subsubitem \textit{dance\_radius (float)}
-            \subsubitem \textit{dance\_reduction (float)}
-        \subitem \textit{OriginalFFA:}
-            \subsubitem \textit{gamma (float)}: Light Absorption Coefficient
-            \subsubitem \textit{beta\_base (float)}: Attraction Coefficient Base Value
-            \subsubitem \textit{alpha (float)}: Mutation Coefficient
-            \subsubitem \textit{alpha\_damp (float)}: Mutation Coefficient Damp Rate
-            \subsubitem \textit{delta (float)}: Mutation Step Size
-            \subsubitem \textit{exponent (int)}: Exponent
-        \subitem \textit{OriginalPSO:}
-            \subsubitem \textit{c1 (float)}: local coefficient
-            \subsubitem \textit{c2 (float)}: global coefficient
-            \subsubitem \textit{w\_min (float)}: Weight min of bird
-            \subsubitem \textit{w\_max (float)}: Weight max of bird
-
-\end{itemize}
-
-\subsection{Optimizer Parameters}
-\label{subsec:methodology-optimizer-parameters}
-
-For all optimizers and problems, were selected the following parameters:
-
-\begin{itemize}
-    \item \textit{Runs}: 100 runs
-    \item \textit{Epochs}: 100 epochs
-    \item \textit{Population}: 100 initial points
-\end{itemize}
-
-The initial solutions were randomly selected using the same seed for all algorithms.
-
-\section{Results}
-\label{sec:results}
-\subsection{Spring Tension Design}
-\label{ssubec:spring_problem}
+The best results for all algorithms are presented in Table~\ref{best_fits:pressure_vessel_problem}:
 
@@
 \centering
-\caption{Statistical Information about function values for Spring Tension Design}
-\label{function_values:spring_problem}
+\caption{Best Fits for Pressure Vessel Design}
+\label{best_fits:pressure_vessel_problem}
 \resizebox{\columnwidth}{!}{%
@@
 \toprule
-Algorithm &      Min F &     Mean F &   Median F &      Max F &   StdDev F \\
+Algorithm &      $x_1$ &      $x_2$ &       $x_3$ &        $x_4$ &         $f_x$ \\
 \midrule
-       EP & 0.01250534 & 0.01255960 & 0.01253156 & 0.01453933 & 0.00020190 \\
-       ES & 0.01252956 & 0.01281857 & 0.01274283 & 0.01346214 & 0.00024181 \\
-       GA & 0.01252305 & 0.01628575 & 0.01616768 & 0.02561808 & 0.00273276 \\
-    BeesA & 0.01250200 & 0.01268010 & 0.01261691 & 0.01406679 & 0.00021629 \\
-      FFA & 0.01249803 & 0.01254780 & 0.01253499 & 0.01268116 & 0.00003152 \\
-      PSO & 0.01252626 & 0.01390866 & 0.01318774 & 0.03036537 & 0.00342240 \\
+       EP & 0.75000000 & 0.35000000 & 40.68318345 & 195.00000000 & 5534.57345496 \\
+       ES & 0.75000000 & 0.35000000 & 40.68322151 & 195.00000000 & 5534.57917966 \\
+       GA & 0.75000816 & 0.35003661 & 40.68379662 & 195.00019653 & 5534.83662424 \\
+    BeesA & 0.75000000 & 0.35000000 & 40.68319525 & 195.00000000 & 5534.57516657 \\
+      FFA & 0.75000000 & 0.35000000 & 40.68318772 & 195.00000000 & 5534.57401617 \\
+      PSO & 0.75000000 & 0.35000000 & 40.68318348 & 195.00000000 & 5534.57345480 \\
 \bottomrule
@@
 
-\begin{figure}[H]
-\centering
-\caption{Boxplot for Spring Tension Design}
-\label{fig:spring_tension_design_boxplot}
-\includegraphics[scale=0.5]{images/spring_problem_boxplot.png}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\caption{Convergence lines for Spring Tension Design}
-\label{fig:spring_problem_convergence}
-\includegraphics[width= 0.4 \textwidth]{images/spring_problem_convergence.png}
-\end{figure}
-
-\subsection{Pressure Vessel Design (Original)}
-\label{subsec:pressure_vessel_problem_original}
-
-\begin{table}[H]
-\centering
-\caption{Statistical Information about function values for Pressure Vessel Design (Original)}
-\label{function_values:pressure_vessel_problem_original}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrrrrr}
-\toprule
-Algorithm &         Min F &         Mean F &       Median F &          Max F &       StdDev F \\
-\midrule
-       EP &    0.08150806 &     0.15642850 &     0.09093798 &     1.32637552 &     0.16807714 \\
-       ES &    0.08161190 &   718.92910990 &     1.00278859 &  9443.54269260 &  2060.07774212 \\
-       GA &   17.06920868 &   525.00734162 &   361.53879602 &  3112.03503082 &   454.52386703 \\
-    BeesA & 2393.70106213 & 17564.33024022 & 15751.91467117 & 53850.38271384 & 10514.60780411 \\
-      FFA &    0.08306113 &     0.13296127 &     0.13106271 &     0.20084847 &     0.02396876 \\
-      PSO &    0.08149204 &     0.24191732 &     0.08159173 &    10.00611523 &     1.00072349 \\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{figure}[H]
-\centering
-\caption{Boxplot for Pressure Vessel Design (Original)}
-\label{fig:pressure_vessel_design_original_boxplot}
-\includegraphics[scale=0.5]{images/pressure_vessel_problem_original_boxplot.png}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\caption{Convergence lines for Pressure Vessel Design (Original)}
-\label{fig:pressure_vessel_problem_original_convergence}
-\includegraphics[width= 0.4 \textwidth]{images/pressure_vessel_problem_original_convergence.png}
-\end{figure}
-
-\subsection{Pressure Vessel Design}
-\label{subsec:pressure_vessel_problem}
-
-\begin{table}
-\centering
-\caption{Statistical Information about function values for Pressure Vessel Design}
-\label{function_values:pressure_vessel_problem}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrrrrr}
-\toprule
-Algorithm &         Min F &        Mean F &      Median F &         Max F &   StdDev F \\
-\midrule
-       EP & 5534.57345496 & 5534.63426098 & 5534.61416291 & 5534.92993607 & 0.05804548 \\
-       ES & 5534.57917966 & 5535.28165367 & 5535.06149254 & 5538.03003895 & 0.65098467 \\
-       GA & 5534.83662424 & 5538.36788889 & 5536.92932748 & 5550.91639342 & 3.57079951 \\
-    BeesA & 5534.57516657 & 5537.97495231 & 5537.04824684 & 5548.55587234 & 3.28239740 \\
-      FFA & 5534.57401617 & 5534.58849395 & 5534.58435493 & 5534.63296149 & 0.01341777 \\
-      PSO & 5534.57345480 & 5534.57381593 & 5534.57355270 & 5534.57625290 & 0.00053848 \\
-\bottomrule
-\end{tabular}
-}
-\end{table}
-
-\begin{figure}[H]
-\centering
-\caption{Boxplot for Pressure Vessel Design}
-\label{fig:pressure_vessel_design_boxplot}
-\includegraphics[scale=0.5]{images/pressure_vessel_problem_boxplot.png}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\caption{Convergence lines for Pressure Vessel Design}
-\label{fig:pressure_vessel_problem_convergence}
-\includegraphics[width=0.4 \textwidth]{images/pressure_vessel_problem_convergence.png}
-\end{figure}
-
-\subsection{Significance Test}
-\label{subsec:pressure_vessel_problem_significance_test}
-
-\begin{table}[H]
-\centering
-\caption{Significance Test Using Friedman Chi-Squared Test}
-\label{friedman_test}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrr}
-\toprule
-                          Problem &   Statistics &    p-value \\
-\midrule
-            Spring Tension Design & 339.05714286 & 0.00000000 \\
-           Pressure Vessel Design & 436.16000000 & 0.00000000 \\
-Pressure Vessel Design (Original) & 425.07428571 & 0.00000000 \\
-\bottomrule
-\end{tabular}
-}
-\end{table}
-
-\section{Discussion}
-
-The main objective of this work is demonstrate the inner work of a optimization class of algorithms called \textit{Quasi-Newton algorithms}.
-Four of them are presented, along with the results and analysis regarding convergence, function evaluations and function objective values.
-
-For implementation, it was decided to put constraints on search space, because for the original search space of some functions, like Ackley and Rastrigin, there are other minimas that will confuse every algorithm tested for this paper, and there is no sense on test a local minima procedure on these conditions.
-To restrain the initial solution to some region in the search space was a cheap and ready solution to avoid the algorithms to stop because of stumbling upon the wrong minimum.
-
-The \textit{Levenberg-Marquardt Algorithm} implemented for this paper is very sensitive to hyperparameters, namely $\alpha$ and $\lambda$, which was not tunned to every function, so, the conspicuous performance variation is noticeable along the results.
-LMA is known to be fast and reliable, but in our implementation it was found a little tricky to get the hyperparameters right for all the test functions.
-But for Rosenbrock and Rastrigin, it is the best option, even for lame implementations like ours.
-
-The \textit{Broyden–Fletcher–Goldfarb–Shanno} Algorithm was the only one that we decided to use it as is from \textit{SciPy}, because it has features desired for this work, like counting of function evaluations, gradient evaluation and iterations.
-It performed very well for Ackley and Booth Functions, and reasonably well for other functions.
-
-The \textit{Davidon–Fletcher–Powell} Algorithm is not implemented in \textit{SciPy} but its equations shows that it is the dual of BFGS, so, it was easy to implement using some \textit{SciPy} code for BFGS algorithm.
-In the DFP procedure, there is a Hessian inversion to be evaluated every iteration, then, numerical imprecision would be taken into consideration evaluating its results.
-While in some cases it has a superb performance (Like Ackley Function), it has very poor performance in Rosenbrock Function and even in Beale Function.
-The increase of dimensions makes DFP suffer of numerical imprecision due to the Hessian inversion, except for Rastrigin, and it is the loser algorithm in other functions.
-
-Finally, the \textit{Limited memory BFGS} has an average performance among the functions.
-The original algorithm was implemented using code found in the url https://github.com/qkolj/L-BFGS/blob/master/L-BFGS.ipynb.
-
-In fact, there are no Quasi-Newton algorithms that solver the minima problem for an any function.
-From the standpoint of performance and convergence, all the algorithms have an average performance and a reasonable convergence, although we have to restrain the search space to a small area near the optimal solution.
-
-\end{document}
+It is noticeable in this table that the best results and the best minimizers are quite the same,
+so it cannot be said that all algorithms will solve the problem from this standpoint.

### 2023-01-21 release/code/latex/includes/pressure_vessel_problem_boxplot.tex
Release Added

--- 2023-01-19 latex/article.tex
@@
-\documentclass[conference]{IEEEtran}
-\IEEEoverridecommandlockouts
-% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-\usepackage{cite}
-\usepackage{amsmath,amssymb,amsfonts}
-\usepackage{mathtools}
-\usepackage{algpseudocode}
-\usepackage{algorithm}
-\usepackage{algorithmicx}
-\usepackage{microtype}
-\usepackage{float}
-\usepackage{adjustbox}
-\usepackage{booktabs,makecell,tabularx}
-\usepackage{graphicx}
-\usepackage{textcomp}
-\usepackage{verbatim}
-\usepackage{xcolor}
-\usepackage{graphics} % for pdf, bitmapped graphics files
-\usepackage{epsfig} % for postscript graphics files
-\usepackage{mathptmx} % assumes new font selection scheme installed
-\usepackage{multicol}
-\usepackage[english]{babel}
-\usepackage[T1]{fontenc}
-\restylefloat{table}
-\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
-    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
-\begin{document}
-\title{Swarm and Evolutionary Based Algorithms used for Optimization}
-\author{
-	\IEEEauthorblockN{Augusto Mathias Adams\IEEEauthorrefmark{1}, Caio Phillipe Mizerkowski\IEEEauthorrefmark{2}, Christian Piltz Araújo\IEEEauthorrefmark{3} and Vinicius Eduardo dos Reis\IEEEauthorrefmark{4}}\\
-	\IEEEauthorblockA{\IEEEauthorrefmark{1}GRR20172143, augusto.adams@ufpr.br, \IEEEauthorrefmark{2}GRR20166403, caiomizerkowski@gmail.com,\\ \IEEEauthorrefmark{3}GRR20172197, christian0294@yahoo.com.br, \IEEEauthorrefmark{4}GRR20175957, eduardo.reis02@gmail.com}
-}
-
-\maketitle
-
-\begin{abstract}
-    In this paper, a study of evolution and swarm based algorithms is presented,
-    using two classical engineering problems: \textit{Spring Tension} and \textit{Pressure Vessel
-    Designs}. The test code for the problems was made using the \textit{Python Language},
-    version 3.10 and uses \textit{MealPy} package, version 2.5.1,  to provide the algorithms.
-    The algorithms were randomly chosen from a vast list of \textit{MealPy}'s algorithms:
-    \textit{Evolutionary Programming (LevyEP)}, \textit{Evolution Strategies (OriginalES)} and
-    \textit{Genetic Algorithm (BaseGA)} from \textit{evolutionary\_based} subpackage;
-    \textit{Bees Algorithm (OriginalBeesA)}, \textit{Firefly Algorithm (OriginalFFA)} and
-    \textit{Particle Swarm Optimization (OriginalPSO)} from \textit{swarm\_based} subpackage.
-    Each problem was modeled using \textit{SciPy} package, with constraints implemented as
-    \textit{penalty functions}. Each algorithm were optimized separately to extract the best
-    solutions from each problem using the \textit{MealPy}'s \textit{Tuner} utility.
-    The results, however, are dependant of algorithm and/or problem solved and the Friedman's chi
-    squared test for similarity make it noticeable because, although the values for best fits are
-    similar, running the same algorithm with different initial conditions does not converge to similar
-    values.
-\end{abstract}
-
-\begin{IEEEkeywords}
-	Optimization Methods, Evolutionary Programming, Evolutionary and Swarm Based Strategies.
-\end{IEEEkeywords}
-
-\section{Definitions}
-\label{sec:definitions}
-
-The main objective of this paper is study evolutionary and swarm intelligence algorithms.
-We present the main concepts of these two algorithm's classes, along with the chosen algorithms
-definitions in this section. All citations made in this document are due to Swarm Intelligence classes
-and to \textit{MealPy}'s documentation, which points out the theoretical documentation for each
-implemented algorithm.
-
-\textit{\textbf{Evolution}}: From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolutionary Algorithms belong to the Evolutionary Computation
-field of study concerned with computational methods inspired by the process
-and mechanisms of biological evolution. The process of evolution by
-means of natural selection (descent with modification) was proposed by
-Darwin to account for the variety of life and its suitability (adaptive
-fit) for its environment. The mechanisms of evolution describe how
-evolution actually takes place through the modification and propagation
-of genetic material (proteins). Evolutionary Algorithms are concerned
-with investigating computational systems that resemble simplified ver-
-sions of the processes and mechanisms of evolution toward achieving
-the effects of these processes and mechanisms, namely the development
-of adaptive systems. Additional subject areas that fall within the realm
-of Evolutionary Computation are algorithms that seek to exploit the
-properties from the related fields of Population Genetics, Population
-Ecology, Coevolutionary Biology, and Developmental Biology.
-
-\textit{\textbf{Swarm Intelligence}}: From Jason Brownlee's \textit{``Clever Algorithms''} -
-Swarm intelligence is the study of computational systems inspired by
-the ‘collective intelligence’. Collective Intelligence emerges through the
-cooperation of large numbers of homogeneous agents in the environment.
-Examples include schools of fish, flocks of birds, and colonies of ants.
-Such intelligence is decentralized, self-organizing and distributed through
-out an environment. In nature such systems are commonly used to
-solve problems such as effective foraging for food, prey evading, or
-colony re-location. The information is typically stored throughout the
-participating homogeneous agents, or is stored or communicated in
-the environment itself such as through the use of pheromones in ants,
-dancing in bees, and proximity in fish and birds.
-
-\textit{\textbf{Evolutionary Programming:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolutionary Programming is a Global Optimization algorithm and is an instance of an Evolutionary
-Algorithm from the field of Evolutionary Computation. The approach is a sibling of other Evolutionary
-Algorithms such as the Genetic Algorithm, and Learning Classifier Systems. It is sometimes confused with Genetic
-Programming given the similarity in name, and more recently it shows a strong functional similarity to Evolution Strategies.
-Evolutionary Programming is inspired by the theory of evolution by means of natural selection. Specifically, the technique is inspired by
-macro-level or the species-level process of evolution (phenotype, hereditary, variation) and is not concerned with the genetic mechanisms of
-evolution (genome, chromosomes, genes, alleles).
-
-\textit{\textbf{Evolutionary Strategies:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolution Strategies is a global optimization algorithm and is an instance of an Evolutionary Algorithm from the field of Evolutionary
-Computation. Evolution Strategies is a sibling technique to other Evolutionary Algorithms such as Genetic Algorithms (Section 3.2), Genetic
-Programming (Section 3.3), Learning Classifier Systems, and Evolutionary Programming. A popular descendant of
-the Evolution Strategies algorithm is the Covariance Matrix Adaptation Evolution Strategies (CMA-ES).
-
-\textit{\textbf{Genetic Algorithms:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-The Genetic Algorithm is an Adaptive Strategy and a Global Optimization technique. It is an Evolutionary Algorithm and belongs to the
-broader study of Evolutionary Computation. The Genetic Algorithm is a sibling of other Evolutionary Algorithms such as Genetic Programming,
- Evolution Strategies, Evolutionary Programming, and Learning Classifier Systems. The Genetic Algorithm is a parent of a large number of variant techniques
-and sub-fields too numerous to list. The Genetic Algorithm is inspired by population genetics (including heredity and gene frequencies),
-and evolution at the population level, as well as the Mendelian understanding of the structure (such as chromosomes, genes, alleles) and mechanisms
-(such as recombination and mutation). This is the so-called new or modern synthesis of evolutionary biology.
-
-\textit{\textbf{Particle Swarm Optimization:}} From Jason Brownlee's \textit{``Clever Algorithms''} - Particle Swarm Optimization belongs to the field of
-Swarm Intelligence and Collective Intelligence and is a sub-field of Computational Intelligence. Particle Swarm Optimization is related to other Swarm Intelligence
-algorithms such as Ant Colony Optimization and it is a baseline algorithm for many variations, too numerous to list. It is inspired by the social foraging behavior
-of some animals such as flocking behavior of birds and the schooling behavior of fish.
-
-\textit{\textbf{Firefly Algorithm:}} From Xin-She Yang \textit{``Nature-Inspired Metaheuristic Algorithms''} -
-The flashing light of fireflies is an amazing sight in the summer sky in the tropical and temperate regions. There are about two thousand firefly
-species, and most fireflies produce short and rhythmic flashes. The pattern of flashes is often unique for a particular species. The flashing light is
-produced by a process of bioluminescence, and the true functions of suchsignaling systems are still being debated. However, two fundamental functions
-of such flashes are to attract mating partners (communication), and to attract potential prey. In addition, flashing may also serve as a protective warning
-mechanism to remind potential predators of the bitter taste of fireflies. The firefly algorithm tries to mimic the attractiveness of Fireflies and has three
-basic rules:
-
-\begin{itemize}
-    \item All fireflies are unisex so that one firefly will be attracted to other
-          fireflies regardless of their sex;
-    \item Attractiveness is proportional to the their brightness, thus for any two
-          flashing fireflies, the less brighter one will move towards the brighter
-          one. The attractiveness is proportional to the brightness and they
-          both decrease as their distance increases. If there is no brighter one
-          than a particular firefly, it will move randomly;
-    \item The brightness of a firefly is affected or determined by the landscape
-          of the objective function.
-\end{itemize}
-
-\textit{\textbf{Bees Algorithm:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-The Bees Algorithm beings to Bee Inspired Algorithms and the field of Swarm Intelligence, and more broadly the fields of Computational
-Intelligence and Metaheuristics. The Bees Algorithm is related to other Bee Inspired Algorithms, such as Bee Colony Optimization, and other
-Swarm Intelligence algorithms such as Ant Colony Optimization and Particle Swarm Optimization.
-It is inspired by the foraging behavior of honey bees. Honey bees collect nectar from vast areas around their hive (more than
-10 kilometers). Bee Colonies have been observed to send bees to collect nectar from flower patches relative to the amount of food available at
-each patch. Bees communicate with each other at the hive via a waggle dance that informs other bees in the hive as to the direction, distance,
-and quality rating of food sources.
-
-\section{Methodology}
-\label{sec:methodology}
-
-\subsection{Optimization Problem Selection}
-\label{subsec:optimization-problem-selection}
-The two problems selected for this paper were \textit{Spring Tension Design} and \textit{Pressure Vessel Design}. Although it was simple
-to choose the first two problems from the computational work statements, the choice was more than justified because these aroblems are well
-known in the literature.
-Thus, the problem selection was driven by which has more than one source to compare results.
-
-\subsubsection{Spring Tension Design}
-\label{subsubsec:methodology-spring-tension-design}
-From \textit{Nature-Inspired Metaheuristic Algorithms - Xin-She Yang} -
-The design of a tension and compression spring is a well-known benchmark
-optimization problem.
-The main aim is to minimize the weight subject
-to constraints on deflection, stress, surge frequency and geometry. It involves
-three design variables: the wire diameter $x_1$ , coil diameter $x_2$ and
-number/length of the coil $x_3$.
-This problem can be summarized as:
-
-\begin{equation}
-    f (x) = x_1^2 x_2 (2 + x_3)
-\end{equation}
-
-subject to
-
-\begin{equation}
-    \begin{split}
-        g_1(x) = \frac{x_2^3 x_3}{71785 x_1^4} \leq 0\\
-        g_2(x) = \frac{4 x_2^2 - x_1 x_2}{12566 \left( x_1^3 x_2 - x_1^4\right)}\\
-        + \frac{1}{5108 x_1^2} -1 \leq 0\\
-        g_3(x) = 1 - \frac{140.45 x_1}{x_2^2 x_3} \leq 0\\
-        g_4 = \frac{x_1 + x_2}{1.5} - 1 \leq 0
-    \end{split}
-\end{equation}
-
-The original bounding limits of the variables, extracted from computational work
-statements, are:
-
-\begin{equation}
-    \begin{split}
-        0.05 \leq x_1 \leq 2.0\\
-        0.25 \leq x_2 \leq 1.3\\
-        2.0 \leq x_3 \leq 15.0
-    \end{split}
-\end{equation}
-
-\subsubsection{Pressure Vessel Design}
-\label{subsubsec:methodology-pressure-vessel-design}
-From \textit{Solving Design of Pressure Vessel Engineering
-Problem Using a Fruit Fly Optimization Algorithm - XIANTING KE et al} -
-A pressure vessel design model involves four decision variables: $x_1$ is defined
-thickness of the pressure vessel $T_s$ , $x_2$ stands for
-thickness of the head $T_H$ , $x_3$ represents inner radius of the
-vessel $R$ , and $x_4$ is on behalf of length of the vessel
-barring head $L$ , the total variables described as $( x_1 , x_2 , x_3 , x_4 )$.
-The objective function of the problem is to minimize the total cost, including
-the cost of material, forming, and welding.
-The general pressure vessel design optimization model is expressed as:
-
-\begin{equation}
-	\begin{split}
-        f(x) = 0.6224 x_1 x_3 x_4 + 1.7781 x_2 x_3^2 \\
-        + 3.1661 x_1^2 x_4 + 19.84 x_1^2 x_3
-	\end{split}
-\end{equation}
-
-subject to:
-
-\begin{equation}
-    \begin{split}
-        g_1(x) = - x_1 + 0.0193 x_3 \leq 0\\
-        g_2(x) = - x_2 + 0.00954 x_3 \leq 0\\
-        g_3(x) = - \pi x_3^2 x_4 -\frac{4}{3}\pi x_3^3 + 1296000 \leq 0\\
-        g_4(x) = x_4 -240 \leq 0\\
-    \end{split}
-\end{equation}
-
-The original bounding limits of the variables, extracted from computational work
-statements, are:
-
-\begin{equation}
-    \begin{split}
-        0 \leq x_1 \leq 99\\
-        0 \leq x_2 \leq 99\\
-        10 \leq x_3 \leq 200\\
-        10 \leq x_4 \leq 200\\
-    \end{split}
-\end{equation}
-
-For some reason these settings does not work at all with the selected optimizers, so
-some research in the literature \textit{Solving Design of Pressure Vessel Engineering
-Problem Using a Fruit Fly Optimization Algorithm - XIANTING KE et al} suggest the
-following bounding limits:
-
-\begin{equation}
-    \begin{split}
-        0.0625 \leq x_1 \leq 99 \times 0.0625\\
-        0.0625 \leq x_2 \leq 99 \times 0.0625\\
-        10 \leq x_3 \leq 200\\
-        10 \leq x_4 \leq 200
-    \end{split}
-\end{equation}
-
-But these settings produce many random, bizarre and noisy results in all selected optimizers. Then
-a proud-and-lame-homemade set of variable boundings comes in handy, obtained by tweaking the original
-boundings:
-
-\begin{equation}
-    \begin{split}
-        0.75 \leq x_1 \leq 0.8\\
-        0.35 \leq x_2 \leq 0.4\\
-        39.5 \leq x_3 \leq 41.0\\
-        195.0 \leq x_4 \leq 205.0\\
-    \end{split}
-\end{equation}
-
-It is not intended here to point out modeling errors of any kind, nor point out package
-errors made by the authors or ours, but the homemade bounding limits was necessary to
-reach the literature results.
-
-\subsection{Constraint Implementation}
-\label{subsec:methodology-constraint-implementation}
-The constraints that all problems are subjected were implemented as \textit{penalty functions},
-that is, it adds a high value when the constraint is not satisfied, zero otherwise. It is an optional requirement
-from computational work in question and is the recommended way to put constraints from \textit{MealPy}'s
-Manual.
-
-\subsection{Programming Language}
-\label{subsec:methodology-programming-language}
-
-The chosen programming language for the test code was \textit{Python Language}, version 3.10, because it is an opensource language easy to
-program and has a huge amount of packages regarding artificial intelligence, genetic algorithms and swarm based algorithms.
-From these packages it was selected \textit{MealPy} package, version 2.5.1, because it comprises all the algorithm's classed tested in this paper.
-
-\subsection{Algorithm Selection}
-\label{subsec:methodology-algorithm-selection}
-
-The algorithm selection was made in two steps: first, it was extracted simple version of the two classes (evolutionary and swarm based) and
-then it was used a simple shuffle using Python's \textit{random.shuffle} in a terminal - no script was required.
-
-The chosen algorithms were:
-
-\begin{itemize}
-    \item \textit{\textbf{Evolution Based Algorithms: }} LevyEP (Evolutionary Programming),
-    OriginalES (Evolution Strategy) and BaseGA (Genetic Algorithm)
-    \item \textit{\textbf{Swarm Based Algorithms: }} OriginalBeesA (Bees Algorithm),
-    OriginalFFA (Original Firefly Algorithm) and OriginalPSO (Particle Swarm Optimization)
-\end{itemize}
-
-\subsection{Optimizer Tuning}
-\label{subsec:methodology-optimizer-tuning}
-
-The hyperparameters for each optimizer were tuned using the \textit{MealPy}'s \textit{Tuner} utility.
-It is a recomended procedure to tune hyperparameters for each optimizer and problem, according to
-\textit{MealPy}'s Manual.
-The \textit{Tuner} utility is a very simple grid search metaheuristic search tool
-that test each grid configuration for a specified oprimizer runs.
-Although simple, it is a very expensive procedure that took 2 days to complete. It was defined 10 runs for each
-configuration, with the following set of hyperparameter:
-
-\begin{itemize}
-    \item \textit{\textbf{Evolution Based Algorithms: }}
-        \subitem \textit{LevyEP:}
-            \subsubitem \textit{bout\_size (float)}: percentage of child agents implement tournament selection.
-        \subitem \textit{OriginalES:}
-            \subsubitem \textit{lamda (float)}: Percentage of child agents evolving in the next generation.
-        \subitem \textit{BaseGA:}
-            \subsubitem \textit{pc (float)}: cross-over probability
-            \subsubitem \textit{pm (float)}: mutation probability
-    \item \textit{\textbf{Swarm Based Algorithms: }}
-        \subitem \textit{OriginalBeesA:}
-            \subsubitem \textit{selected\_site\_ratio (float)}
-            \subsubitem \textit{elite\_site\_ratio (float)}
-            \subsubitem \textit{selected\_site\_bee\_ratio (float)}
-            \subsubitem \textit{elite\_site\_bee\_ratio (float)}
-            \subsubitem \textit{dance\_radius (float)}
-            \subsubitem \textit{dance\_reduction (float)}
-        \subitem \textit{OriginalFFA:}
-            \subsubitem \textit{gamma (float)}: Light Absorption Coefficient
-            \subsubitem \textit{beta\_base (float)}: Attraction Coefficient Base Value
-            \subsubitem \textit{alpha (float)}: Mutation Coefficient
-            \subsubitem \textit{alpha\_damp (float)}: Mutation Coefficient Damp Rate
-            \subsubitem \textit{delta (float)}: Mutation Step Size
-            \subsubitem \textit{exponent (int)}: Exponent
-        \subitem \textit{OriginalPSO:}
-            \subsubitem \textit{c1 (float)}: local coefficient
-            \subsubitem \textit{c2 (float)}: global coefficient
-            \subsubitem \textit{w\_min (float)}: Weight min of bird
-            \subsubitem \textit{w\_max (float)}: Weight max of bird
-
-\end{itemize}
-
-\subsection{Optimizer Parameters}
-\label{subsec:methodology-optimizer-parameters}
-
-For all optimizers and problems, were selected the following parameters:
-
-\begin{itemize}
-    \item \textit{Runs}: 100 runs
-    \item \textit{Epochs}: 100 epochs
-    \item \textit{Population}: 100 initial points
-\end{itemize}
-
-The initial solutions were randomly selected using the same seed for all algorithms.
-
-\section{Results}
-\label{sec:results}
-\subsection{Spring Tension Design}
-\label{ssubec:spring_problem}
-
-\begin{table}[H]
-\centering
-\caption{Statistical Information about function values for Spring Tension Design}
-\label{function_values:spring_problem}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrrrrr}
-\toprule
-Algorithm &      Min F &     Mean F &   Median F &      Max F &   StdDev F \\
-\midrule
-       EP & 0.01250534 & 0.01255960 & 0.01253156 & 0.01453933 & 0.00020190 \\
-       ES & 0.01252956 & 0.01281857 & 0.01274283 & 0.01346214 & 0.00024181 \\
-       GA & 0.01252305 & 0.01628575 & 0.01616768 & 0.02561808 & 0.00273276 \\
-    BeesA & 0.01250200 & 0.01268010 & 0.01261691 & 0.01406679 & 0.00021629 \\
-      FFA & 0.01249803 & 0.01254780 & 0.01253499 & 0.01268116 & 0.00003152 \\
-      PSO & 0.01252626 & 0.01390866 & 0.01318774 & 0.03036537 & 0.00342240 \\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{figure}[H]
-\centering
-\caption{Boxplot for Spring Tension Design}
-\label{fig:spring_tension_design_boxplot}
-\includegraphics[scale=0.5]{images/spring_problem_boxplot.png}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\caption{Convergence lines for Spring Tension Design}
-\label{fig:spring_problem_convergence}
-\includegraphics[width= 0.4 \textwidth]{images/spring_problem_convergence.png}
-\end{figure}
-
-\subsection{Pressure Vessel Design (Original)}
-\label{subsec:pressure_vessel_problem_original}
-
-\begin{table}[H]
-\centering
-\caption{Statistical Information about function values for Pressure Vessel Design (Original)}
-\label{function_values:pressure_vessel_problem_original}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrrrrr}
-\toprule
-Algorithm &         Min F &         Mean F &       Median F &          Max F &       StdDev F \\
-\midrule
-       EP &    0.08150806 &     0.15642850 &     0.09093798 &     1.32637552 &     0.16807714 \\
-       ES &    0.08161190 &   718.92910990 &     1.00278859 &  9443.54269260 &  2060.07774212 \\
-       GA &   17.06920868 &   525.00734162 &   361.53879602 &  3112.03503082 &   454.52386703 \\
-    BeesA & 2393.70106213 & 17564.33024022 & 15751.91467117 & 53850.38271384 & 10514.60780411 \\
-      FFA &    0.08306113 &     0.13296127 &     0.13106271 &     0.20084847 &     0.02396876 \\
-      PSO &    0.08149204 &     0.24191732 &     0.08159173 &    10.00611523 &     1.00072349 \\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{figure}[H]
-\centering
-\caption{Boxplot for Pressure Vessel Design (Original)}
-\label{fig:pressure_vessel_design_original_boxplot}
-\includegraphics[scale=0.5]{images/pressure_vessel_problem_original_boxplot.png}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\caption{Convergence lines for Pressure Vessel Design (Original)}
-\label{fig:pressure_vessel_problem_original_convergence}
-\includegraphics[width= 0.4 \textwidth]{images/pressure_vessel_problem_original_convergence.png}
-\end{figure}
-
-\subsection{Pressure Vessel Design}
-\label{subsec:pressure_vessel_problem}
-
-\begin{table}
-\centering
-\caption{Statistical Information about function values for Pressure Vessel Design}
-\label{function_values:pressure_vessel_problem}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrrrrr}
-\toprule
-Algorithm &         Min F &        Mean F &      Median F &         Max F &   StdDev F \\
-\midrule
-       EP & 5534.57345496 & 5534.63426098 & 5534.61416291 & 5534.92993607 & 0.05804548 \\
-       ES & 5534.57917966 & 5535.28165367 & 5535.06149254 & 5538.03003895 & 0.65098467 \\
-       GA & 5534.83662424 & 5538.36788889 & 5536.92932748 & 5550.91639342 & 3.57079951 \\
-    BeesA & 5534.57516657 & 5537.97495231 & 5537.04824684 & 5548.55587234 & 3.28239740 \\
-      FFA & 5534.57401617 & 5534.58849395 & 5534.58435493 & 5534.63296149 & 0.01341777 \\
-      PSO & 5534.57345480 & 5534.57381593 & 5534.57355270 & 5534.57625290 & 0.00053848 \\
-\bottomrule
-\end{tabular}
-}
-\end{table}
+A quick way to access the Table~\ref{function_values:pressure_vessel_problem} is shown on Figure~\ref{fig:pressure_vessel_design_boxplot}.
 
@@
 
-\begin{figure}[H]
-\centering
-\caption{Convergence lines for Pressure Vessel Design}
-\label{fig:pressure_vessel_problem_convergence}
-\includegraphics[width=0.4 \textwidth]{images/pressure_vessel_problem_convergence.png}
-\end{figure}
-
-\subsection{Significance Test}
-\label{subsec:pressure_vessel_problem_significance_test}
-
-\begin{table}[H]
-\centering
-\caption{Significance Test Using Friedman Chi-Squared Test}
-\label{friedman_test}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrr}
-\toprule
-                          Problem &   Statistics &    p-value \\
-\midrule
-            Spring Tension Design & 339.05714286 & 0.00000000 \\
-           Pressure Vessel Design & 436.16000000 & 0.00000000 \\
-Pressure Vessel Design (Original) & 425.07428571 & 0.00000000 \\
-\bottomrule
-\end{tabular}
-}
-\end{table}
-
-\section{Discussion}
-
-The main objective of this work is demonstrate the inner work of a optimization class of algorithms called \textit{Quasi-Newton algorithms}.
-Four of them are presented, along with the results and analysis regarding convergence, function evaluations and function objective values.
-
-For implementation, it was decided to put constraints on search space, because for the original search space of some functions, like Ackley and Rastrigin, there are other minimas that will confuse every algorithm tested for this paper, and there is no sense on test a local minima procedure on these conditions.
-To restrain the initial solution to some region in the search space was a cheap and ready solution to avoid the algorithms to stop because of stumbling upon the wrong minimum.
-
-The \textit{Levenberg-Marquardt Algorithm} implemented for this paper is very sensitive to hyperparameters, namely $\alpha$ and $\lambda$, which was not tunned to every function, so, the conspicuous performance variation is noticeable along the results.
-LMA is known to be fast and reliable, but in our implementation it was found a little tricky to get the hyperparameters right for all the test functions.
-But for Rosenbrock and Rastrigin, it is the best option, even for lame implementations like ours.
-
-The \textit{Broyden–Fletcher–Goldfarb–Shanno} Algorithm was the only one that we decided to use it as is from \textit{SciPy}, because it has features desired for this work, like counting of function evaluations, gradient evaluation and iterations.
-It performed very well for Ackley and Booth Functions, and reasonably well for other functions.
-
-The \textit{Davidon–Fletcher–Powell} Algorithm is not implemented in \textit{SciPy} but its equations shows that it is the dual of BFGS, so, it was easy to implement using some \textit{SciPy} code for BFGS algorithm.
-In the DFP procedure, there is a Hessian inversion to be evaluated every iteration, then, numerical imprecision would be taken into consideration evaluating its results.
-While in some cases it has a superb performance (Like Ackley Function), it has very poor performance in Rosenbrock Function and even in Beale Function.
-The increase of dimensions makes DFP suffer of numerical imprecision due to the Hessian inversion, except for Rastrigin, and it is the loser algorithm in other functions.
-
-Finally, the \textit{Limited memory BFGS} has an average performance among the functions.
-The original algorithm was implemented using code found in the url https://github.com/qkolj/L-BFGS/blob/master/L-BFGS.ipynb.
-
-In fact, there are no Quasi-Newton algorithms that solver the minima problem for an any function.
-From the standpoint of performance and convergence, all the algorithms have an average performance and a reasonable convergence, although we have to restrain the search space to a small area near the optimal solution.
-
-\end{document}
+It shows the same information as the Table~\ref{function_values:pressure_vessel_problem}
+and it evidences that not all algorithms have the same mean, so it is a clear evidence
+that not all algorithm give similar results from an arbitrary starting point (population).

### 2023-01-21 release/code/latex/includes/pressure_vessel_problem_convergence.tex
Release Added

--- 2023-01-19 latex/article.tex
@@
-\documentclass[conference]{IEEEtran}
-\IEEEoverridecommandlockouts
-% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-\usepackage{cite}
-\usepackage{amsmath,amssymb,amsfonts}
-\usepackage{mathtools}
-\usepackage{algpseudocode}
-\usepackage{algorithm}
-\usepackage{algorithmicx}
-\usepackage{microtype}
-\usepackage{float}
-\usepackage{adjustbox}
-\usepackage{booktabs,makecell,tabularx}
-\usepackage{graphicx}
-\usepackage{textcomp}
-\usepackage{verbatim}
-\usepackage{xcolor}
-\usepackage{graphics} % for pdf, bitmapped graphics files
-\usepackage{epsfig} % for postscript graphics files
-\usepackage{mathptmx} % assumes new font selection scheme installed
-\usepackage{multicol}
-\usepackage[english]{babel}
-\usepackage[T1]{fontenc}
-\restylefloat{table}
-\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
-    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
-\begin{document}
-\title{Swarm and Evolutionary Based Algorithms used for Optimization}
-\author{
-	\IEEEauthorblockN{Augusto Mathias Adams\IEEEauthorrefmark{1}, Caio Phillipe Mizerkowski\IEEEauthorrefmark{2}, Christian Piltz Araújo\IEEEauthorrefmark{3} and Vinicius Eduardo dos Reis\IEEEauthorrefmark{4}}\\
-	\IEEEauthorblockA{\IEEEauthorrefmark{1}GRR20172143, augusto.adams@ufpr.br, \IEEEauthorrefmark{2}GRR20166403, caiomizerkowski@gmail.com,\\ \IEEEauthorrefmark{3}GRR20172197, christian0294@yahoo.com.br, \IEEEauthorrefmark{4}GRR20175957, eduardo.reis02@gmail.com}
-}
-
-\maketitle
-
-\begin{abstract}
-    In this paper, a study of evolution and swarm based algorithms is presented,
-    using two classical engineering problems: \textit{Spring Tension} and \textit{Pressure Vessel
-    Designs}. The test code for the problems was made using the \textit{Python Language},
-    version 3.10 and uses \textit{MealPy} package, version 2.5.1,  to provide the algorithms.
-    The algorithms were randomly chosen from a vast list of \textit{MealPy}'s algorithms:
-    \textit{Evolutionary Programming (LevyEP)}, \textit{Evolution Strategies (OriginalES)} and
-    \textit{Genetic Algorithm (BaseGA)} from \textit{evolutionary\_based} subpackage;
-    \textit{Bees Algorithm (OriginalBeesA)}, \textit{Firefly Algorithm (OriginalFFA)} and
-    \textit{Particle Swarm Optimization (OriginalPSO)} from \textit{swarm\_based} subpackage.
-    Each problem was modeled using \textit{SciPy} package, with constraints implemented as
-    \textit{penalty functions}. Each algorithm were optimized separately to extract the best
-    solutions from each problem using the \textit{MealPy}'s \textit{Tuner} utility.
-    The results, however, are dependant of algorithm and/or problem solved and the Friedman's chi
-    squared test for similarity make it noticeable because, although the values for best fits are
-    similar, running the same algorithm with different initial conditions does not converge to similar
-    values.
-\end{abstract}
-
-\begin{IEEEkeywords}
-	Optimization Methods, Evolutionary Programming, Evolutionary and Swarm Based Strategies.
-\end{IEEEkeywords}
-
-\section{Definitions}
-\label{sec:definitions}
-
-The main objective of this paper is study evolutionary and swarm intelligence algorithms.
-We present the main concepts of these two algorithm's classes, along with the chosen algorithms
-definitions in this section. All citations made in this document are due to Swarm Intelligence classes
-and to \textit{MealPy}'s documentation, which points out the theoretical documentation for each
-implemented algorithm.
-
-\textit{\textbf{Evolution}}: From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolutionary Algorithms belong to the Evolutionary Computation
-field of study concerned with computational methods inspired by the process
-and mechanisms of biological evolution. The process of evolution by
-means of natural selection (descent with modification) was proposed by
-Darwin to account for the variety of life and its suitability (adaptive
-fit) for its environment. The mechanisms of evolution describe how
-evolution actually takes place through the modification and propagation
-of genetic material (proteins). Evolutionary Algorithms are concerned
-with investigating computational systems that resemble simplified ver-
-sions of the processes and mechanisms of evolution toward achieving
-the effects of these processes and mechanisms, namely the development
-of adaptive systems. Additional subject areas that fall within the realm
-of Evolutionary Computation are algorithms that seek to exploit the
-properties from the related fields of Population Genetics, Population
-Ecology, Coevolutionary Biology, and Developmental Biology.
-
-\textit{\textbf{Swarm Intelligence}}: From Jason Brownlee's \textit{``Clever Algorithms''} -
-Swarm intelligence is the study of computational systems inspired by
-the ‘collective intelligence’. Collective Intelligence emerges through the
-cooperation of large numbers of homogeneous agents in the environment.
-Examples include schools of fish, flocks of birds, and colonies of ants.
-Such intelligence is decentralized, self-organizing and distributed through
-out an environment. In nature such systems are commonly used to
-solve problems such as effective foraging for food, prey evading, or
-colony re-location. The information is typically stored throughout the
-participating homogeneous agents, or is stored or communicated in
-the environment itself such as through the use of pheromones in ants,
-dancing in bees, and proximity in fish and birds.
-
-\textit{\textbf{Evolutionary Programming:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolutionary Programming is a Global Optimization algorithm and is an instance of an Evolutionary
-Algorithm from the field of Evolutionary Computation. The approach is a sibling of other Evolutionary
-Algorithms such as the Genetic Algorithm, and Learning Classifier Systems. It is sometimes confused with Genetic
-Programming given the similarity in name, and more recently it shows a strong functional similarity to Evolution Strategies.
-Evolutionary Programming is inspired by the theory of evolution by means of natural selection. Specifically, the technique is inspired by
-macro-level or the species-level process of evolution (phenotype, hereditary, variation) and is not concerned with the genetic mechanisms of
-evolution (genome, chromosomes, genes, alleles).
-
-\textit{\textbf{Evolutionary Strategies:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolution Strategies is a global optimization algorithm and is an instance of an Evolutionary Algorithm from the field of Evolutionary
-Computation. Evolution Strategies is a sibling technique to other Evolutionary Algorithms such as Genetic Algorithms (Section 3.2), Genetic
-Programming (Section 3.3), Learning Classifier Systems, and Evolutionary Programming. A popular descendant of
-the Evolution Strategies algorithm is the Covariance Matrix Adaptation Evolution Strategies (CMA-ES).
-
-\textit{\textbf{Genetic Algorithms:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-The Genetic Algorithm is an Adaptive Strategy and a Global Optimization technique. It is an Evolutionary Algorithm and belongs to the
-broader study of Evolutionary Computation. The Genetic Algorithm is a sibling of other Evolutionary Algorithms such as Genetic Programming,
- Evolution Strategies, Evolutionary Programming, and Learning Classifier Systems. The Genetic Algorithm is a parent of a large number of variant techniques
-and sub-fields too numerous to list. The Genetic Algorithm is inspired by population genetics (including heredity and gene frequencies),
-and evolution at the population level, as well as the Mendelian understanding of the structure (such as chromosomes, genes, alleles) and mechanisms
-(such as recombination and mutation). This is the so-called new or modern synthesis of evolutionary biology.
-
-\textit{\textbf{Particle Swarm Optimization:}} From Jason Brownlee's \textit{``Clever Algorithms''} - Particle Swarm Optimization belongs to the field of
-Swarm Intelligence and Collective Intelligence and is a sub-field of Computational Intelligence. Particle Swarm Optimization is related to other Swarm Intelligence
-algorithms such as Ant Colony Optimization and it is a baseline algorithm for many variations, too numerous to list. It is inspired by the social foraging behavior
-of some animals such as flocking behavior of birds and the schooling behavior of fish.
-
-\textit{\textbf{Firefly Algorithm:}} From Xin-She Yang \textit{``Nature-Inspired Metaheuristic Algorithms''} -
-The flashing light of fireflies is an amazing sight in the summer sky in the tropical and temperate regions. There are about two thousand firefly
-species, and most fireflies produce short and rhythmic flashes. The pattern of flashes is often unique for a particular species. The flashing light is
-produced by a process of bioluminescence, and the true functions of suchsignaling systems are still being debated. However, two fundamental functions
-of such flashes are to attract mating partners (communication), and to attract potential prey. In addition, flashing may also serve as a protective warning
-mechanism to remind potential predators of the bitter taste of fireflies. The firefly algorithm tries to mimic the attractiveness of Fireflies and has three
-basic rules:
-
-\begin{itemize}
-    \item All fireflies are unisex so that one firefly will be attracted to other
-          fireflies regardless of their sex;
-    \item Attractiveness is proportional to the their brightness, thus for any two
-          flashing fireflies, the less brighter one will move towards the brighter
-          one. The attractiveness is proportional to the brightness and they
-          both decrease as their distance increases. If there is no brighter one
-          than a particular firefly, it will move randomly;
-    \item The brightness of a firefly is affected or determined by the landscape
-          of the objective function.
-\end{itemize}
-
-\textit{\textbf{Bees Algorithm:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-The Bees Algorithm beings to Bee Inspired Algorithms and the field of Swarm Intelligence, and more broadly the fields of Computational
-Intelligence and Metaheuristics. The Bees Algorithm is related to other Bee Inspired Algorithms, such as Bee Colony Optimization, and other
-Swarm Intelligence algorithms such as Ant Colony Optimization and Particle Swarm Optimization.
-It is inspired by the foraging behavior of honey bees. Honey bees collect nectar from vast areas around their hive (more than
-10 kilometers). Bee Colonies have been observed to send bees to collect nectar from flower patches relative to the amount of food available at
-each patch. Bees communicate with each other at the hive via a waggle dance that informs other bees in the hive as to the direction, distance,
-and quality rating of food sources.
-
-\section{Methodology}
-\label{sec:methodology}
-
-\subsection{Optimization Problem Selection}
-\label{subsec:optimization-problem-selection}
-The two problems selected for this paper were \textit{Spring Tension Design} and \textit{Pressure Vessel Design}. Although it was simple
-to choose the first two problems from the computational work statements, the choice was more than justified because these aroblems are well
-known in the literature.
-Thus, the problem selection was driven by which has more than one source to compare results.
-
-\subsubsection{Spring Tension Design}
-\label{subsubsec:methodology-spring-tension-design}
-From \textit{Nature-Inspired Metaheuristic Algorithms - Xin-She Yang} -
-The design of a tension and compression spring is a well-known benchmark
-optimization problem.
-The main aim is to minimize the weight subject
-to constraints on deflection, stress, surge frequency and geometry. It involves
-three design variables: the wire diameter $x_1$ , coil diameter $x_2$ and
-number/length of the coil $x_3$.
-This problem can be summarized as:
-
-\begin{equation}
-    f (x) = x_1^2 x_2 (2 + x_3)
-\end{equation}
-
-subject to
-
-\begin{equation}
-    \begin{split}
-        g_1(x) = \frac{x_2^3 x_3}{71785 x_1^4} \leq 0\\
-        g_2(x) = \frac{4 x_2^2 - x_1 x_2}{12566 \left( x_1^3 x_2 - x_1^4\right)}\\
-        + \frac{1}{5108 x_1^2} -1 \leq 0\\
-        g_3(x) = 1 - \frac{140.45 x_1}{x_2^2 x_3} \leq 0\\
-        g_4 = \frac{x_1 + x_2}{1.5} - 1 \leq 0
-    \end{split}
-\end{equation}
-
-The original bounding limits of the variables, extracted from computational work
-statements, are:
-
-\begin{equation}
-    \begin{split}
-        0.05 \leq x_1 \leq 2.0\\
-        0.25 \leq x_2 \leq 1.3\\
-        2.0 \leq x_3 \leq 15.0
-    \end{split}
-\end{equation}
-
-\subsubsection{Pressure Vessel Design}
-\label{subsubsec:methodology-pressure-vessel-design}
-From \textit{Solving Design of Pressure Vessel Engineering
-Problem Using a Fruit Fly Optimization Algorithm - XIANTING KE et al} -
-A pressure vessel design model involves four decision variables: $x_1$ is defined
-thickness of the pressure vessel $T_s$ , $x_2$ stands for
-thickness of the head $T_H$ , $x_3$ represents inner radius of the
-vessel $R$ , and $x_4$ is on behalf of length of the vessel
-barring head $L$ , the total variables described as $( x_1 , x_2 , x_3 , x_4 )$.
-The objective function of the problem is to minimize the total cost, including
-the cost of material, forming, and welding.
-The general pressure vessel design optimization model is expressed as:
-
-\begin{equation}
-	\begin{split}
-        f(x) = 0.6224 x_1 x_3 x_4 + 1.7781 x_2 x_3^2 \\
-        + 3.1661 x_1^2 x_4 + 19.84 x_1^2 x_3
-	\end{split}
-\end{equation}
-
-subject to:
-
-\begin{equation}
-    \begin{split}
-        g_1(x) = - x_1 + 0.0193 x_3 \leq 0\\
-        g_2(x) = - x_2 + 0.00954 x_3 \leq 0\\
-        g_3(x) = - \pi x_3^2 x_4 -\frac{4}{3}\pi x_3^3 + 1296000 \leq 0\\
-        g_4(x) = x_4 -240 \leq 0\\
-    \end{split}
-\end{equation}
-
-The original bounding limits of the variables, extracted from computational work
-statements, are:
-
-\begin{equation}
-    \begin{split}
-        0 \leq x_1 \leq 99\\
-        0 \leq x_2 \leq 99\\
-        10 \leq x_3 \leq 200\\
-        10 \leq x_4 \leq 200\\
-    \end{split}
-\end{equation}
-
-For some reason these settings does not work at all with the selected optimizers, so
-some research in the literature \textit{Solving Design of Pressure Vessel Engineering
-Problem Using a Fruit Fly Optimization Algorithm - XIANTING KE et al} suggest the
-following bounding limits:
-
-\begin{equation}
-    \begin{split}
-        0.0625 \leq x_1 \leq 99 \times 0.0625\\
-        0.0625 \leq x_2 \leq 99 \times 0.0625\\
-        10 \leq x_3 \leq 200\\
-        10 \leq x_4 \leq 200
-    \end{split}
-\end{equation}
-
-But these settings produce many random, bizarre and noisy results in all selected optimizers. Then
-a proud-and-lame-homemade set of variable boundings comes in handy, obtained by tweaking the original
-boundings:
-
-\begin{equation}
-    \begin{split}
-        0.75 \leq x_1 \leq 0.8\\
-        0.35 \leq x_2 \leq 0.4\\
-        39.5 \leq x_3 \leq 41.0\\
-        195.0 \leq x_4 \leq 205.0\\
-    \end{split}
-\end{equation}
-
-It is not intended here to point out modeling errors of any kind, nor point out package
-errors made by the authors or ours, but the homemade bounding limits was necessary to
-reach the literature results.
-
-\subsection{Constraint Implementation}
-\label{subsec:methodology-constraint-implementation}
-The constraints that all problems are subjected were implemented as \textit{penalty functions},
-that is, it adds a high value when the constraint is not satisfied, zero otherwise. It is an optional requirement
-from computational work in question and is the recommended way to put constraints from \textit{MealPy}'s
-Manual.
-
-\subsection{Programming Language}
-\label{subsec:methodology-programming-language}
-
-The chosen programming language for the test code was \textit{Python Language}, version 3.10, because it is an opensource language easy to
-program and has a huge amount of packages regarding artificial intelligence, genetic algorithms and swarm based algorithms.
-From these packages it was selected \textit{MealPy} package, version 2.5.1, because it comprises all the algorithm's classed tested in this paper.
-
-\subsection{Algorithm Selection}
-\label{subsec:methodology-algorithm-selection}
-
-The algorithm selection was made in two steps: first, it was extracted simple version of the two classes (evolutionary and swarm based) and
-then it was used a simple shuffle using Python's \textit{random.shuffle} in a terminal - no script was required.
-
-The chosen algorithms were:
-
-\begin{itemize}
-    \item \textit{\textbf{Evolution Based Algorithms: }} LevyEP (Evolutionary Programming),
-    OriginalES (Evolution Strategy) and BaseGA (Genetic Algorithm)
-    \item \textit{\textbf{Swarm Based Algorithms: }} OriginalBeesA (Bees Algorithm),
-    OriginalFFA (Original Firefly Algorithm) and OriginalPSO (Particle Swarm Optimization)
-\end{itemize}
-
-\subsection{Optimizer Tuning}
-\label{subsec:methodology-optimizer-tuning}
-
-The hyperparameters for each optimizer were tuned using the \textit{MealPy}'s \textit{Tuner} utility.
-It is a recomended procedure to tune hyperparameters for each optimizer and problem, according to
-\textit{MealPy}'s Manual.
-The \textit{Tuner} utility is a very simple grid search metaheuristic search tool
-that test each grid configuration for a specified oprimizer runs.
-Although simple, it is a very expensive procedure that took 2 days to complete. It was defined 10 runs for each
-configuration, with the following set of hyperparameter:
-
-\begin{itemize}
-    \item \textit{\textbf{Evolution Based Algorithms: }}
-        \subitem \textit{LevyEP:}
-            \subsubitem \textit{bout\_size (float)}: percentage of child agents implement tournament selection.
-        \subitem \textit{OriginalES:}
-            \subsubitem \textit{lamda (float)}: Percentage of child agents evolving in the next generation.
-        \subitem \textit{BaseGA:}
-            \subsubitem \textit{pc (float)}: cross-over probability
-            \subsubitem \textit{pm (float)}: mutation probability
-    \item \textit{\textbf{Swarm Based Algorithms: }}
-        \subitem \textit{OriginalBeesA:}
-            \subsubitem \textit{selected\_site\_ratio (float)}
-            \subsubitem \textit{elite\_site\_ratio (float)}
-            \subsubitem \textit{selected\_site\_bee\_ratio (float)}
-            \subsubitem \textit{elite\_site\_bee\_ratio (float)}
-            \subsubitem \textit{dance\_radius (float)}
-            \subsubitem \textit{dance\_reduction (float)}
-        \subitem \textit{OriginalFFA:}
-            \subsubitem \textit{gamma (float)}: Light Absorption Coefficient
-            \subsubitem \textit{beta\_base (float)}: Attraction Coefficient Base Value
-            \subsubitem \textit{alpha (float)}: Mutation Coefficient
-            \subsubitem \textit{alpha\_damp (float)}: Mutation Coefficient Damp Rate
-            \subsubitem \textit{delta (float)}: Mutation Step Size
-            \subsubitem \textit{exponent (int)}: Exponent
-        \subitem \textit{OriginalPSO:}
-            \subsubitem \textit{c1 (float)}: local coefficient
-            \subsubitem \textit{c2 (float)}: global coefficient
-            \subsubitem \textit{w\_min (float)}: Weight min of bird
-            \subsubitem \textit{w\_max (float)}: Weight max of bird
-
-\end{itemize}
-
-\subsection{Optimizer Parameters}
-\label{subsec:methodology-optimizer-parameters}
-
-For all optimizers and problems, were selected the following parameters:
-
-\begin{itemize}
-    \item \textit{Runs}: 100 runs
-    \item \textit{Epochs}: 100 epochs
-    \item \textit{Population}: 100 initial points
-\end{itemize}
-
-The initial solutions were randomly selected using the same seed for all algorithms.
-
-\section{Results}
-\label{sec:results}
-\subsection{Spring Tension Design}
-\label{ssubec:spring_problem}
-
-\begin{table}[H]
-\centering
-\caption{Statistical Information about function values for Spring Tension Design}
-\label{function_values:spring_problem}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrrrrr}
-\toprule
-Algorithm &      Min F &     Mean F &   Median F &      Max F &   StdDev F \\
-\midrule
-       EP & 0.01250534 & 0.01255960 & 0.01253156 & 0.01453933 & 0.00020190 \\
-       ES & 0.01252956 & 0.01281857 & 0.01274283 & 0.01346214 & 0.00024181 \\
-       GA & 0.01252305 & 0.01628575 & 0.01616768 & 0.02561808 & 0.00273276 \\
-    BeesA & 0.01250200 & 0.01268010 & 0.01261691 & 0.01406679 & 0.00021629 \\
-      FFA & 0.01249803 & 0.01254780 & 0.01253499 & 0.01268116 & 0.00003152 \\
-      PSO & 0.01252626 & 0.01390866 & 0.01318774 & 0.03036537 & 0.00342240 \\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{figure}[H]
-\centering
-\caption{Boxplot for Spring Tension Design}
-\label{fig:spring_tension_design_boxplot}
-\includegraphics[scale=0.5]{images/spring_problem_boxplot.png}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\caption{Convergence lines for Spring Tension Design}
-\label{fig:spring_problem_convergence}
-\includegraphics[width= 0.4 \textwidth]{images/spring_problem_convergence.png}
-\end{figure}
-
-\subsection{Pressure Vessel Design (Original)}
-\label{subsec:pressure_vessel_problem_original}
-
-\begin{table}[H]
-\centering
-\caption{Statistical Information about function values for Pressure Vessel Design (Original)}
-\label{function_values:pressure_vessel_problem_original}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrrrrr}
-\toprule
-Algorithm &         Min F &         Mean F &       Median F &          Max F &       StdDev F \\
-\midrule
-       EP &    0.08150806 &     0.15642850 &     0.09093798 &     1.32637552 &     0.16807714 \\
-       ES &    0.08161190 &   718.92910990 &     1.00278859 &  9443.54269260 &  2060.07774212 \\
-       GA &   17.06920868 &   525.00734162 &   361.53879602 &  3112.03503082 &   454.52386703 \\
-    BeesA & 2393.70106213 & 17564.33024022 & 15751.91467117 & 53850.38271384 & 10514.60780411 \\
-      FFA &    0.08306113 &     0.13296127 &     0.13106271 &     0.20084847 &     0.02396876 \\
-      PSO &    0.08149204 &     0.24191732 &     0.08159173 &    10.00611523 &     1.00072349 \\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{figure}[H]
-\centering
-\caption{Boxplot for Pressure Vessel Design (Original)}
-\label{fig:pressure_vessel_design_original_boxplot}
-\includegraphics[scale=0.5]{images/pressure_vessel_problem_original_boxplot.png}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\caption{Convergence lines for Pressure Vessel Design (Original)}
-\label{fig:pressure_vessel_problem_original_convergence}
-\includegraphics[width= 0.4 \textwidth]{images/pressure_vessel_problem_original_convergence.png}
-\end{figure}
-
-\subsection{Pressure Vessel Design}
-\label{subsec:pressure_vessel_problem}
-
-\begin{table}
-\centering
-\caption{Statistical Information about function values for Pressure Vessel Design}
-\label{function_values:pressure_vessel_problem}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrrrrr}
-\toprule
-Algorithm &         Min F &        Mean F &      Median F &         Max F &   StdDev F \\
-\midrule
-       EP & 5534.57345496 & 5534.63426098 & 5534.61416291 & 5534.92993607 & 0.05804548 \\
-       ES & 5534.57917966 & 5535.28165367 & 5535.06149254 & 5538.03003895 & 0.65098467 \\
-       GA & 5534.83662424 & 5538.36788889 & 5536.92932748 & 5550.91639342 & 3.57079951 \\
-    BeesA & 5534.57516657 & 5537.97495231 & 5537.04824684 & 5548.55587234 & 3.28239740 \\
-      FFA & 5534.57401617 & 5534.58849395 & 5534.58435493 & 5534.63296149 & 0.01341777 \\
-      PSO & 5534.57345480 & 5534.57381593 & 5534.57355270 & 5534.57625290 & 0.00053848 \\
-\bottomrule
-\end{tabular}
-}
-\end{table}
-
-\begin{figure}[H]
-\centering
-\caption{Boxplot for Pressure Vessel Design}
-\label{fig:pressure_vessel_design_boxplot}
-\includegraphics[scale=0.5]{images/pressure_vessel_problem_boxplot.png}
-\end{figure}
+Figure~\ref{fig:pressure_vessel_problem_convergence} shows the
+function maximum, minimum and mean function of algorithm's evolution:
 
@@
 
-\subsection{Significance Test}
-\label{subsec:pressure_vessel_problem_significance_test}
-
-\begin{table}[H]
-\centering
-\caption{Significance Test Using Friedman Chi-Squared Test}
-\label{friedman_test}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrr}
-\toprule
-                          Problem &   Statistics &    p-value \\
-\midrule
-            Spring Tension Design & 339.05714286 & 0.00000000 \\
-           Pressure Vessel Design & 436.16000000 & 0.00000000 \\
-Pressure Vessel Design (Original) & 425.07428571 & 0.00000000 \\
-\bottomrule
-\end{tabular}
-}
-\end{table}
-
-\section{Discussion}
-
-The main objective of this work is demonstrate the inner work of a optimization class of algorithms called \textit{Quasi-Newton algorithms}.
-Four of them are presented, along with the results and analysis regarding convergence, function evaluations and function objective values.
-
-For implementation, it was decided to put constraints on search space, because for the original search space of some functions, like Ackley and Rastrigin, there are other minimas that will confuse every algorithm tested for this paper, and there is no sense on test a local minima procedure on these conditions.
-To restrain the initial solution to some region in the search space was a cheap and ready solution to avoid the algorithms to stop because of stumbling upon the wrong minimum.
-
-The \textit{Levenberg-Marquardt Algorithm} implemented for this paper is very sensitive to hyperparameters, namely $\alpha$ and $\lambda$, which was not tunned to every function, so, the conspicuous performance variation is noticeable along the results.
-LMA is known to be fast and reliable, but in our implementation it was found a little tricky to get the hyperparameters right for all the test functions.
-But for Rosenbrock and Rastrigin, it is the best option, even for lame implementations like ours.
-
-The \textit{Broyden–Fletcher–Goldfarb–Shanno} Algorithm was the only one that we decided to use it as is from \textit{SciPy}, because it has features desired for this work, like counting of function evaluations, gradient evaluation and iterations.
-It performed very well for Ackley and Booth Functions, and reasonably well for other functions.
-
-The \textit{Davidon–Fletcher–Powell} Algorithm is not implemented in \textit{SciPy} but its equations shows that it is the dual of BFGS, so, it was easy to implement using some \textit{SciPy} code for BFGS algorithm.
-In the DFP procedure, there is a Hessian inversion to be evaluated every iteration, then, numerical imprecision would be taken into consideration evaluating its results.
-While in some cases it has a superb performance (Like Ackley Function), it has very poor performance in Rosenbrock Function and even in Beale Function.
-The increase of dimensions makes DFP suffer of numerical imprecision due to the Hessian inversion, except for Rastrigin, and it is the loser algorithm in other functions.
-
-Finally, the \textit{Limited memory BFGS} has an average performance among the functions.
-The original algorithm was implemented using code found in the url https://github.com/qkolj/L-BFGS/blob/master/L-BFGS.ipynb.
-
-In fact, there are no Quasi-Newton algorithms that solver the minima problem for an any function.
-From the standpoint of performance and convergence, all the algorithms have an average performance and a reasonable convergence, although we have to restrain the search space to a small area near the optimal solution.
-
-\end{document}
+EP, ES and PSO quickly converges all the solution once it find a viable minimum, whe GA, BeesA and FFA
+maintain exploration and exploitation for all the epochs.
+From Table~\ref{function_values:pressure_vessel_problem},
+PSO has the best solution stability for the proud-and-lame-homemade custom bounding problem.

### 2023-01-21 release/code/latex/includes/pressure_vessel_problem_original.tex
Release Added

--- 2023-01-19 latex/article.tex
@@
-\documentclass[conference]{IEEEtran}
-\IEEEoverridecommandlockouts
-% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-\usepackage{cite}
-\usepackage{amsmath,amssymb,amsfonts}
-\usepackage{mathtools}
-\usepackage{algpseudocode}
-\usepackage{algorithm}
-\usepackage{algorithmicx}
-\usepackage{microtype}
-\usepackage{float}
-\usepackage{adjustbox}
-\usepackage{booktabs,makecell,tabularx}
-\usepackage{graphicx}
-\usepackage{textcomp}
-\usepackage{verbatim}
-\usepackage{xcolor}
-\usepackage{graphics} % for pdf, bitmapped graphics files
-\usepackage{epsfig} % for postscript graphics files
-\usepackage{mathptmx} % assumes new font selection scheme installed
-\usepackage{multicol}
-\usepackage[english]{babel}
-\usepackage[T1]{fontenc}
-\restylefloat{table}
-\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
-    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
-\begin{document}
-\title{Swarm and Evolutionary Based Algorithms used for Optimization}
-\author{
-	\IEEEauthorblockN{Augusto Mathias Adams\IEEEauthorrefmark{1}, Caio Phillipe Mizerkowski\IEEEauthorrefmark{2}, Christian Piltz Araújo\IEEEauthorrefmark{3} and Vinicius Eduardo dos Reis\IEEEauthorrefmark{4}}\\
-	\IEEEauthorblockA{\IEEEauthorrefmark{1}GRR20172143, augusto.adams@ufpr.br, \IEEEauthorrefmark{2}GRR20166403, caiomizerkowski@gmail.com,\\ \IEEEauthorrefmark{3}GRR20172197, christian0294@yahoo.com.br, \IEEEauthorrefmark{4}GRR20175957, eduardo.reis02@gmail.com}
-}
-
-\maketitle
-
-\begin{abstract}
-    In this paper, a study of evolution and swarm based algorithms is presented,
-    using two classical engineering problems: \textit{Spring Tension} and \textit{Pressure Vessel
-    Designs}. The test code for the problems was made using the \textit{Python Language},
-    version 3.10 and uses \textit{MealPy} package, version 2.5.1,  to provide the algorithms.
-    The algorithms were randomly chosen from a vast list of \textit{MealPy}'s algorithms:
-    \textit{Evolutionary Programming (LevyEP)}, \textit{Evolution Strategies (OriginalES)} and
-    \textit{Genetic Algorithm (BaseGA)} from \textit{evolutionary\_based} subpackage;
-    \textit{Bees Algorithm (OriginalBeesA)}, \textit{Firefly Algorithm (OriginalFFA)} and
-    \textit{Particle Swarm Optimization (OriginalPSO)} from \textit{swarm\_based} subpackage.
-    Each problem was modeled using \textit{SciPy} package, with constraints implemented as
-    \textit{penalty functions}. Each algorithm were optimized separately to extract the best
-    solutions from each problem using the \textit{MealPy}'s \textit{Tuner} utility.
-    The results, however, are dependant of algorithm and/or problem solved and the Friedman's chi
-    squared test for similarity make it noticeable because, although the values for best fits are
-    similar, running the same algorithm with different initial conditions does not converge to similar
-    values.
-\end{abstract}
-
-\begin{IEEEkeywords}
-	Optimization Methods, Evolutionary Programming, Evolutionary and Swarm Based Strategies.
-\end{IEEEkeywords}
-
-\section{Definitions}
-\label{sec:definitions}
-
-The main objective of this paper is study evolutionary and swarm intelligence algorithms.
-We present the main concepts of these two algorithm's classes, along with the chosen algorithms
-definitions in this section. All citations made in this document are due to Swarm Intelligence classes
-and to \textit{MealPy}'s documentation, which points out the theoretical documentation for each
-implemented algorithm.
-
-\textit{\textbf{Evolution}}: From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolutionary Algorithms belong to the Evolutionary Computation
-field of study concerned with computational methods inspired by the process
-and mechanisms of biological evolution. The process of evolution by
-means of natural selection (descent with modification) was proposed by
-Darwin to account for the variety of life and its suitability (adaptive
-fit) for its environment. The mechanisms of evolution describe how
-evolution actually takes place through the modification and propagation
-of genetic material (proteins). Evolutionary Algorithms are concerned
-with investigating computational systems that resemble simplified ver-
-sions of the processes and mechanisms of evolution toward achieving
-the effects of these processes and mechanisms, namely the development
-of adaptive systems. Additional subject areas that fall within the realm
-of Evolutionary Computation are algorithms that seek to exploit the
-properties from the related fields of Population Genetics, Population
-Ecology, Coevolutionary Biology, and Developmental Biology.
-
-\textit{\textbf{Swarm Intelligence}}: From Jason Brownlee's \textit{``Clever Algorithms''} -
-Swarm intelligence is the study of computational systems inspired by
-the ‘collective intelligence’. Collective Intelligence emerges through the
-cooperation of large numbers of homogeneous agents in the environment.
-Examples include schools of fish, flocks of birds, and colonies of ants.
-Such intelligence is decentralized, self-organizing and distributed through
-out an environment. In nature such systems are commonly used to
-solve problems such as effective foraging for food, prey evading, or
-colony re-location. The information is typically stored throughout the
-participating homogeneous agents, or is stored or communicated in
-the environment itself such as through the use of pheromones in ants,
-dancing in bees, and proximity in fish and birds.
-
-\textit{\textbf{Evolutionary Programming:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolutionary Programming is a Global Optimization algorithm and is an instance of an Evolutionary
-Algorithm from the field of Evolutionary Computation. The approach is a sibling of other Evolutionary
-Algorithms such as the Genetic Algorithm, and Learning Classifier Systems. It is sometimes confused with Genetic
-Programming given the similarity in name, and more recently it shows a strong functional similarity to Evolution Strategies.
-Evolutionary Programming is inspired by the theory of evolution by means of natural selection. Specifically, the technique is inspired by
-macro-level or the species-level process of evolution (phenotype, hereditary, variation) and is not concerned with the genetic mechanisms of
-evolution (genome, chromosomes, genes, alleles).
-
-\textit{\textbf{Evolutionary Strategies:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolution Strategies is a global optimization algorithm and is an instance of an Evolutionary Algorithm from the field of Evolutionary
-Computation. Evolution Strategies is a sibling technique to other Evolutionary Algorithms such as Genetic Algorithms (Section 3.2), Genetic
-Programming (Section 3.3), Learning Classifier Systems, and Evolutionary Programming. A popular descendant of
-the Evolution Strategies algorithm is the Covariance Matrix Adaptation Evolution Strategies (CMA-ES).
-
-\textit{\textbf{Genetic Algorithms:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-The Genetic Algorithm is an Adaptive Strategy and a Global Optimization technique. It is an Evolutionary Algorithm and belongs to the
-broader study of Evolutionary Computation. The Genetic Algorithm is a sibling of other Evolutionary Algorithms such as Genetic Programming,
- Evolution Strategies, Evolutionary Programming, and Learning Classifier Systems. The Genetic Algorithm is a parent of a large number of variant techniques
-and sub-fields too numerous to list. The Genetic Algorithm is inspired by population genetics (including heredity and gene frequencies),
-and evolution at the population level, as well as the Mendelian understanding of the structure (such as chromosomes, genes, alleles) and mechanisms
-(such as recombination and mutation). This is the so-called new or modern synthesis of evolutionary biology.
-
-\textit{\textbf{Particle Swarm Optimization:}} From Jason Brownlee's \textit{``Clever Algorithms''} - Particle Swarm Optimization belongs to the field of
-Swarm Intelligence and Collective Intelligence and is a sub-field of Computational Intelligence. Particle Swarm Optimization is related to other Swarm Intelligence
-algorithms such as Ant Colony Optimization and it is a baseline algorithm for many variations, too numerous to list. It is inspired by the social foraging behavior
-of some animals such as flocking behavior of birds and the schooling behavior of fish.
-
-\textit{\textbf{Firefly Algorithm:}} From Xin-She Yang \textit{``Nature-Inspired Metaheuristic Algorithms''} -
-The flashing light of fireflies is an amazing sight in the summer sky in the tropical and temperate regions. There are about two thousand firefly
-species, and most fireflies produce short and rhythmic flashes. The pattern of flashes is often unique for a particular species. The flashing light is
-produced by a process of bioluminescence, and the true functions of suchsignaling systems are still being debated. However, two fundamental functions
-of such flashes are to attract mating partners (communication), and to attract potential prey. In addition, flashing may also serve as a protective warning
-mechanism to remind potential predators of the bitter taste of fireflies. The firefly algorithm tries to mimic the attractiveness of Fireflies and has three
-basic rules:
-
-\begin{itemize}
-    \item All fireflies are unisex so that one firefly will be attracted to other
-          fireflies regardless of their sex;
-    \item Attractiveness is proportional to the their brightness, thus for any two
-          flashing fireflies, the less brighter one will move towards the brighter
-          one. The attractiveness is proportional to the brightness and they
-          both decrease as their distance increases. If there is no brighter one
-          than a particular firefly, it will move randomly;
-    \item The brightness of a firefly is affected or determined by the landscape
-          of the objective function.
-\end{itemize}
-
-\textit{\textbf{Bees Algorithm:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-The Bees Algorithm beings to Bee Inspired Algorithms and the field of Swarm Intelligence, and more broadly the fields of Computational
-Intelligence and Metaheuristics. The Bees Algorithm is related to other Bee Inspired Algorithms, such as Bee Colony Optimization, and other
-Swarm Intelligence algorithms such as Ant Colony Optimization and Particle Swarm Optimization.
-It is inspired by the foraging behavior of honey bees. Honey bees collect nectar from vast areas around their hive (more than
-10 kilometers). Bee Colonies have been observed to send bees to collect nectar from flower patches relative to the amount of food available at
-each patch. Bees communicate with each other at the hive via a waggle dance that informs other bees in the hive as to the direction, distance,
-and quality rating of food sources.
-
-\section{Methodology}
-\label{sec:methodology}
-
-\subsection{Optimization Problem Selection}
-\label{subsec:optimization-problem-selection}
-The two problems selected for this paper were \textit{Spring Tension Design} and \textit{Pressure Vessel Design}. Although it was simple
-to choose the first two problems from the computational work statements, the choice was more than justified because these aroblems are well
-known in the literature.
-Thus, the problem selection was driven by which has more than one source to compare results.
-
-\subsubsection{Spring Tension Design}
-\label{subsubsec:methodology-spring-tension-design}
-From \textit{Nature-Inspired Metaheuristic Algorithms - Xin-She Yang} -
-The design of a tension and compression spring is a well-known benchmark
-optimization problem.
-The main aim is to minimize the weight subject
-to constraints on deflection, stress, surge frequency and geometry. It involves
-three design variables: the wire diameter $x_1$ , coil diameter $x_2$ and
-number/length of the coil $x_3$.
-This problem can be summarized as:
-
-\begin{equation}
-    f (x) = x_1^2 x_2 (2 + x_3)
-\end{equation}
-
-subject to
-
-\begin{equation}
-    \begin{split}
-        g_1(x) = \frac{x_2^3 x_3}{71785 x_1^4} \leq 0\\
-        g_2(x) = \frac{4 x_2^2 - x_1 x_2}{12566 \left( x_1^3 x_2 - x_1^4\right)}\\
-        + \frac{1}{5108 x_1^2} -1 \leq 0\\
-        g_3(x) = 1 - \frac{140.45 x_1}{x_2^2 x_3} \leq 0\\
-        g_4 = \frac{x_1 + x_2}{1.5} - 1 \leq 0
-    \end{split}
-\end{equation}
-
-The original bounding limits of the variables, extracted from computational work
-statements, are:
-
-\begin{equation}
-    \begin{split}
-        0.05 \leq x_1 \leq 2.0\\
-        0.25 \leq x_2 \leq 1.3\\
-        2.0 \leq x_3 \leq 15.0
-    \end{split}
-\end{equation}
-
-\subsubsection{Pressure Vessel Design}
-\label{subsubsec:methodology-pressure-vessel-design}
-From \textit{Solving Design of Pressure Vessel Engineering
-Problem Using a Fruit Fly Optimization Algorithm - XIANTING KE et al} -
-A pressure vessel design model involves four decision variables: $x_1$ is defined
-thickness of the pressure vessel $T_s$ , $x_2$ stands for
-thickness of the head $T_H$ , $x_3$ represents inner radius of the
-vessel $R$ , and $x_4$ is on behalf of length of the vessel
-barring head $L$ , the total variables described as $( x_1 , x_2 , x_3 , x_4 )$.
-The objective function of the problem is to minimize the total cost, including
-the cost of material, forming, and welding.
-The general pressure vessel design optimization model is expressed as:
-
-\begin{equation}
-	\begin{split}
-        f(x) = 0.6224 x_1 x_3 x_4 + 1.7781 x_2 x_3^2 \\
-        + 3.1661 x_1^2 x_4 + 19.84 x_1^2 x_3
-	\end{split}
-\end{equation}
-
-subject to:
-
-\begin{equation}
-    \begin{split}
-        g_1(x) = - x_1 + 0.0193 x_3 \leq 0\\
-        g_2(x) = - x_2 + 0.00954 x_3 \leq 0\\
-        g_3(x) = - \pi x_3^2 x_4 -\frac{4}{3}\pi x_3^3 + 1296000 \leq 0\\
-        g_4(x) = x_4 -240 \leq 0\\
-    \end{split}
-\end{equation}
-
-The original bounding limits of the variables, extracted from computational work
-statements, are:
-
-\begin{equation}
-    \begin{split}
-        0 \leq x_1 \leq 99\\
-        0 \leq x_2 \leq 99\\
-        10 \leq x_3 \leq 200\\
-        10 \leq x_4 \leq 200\\
-    \end{split}
-\end{equation}
-
-For some reason these settings does not work at all with the selected optimizers, so
-some research in the literature \textit{Solving Design of Pressure Vessel Engineering
-Problem Using a Fruit Fly Optimization Algorithm - XIANTING KE et al} suggest the
-following bounding limits:
-
-\begin{equation}
-    \begin{split}
-        0.0625 \leq x_1 \leq 99 \times 0.0625\\
-        0.0625 \leq x_2 \leq 99 \times 0.0625\\
-        10 \leq x_3 \leq 200\\
-        10 \leq x_4 \leq 200
-    \end{split}
-\end{equation}
-
-But these settings produce many random, bizarre and noisy results in all selected optimizers. Then
-a proud-and-lame-homemade set of variable boundings comes in handy, obtained by tweaking the original
-boundings:
-
-\begin{equation}
-    \begin{split}
-        0.75 \leq x_1 \leq 0.8\\
-        0.35 \leq x_2 \leq 0.4\\
-        39.5 \leq x_3 \leq 41.0\\
-        195.0 \leq x_4 \leq 205.0\\
-    \end{split}
-\end{equation}
-
-It is not intended here to point out modeling errors of any kind, nor point out package
-errors made by the authors or ours, but the homemade bounding limits was necessary to
-reach the literature results.
-
-\subsection{Constraint Implementation}
-\label{subsec:methodology-constraint-implementation}
-The constraints that all problems are subjected were implemented as \textit{penalty functions},
-that is, it adds a high value when the constraint is not satisfied, zero otherwise. It is an optional requirement
-from computational work in question and is the recommended way to put constraints from \textit{MealPy}'s
-Manual.
-
-\subsection{Programming Language}
-\label{subsec:methodology-programming-language}
-
-The chosen programming language for the test code was \textit{Python Language}, version 3.10, because it is an opensource language easy to
-program and has a huge amount of packages regarding artificial intelligence, genetic algorithms and swarm based algorithms.
-From these packages it was selected \textit{MealPy} package, version 2.5.1, because it comprises all the algorithm's classed tested in this paper.
-
-\subsection{Algorithm Selection}
-\label{subsec:methodology-algorithm-selection}
-
-The algorithm selection was made in two steps: first, it was extracted simple version of the two classes (evolutionary and swarm based) and
-then it was used a simple shuffle using Python's \textit{random.shuffle} in a terminal - no script was required.
-
-The chosen algorithms were:
-
-\begin{itemize}
-    \item \textit{\textbf{Evolution Based Algorithms: }} LevyEP (Evolutionary Programming),
-    OriginalES (Evolution Strategy) and BaseGA (Genetic Algorithm)
-    \item \textit{\textbf{Swarm Based Algorithms: }} OriginalBeesA (Bees Algorithm),
-    OriginalFFA (Original Firefly Algorithm) and OriginalPSO (Particle Swarm Optimization)
-\end{itemize}
-
-\subsection{Optimizer Tuning}
-\label{subsec:methodology-optimizer-tuning}
-
-The hyperparameters for each optimizer were tuned using the \textit{MealPy}'s \textit{Tuner} utility.
-It is a recomended procedure to tune hyperparameters for each optimizer and problem, according to
-\textit{MealPy}'s Manual.
-The \textit{Tuner} utility is a very simple grid search metaheuristic search tool
-that test each grid configuration for a specified oprimizer runs.
-Although simple, it is a very expensive procedure that took 2 days to complete. It was defined 10 runs for each
-configuration, with the following set of hyperparameter:
-
-\begin{itemize}
-    \item \textit{\textbf{Evolution Based Algorithms: }}
-        \subitem \textit{LevyEP:}
-            \subsubitem \textit{bout\_size (float)}: percentage of child agents implement tournament selection.
-        \subitem \textit{OriginalES:}
-            \subsubitem \textit{lamda (float)}: Percentage of child agents evolving in the next generation.
-        \subitem \textit{BaseGA:}
-            \subsubitem \textit{pc (float)}: cross-over probability
-            \subsubitem \textit{pm (float)}: mutation probability
-    \item \textit{\textbf{Swarm Based Algorithms: }}
-        \subitem \textit{OriginalBeesA:}
-            \subsubitem \textit{selected\_site\_ratio (float)}
-            \subsubitem \textit{elite\_site\_ratio (float)}
-            \subsubitem \textit{selected\_site\_bee\_ratio (float)}
-            \subsubitem \textit{elite\_site\_bee\_ratio (float)}
-            \subsubitem \textit{dance\_radius (float)}
-            \subsubitem \textit{dance\_reduction (float)}
-        \subitem \textit{OriginalFFA:}
-            \subsubitem \textit{gamma (float)}: Light Absorption Coefficient
-            \subsubitem \textit{beta\_base (float)}: Attraction Coefficient Base Value
-            \subsubitem \textit{alpha (float)}: Mutation Coefficient
-            \subsubitem \textit{alpha\_damp (float)}: Mutation Coefficient Damp Rate
-            \subsubitem \textit{delta (float)}: Mutation Step Size
-            \subsubitem \textit{exponent (int)}: Exponent
-        \subitem \textit{OriginalPSO:}
-            \subsubitem \textit{c1 (float)}: local coefficient
-            \subsubitem \textit{c2 (float)}: global coefficient
-            \subsubitem \textit{w\_min (float)}: Weight min of bird
-            \subsubitem \textit{w\_max (float)}: Weight max of bird
-
-\end{itemize}
-
-\subsection{Optimizer Parameters}
-\label{subsec:methodology-optimizer-parameters}
-
-For all optimizers and problems, were selected the following parameters:
-
-\begin{itemize}
-    \item \textit{Runs}: 100 runs
-    \item \textit{Epochs}: 100 epochs
-    \item \textit{Population}: 100 initial points
-\end{itemize}
-
-The initial solutions were randomly selected using the same seed for all algorithms.
-
-\section{Results}
-\label{sec:results}
-\subsection{Spring Tension Design}
-\label{ssubec:spring_problem}
-
-\begin{table}[H]
-\centering
-\caption{Statistical Information about function values for Spring Tension Design}
-\label{function_values:spring_problem}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrrrrr}
-\toprule
-Algorithm &      Min F &     Mean F &   Median F &      Max F &   StdDev F \\
-\midrule
-       EP & 0.01250534 & 0.01255960 & 0.01253156 & 0.01453933 & 0.00020190 \\
-       ES & 0.01252956 & 0.01281857 & 0.01274283 & 0.01346214 & 0.00024181 \\
-       GA & 0.01252305 & 0.01628575 & 0.01616768 & 0.02561808 & 0.00273276 \\
-    BeesA & 0.01250200 & 0.01268010 & 0.01261691 & 0.01406679 & 0.00021629 \\
-      FFA & 0.01249803 & 0.01254780 & 0.01253499 & 0.01268116 & 0.00003152 \\
-      PSO & 0.01252626 & 0.01390866 & 0.01318774 & 0.03036537 & 0.00342240 \\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{figure}[H]
-\centering
-\caption{Boxplot for Spring Tension Design}
-\label{fig:spring_tension_design_boxplot}
-\includegraphics[scale=0.5]{images/spring_problem_boxplot.png}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\caption{Convergence lines for Spring Tension Design}
-\label{fig:spring_problem_convergence}
-\includegraphics[width= 0.4 \textwidth]{images/spring_problem_convergence.png}
-\end{figure}
-
-\subsection{Pressure Vessel Design (Original)}
-\label{subsec:pressure_vessel_problem_original}
+Additional information is given by the Table~\ref{function_values:pressure_vessel_problem_original},
+where are summarized statistics from all 100 results given by different starting points (populations).
 
@@
 \caption{Statistical Information about function values for Pressure Vessel Design (Original)}
+\resizebox{\columnwidth}{!}{%
 \label{function_values:pressure_vessel_problem_original}
-\resizebox{\columnwidth}{!}{%
 \begin{tabular}{lrrrrr}
@@
 
-\begin{figure}[H]
-\centering
-\caption{Boxplot for Pressure Vessel Design (Original)}
-\label{fig:pressure_vessel_design_original_boxplot}
-\includegraphics[scale=0.5]{images/pressure_vessel_problem_original_boxplot.png}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\caption{Convergence lines for Pressure Vessel Design (Original)}
-\label{fig:pressure_vessel_problem_original_convergence}
-\includegraphics[width= 0.4 \textwidth]{images/pressure_vessel_problem_original_convergence.png}
-\end{figure}
-
-\subsection{Pressure Vessel Design}
-\label{subsec:pressure_vessel_problem}
-
-\begin{table}
-\centering
-\caption{Statistical Information about function values for Pressure Vessel Design}
-\label{function_values:pressure_vessel_problem}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrrrrr}
-\toprule
-Algorithm &         Min F &        Mean F &      Median F &         Max F &   StdDev F \\
-\midrule
-       EP & 5534.57345496 & 5534.63426098 & 5534.61416291 & 5534.92993607 & 0.05804548 \\
-       ES & 5534.57917966 & 5535.28165367 & 5535.06149254 & 5538.03003895 & 0.65098467 \\
-       GA & 5534.83662424 & 5538.36788889 & 5536.92932748 & 5550.91639342 & 3.57079951 \\
-    BeesA & 5534.57516657 & 5537.97495231 & 5537.04824684 & 5548.55587234 & 3.28239740 \\
-      FFA & 5534.57401617 & 5534.58849395 & 5534.58435493 & 5534.63296149 & 0.01341777 \\
-      PSO & 5534.57345480 & 5534.57381593 & 5534.57355270 & 5534.57625290 & 0.00053848 \\
-\bottomrule
-\end{tabular}
-}
-\end{table}
-
-\begin{figure}[H]
-\centering
-\caption{Boxplot for Pressure Vessel Design}
-\label{fig:pressure_vessel_design_boxplot}
-\includegraphics[scale=0.5]{images/pressure_vessel_problem_boxplot.png}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\caption{Convergence lines for Pressure Vessel Design}
-\label{fig:pressure_vessel_problem_convergence}
-\includegraphics[width=0.4 \textwidth]{images/pressure_vessel_problem_convergence.png}
-\end{figure}
-
-\subsection{Significance Test}
-\label{subsec:pressure_vessel_problem_significance_test}
-
-\begin{table}[H]
-\centering
-\caption{Significance Test Using Friedman Chi-Squared Test}
-\label{friedman_test}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrr}
-\toprule
-                          Problem &   Statistics &    p-value \\
-\midrule
-            Spring Tension Design & 339.05714286 & 0.00000000 \\
-           Pressure Vessel Design & 436.16000000 & 0.00000000 \\
-Pressure Vessel Design (Original) & 425.07428571 & 0.00000000 \\
-\bottomrule
-\end{tabular}
-}
-\end{table}
-
-\section{Discussion}
-
-The main objective of this work is demonstrate the inner work of a optimization class of algorithms called \textit{Quasi-Newton algorithms}.
-Four of them are presented, along with the results and analysis regarding convergence, function evaluations and function objective values.
-
-For implementation, it was decided to put constraints on search space, because for the original search space of some functions, like Ackley and Rastrigin, there are other minimas that will confuse every algorithm tested for this paper, and there is no sense on test a local minima procedure on these conditions.
-To restrain the initial solution to some region in the search space was a cheap and ready solution to avoid the algorithms to stop because of stumbling upon the wrong minimum.
-
-The \textit{Levenberg-Marquardt Algorithm} implemented for this paper is very sensitive to hyperparameters, namely $\alpha$ and $\lambda$, which was not tunned to every function, so, the conspicuous performance variation is noticeable along the results.
-LMA is known to be fast and reliable, but in our implementation it was found a little tricky to get the hyperparameters right for all the test functions.
-But for Rosenbrock and Rastrigin, it is the best option, even for lame implementations like ours.
-
-The \textit{Broyden–Fletcher–Goldfarb–Shanno} Algorithm was the only one that we decided to use it as is from \textit{SciPy}, because it has features desired for this work, like counting of function evaluations, gradient evaluation and iterations.
-It performed very well for Ackley and Booth Functions, and reasonably well for other functions.
-
-The \textit{Davidon–Fletcher–Powell} Algorithm is not implemented in \textit{SciPy} but its equations shows that it is the dual of BFGS, so, it was easy to implement using some \textit{SciPy} code for BFGS algorithm.
-In the DFP procedure, there is a Hessian inversion to be evaluated every iteration, then, numerical imprecision would be taken into consideration evaluating its results.
-While in some cases it has a superb performance (Like Ackley Function), it has very poor performance in Rosenbrock Function and even in Beale Function.
-The increase of dimensions makes DFP suffer of numerical imprecision due to the Hessian inversion, except for Rastrigin, and it is the loser algorithm in other functions.
-
-Finally, the \textit{Limited memory BFGS} has an average performance among the functions.
-The original algorithm was implemented using code found in the url https://github.com/qkolj/L-BFGS/blob/master/L-BFGS.ipynb.
-
-In fact, there are no Quasi-Newton algorithms that solver the minima problem for an any function.
-From the standpoint of performance and convergence, all the algorithms have an average performance and a reasonable convergence, although we have to restrain the search space to a small area near the optimal solution.
-
-\end{document}
+From statistical viewpoint, no algorithm tested for this paper have stable solutions.

### 2023-01-21 release/code/latex/includes/pressure_vessel_problem_original_best_fits.tex
Release Added

--- 2023-01-19 latex/article.tex
@@
-\documentclass[conference]{IEEEtran}
-\IEEEoverridecommandlockouts
-% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-\usepackage{cite}
-\usepackage{amsmath,amssymb,amsfonts}
-\usepackage{mathtools}
-\usepackage{algpseudocode}
-\usepackage{algorithm}
-\usepackage{algorithmicx}
-\usepackage{microtype}
-\usepackage{float}
-\usepackage{adjustbox}
-\usepackage{booktabs,makecell,tabularx}
-\usepackage{graphicx}
-\usepackage{textcomp}
-\usepackage{verbatim}
-\usepackage{xcolor}
-\usepackage{graphics} % for pdf, bitmapped graphics files
-\usepackage{epsfig} % for postscript graphics files
-\usepackage{mathptmx} % assumes new font selection scheme installed
-\usepackage{multicol}
-\usepackage[english]{babel}
-\usepackage[T1]{fontenc}
-\restylefloat{table}
-\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
-    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
-\begin{document}
-\title{Swarm and Evolutionary Based Algorithms used for Optimization}
-\author{
-	\IEEEauthorblockN{Augusto Mathias Adams\IEEEauthorrefmark{1}, Caio Phillipe Mizerkowski\IEEEauthorrefmark{2}, Christian Piltz Araújo\IEEEauthorrefmark{3} and Vinicius Eduardo dos Reis\IEEEauthorrefmark{4}}\\
-	\IEEEauthorblockA{\IEEEauthorrefmark{1}GRR20172143, augusto.adams@ufpr.br, \IEEEauthorrefmark{2}GRR20166403, caiomizerkowski@gmail.com,\\ \IEEEauthorrefmark{3}GRR20172197, christian0294@yahoo.com.br, \IEEEauthorrefmark{4}GRR20175957, eduardo.reis02@gmail.com}
-}
+In this section are presented the results for the original variable boundings of Pressure Vessel Design,
+as exposed in Section~\ref{subsubsec:methodology-pressure-vessel-design}.
 
-\maketitle
-
-\begin{abstract}
-    In this paper, a study of evolution and swarm based algorithms is presented,
-    using two classical engineering problems: \textit{Spring Tension} and \textit{Pressure Vessel
-    Designs}. The test code for the problems was made using the \textit{Python Language},
-    version 3.10 and uses \textit{MealPy} package, version 2.5.1,  to provide the algorithms.
-    The algorithms were randomly chosen from a vast list of \textit{MealPy}'s algorithms:
-    \textit{Evolutionary Programming (LevyEP)}, \textit{Evolution Strategies (OriginalES)} and
-    \textit{Genetic Algorithm (BaseGA)} from \textit{evolutionary\_based} subpackage;
-    \textit{Bees Algorithm (OriginalBeesA)}, \textit{Firefly Algorithm (OriginalFFA)} and
-    \textit{Particle Swarm Optimization (OriginalPSO)} from \textit{swarm\_based} subpackage.
-    Each problem was modeled using \textit{SciPy} package, with constraints implemented as
-    \textit{penalty functions}. Each algorithm were optimized separately to extract the best
-    solutions from each problem using the \textit{MealPy}'s \textit{Tuner} utility.
-    The results, however, are dependant of algorithm and/or problem solved and the Friedman's chi
-    squared test for similarity make it noticeable because, although the values for best fits are
-    similar, running the same algorithm with different initial conditions does not converge to similar
-    values.
-\end{abstract}
-
-\begin{IEEEkeywords}
-	Optimization Methods, Evolutionary Programming, Evolutionary and Swarm Based Strategies.
-\end{IEEEkeywords}
-
-\section{Definitions}
-\label{sec:definitions}
-
-The main objective of this paper is study evolutionary and swarm intelligence algorithms.
-We present the main concepts of these two algorithm's classes, along with the chosen algorithms
-definitions in this section. All citations made in this document are due to Swarm Intelligence classes
-and to \textit{MealPy}'s documentation, which points out the theoretical documentation for each
-implemented algorithm.
-
-\textit{\textbf{Evolution}}: From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolutionary Algorithms belong to the Evolutionary Computation
-field of study concerned with computational methods inspired by the process
-and mechanisms of biological evolution. The process of evolution by
-means of natural selection (descent with modification) was proposed by
-Darwin to account for the variety of life and its suitability (adaptive
-fit) for its environment. The mechanisms of evolution describe how
-evolution actually takes place through the modification and propagation
-of genetic material (proteins). Evolutionary Algorithms are concerned
-with investigating computational systems that resemble simplified ver-
-sions of the processes and mechanisms of evolution toward achieving
-the effects of these processes and mechanisms, namely the development
-of adaptive systems. Additional subject areas that fall within the realm
-of Evolutionary Computation are algorithms that seek to exploit the
-properties from the related fields of Population Genetics, Population
-Ecology, Coevolutionary Biology, and Developmental Biology.
-
-\textit{\textbf{Swarm Intelligence}}: From Jason Brownlee's \textit{``Clever Algorithms''} -
-Swarm intelligence is the study of computational systems inspired by
-the ‘collective intelligence’. Collective Intelligence emerges through the
-cooperation of large numbers of homogeneous agents in the environment.
-Examples include schools of fish, flocks of birds, and colonies of ants.
-Such intelligence is decentralized, self-organizing and distributed through
-out an environment. In nature such systems are commonly used to
-solve problems such as effective foraging for food, prey evading, or
-colony re-location. The information is typically stored throughout the
-participating homogeneous agents, or is stored or communicated in
-the environment itself such as through the use of pheromones in ants,
-dancing in bees, and proximity in fish and birds.
-
-\textit{\textbf{Evolutionary Programming:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolutionary Programming is a Global Optimization algorithm and is an instance of an Evolutionary
-Algorithm from the field of Evolutionary Computation. The approach is a sibling of other Evolutionary
-Algorithms such as the Genetic Algorithm, and Learning Classifier Systems. It is sometimes confused with Genetic
-Programming given the similarity in name, and more recently it shows a strong functional similarity to Evolution Strategies.
-Evolutionary Programming is inspired by the theory of evolution by means of natural selection. Specifically, the technique is inspired by
-macro-level or the species-level process of evolution (phenotype, hereditary, variation) and is not concerned with the genetic mechanisms of
-evolution (genome, chromosomes, genes, alleles).
-
-\textit{\textbf{Evolutionary Strategies:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolution Strategies is a global optimization algorithm and is an instance of an Evolutionary Algorithm from the field of Evolutionary
-Computation. Evolution Strategies is a sibling technique to other Evolutionary Algorithms such as Genetic Algorithms (Section 3.2), Genetic
-Programming (Section 3.3), Learning Classifier Systems, and Evolutionary Programming. A popular descendant of
-the Evolution Strategies algorithm is the Covariance Matrix Adaptation Evolution Strategies (CMA-ES).
-
-\textit{\textbf{Genetic Algorithms:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-The Genetic Algorithm is an Adaptive Strategy and a Global Optimization technique. It is an Evolutionary Algorithm and belongs to the
-broader study of Evolutionary Computation. The Genetic Algorithm is a sibling of other Evolutionary Algorithms such as Genetic Programming,
- Evolution Strategies, Evolutionary Programming, and Learning Classifier Systems. The Genetic Algorithm is a parent of a large number of variant techniques
-and sub-fields too numerous to list. The Genetic Algorithm is inspired by population genetics (including heredity and gene frequencies),
-and evolution at the population level, as well as the Mendelian understanding of the structure (such as chromosomes, genes, alleles) and mechanisms
-(such as recombination and mutation). This is the so-called new or modern synthesis of evolutionary biology.
-
-\textit{\textbf{Particle Swarm Optimization:}} From Jason Brownlee's \textit{``Clever Algorithms''} - Particle Swarm Optimization belongs to the field of
-Swarm Intelligence and Collective Intelligence and is a sub-field of Computational Intelligence. Particle Swarm Optimization is related to other Swarm Intelligence
-algorithms such as Ant Colony Optimization and it is a baseline algorithm for many variations, too numerous to list. It is inspired by the social foraging behavior
-of some animals such as flocking behavior of birds and the schooling behavior of fish.
-
-\textit{\textbf{Firefly Algorithm:}} From Xin-She Yang \textit{``Nature-Inspired Metaheuristic Algorithms''} -
-The flashing light of fireflies is an amazing sight in the summer sky in the tropical and temperate regions. There are about two thousand firefly
-species, and most fireflies produce short and rhythmic flashes. The pattern of flashes is often unique for a particular species. The flashing light is
-produced by a process of bioluminescence, and the true functions of suchsignaling systems are still being debated. However, two fundamental functions
-of such flashes are to attract mating partners (communication), and to attract potential prey. In addition, flashing may also serve as a protective warning
-mechanism to remind potential predators of the bitter taste of fireflies. The firefly algorithm tries to mimic the attractiveness of Fireflies and has three
-basic rules:
-
-\begin{itemize}
-    \item All fireflies are unisex so that one firefly will be attracted to other
-          fireflies regardless of their sex;
-    \item Attractiveness is proportional to the their brightness, thus for any two
-          flashing fireflies, the less brighter one will move towards the brighter
-          one. The attractiveness is proportional to the brightness and they
-          both decrease as their distance increases. If there is no brighter one
-          than a particular firefly, it will move randomly;
-    \item The brightness of a firefly is affected or determined by the landscape
-          of the objective function.
-\end{itemize}
-
-\textit{\textbf{Bees Algorithm:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-The Bees Algorithm beings to Bee Inspired Algorithms and the field of Swarm Intelligence, and more broadly the fields of Computational
-Intelligence and Metaheuristics. The Bees Algorithm is related to other Bee Inspired Algorithms, such as Bee Colony Optimization, and other
-Swarm Intelligence algorithms such as Ant Colony Optimization and Particle Swarm Optimization.
-It is inspired by the foraging behavior of honey bees. Honey bees collect nectar from vast areas around their hive (more than
-10 kilometers). Bee Colonies have been observed to send bees to collect nectar from flower patches relative to the amount of food available at
-each patch. Bees communicate with each other at the hive via a waggle dance that informs other bees in the hive as to the direction, distance,
-and quality rating of food sources.
-
-\section{Methodology}
-\label{sec:methodology}
-
-\subsection{Optimization Problem Selection}
-\label{subsec:optimization-problem-selection}
-The two problems selected for this paper were \textit{Spring Tension Design} and \textit{Pressure Vessel Design}. Although it was simple
-to choose the first two problems from the computational work statements, the choice was more than justified because these aroblems are well
-known in the literature.
-Thus, the problem selection was driven by which has more than one source to compare results.
-
-\subsubsection{Spring Tension Design}
-\label{subsubsec:methodology-spring-tension-design}
-From \textit{Nature-Inspired Metaheuristic Algorithms - Xin-She Yang} -
-The design of a tension and compression spring is a well-known benchmark
-optimization problem.
-The main aim is to minimize the weight subject
-to constraints on deflection, stress, surge frequency and geometry. It involves
-three design variables: the wire diameter $x_1$ , coil diameter $x_2$ and
-number/length of the coil $x_3$.
-This problem can be summarized as:
-
-\begin{equation}
-    f (x) = x_1^2 x_2 (2 + x_3)
-\end{equation}
-
-subject to
-
-\begin{equation}
-    \begin{split}
-        g_1(x) = \frac{x_2^3 x_3}{71785 x_1^4} \leq 0\\
-        g_2(x) = \frac{4 x_2^2 - x_1 x_2}{12566 \left( x_1^3 x_2 - x_1^4\right)}\\
-        + \frac{1}{5108 x_1^2} -1 \leq 0\\
-        g_3(x) = 1 - \frac{140.45 x_1}{x_2^2 x_3} \leq 0\\
-        g_4 = \frac{x_1 + x_2}{1.5} - 1 \leq 0
-    \end{split}
-\end{equation}
-
-The original bounding limits of the variables, extracted from computational work
-statements, are:
-
-\begin{equation}
-    \begin{split}
-        0.05 \leq x_1 \leq 2.0\\
-        0.25 \leq x_2 \leq 1.3\\
-        2.0 \leq x_3 \leq 15.0
-    \end{split}
-\end{equation}
-
-\subsubsection{Pressure Vessel Design}
-\label{subsubsec:methodology-pressure-vessel-design}
-From \textit{Solving Design of Pressure Vessel Engineering
-Problem Using a Fruit Fly Optimization Algorithm - XIANTING KE et al} -
-A pressure vessel design model involves four decision variables: $x_1$ is defined
-thickness of the pressure vessel $T_s$ , $x_2$ stands for
-thickness of the head $T_H$ , $x_3$ represents inner radius of the
-vessel $R$ , and $x_4$ is on behalf of length of the vessel
-barring head $L$ , the total variables described as $( x_1 , x_2 , x_3 , x_4 )$.
-The objective function of the problem is to minimize the total cost, including
-the cost of material, forming, and welding.
-The general pressure vessel design optimization model is expressed as:
-
-\begin{equation}
-	\begin{split}
-        f(x) = 0.6224 x_1 x_3 x_4 + 1.7781 x_2 x_3^2 \\
-        + 3.1661 x_1^2 x_4 + 19.84 x_1^2 x_3
-	\end{split}
-\end{equation}
-
-subject to:
-
-\begin{equation}
-    \begin{split}
-        g_1(x) = - x_1 + 0.0193 x_3 \leq 0\\
-        g_2(x) = - x_2 + 0.00954 x_3 \leq 0\\
-        g_3(x) = - \pi x_3^2 x_4 -\frac{4}{3}\pi x_3^3 + 1296000 \leq 0\\
-        g_4(x) = x_4 -240 \leq 0\\
-    \end{split}
-\end{equation}
-
-The original bounding limits of the variables, extracted from computational work
-statements, are:
-
-\begin{equation}
-    \begin{split}
-        0 \leq x_1 \leq 99\\
-        0 \leq x_2 \leq 99\\
-        10 \leq x_3 \leq 200\\
-        10 \leq x_4 \leq 200\\
-    \end{split}
-\end{equation}
-
-For some reason these settings does not work at all with the selected optimizers, so
-some research in the literature \textit{Solving Design of Pressure Vessel Engineering
-Problem Using a Fruit Fly Optimization Algorithm - XIANTING KE et al} suggest the
-following bounding limits:
-
-\begin{equation}
-    \begin{split}
-        0.0625 \leq x_1 \leq 99 \times 0.0625\\
-        0.0625 \leq x_2 \leq 99 \times 0.0625\\
-        10 \leq x_3 \leq 200\\
-        10 \leq x_4 \leq 200
-    \end{split}
-\end{equation}
-
-But these settings produce many random, bizarre and noisy results in all selected optimizers. Then
-a proud-and-lame-homemade set of variable boundings comes in handy, obtained by tweaking the original
-boundings:
-
-\begin{equation}
-    \begin{split}
-        0.75 \leq x_1 \leq 0.8\\
-        0.35 \leq x_2 \leq 0.4\\
-        39.5 \leq x_3 \leq 41.0\\
-        195.0 \leq x_4 \leq 205.0\\
-    \end{split}
-\end{equation}
-
-It is not intended here to point out modeling errors of any kind, nor point out package
-errors made by the authors or ours, but the homemade bounding limits was necessary to
-reach the literature results.
-
-\subsection{Constraint Implementation}
-\label{subsec:methodology-constraint-implementation}
-The constraints that all problems are subjected were implemented as \textit{penalty functions},
-that is, it adds a high value when the constraint is not satisfied, zero otherwise. It is an optional requirement
-from computational work in question and is the recommended way to put constraints from \textit{MealPy}'s
-Manual.
-
-\subsection{Programming Language}
-\label{subsec:methodology-programming-language}
-
-The chosen programming language for the test code was \textit{Python Language}, version 3.10, because it is an opensource language easy to
-program and has a huge amount of packages regarding artificial intelligence, genetic algorithms and swarm based algorithms.
-From these packages it was selected \textit{MealPy} package, version 2.5.1, because it comprises all the algorithm's classed tested in this paper.
-
-\subsection{Algorithm Selection}
-\label{subsec:methodology-algorithm-selection}
-
-The algorithm selection was made in two steps: first, it was extracted simple version of the two classes (evolutionary and swarm based) and
-then it was used a simple shuffle using Python's \textit{random.shuffle} in a terminal - no script was required.
-
-The chosen algorithms were:
-
-\begin{itemize}
-    \item \textit{\textbf{Evolution Based Algorithms: }} LevyEP (Evolutionary Programming),
-    OriginalES (Evolution Strategy) and BaseGA (Genetic Algorithm)
-    \item \textit{\textbf{Swarm Based Algorithms: }} OriginalBeesA (Bees Algorithm),
-    OriginalFFA (Original Firefly Algorithm) and OriginalPSO (Particle Swarm Optimization)
-\end{itemize}
-
-\subsection{Optimizer Tuning}
-\label{subsec:methodology-optimizer-tuning}
-
-The hyperparameters for each optimizer were tuned using the \textit{MealPy}'s \textit{Tuner} utility.
-It is a recomended procedure to tune hyperparameters for each optimizer and problem, according to
-\textit{MealPy}'s Manual.
-The \textit{Tuner} utility is a very simple grid search metaheuristic search tool
-that test each grid configuration for a specified oprimizer runs.
-Although simple, it is a very expensive procedure that took 2 days to complete. It was defined 10 runs for each
-configuration, with the following set of hyperparameter:
-
-\begin{itemize}
-    \item \textit{\textbf{Evolution Based Algorithms: }}
-        \subitem \textit{LevyEP:}
-            \subsubitem \textit{bout\_size (float)}: percentage of child agents implement tournament selection.
-        \subitem \textit{OriginalES:}
-            \subsubitem \textit{lamda (float)}: Percentage of child agents evolving in the next generation.
-        \subitem \textit{BaseGA:}
-            \subsubitem \textit{pc (float)}: cross-over probability
-            \subsubitem \textit{pm (float)}: mutation probability
-    \item \textit{\textbf{Swarm Based Algorithms: }}
-        \subitem \textit{OriginalBeesA:}
-            \subsubitem \textit{selected\_site\_ratio (float)}
-            \subsubitem \textit{elite\_site\_ratio (float)}
-            \subsubitem \textit{selected\_site\_bee\_ratio (float)}
-            \subsubitem \textit{elite\_site\_bee\_ratio (float)}
-            \subsubitem \textit{dance\_radius (float)}
-            \subsubitem \textit{dance\_reduction (float)}
-        \subitem \textit{OriginalFFA:}
-            \subsubitem \textit{gamma (float)}: Light Absorption Coefficient
-            \subsubitem \textit{beta\_base (float)}: Attraction Coefficient Base Value
-            \subsubitem \textit{alpha (float)}: Mutation Coefficient
-            \subsubitem \textit{alpha\_damp (float)}: Mutation Coefficient Damp Rate
-            \subsubitem \textit{delta (float)}: Mutation Step Size
-            \subsubitem \textit{exponent (int)}: Exponent
-        \subitem \textit{OriginalPSO:}
-            \subsubitem \textit{c1 (float)}: local coefficient
-            \subsubitem \textit{c2 (float)}: global coefficient
-            \subsubitem \textit{w\_min (float)}: Weight min of bird
-            \subsubitem \textit{w\_max (float)}: Weight max of bird
-
-\end{itemize}
-
-\subsection{Optimizer Parameters}
-\label{subsec:methodology-optimizer-parameters}
-
-For all optimizers and problems, were selected the following parameters:
-
-\begin{itemize}
-    \item \textit{Runs}: 100 runs
-    \item \textit{Epochs}: 100 epochs
-    \item \textit{Population}: 100 initial points
-\end{itemize}
-
-The initial solutions were randomly selected using the same seed for all algorithms.
-
-\section{Results}
-\label{sec:results}
-\subsection{Spring Tension Design}
-\label{ssubec:spring_problem}
+The best results for all algorithms are presented in Table~\ref{best_fits:pressure_vessel_problem_original}:
 
@@
 \centering
-\caption{Statistical Information about function values for Spring Tension Design}
-\label{function_values:spring_problem}
+\caption{Best Fits for Pressure Vessel Design (Original)}
+\label{best_fits:pressure_vessel_problem_original}
 \resizebox{\columnwidth}{!}{%
@@
 \toprule
-Algorithm &      Min F &     Mean F &   Median F &      Max F &   StdDev F \\
+Algorithm &      $x_1$ &      $x_2$ &        $x_3$ &        $x_4$ &         $f_x$ \\
 \midrule
-       EP & 0.01250534 & 0.01255960 & 0.01253156 & 0.01453933 & 0.00020190 \\
-       ES & 0.01252956 & 0.01281857 & 0.01274283 & 0.01346214 & 0.00024181 \\
-       GA & 0.01252305 & 0.01628575 & 0.01616768 & 0.02561808 & 0.00273276 \\
-    BeesA & 0.01250200 & 0.01268010 & 0.01261691 & 0.01406679 & 0.00021629 \\
-      FFA & 0.01249803 & 0.01254780 & 0.01253499 & 0.01268116 & 0.00003152 \\
-      PSO & 0.01252626 & 0.01390866 & 0.01318774 & 0.03036537 & 0.00342240 \\
+       EP & 0.00000000 & 0.00000000 &  40.32041055 & 200.00000000 &    0.08150806 \\
+       ES & 0.00000000 & 0.00000000 &  40.32554414 & 200.00000000 &    0.08161190 \\
+       GA & 0.00337818 & 0.00106498 &  46.44471109 & 129.50295637 &   17.06920868 \\
+    BeesA & 0.07617198 & 0.07091908 & 104.75191725 &  44.23570263 & 2393.70106213 \\
+      FFA & 0.00000000 & 0.00000000 &  40.39658670 & 200.00000000 &    0.08306113 \\
+      PSO & 0.00000000 & 0.00000000 &  40.31961791 & 200.00000000 &    0.08149204 \\
 \bottomrule
@@
 
-\begin{figure}[H]
-\centering
-\caption{Boxplot for Spring Tension Design}
-\label{fig:spring_tension_design_boxplot}
-\includegraphics[scale=0.5]{images/spring_problem_boxplot.png}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\caption{Convergence lines for Spring Tension Design}
-\label{fig:spring_problem_convergence}
-\includegraphics[width= 0.4 \textwidth]{images/spring_problem_convergence.png}
-\end{figure}
-
-\subsection{Pressure Vessel Design (Original)}
-\label{subsec:pressure_vessel_problem_original}
-
-\begin{table}[H]
-\centering
-\caption{Statistical Information about function values for Pressure Vessel Design (Original)}
-\label{function_values:pressure_vessel_problem_original}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrrrrr}
-\toprule
-Algorithm &         Min F &         Mean F &       Median F &          Max F &       StdDev F \\
-\midrule
-       EP &    0.08150806 &     0.15642850 &     0.09093798 &     1.32637552 &     0.16807714 \\
-       ES &    0.08161190 &   718.92910990 &     1.00278859 &  9443.54269260 &  2060.07774212 \\
-       GA &   17.06920868 &   525.00734162 &   361.53879602 &  3112.03503082 &   454.52386703 \\
-    BeesA & 2393.70106213 & 17564.33024022 & 15751.91467117 & 53850.38271384 & 10514.60780411 \\
-      FFA &    0.08306113 &     0.13296127 &     0.13106271 &     0.20084847 &     0.02396876 \\
-      PSO &    0.08149204 &     0.24191732 &     0.08159173 &    10.00611523 &     1.00072349 \\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{figure}[H]
-\centering
-\caption{Boxplot for Pressure Vessel Design (Original)}
-\label{fig:pressure_vessel_design_original_boxplot}
-\includegraphics[scale=0.5]{images/pressure_vessel_problem_original_boxplot.png}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\caption{Convergence lines for Pressure Vessel Design (Original)}
-\label{fig:pressure_vessel_problem_original_convergence}
-\includegraphics[width= 0.4 \textwidth]{images/pressure_vessel_problem_original_convergence.png}
-\end{figure}
-
-\subsection{Pressure Vessel Design}
-\label{subsec:pressure_vessel_problem}
-
-\begin{table}
-\centering
-\caption{Statistical Information about function values for Pressure Vessel Design}
-\label{function_values:pressure_vessel_problem}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrrrrr}
-\toprule
-Algorithm &         Min F &        Mean F &      Median F &         Max F &   StdDev F \\
-\midrule
-       EP & 5534.57345496 & 5534.63426098 & 5534.61416291 & 5534.92993607 & 0.05804548 \\
-       ES & 5534.57917966 & 5535.28165367 & 5535.06149254 & 5538.03003895 & 0.65098467 \\
-       GA & 5534.83662424 & 5538.36788889 & 5536.92932748 & 5550.91639342 & 3.57079951 \\
-    BeesA & 5534.57516657 & 5537.97495231 & 5537.04824684 & 5548.55587234 & 3.28239740 \\
-      FFA & 5534.57401617 & 5534.58849395 & 5534.58435493 & 5534.63296149 & 0.01341777 \\
-      PSO & 5534.57345480 & 5534.57381593 & 5534.57355270 & 5534.57625290 & 0.00053848 \\
-\bottomrule
-\end{tabular}
-}
-\end{table}
-
-\begin{figure}[H]
-\centering
-\caption{Boxplot for Pressure Vessel Design}
-\label{fig:pressure_vessel_design_boxplot}
-\includegraphics[scale=0.5]{images/pressure_vessel_problem_boxplot.png}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\caption{Convergence lines for Pressure Vessel Design}
-\label{fig:pressure_vessel_problem_convergence}
-\includegraphics[width=0.4 \textwidth]{images/pressure_vessel_problem_convergence.png}
-\end{figure}
-
-\subsection{Significance Test}
-\label{subsec:pressure_vessel_problem_significance_test}
-
-\begin{table}[H]
-\centering
-\caption{Significance Test Using Friedman Chi-Squared Test}
-\label{friedman_test}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrr}
-\toprule
-                          Problem &   Statistics &    p-value \\
-\midrule
-            Spring Tension Design & 339.05714286 & 0.00000000 \\
-           Pressure Vessel Design & 436.16000000 & 0.00000000 \\
-Pressure Vessel Design (Original) & 425.07428571 & 0.00000000 \\
-\bottomrule
-\end{tabular}
-}
-\end{table}
-
-\section{Discussion}
-
-The main objective of this work is demonstrate the inner work of a optimization class of algorithms called \textit{Quasi-Newton algorithms}.
-Four of them are presented, along with the results and analysis regarding convergence, function evaluations and function objective values.
-
-For implementation, it was decided to put constraints on search space, because for the original search space of some functions, like Ackley and Rastrigin, there are other minimas that will confuse every algorithm tested for this paper, and there is no sense on test a local minima procedure on these conditions.
-To restrain the initial solution to some region in the search space was a cheap and ready solution to avoid the algorithms to stop because of stumbling upon the wrong minimum.
-
-The \textit{Levenberg-Marquardt Algorithm} implemented for this paper is very sensitive to hyperparameters, namely $\alpha$ and $\lambda$, which was not tunned to every function, so, the conspicuous performance variation is noticeable along the results.
-LMA is known to be fast and reliable, but in our implementation it was found a little tricky to get the hyperparameters right for all the test functions.
-But for Rosenbrock and Rastrigin, it is the best option, even for lame implementations like ours.
-
-The \textit{Broyden–Fletcher–Goldfarb–Shanno} Algorithm was the only one that we decided to use it as is from \textit{SciPy}, because it has features desired for this work, like counting of function evaluations, gradient evaluation and iterations.
-It performed very well for Ackley and Booth Functions, and reasonably well for other functions.
-
-The \textit{Davidon–Fletcher–Powell} Algorithm is not implemented in \textit{SciPy} but its equations shows that it is the dual of BFGS, so, it was easy to implement using some \textit{SciPy} code for BFGS algorithm.
-In the DFP procedure, there is a Hessian inversion to be evaluated every iteration, then, numerical imprecision would be taken into consideration evaluating its results.
-While in some cases it has a superb performance (Like Ackley Function), it has very poor performance in Rosenbrock Function and even in Beale Function.
-The increase of dimensions makes DFP suffer of numerical imprecision due to the Hessian inversion, except for Rastrigin, and it is the loser algorithm in other functions.
-
-Finally, the \textit{Limited memory BFGS} has an average performance among the functions.
-The original algorithm was implemented using code found in the url https://github.com/qkolj/L-BFGS/blob/master/L-BFGS.ipynb.
-
-In fact, there are no Quasi-Newton algorithms that solver the minima problem for an any function.
-From the standpoint of performance and convergence, all the algorithms have an average performance and a reasonable convergence, although we have to restrain the search space to a small area near the optimal solution.
-
-\end{document}
+While EP, ES, FFA and PSO seems to give similar results, it is noticeable that the cost function
+gave some discrepant results for GA and BeesA.

### 2023-01-21 release/code/latex/includes/pressure_vessel_problem_original_convergence.tex
Release Added

--- 2023-01-19 latex/article.tex
@@
-\documentclass[conference]{IEEEtran}
-\IEEEoverridecommandlockouts
-% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-\usepackage{cite}
-\usepackage{amsmath,amssymb,amsfonts}
-\usepackage{mathtools}
-\usepackage{algpseudocode}
-\usepackage{algorithm}
-\usepackage{algorithmicx}
-\usepackage{microtype}
-\usepackage{float}
-\usepackage{adjustbox}
-\usepackage{booktabs,makecell,tabularx}
-\usepackage{graphicx}
-\usepackage{textcomp}
-\usepackage{verbatim}
-\usepackage{xcolor}
-\usepackage{graphics} % for pdf, bitmapped graphics files
-\usepackage{epsfig} % for postscript graphics files
-\usepackage{mathptmx} % assumes new font selection scheme installed
-\usepackage{multicol}
-\usepackage[english]{babel}
-\usepackage[T1]{fontenc}
-\restylefloat{table}
-\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
-    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
-\begin{document}
-\title{Swarm and Evolutionary Based Algorithms used for Optimization}
-\author{
-	\IEEEauthorblockN{Augusto Mathias Adams\IEEEauthorrefmark{1}, Caio Phillipe Mizerkowski\IEEEauthorrefmark{2}, Christian Piltz Araújo\IEEEauthorrefmark{3} and Vinicius Eduardo dos Reis\IEEEauthorrefmark{4}}\\
-	\IEEEauthorblockA{\IEEEauthorrefmark{1}GRR20172143, augusto.adams@ufpr.br, \IEEEauthorrefmark{2}GRR20166403, caiomizerkowski@gmail.com,\\ \IEEEauthorrefmark{3}GRR20172197, christian0294@yahoo.com.br, \IEEEauthorrefmark{4}GRR20175957, eduardo.reis02@gmail.com}
-}
-
-\maketitle
-
-\begin{abstract}
-    In this paper, a study of evolution and swarm based algorithms is presented,
-    using two classical engineering problems: \textit{Spring Tension} and \textit{Pressure Vessel
-    Designs}. The test code for the problems was made using the \textit{Python Language},
-    version 3.10 and uses \textit{MealPy} package, version 2.5.1,  to provide the algorithms.
-    The algorithms were randomly chosen from a vast list of \textit{MealPy}'s algorithms:
-    \textit{Evolutionary Programming (LevyEP)}, \textit{Evolution Strategies (OriginalES)} and
-    \textit{Genetic Algorithm (BaseGA)} from \textit{evolutionary\_based} subpackage;
-    \textit{Bees Algorithm (OriginalBeesA)}, \textit{Firefly Algorithm (OriginalFFA)} and
-    \textit{Particle Swarm Optimization (OriginalPSO)} from \textit{swarm\_based} subpackage.
-    Each problem was modeled using \textit{SciPy} package, with constraints implemented as
-    \textit{penalty functions}. Each algorithm were optimized separately to extract the best
-    solutions from each problem using the \textit{MealPy}'s \textit{Tuner} utility.
-    The results, however, are dependant of algorithm and/or problem solved and the Friedman's chi
-    squared test for similarity make it noticeable because, although the values for best fits are
-    similar, running the same algorithm with different initial conditions does not converge to similar
-    values.
-\end{abstract}
-
-\begin{IEEEkeywords}
-	Optimization Methods, Evolutionary Programming, Evolutionary and Swarm Based Strategies.
-\end{IEEEkeywords}
-
-\section{Definitions}
-\label{sec:definitions}
-
-The main objective of this paper is study evolutionary and swarm intelligence algorithms.
-We present the main concepts of these two algorithm's classes, along with the chosen algorithms
-definitions in this section. All citations made in this document are due to Swarm Intelligence classes
-and to \textit{MealPy}'s documentation, which points out the theoretical documentation for each
-implemented algorithm.
-
-\textit{\textbf{Evolution}}: From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolutionary Algorithms belong to the Evolutionary Computation
-field of study concerned with computational methods inspired by the process
-and mechanisms of biological evolution. The process of evolution by
-means of natural selection (descent with modification) was proposed by
-Darwin to account for the variety of life and its suitability (adaptive
-fit) for its environment. The mechanisms of evolution describe how
-evolution actually takes place through the modification and propagation
-of genetic material (proteins). Evolutionary Algorithms are concerned
-with investigating computational systems that resemble simplified ver-
-sions of the processes and mechanisms of evolution toward achieving
-the effects of these processes and mechanisms, namely the development
-of adaptive systems. Additional subject areas that fall within the realm
-of Evolutionary Computation are algorithms that seek to exploit the
-properties from the related fields of Population Genetics, Population
-Ecology, Coevolutionary Biology, and Developmental Biology.
-
-\textit{\textbf{Swarm Intelligence}}: From Jason Brownlee's \textit{``Clever Algorithms''} -
-Swarm intelligence is the study of computational systems inspired by
-the ‘collective intelligence’. Collective Intelligence emerges through the
-cooperation of large numbers of homogeneous agents in the environment.
-Examples include schools of fish, flocks of birds, and colonies of ants.
-Such intelligence is decentralized, self-organizing and distributed through
-out an environment. In nature such systems are commonly used to
-solve problems such as effective foraging for food, prey evading, or
-colony re-location. The information is typically stored throughout the
-participating homogeneous agents, or is stored or communicated in
-the environment itself such as through the use of pheromones in ants,
-dancing in bees, and proximity in fish and birds.
-
-\textit{\textbf{Evolutionary Programming:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolutionary Programming is a Global Optimization algorithm and is an instance of an Evolutionary
-Algorithm from the field of Evolutionary Computation. The approach is a sibling of other Evolutionary
-Algorithms such as the Genetic Algorithm, and Learning Classifier Systems. It is sometimes confused with Genetic
-Programming given the similarity in name, and more recently it shows a strong functional similarity to Evolution Strategies.
-Evolutionary Programming is inspired by the theory of evolution by means of natural selection. Specifically, the technique is inspired by
-macro-level or the species-level process of evolution (phenotype, hereditary, variation) and is not concerned with the genetic mechanisms of
-evolution (genome, chromosomes, genes, alleles).
-
-\textit{\textbf{Evolutionary Strategies:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolution Strategies is a global optimization algorithm and is an instance of an Evolutionary Algorithm from the field of Evolutionary
-Computation. Evolution Strategies is a sibling technique to other Evolutionary Algorithms such as Genetic Algorithms (Section 3.2), Genetic
-Programming (Section 3.3), Learning Classifier Systems, and Evolutionary Programming. A popular descendant of
-the Evolution Strategies algorithm is the Covariance Matrix Adaptation Evolution Strategies (CMA-ES).
-
-\textit{\textbf{Genetic Algorithms:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-The Genetic Algorithm is an Adaptive Strategy and a Global Optimization technique. It is an Evolutionary Algorithm and belongs to the
-broader study of Evolutionary Computation. The Genetic Algorithm is a sibling of other Evolutionary Algorithms such as Genetic Programming,
- Evolution Strategies, Evolutionary Programming, and Learning Classifier Systems. The Genetic Algorithm is a parent of a large number of variant techniques
-and sub-fields too numerous to list. The Genetic Algorithm is inspired by population genetics (including heredity and gene frequencies),
-and evolution at the population level, as well as the Mendelian understanding of the structure (such as chromosomes, genes, alleles) and mechanisms
-(such as recombination and mutation). This is the so-called new or modern synthesis of evolutionary biology.
-
-\textit{\textbf{Particle Swarm Optimization:}} From Jason Brownlee's \textit{``Clever Algorithms''} - Particle Swarm Optimization belongs to the field of
-Swarm Intelligence and Collective Intelligence and is a sub-field of Computational Intelligence. Particle Swarm Optimization is related to other Swarm Intelligence
-algorithms such as Ant Colony Optimization and it is a baseline algorithm for many variations, too numerous to list. It is inspired by the social foraging behavior
-of some animals such as flocking behavior of birds and the schooling behavior of fish.
-
-\textit{\textbf{Firefly Algorithm:}} From Xin-She Yang \textit{``Nature-Inspired Metaheuristic Algorithms''} -
-The flashing light of fireflies is an amazing sight in the summer sky in the tropical and temperate regions. There are about two thousand firefly
-species, and most fireflies produce short and rhythmic flashes. The pattern of flashes is often unique for a particular species. The flashing light is
-produced by a process of bioluminescence, and the true functions of suchsignaling systems are still being debated. However, two fundamental functions
-of such flashes are to attract mating partners (communication), and to attract potential prey. In addition, flashing may also serve as a protective warning
-mechanism to remind potential predators of the bitter taste of fireflies. The firefly algorithm tries to mimic the attractiveness of Fireflies and has three
-basic rules:
-
-\begin{itemize}
-    \item All fireflies are unisex so that one firefly will be attracted to other
-          fireflies regardless of their sex;
-    \item Attractiveness is proportional to the their brightness, thus for any two
-          flashing fireflies, the less brighter one will move towards the brighter
-          one. The attractiveness is proportional to the brightness and they
-          both decrease as their distance increases. If there is no brighter one
-          than a particular firefly, it will move randomly;
-    \item The brightness of a firefly is affected or determined by the landscape
-          of the objective function.
-\end{itemize}
-
-\textit{\textbf{Bees Algorithm:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-The Bees Algorithm beings to Bee Inspired Algorithms and the field of Swarm Intelligence, and more broadly the fields of Computational
-Intelligence and Metaheuristics. The Bees Algorithm is related to other Bee Inspired Algorithms, such as Bee Colony Optimization, and other
-Swarm Intelligence algorithms such as Ant Colony Optimization and Particle Swarm Optimization.
-It is inspired by the foraging behavior of honey bees. Honey bees collect nectar from vast areas around their hive (more than
-10 kilometers). Bee Colonies have been observed to send bees to collect nectar from flower patches relative to the amount of food available at
-each patch. Bees communicate with each other at the hive via a waggle dance that informs other bees in the hive as to the direction, distance,
-and quality rating of food sources.
-
-\section{Methodology}
-\label{sec:methodology}
-
-\subsection{Optimization Problem Selection}
-\label{subsec:optimization-problem-selection}
-The two problems selected for this paper were \textit{Spring Tension Design} and \textit{Pressure Vessel Design}. Although it was simple
-to choose the first two problems from the computational work statements, the choice was more than justified because these aroblems are well
-known in the literature.
-Thus, the problem selection was driven by which has more than one source to compare results.
-
-\subsubsection{Spring Tension Design}
-\label{subsubsec:methodology-spring-tension-design}
-From \textit{Nature-Inspired Metaheuristic Algorithms - Xin-She Yang} -
-The design of a tension and compression spring is a well-known benchmark
-optimization problem.
-The main aim is to minimize the weight subject
-to constraints on deflection, stress, surge frequency and geometry. It involves
-three design variables: the wire diameter $x_1$ , coil diameter $x_2$ and
-number/length of the coil $x_3$.
-This problem can be summarized as:
-
-\begin{equation}
-    f (x) = x_1^2 x_2 (2 + x_3)
-\end{equation}
-
-subject to
-
-\begin{equation}
-    \begin{split}
-        g_1(x) = \frac{x_2^3 x_3}{71785 x_1^4} \leq 0\\
-        g_2(x) = \frac{4 x_2^2 - x_1 x_2}{12566 \left( x_1^3 x_2 - x_1^4\right)}\\
-        + \frac{1}{5108 x_1^2} -1 \leq 0\\
-        g_3(x) = 1 - \frac{140.45 x_1}{x_2^2 x_3} \leq 0\\
-        g_4 = \frac{x_1 + x_2}{1.5} - 1 \leq 0
-    \end{split}
-\end{equation}
-
-The original bounding limits of the variables, extracted from computational work
-statements, are:
-
-\begin{equation}
-    \begin{split}
-        0.05 \leq x_1 \leq 2.0\\
-        0.25 \leq x_2 \leq 1.3\\
-        2.0 \leq x_3 \leq 15.0
-    \end{split}
-\end{equation}
-
-\subsubsection{Pressure Vessel Design}
-\label{subsubsec:methodology-pressure-vessel-design}
-From \textit{Solving Design of Pressure Vessel Engineering
-Problem Using a Fruit Fly Optimization Algorithm - XIANTING KE et al} -
-A pressure vessel design model involves four decision variables: $x_1$ is defined
-thickness of the pressure vessel $T_s$ , $x_2$ stands for
-thickness of the head $T_H$ , $x_3$ represents inner radius of the
-vessel $R$ , and $x_4$ is on behalf of length of the vessel
-barring head $L$ , the total variables described as $( x_1 , x_2 , x_3 , x_4 )$.
-The objective function of the problem is to minimize the total cost, including
-the cost of material, forming, and welding.
-The general pressure vessel design optimization model is expressed as:
-
-\begin{equation}
-	\begin{split}
-        f(x) = 0.6224 x_1 x_3 x_4 + 1.7781 x_2 x_3^2 \\
-        + 3.1661 x_1^2 x_4 + 19.84 x_1^2 x_3
-	\end{split}
-\end{equation}
-
-subject to:
-
-\begin{equation}
-    \begin{split}
-        g_1(x) = - x_1 + 0.0193 x_3 \leq 0\\
-        g_2(x) = - x_2 + 0.00954 x_3 \leq 0\\
-        g_3(x) = - \pi x_3^2 x_4 -\frac{4}{3}\pi x_3^3 + 1296000 \leq 0\\
-        g_4(x) = x_4 -240 \leq 0\\
-    \end{split}
-\end{equation}
-
-The original bounding limits of the variables, extracted from computational work
-statements, are:
-
-\begin{equation}
-    \begin{split}
-        0 \leq x_1 \leq 99\\
-        0 \leq x_2 \leq 99\\
-        10 \leq x_3 \leq 200\\
-        10 \leq x_4 \leq 200\\
-    \end{split}
-\end{equation}
-
-For some reason these settings does not work at all with the selected optimizers, so
-some research in the literature \textit{Solving Design of Pressure Vessel Engineering
-Problem Using a Fruit Fly Optimization Algorithm - XIANTING KE et al} suggest the
-following bounding limits:
-
-\begin{equation}
-    \begin{split}
-        0.0625 \leq x_1 \leq 99 \times 0.0625\\
-        0.0625 \leq x_2 \leq 99 \times 0.0625\\
-        10 \leq x_3 \leq 200\\
-        10 \leq x_4 \leq 200
-    \end{split}
-\end{equation}
-
-But these settings produce many random, bizarre and noisy results in all selected optimizers. Then
-a proud-and-lame-homemade set of variable boundings comes in handy, obtained by tweaking the original
-boundings:
-
-\begin{equation}
-    \begin{split}
-        0.75 \leq x_1 \leq 0.8\\
-        0.35 \leq x_2 \leq 0.4\\
-        39.5 \leq x_3 \leq 41.0\\
-        195.0 \leq x_4 \leq 205.0\\
-    \end{split}
-\end{equation}
-
-It is not intended here to point out modeling errors of any kind, nor point out package
-errors made by the authors or ours, but the homemade bounding limits was necessary to
-reach the literature results.
-
-\subsection{Constraint Implementation}
-\label{subsec:methodology-constraint-implementation}
-The constraints that all problems are subjected were implemented as \textit{penalty functions},
-that is, it adds a high value when the constraint is not satisfied, zero otherwise. It is an optional requirement
-from computational work in question and is the recommended way to put constraints from \textit{MealPy}'s
-Manual.
-
-\subsection{Programming Language}
-\label{subsec:methodology-programming-language}
-
-The chosen programming language for the test code was \textit{Python Language}, version 3.10, because it is an opensource language easy to
-program and has a huge amount of packages regarding artificial intelligence, genetic algorithms and swarm based algorithms.
-From these packages it was selected \textit{MealPy} package, version 2.5.1, because it comprises all the algorithm's classed tested in this paper.
-
-\subsection{Algorithm Selection}
-\label{subsec:methodology-algorithm-selection}
-
-The algorithm selection was made in two steps: first, it was extracted simple version of the two classes (evolutionary and swarm based) and
-then it was used a simple shuffle using Python's \textit{random.shuffle} in a terminal - no script was required.
-
-The chosen algorithms were:
-
-\begin{itemize}
-    \item \textit{\textbf{Evolution Based Algorithms: }} LevyEP (Evolutionary Programming),
-    OriginalES (Evolution Strategy) and BaseGA (Genetic Algorithm)
-    \item \textit{\textbf{Swarm Based Algorithms: }} OriginalBeesA (Bees Algorithm),
-    OriginalFFA (Original Firefly Algorithm) and OriginalPSO (Particle Swarm Optimization)
-\end{itemize}
-
-\subsection{Optimizer Tuning}
-\label{subsec:methodology-optimizer-tuning}
-
-The hyperparameters for each optimizer were tuned using the \textit{MealPy}'s \textit{Tuner} utility.
-It is a recomended procedure to tune hyperparameters for each optimizer and problem, according to
-\textit{MealPy}'s Manual.
-The \textit{Tuner} utility is a very simple grid search metaheuristic search tool
-that test each grid configuration for a specified oprimizer runs.
-Although simple, it is a very expensive procedure that took 2 days to complete. It was defined 10 runs for each
-configuration, with the following set of hyperparameter:
-
-\begin{itemize}
-    \item \textit{\textbf{Evolution Based Algorithms: }}
-        \subitem \textit{LevyEP:}
-            \subsubitem \textit{bout\_size (float)}: percentage of child agents implement tournament selection.
-        \subitem \textit{OriginalES:}
-            \subsubitem \textit{lamda (float)}: Percentage of child agents evolving in the next generation.
-        \subitem \textit{BaseGA:}
-            \subsubitem \textit{pc (float)}: cross-over probability
-            \subsubitem \textit{pm (float)}: mutation probability
-    \item \textit{\textbf{Swarm Based Algorithms: }}
-        \subitem \textit{OriginalBeesA:}
-            \subsubitem \textit{selected\_site\_ratio (float)}
-            \subsubitem \textit{elite\_site\_ratio (float)}
-            \subsubitem \textit{selected\_site\_bee\_ratio (float)}
-            \subsubitem \textit{elite\_site\_bee\_ratio (float)}
-            \subsubitem \textit{dance\_radius (float)}
-            \subsubitem \textit{dance\_reduction (float)}
-        \subitem \textit{OriginalFFA:}
-            \subsubitem \textit{gamma (float)}: Light Absorption Coefficient
-            \subsubitem \textit{beta\_base (float)}: Attraction Coefficient Base Value
-            \subsubitem \textit{alpha (float)}: Mutation Coefficient
-            \subsubitem \textit{alpha\_damp (float)}: Mutation Coefficient Damp Rate
-            \subsubitem \textit{delta (float)}: Mutation Step Size
-            \subsubitem \textit{exponent (int)}: Exponent
-        \subitem \textit{OriginalPSO:}
-            \subsubitem \textit{c1 (float)}: local coefficient
-            \subsubitem \textit{c2 (float)}: global coefficient
-            \subsubitem \textit{w\_min (float)}: Weight min of bird
-            \subsubitem \textit{w\_max (float)}: Weight max of bird
-
-\end{itemize}
-
-\subsection{Optimizer Parameters}
-\label{subsec:methodology-optimizer-parameters}
-
-For all optimizers and problems, were selected the following parameters:
-
-\begin{itemize}
-    \item \textit{Runs}: 100 runs
-    \item \textit{Epochs}: 100 epochs
-    \item \textit{Population}: 100 initial points
-\end{itemize}
-
-The initial solutions were randomly selected using the same seed for all algorithms.
-
-\section{Results}
-\label{sec:results}
-\subsection{Spring Tension Design}
-\label{ssubec:spring_problem}
-
-\begin{table}[H]
-\centering
-\caption{Statistical Information about function values for Spring Tension Design}
-\label{function_values:spring_problem}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrrrrr}
-\toprule
-Algorithm &      Min F &     Mean F &   Median F &      Max F &   StdDev F \\
-\midrule
-       EP & 0.01250534 & 0.01255960 & 0.01253156 & 0.01453933 & 0.00020190 \\
-       ES & 0.01252956 & 0.01281857 & 0.01274283 & 0.01346214 & 0.00024181 \\
-       GA & 0.01252305 & 0.01628575 & 0.01616768 & 0.02561808 & 0.00273276 \\
-    BeesA & 0.01250200 & 0.01268010 & 0.01261691 & 0.01406679 & 0.00021629 \\
-      FFA & 0.01249803 & 0.01254780 & 0.01253499 & 0.01268116 & 0.00003152 \\
-      PSO & 0.01252626 & 0.01390866 & 0.01318774 & 0.03036537 & 0.00342240 \\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{figure}[H]
-\centering
-\caption{Boxplot for Spring Tension Design}
-\label{fig:spring_tension_design_boxplot}
-\includegraphics[scale=0.5]{images/spring_problem_boxplot.png}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\caption{Convergence lines for Spring Tension Design}
-\label{fig:spring_problem_convergence}
-\includegraphics[width= 0.4 \textwidth]{images/spring_problem_convergence.png}
-\end{figure}
-
-\subsection{Pressure Vessel Design (Original)}
-\label{subsec:pressure_vessel_problem_original}
-
-\begin{table}[H]
-\centering
-\caption{Statistical Information about function values for Pressure Vessel Design (Original)}
-\label{function_values:pressure_vessel_problem_original}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrrrrr}
-\toprule
-Algorithm &         Min F &         Mean F &       Median F &          Max F &       StdDev F \\
-\midrule
-       EP &    0.08150806 &     0.15642850 &     0.09093798 &     1.32637552 &     0.16807714 \\
-       ES &    0.08161190 &   718.92910990 &     1.00278859 &  9443.54269260 &  2060.07774212 \\
-       GA &   17.06920868 &   525.00734162 &   361.53879602 &  3112.03503082 &   454.52386703 \\
-    BeesA & 2393.70106213 & 17564.33024022 & 15751.91467117 & 53850.38271384 & 10514.60780411 \\
-      FFA &    0.08306113 &     0.13296127 &     0.13106271 &     0.20084847 &     0.02396876 \\
-      PSO &    0.08149204 &     0.24191732 &     0.08159173 &    10.00611523 &     1.00072349 \\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{figure}[H]
-\centering
-\caption{Boxplot for Pressure Vessel Design (Original)}
-\label{fig:pressure_vessel_design_original_boxplot}
-\includegraphics[scale=0.5]{images/pressure_vessel_problem_original_boxplot.png}
-\end{figure}
+Figure~\ref{fig:pressure_vessel_problem_original_convergence} shows the
+function maximum, minimum and mean function of algorithm's evolution:
 
@@
 \label{fig:pressure_vessel_problem_original_convergence}
-\includegraphics[width= 0.4 \textwidth]{images/pressure_vessel_problem_original_convergence.png}
+\includegraphics[width=0.4 \textwidth]{images/pressure_vessel_problem_original_convergence.png}
 \end{figure}
 
-\subsection{Pressure Vessel Design}
-\label{subsec:pressure_vessel_problem}
-
-\begin{table}
-\centering
-\caption{Statistical Information about function values for Pressure Vessel Design}
-\label{function_values:pressure_vessel_problem}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrrrrr}
-\toprule
-Algorithm &         Min F &        Mean F &      Median F &         Max F &   StdDev F \\
-\midrule
-       EP & 5534.57345496 & 5534.63426098 & 5534.61416291 & 5534.92993607 & 0.05804548 \\
-       ES & 5534.57917966 & 5535.28165367 & 5535.06149254 & 5538.03003895 & 0.65098467 \\
-       GA & 5534.83662424 & 5538.36788889 & 5536.92932748 & 5550.91639342 & 3.57079951 \\
-    BeesA & 5534.57516657 & 5537.97495231 & 5537.04824684 & 5548.55587234 & 3.28239740 \\
-      FFA & 5534.57401617 & 5534.58849395 & 5534.58435493 & 5534.63296149 & 0.01341777 \\
-      PSO & 5534.57345480 & 5534.57381593 & 5534.57355270 & 5534.57625290 & 0.00053848 \\
-\bottomrule
-\end{tabular}
-}
-\end{table}
-
-\begin{figure}[H]
-\centering
-\caption{Boxplot for Pressure Vessel Design}
-\label{fig:pressure_vessel_design_boxplot}
-\includegraphics[scale=0.5]{images/pressure_vessel_problem_boxplot.png}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\caption{Convergence lines for Pressure Vessel Design}
-\label{fig:pressure_vessel_problem_convergence}
-\includegraphics[width=0.4 \textwidth]{images/pressure_vessel_problem_convergence.png}
-\end{figure}
-
-\subsection{Significance Test}
-\label{subsec:pressure_vessel_problem_significance_test}
-
-\begin{table}[H]
-\centering
-\caption{Significance Test Using Friedman Chi-Squared Test}
-\label{friedman_test}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrr}
-\toprule
-                          Problem &   Statistics &    p-value \\
-\midrule
-            Spring Tension Design & 339.05714286 & 0.00000000 \\
-           Pressure Vessel Design & 436.16000000 & 0.00000000 \\
-Pressure Vessel Design (Original) & 425.07428571 & 0.00000000 \\
-\bottomrule
-\end{tabular}
-}
-\end{table}
-
-\section{Discussion}
-
-The main objective of this work is demonstrate the inner work of a optimization class of algorithms called \textit{Quasi-Newton algorithms}.
-Four of them are presented, along with the results and analysis regarding convergence, function evaluations and function objective values.
-
-For implementation, it was decided to put constraints on search space, because for the original search space of some functions, like Ackley and Rastrigin, there are other minimas that will confuse every algorithm tested for this paper, and there is no sense on test a local minima procedure on these conditions.
-To restrain the initial solution to some region in the search space was a cheap and ready solution to avoid the algorithms to stop because of stumbling upon the wrong minimum.
-
-The \textit{Levenberg-Marquardt Algorithm} implemented for this paper is very sensitive to hyperparameters, namely $\alpha$ and $\lambda$, which was not tunned to every function, so, the conspicuous performance variation is noticeable along the results.
-LMA is known to be fast and reliable, but in our implementation it was found a little tricky to get the hyperparameters right for all the test functions.
-But for Rosenbrock and Rastrigin, it is the best option, even for lame implementations like ours.
-
-The \textit{Broyden–Fletcher–Goldfarb–Shanno} Algorithm was the only one that we decided to use it as is from \textit{SciPy}, because it has features desired for this work, like counting of function evaluations, gradient evaluation and iterations.
-It performed very well for Ackley and Booth Functions, and reasonably well for other functions.
-
-The \textit{Davidon–Fletcher–Powell} Algorithm is not implemented in \textit{SciPy} but its equations shows that it is the dual of BFGS, so, it was easy to implement using some \textit{SciPy} code for BFGS algorithm.
-In the DFP procedure, there is a Hessian inversion to be evaluated every iteration, then, numerical imprecision would be taken into consideration evaluating its results.
-While in some cases it has a superb performance (Like Ackley Function), it has very poor performance in Rosenbrock Function and even in Beale Function.
-The increase of dimensions makes DFP suffer of numerical imprecision due to the Hessian inversion, except for Rastrigin, and it is the loser algorithm in other functions.
-
-Finally, the \textit{Limited memory BFGS} has an average performance among the functions.
-The original algorithm was implemented using code found in the url https://github.com/qkolj/L-BFGS/blob/master/L-BFGS.ipynb.
-
-In fact, there are no Quasi-Newton algorithms that solver the minima problem for an any function.
-From the standpoint of performance and convergence, all the algorithms have an average performance and a reasonable convergence, although we have to restrain the search space to a small area near the optimal solution.
-
-\end{document}
+All algorithms tested have slow evolution for the original variable boundings, as it is shown in the convergence evolution.

### 2023-01-21 release/code/latex/includes/pressure_vessel_problem_wilcoxon_test.tex
Release Added

--- 2023-01-19 latex/article.tex
@@
-\documentclass[conference]{IEEEtran}
-\IEEEoverridecommandlockouts
-% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-\usepackage{cite}
-\usepackage{amsmath,amssymb,amsfonts}
-\usepackage{mathtools}
-\usepackage{algpseudocode}
-\usepackage{algorithm}
-\usepackage{algorithmicx}
-\usepackage{microtype}
-\usepackage{float}
-\usepackage{adjustbox}
-\usepackage{booktabs,makecell,tabularx}
-\usepackage{graphicx}
-\usepackage{textcomp}
-\usepackage{verbatim}
-\usepackage{xcolor}
-\usepackage{graphics} % for pdf, bitmapped graphics files
-\usepackage{epsfig} % for postscript graphics files
-\usepackage{mathptmx} % assumes new font selection scheme installed
-\usepackage{multicol}
-\usepackage[english]{babel}
-\usepackage[T1]{fontenc}
-\restylefloat{table}
-\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
-    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
-\begin{document}
-\title{Swarm and Evolutionary Based Algorithms used for Optimization}
-\author{
-	\IEEEauthorblockN{Augusto Mathias Adams\IEEEauthorrefmark{1}, Caio Phillipe Mizerkowski\IEEEauthorrefmark{2}, Christian Piltz Araújo\IEEEauthorrefmark{3} and Vinicius Eduardo dos Reis\IEEEauthorrefmark{4}}\\
-	\IEEEauthorblockA{\IEEEauthorrefmark{1}GRR20172143, augusto.adams@ufpr.br, \IEEEauthorrefmark{2}GRR20166403, caiomizerkowski@gmail.com,\\ \IEEEauthorrefmark{3}GRR20172197, christian0294@yahoo.com.br, \IEEEauthorrefmark{4}GRR20175957, eduardo.reis02@gmail.com}
-}
-
-\maketitle
-
-\begin{abstract}
-    In this paper, a study of evolution and swarm based algorithms is presented,
-    using two classical engineering problems: \textit{Spring Tension} and \textit{Pressure Vessel
-    Designs}. The test code for the problems was made using the \textit{Python Language},
-    version 3.10 and uses \textit{MealPy} package, version 2.5.1,  to provide the algorithms.
-    The algorithms were randomly chosen from a vast list of \textit{MealPy}'s algorithms:
-    \textit{Evolutionary Programming (LevyEP)}, \textit{Evolution Strategies (OriginalES)} and
-    \textit{Genetic Algorithm (BaseGA)} from \textit{evolutionary\_based} subpackage;
-    \textit{Bees Algorithm (OriginalBeesA)}, \textit{Firefly Algorithm (OriginalFFA)} and
-    \textit{Particle Swarm Optimization (OriginalPSO)} from \textit{swarm\_based} subpackage.
-    Each problem was modeled using \textit{SciPy} package, with constraints implemented as
-    \textit{penalty functions}. Each algorithm were optimized separately to extract the best
-    solutions from each problem using the \textit{MealPy}'s \textit{Tuner} utility.
-    The results, however, are dependant of algorithm and/or problem solved and the Friedman's chi
-    squared test for similarity make it noticeable because, although the values for best fits are
-    similar, running the same algorithm with different initial conditions does not converge to similar
-    values.
-\end{abstract}
-
-\begin{IEEEkeywords}
-	Optimization Methods, Evolutionary Programming, Evolutionary and Swarm Based Strategies.
-\end{IEEEkeywords}
-
-\section{Definitions}
-\label{sec:definitions}
-
-The main objective of this paper is study evolutionary and swarm intelligence algorithms.
-We present the main concepts of these two algorithm's classes, along with the chosen algorithms
-definitions in this section. All citations made in this document are due to Swarm Intelligence classes
-and to \textit{MealPy}'s documentation, which points out the theoretical documentation for each
-implemented algorithm.
-
-\textit{\textbf{Evolution}}: From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolutionary Algorithms belong to the Evolutionary Computation
-field of study concerned with computational methods inspired by the process
-and mechanisms of biological evolution. The process of evolution by
-means of natural selection (descent with modification) was proposed by
-Darwin to account for the variety of life and its suitability (adaptive
-fit) for its environment. The mechanisms of evolution describe how
-evolution actually takes place through the modification and propagation
-of genetic material (proteins). Evolutionary Algorithms are concerned
-with investigating computational systems that resemble simplified ver-
-sions of the processes and mechanisms of evolution toward achieving
-the effects of these processes and mechanisms, namely the development
-of adaptive systems. Additional subject areas that fall within the realm
-of Evolutionary Computation are algorithms that seek to exploit the
-properties from the related fields of Population Genetics, Population
-Ecology, Coevolutionary Biology, and Developmental Biology.
-
-\textit{\textbf{Swarm Intelligence}}: From Jason Brownlee's \textit{``Clever Algorithms''} -
-Swarm intelligence is the study of computational systems inspired by
-the ‘collective intelligence’. Collective Intelligence emerges through the
-cooperation of large numbers of homogeneous agents in the environment.
-Examples include schools of fish, flocks of birds, and colonies of ants.
-Such intelligence is decentralized, self-organizing and distributed through
-out an environment. In nature such systems are commonly used to
-solve problems such as effective foraging for food, prey evading, or
-colony re-location. The information is typically stored throughout the
-participating homogeneous agents, or is stored or communicated in
-the environment itself such as through the use of pheromones in ants,
-dancing in bees, and proximity in fish and birds.
-
-\textit{\textbf{Evolutionary Programming:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolutionary Programming is a Global Optimization algorithm and is an instance of an Evolutionary
-Algorithm from the field of Evolutionary Computation. The approach is a sibling of other Evolutionary
-Algorithms such as the Genetic Algorithm, and Learning Classifier Systems. It is sometimes confused with Genetic
-Programming given the similarity in name, and more recently it shows a strong functional similarity to Evolution Strategies.
-Evolutionary Programming is inspired by the theory of evolution by means of natural selection. Specifically, the technique is inspired by
-macro-level or the species-level process of evolution (phenotype, hereditary, variation) and is not concerned with the genetic mechanisms of
-evolution (genome, chromosomes, genes, alleles).
-
-\textit{\textbf{Evolutionary Strategies:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolution Strategies is a global optimization algorithm and is an instance of an Evolutionary Algorithm from the field of Evolutionary
-Computation. Evolution Strategies is a sibling technique to other Evolutionary Algorithms such as Genetic Algorithms (Section 3.2), Genetic
-Programming (Section 3.3), Learning Classifier Systems, and Evolutionary Programming. A popular descendant of
-the Evolution Strategies algorithm is the Covariance Matrix Adaptation Evolution Strategies (CMA-ES).
-
-\textit{\textbf{Genetic Algorithms:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-The Genetic Algorithm is an Adaptive Strategy and a Global Optimization technique. It is an Evolutionary Algorithm and belongs to the
-broader study of Evolutionary Computation. The Genetic Algorithm is a sibling of other Evolutionary Algorithms such as Genetic Programming,
- Evolution Strategies, Evolutionary Programming, and Learning Classifier Systems. The Genetic Algorithm is a parent of a large number of variant techniques
-and sub-fields too numerous to list. The Genetic Algorithm is inspired by population genetics (including heredity and gene frequencies),
-and evolution at the population level, as well as the Mendelian understanding of the structure (such as chromosomes, genes, alleles) and mechanisms
-(such as recombination and mutation). This is the so-called new or modern synthesis of evolutionary biology.
-
-\textit{\textbf{Particle Swarm Optimization:}} From Jason Brownlee's \textit{``Clever Algorithms''} - Particle Swarm Optimization belongs to the field of
-Swarm Intelligence and Collective Intelligence and is a sub-field of Computational Intelligence. Particle Swarm Optimization is related to other Swarm Intelligence
-algorithms such as Ant Colony Optimization and it is a baseline algorithm for many variations, too numerous to list. It is inspired by the social foraging behavior
-of some animals such as flocking behavior of birds and the schooling behavior of fish.
-
-\textit{\textbf{Firefly Algorithm:}} From Xin-She Yang \textit{``Nature-Inspired Metaheuristic Algorithms''} -
-The flashing light of fireflies is an amazing sight in the summer sky in the tropical and temperate regions. There are about two thousand firefly
-species, and most fireflies produce short and rhythmic flashes. The pattern of flashes is often unique for a particular species. The flashing light is
-produced by a process of bioluminescence, and the true functions of suchsignaling systems are still being debated. However, two fundamental functions
-of such flashes are to attract mating partners (communication), and to attract potential prey. In addition, flashing may also serve as a protective warning
-mechanism to remind potential predators of the bitter taste of fireflies. The firefly algorithm tries to mimic the attractiveness of Fireflies and has three
-basic rules:
-
-\begin{itemize}
-    \item All fireflies are unisex so that one firefly will be attracted to other
-          fireflies regardless of their sex;
-    \item Attractiveness is proportional to the their brightness, thus for any two
-          flashing fireflies, the less brighter one will move towards the brighter
-          one. The attractiveness is proportional to the brightness and they
-          both decrease as their distance increases. If there is no brighter one
-          than a particular firefly, it will move randomly;
-    \item The brightness of a firefly is affected or determined by the landscape
-          of the objective function.
-\end{itemize}
-
-\textit{\textbf{Bees Algorithm:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-The Bees Algorithm beings to Bee Inspired Algorithms and the field of Swarm Intelligence, and more broadly the fields of Computational
-Intelligence and Metaheuristics. The Bees Algorithm is related to other Bee Inspired Algorithms, such as Bee Colony Optimization, and other
-Swarm Intelligence algorithms such as Ant Colony Optimization and Particle Swarm Optimization.
-It is inspired by the foraging behavior of honey bees. Honey bees collect nectar from vast areas around their hive (more than
-10 kilometers). Bee Colonies have been observed to send bees to collect nectar from flower patches relative to the amount of food available at
-each patch. Bees communicate with each other at the hive via a waggle dance that informs other bees in the hive as to the direction, distance,
-and quality rating of food sources.
-
-\section{Methodology}
-\label{sec:methodology}
-
-\subsection{Optimization Problem Selection}
-\label{subsec:optimization-problem-selection}
-The two problems selected for this paper were \textit{Spring Tension Design} and \textit{Pressure Vessel Design}. Although it was simple
-to choose the first two problems from the computational work statements, the choice was more than justified because these aroblems are well
-known in the literature.
-Thus, the problem selection was driven by which has more than one source to compare results.
-
-\subsubsection{Spring Tension Design}
-\label{subsubsec:methodology-spring-tension-design}
-From \textit{Nature-Inspired Metaheuristic Algorithms - Xin-She Yang} -
-The design of a tension and compression spring is a well-known benchmark
-optimization problem.
-The main aim is to minimize the weight subject
-to constraints on deflection, stress, surge frequency and geometry. It involves
-three design variables: the wire diameter $x_1$ , coil diameter $x_2$ and
-number/length of the coil $x_3$.
-This problem can be summarized as:
-
-\begin{equation}
-    f (x) = x_1^2 x_2 (2 + x_3)
-\end{equation}
-
-subject to
-
-\begin{equation}
-    \begin{split}
-        g_1(x) = \frac{x_2^3 x_3}{71785 x_1^4} \leq 0\\
-        g_2(x) = \frac{4 x_2^2 - x_1 x_2}{12566 \left( x_1^3 x_2 - x_1^4\right)}\\
-        + \frac{1}{5108 x_1^2} -1 \leq 0\\
-        g_3(x) = 1 - \frac{140.45 x_1}{x_2^2 x_3} \leq 0\\
-        g_4 = \frac{x_1 + x_2}{1.5} - 1 \leq 0
-    \end{split}
-\end{equation}
-
-The original bounding limits of the variables, extracted from computational work
-statements, are:
-
-\begin{equation}
-    \begin{split}
-        0.05 \leq x_1 \leq 2.0\\
-        0.25 \leq x_2 \leq 1.3\\
-        2.0 \leq x_3 \leq 15.0
-    \end{split}
-\end{equation}
-
-\subsubsection{Pressure Vessel Design}
-\label{subsubsec:methodology-pressure-vessel-design}
-From \textit{Solving Design of Pressure Vessel Engineering
-Problem Using a Fruit Fly Optimization Algorithm - XIANTING KE et al} -
-A pressure vessel design model involves four decision variables: $x_1$ is defined
-thickness of the pressure vessel $T_s$ , $x_2$ stands for
-thickness of the head $T_H$ , $x_3$ represents inner radius of the
-vessel $R$ , and $x_4$ is on behalf of length of the vessel
-barring head $L$ , the total variables described as $( x_1 , x_2 , x_3 , x_4 )$.
-The objective function of the problem is to minimize the total cost, including
-the cost of material, forming, and welding.
-The general pressure vessel design optimization model is expressed as:
-
-\begin{equation}
-	\begin{split}
-        f(x) = 0.6224 x_1 x_3 x_4 + 1.7781 x_2 x_3^2 \\
-        + 3.1661 x_1^2 x_4 + 19.84 x_1^2 x_3
-	\end{split}
-\end{equation}
-
-subject to:
-
-\begin{equation}
-    \begin{split}
-        g_1(x) = - x_1 + 0.0193 x_3 \leq 0\\
-        g_2(x) = - x_2 + 0.00954 x_3 \leq 0\\
-        g_3(x) = - \pi x_3^2 x_4 -\frac{4}{3}\pi x_3^3 + 1296000 \leq 0\\
-        g_4(x) = x_4 -240 \leq 0\\
-    \end{split}
-\end{equation}
-
-The original bounding limits of the variables, extracted from computational work
-statements, are:
-
-\begin{equation}
-    \begin{split}
-        0 \leq x_1 \leq 99\\
-        0 \leq x_2 \leq 99\\
-        10 \leq x_3 \leq 200\\
-        10 \leq x_4 \leq 200\\
-    \end{split}
-\end{equation}
-
-For some reason these settings does not work at all with the selected optimizers, so
-some research in the literature \textit{Solving Design of Pressure Vessel Engineering
-Problem Using a Fruit Fly Optimization Algorithm - XIANTING KE et al} suggest the
-following bounding limits:
-
-\begin{equation}
-    \begin{split}
-        0.0625 \leq x_1 \leq 99 \times 0.0625\\
-        0.0625 \leq x_2 \leq 99 \times 0.0625\\
-        10 \leq x_3 \leq 200\\
-        10 \leq x_4 \leq 200
-    \end{split}
-\end{equation}
-
-But these settings produce many random, bizarre and noisy results in all selected optimizers. Then
-a proud-and-lame-homemade set of variable boundings comes in handy, obtained by tweaking the original
-boundings:
-
-\begin{equation}
-    \begin{split}
-        0.75 \leq x_1 \leq 0.8\\
-        0.35 \leq x_2 \leq 0.4\\
-        39.5 \leq x_3 \leq 41.0\\
-        195.0 \leq x_4 \leq 205.0\\
-    \end{split}
-\end{equation}
-
-It is not intended here to point out modeling errors of any kind, nor point out package
-errors made by the authors or ours, but the homemade bounding limits was necessary to
-reach the literature results.
-
-\subsection{Constraint Implementation}
-\label{subsec:methodology-constraint-implementation}
-The constraints that all problems are subjected were implemented as \textit{penalty functions},
-that is, it adds a high value when the constraint is not satisfied, zero otherwise. It is an optional requirement
-from computational work in question and is the recommended way to put constraints from \textit{MealPy}'s
-Manual.
-
-\subsection{Programming Language}
-\label{subsec:methodology-programming-language}
-
-The chosen programming language for the test code was \textit{Python Language}, version 3.10, because it is an opensource language easy to
-program and has a huge amount of packages regarding artificial intelligence, genetic algorithms and swarm based algorithms.
-From these packages it was selected \textit{MealPy} package, version 2.5.1, because it comprises all the algorithm's classed tested in this paper.
-
-\subsection{Algorithm Selection}
-\label{subsec:methodology-algorithm-selection}
-
-The algorithm selection was made in two steps: first, it was extracted simple version of the two classes (evolutionary and swarm based) and
-then it was used a simple shuffle using Python's \textit{random.shuffle} in a terminal - no script was required.
-
-The chosen algorithms were:
-
-\begin{itemize}
-    \item \textit{\textbf{Evolution Based Algorithms: }} LevyEP (Evolutionary Programming),
-    OriginalES (Evolution Strategy) and BaseGA (Genetic Algorithm)
-    \item \textit{\textbf{Swarm Based Algorithms: }} OriginalBeesA (Bees Algorithm),
-    OriginalFFA (Original Firefly Algorithm) and OriginalPSO (Particle Swarm Optimization)
-\end{itemize}
-
-\subsection{Optimizer Tuning}
-\label{subsec:methodology-optimizer-tuning}
-
-The hyperparameters for each optimizer were tuned using the \textit{MealPy}'s \textit{Tuner} utility.
-It is a recomended procedure to tune hyperparameters for each optimizer and problem, according to
-\textit{MealPy}'s Manual.
-The \textit{Tuner} utility is a very simple grid search metaheuristic search tool
-that test each grid configuration for a specified oprimizer runs.
-Although simple, it is a very expensive procedure that took 2 days to complete. It was defined 10 runs for each
-configuration, with the following set of hyperparameter:
-
-\begin{itemize}
-    \item \textit{\textbf{Evolution Based Algorithms: }}
-        \subitem \textit{LevyEP:}
-            \subsubitem \textit{bout\_size (float)}: percentage of child agents implement tournament selection.
-        \subitem \textit{OriginalES:}
-            \subsubitem \textit{lamda (float)}: Percentage of child agents evolving in the next generation.
-        \subitem \textit{BaseGA:}
-            \subsubitem \textit{pc (float)}: cross-over probability
-            \subsubitem \textit{pm (float)}: mutation probability
-    \item \textit{\textbf{Swarm Based Algorithms: }}
-        \subitem \textit{OriginalBeesA:}
-            \subsubitem \textit{selected\_site\_ratio (float)}
-            \subsubitem \textit{elite\_site\_ratio (float)}
-            \subsubitem \textit{selected\_site\_bee\_ratio (float)}
-            \subsubitem \textit{elite\_site\_bee\_ratio (float)}
-            \subsubitem \textit{dance\_radius (float)}
-            \subsubitem \textit{dance\_reduction (float)}
-        \subitem \textit{OriginalFFA:}
-            \subsubitem \textit{gamma (float)}: Light Absorption Coefficient
-            \subsubitem \textit{beta\_base (float)}: Attraction Coefficient Base Value
-            \subsubitem \textit{alpha (float)}: Mutation Coefficient
-            \subsubitem \textit{alpha\_damp (float)}: Mutation Coefficient Damp Rate
-            \subsubitem \textit{delta (float)}: Mutation Step Size
-            \subsubitem \textit{exponent (int)}: Exponent
-        \subitem \textit{OriginalPSO:}
-            \subsubitem \textit{c1 (float)}: local coefficient
-            \subsubitem \textit{c2 (float)}: global coefficient
-            \subsubitem \textit{w\_min (float)}: Weight min of bird
-            \subsubitem \textit{w\_max (float)}: Weight max of bird
-
-\end{itemize}
-
-\subsection{Optimizer Parameters}
-\label{subsec:methodology-optimizer-parameters}
-
-For all optimizers and problems, were selected the following parameters:
-
-\begin{itemize}
-    \item \textit{Runs}: 100 runs
-    \item \textit{Epochs}: 100 epochs
-    \item \textit{Population}: 100 initial points
-\end{itemize}
-
-The initial solutions were randomly selected using the same seed for all algorithms.
-
-\section{Results}
-\label{sec:results}
-\subsection{Spring Tension Design}
-\label{ssubec:spring_problem}
+The Table~\ref{wilcoxon_test:pressure_vessel_problem} gives the Wilcoxon test results
+for \textit{Pressure Vessel Design} using the proud-and-lame-homemade variables bounding
+as exposed in Section~\ref{subsubsec:methodology-pressure-vessel-design}.
 
@@
 \centering
-\caption{Statistical Information about function values for Spring Tension Design}
-\label{function_values:spring_problem}
+\caption{Significance Test Using Wilcoxon Test for Pressure Vessel Design}
+\label{wilcoxon_test:pressure_vessel_problem}
 \resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrrrrr}
+\begin{tabular}{lllllll}
 \toprule
-Algorithm &      Min F &     Mean F &   Median F &      Max F &   StdDev F \\
+  --- & EP & ES & GA & BeesA & FFA & PSO \\
 \midrule
-       EP & 0.01250534 & 0.01255960 & 0.01253156 & 0.01453933 & 0.00020190 \\
-       ES & 0.01252956 & 0.01281857 & 0.01274283 & 0.01346214 & 0.00024181 \\
-       GA & 0.01252305 & 0.01628575 & 0.01616768 & 0.02561808 & 0.00273276 \\
-    BeesA & 0.01250200 & 0.01268010 & 0.01261691 & 0.01406679 & 0.00021629 \\
-      FFA & 0.01249803 & 0.01254780 & 0.01253499 & 0.01268116 & 0.00003152 \\
-      PSO & 0.01252626 & 0.01390866 & 0.01318774 & 0.03036537 & 0.00342240 \\
+   EP & 0.0 & 9.04e-18 & 3.90e-18 & 6.12e-18 & 8.79e-12 & 4.40e-18 \\
+   ES & 9.04e-18 & 0.0 & 1.71e-14 & 1.64e-13 & 4.81e-18 & 3.90e-18 \\
+   GA & 3.90e-18 & 1.71e-14 & 0.0 & 0.38 & 3.90e-18 & 3.90e-18 \\
+BeesA & 6.12e-18 & 1.64e-13 & 0.38 & 0.0 & 4.30e-18 & 3.90e-18 \\
+  FFA & 8.79e-12 & 4.81e-18 & 3.90e-18 & 4.30e-18 & 0.0 & 4.02e-18 \\
+  PSO & 4.40e-18 & 3.90e-18 & 3.90e-18 & 3.90e-18 & 4.02e-18 & 0.0 \\
 \bottomrule
@@
 
-\begin{figure}[H]
-\centering
-\caption{Boxplot for Spring Tension Design}
-\label{fig:spring_tension_design_boxplot}
-\includegraphics[scale=0.5]{images/spring_problem_boxplot.png}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\caption{Convergence lines for Spring Tension Design}
-\label{fig:spring_problem_convergence}
-\includegraphics[width= 0.4 \textwidth]{images/spring_problem_convergence.png}
-\end{figure}
-
-\subsection{Pressure Vessel Design (Original)}
-\label{subsec:pressure_vessel_problem_original}
-
-\begin{table}[H]
-\centering
-\caption{Statistical Information about function values for Pressure Vessel Design (Original)}
-\label{function_values:pressure_vessel_problem_original}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrrrrr}
-\toprule
-Algorithm &         Min F &         Mean F &       Median F &          Max F &       StdDev F \\
-\midrule
-       EP &    0.08150806 &     0.15642850 &     0.09093798 &     1.32637552 &     0.16807714 \\
-       ES &    0.08161190 &   718.92910990 &     1.00278859 &  9443.54269260 &  2060.07774212 \\
-       GA &   17.06920868 &   525.00734162 &   361.53879602 &  3112.03503082 &   454.52386703 \\
-    BeesA & 2393.70106213 & 17564.33024022 & 15751.91467117 & 53850.38271384 & 10514.60780411 \\
-      FFA &    0.08306113 &     0.13296127 &     0.13106271 &     0.20084847 &     0.02396876 \\
-      PSO &    0.08149204 &     0.24191732 &     0.08159173 &    10.00611523 &     1.00072349 \\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{figure}[H]
-\centering
-\caption{Boxplot for Pressure Vessel Design (Original)}
-\label{fig:pressure_vessel_design_original_boxplot}
-\includegraphics[scale=0.5]{images/pressure_vessel_problem_original_boxplot.png}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\caption{Convergence lines for Pressure Vessel Design (Original)}
-\label{fig:pressure_vessel_problem_original_convergence}
-\includegraphics[width= 0.4 \textwidth]{images/pressure_vessel_problem_original_convergence.png}
-\end{figure}
-
-\subsection{Pressure Vessel Design}
-\label{subsec:pressure_vessel_problem}
-
-\begin{table}
-\centering
-\caption{Statistical Information about function values for Pressure Vessel Design}
-\label{function_values:pressure_vessel_problem}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrrrrr}
-\toprule
-Algorithm &         Min F &        Mean F &      Median F &         Max F &   StdDev F \\
-\midrule
-       EP & 5534.57345496 & 5534.63426098 & 5534.61416291 & 5534.92993607 & 0.05804548 \\
-       ES & 5534.57917966 & 5535.28165367 & 5535.06149254 & 5538.03003895 & 0.65098467 \\
-       GA & 5534.83662424 & 5538.36788889 & 5536.92932748 & 5550.91639342 & 3.57079951 \\
-    BeesA & 5534.57516657 & 5537.97495231 & 5537.04824684 & 5548.55587234 & 3.28239740 \\
-      FFA & 5534.57401617 & 5534.58849395 & 5534.58435493 & 5534.63296149 & 0.01341777 \\
-      PSO & 5534.57345480 & 5534.57381593 & 5534.57355270 & 5534.57625290 & 0.00053848 \\
-\bottomrule
-\end{tabular}
-}
-\end{table}
-
-\begin{figure}[H]
-\centering
-\caption{Boxplot for Pressure Vessel Design}
-\label{fig:pressure_vessel_design_boxplot}
-\includegraphics[scale=0.5]{images/pressure_vessel_problem_boxplot.png}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\caption{Convergence lines for Pressure Vessel Design}
-\label{fig:pressure_vessel_problem_convergence}
-\includegraphics[width=0.4 \textwidth]{images/pressure_vessel_problem_convergence.png}
-\end{figure}
-
-\subsection{Significance Test}
-\label{subsec:pressure_vessel_problem_significance_test}
-
-\begin{table}[H]
-\centering
-\caption{Significance Test Using Friedman Chi-Squared Test}
-\label{friedman_test}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrr}
-\toprule
-                          Problem &   Statistics &    p-value \\
-\midrule
-            Spring Tension Design & 339.05714286 & 0.00000000 \\
-           Pressure Vessel Design & 436.16000000 & 0.00000000 \\
-Pressure Vessel Design (Original) & 425.07428571 & 0.00000000 \\
-\bottomrule
-\end{tabular}
-}
-\end{table}
-
-\section{Discussion}
-
-The main objective of this work is demonstrate the inner work of a optimization class of algorithms called \textit{Quasi-Newton algorithms}.
-Four of them are presented, along with the results and analysis regarding convergence, function evaluations and function objective values.
-
-For implementation, it was decided to put constraints on search space, because for the original search space of some functions, like Ackley and Rastrigin, there are other minimas that will confuse every algorithm tested for this paper, and there is no sense on test a local minima procedure on these conditions.
-To restrain the initial solution to some region in the search space was a cheap and ready solution to avoid the algorithms to stop because of stumbling upon the wrong minimum.
-
-The \textit{Levenberg-Marquardt Algorithm} implemented for this paper is very sensitive to hyperparameters, namely $\alpha$ and $\lambda$, which was not tunned to every function, so, the conspicuous performance variation is noticeable along the results.
-LMA is known to be fast and reliable, but in our implementation it was found a little tricky to get the hyperparameters right for all the test functions.
-But for Rosenbrock and Rastrigin, it is the best option, even for lame implementations like ours.
-
-The \textit{Broyden–Fletcher–Goldfarb–Shanno} Algorithm was the only one that we decided to use it as is from \textit{SciPy}, because it has features desired for this work, like counting of function evaluations, gradient evaluation and iterations.
-It performed very well for Ackley and Booth Functions, and reasonably well for other functions.
-
-The \textit{Davidon–Fletcher–Powell} Algorithm is not implemented in \textit{SciPy} but its equations shows that it is the dual of BFGS, so, it was easy to implement using some \textit{SciPy} code for BFGS algorithm.
-In the DFP procedure, there is a Hessian inversion to be evaluated every iteration, then, numerical imprecision would be taken into consideration evaluating its results.
-While in some cases it has a superb performance (Like Ackley Function), it has very poor performance in Rosenbrock Function and even in Beale Function.
-The increase of dimensions makes DFP suffer of numerical imprecision due to the Hessian inversion, except for Rastrigin, and it is the loser algorithm in other functions.
-
-Finally, the \textit{Limited memory BFGS} has an average performance among the functions.
-The original algorithm was implemented using code found in the url https://github.com/qkolj/L-BFGS/blob/master/L-BFGS.ipynb.
-
-In fact, there are no Quasi-Newton algorithms that solver the minima problem for an any function.
-From the standpoint of performance and convergence, all the algorithms have an average performance and a reasonable convergence, although we have to restrain the search space to a small area near the optimal solution.
-
-\end{document}
+EP, ES, FAA and PSO appears to have the same distributions.
+However, BeesA and GA appears to have different distributions.
+This fact confirms the results found in Table~\ref{function_values:pressure_vessel_problem}.

### 2023-01-21 release/code/latex/includes/spring_problem.tex
Release Added

--- 2023-01-19 latex/article.tex
@@
-\documentclass[conference]{IEEEtran}
-\IEEEoverridecommandlockouts
-% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-\usepackage{cite}
-\usepackage{amsmath,amssymb,amsfonts}
-\usepackage{mathtools}
-\usepackage{algpseudocode}
-\usepackage{algorithm}
-\usepackage{algorithmicx}
-\usepackage{microtype}
-\usepackage{float}
-\usepackage{adjustbox}
-\usepackage{booktabs,makecell,tabularx}
-\usepackage{graphicx}
-\usepackage{textcomp}
-\usepackage{verbatim}
-\usepackage{xcolor}
-\usepackage{graphics} % for pdf, bitmapped graphics files
-\usepackage{epsfig} % for postscript graphics files
-\usepackage{mathptmx} % assumes new font selection scheme installed
-\usepackage{multicol}
-\usepackage[english]{babel}
-\usepackage[T1]{fontenc}
-\restylefloat{table}
-\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
-    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
-\begin{document}
-\title{Swarm and Evolutionary Based Algorithms used for Optimization}
-\author{
-	\IEEEauthorblockN{Augusto Mathias Adams\IEEEauthorrefmark{1}, Caio Phillipe Mizerkowski\IEEEauthorrefmark{2}, Christian Piltz Araújo\IEEEauthorrefmark{3} and Vinicius Eduardo dos Reis\IEEEauthorrefmark{4}}\\
-	\IEEEauthorblockA{\IEEEauthorrefmark{1}GRR20172143, augusto.adams@ufpr.br, \IEEEauthorrefmark{2}GRR20166403, caiomizerkowski@gmail.com,\\ \IEEEauthorrefmark{3}GRR20172197, christian0294@yahoo.com.br, \IEEEauthorrefmark{4}GRR20175957, eduardo.reis02@gmail.com}
-}
-
-\maketitle
-
-\begin{abstract}
-    In this paper, a study of evolution and swarm based algorithms is presented,
-    using two classical engineering problems: \textit{Spring Tension} and \textit{Pressure Vessel
-    Designs}. The test code for the problems was made using the \textit{Python Language},
-    version 3.10 and uses \textit{MealPy} package, version 2.5.1,  to provide the algorithms.
-    The algorithms were randomly chosen from a vast list of \textit{MealPy}'s algorithms:
-    \textit{Evolutionary Programming (LevyEP)}, \textit{Evolution Strategies (OriginalES)} and
-    \textit{Genetic Algorithm (BaseGA)} from \textit{evolutionary\_based} subpackage;
-    \textit{Bees Algorithm (OriginalBeesA)}, \textit{Firefly Algorithm (OriginalFFA)} and
-    \textit{Particle Swarm Optimization (OriginalPSO)} from \textit{swarm\_based} subpackage.
-    Each problem was modeled using \textit{SciPy} package, with constraints implemented as
-    \textit{penalty functions}. Each algorithm were optimized separately to extract the best
-    solutions from each problem using the \textit{MealPy}'s \textit{Tuner} utility.
-    The results, however, are dependant of algorithm and/or problem solved and the Friedman's chi
-    squared test for similarity make it noticeable because, although the values for best fits are
-    similar, running the same algorithm with different initial conditions does not converge to similar
-    values.
-\end{abstract}
-
-\begin{IEEEkeywords}
-	Optimization Methods, Evolutionary Programming, Evolutionary and Swarm Based Strategies.
-\end{IEEEkeywords}
-
-\section{Definitions}
-\label{sec:definitions}
-
-The main objective of this paper is study evolutionary and swarm intelligence algorithms.
-We present the main concepts of these two algorithm's classes, along with the chosen algorithms
-definitions in this section. All citations made in this document are due to Swarm Intelligence classes
-and to \textit{MealPy}'s documentation, which points out the theoretical documentation for each
-implemented algorithm.
-
-\textit{\textbf{Evolution}}: From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolutionary Algorithms belong to the Evolutionary Computation
-field of study concerned with computational methods inspired by the process
-and mechanisms of biological evolution. The process of evolution by
-means of natural selection (descent with modification) was proposed by
-Darwin to account for the variety of life and its suitability (adaptive
-fit) for its environment. The mechanisms of evolution describe how
-evolution actually takes place through the modification and propagation
-of genetic material (proteins). Evolutionary Algorithms are concerned
-with investigating computational systems that resemble simplified ver-
-sions of the processes and mechanisms of evolution toward achieving
-the effects of these processes and mechanisms, namely the development
-of adaptive systems. Additional subject areas that fall within the realm
-of Evolutionary Computation are algorithms that seek to exploit the
-properties from the related fields of Population Genetics, Population
-Ecology, Coevolutionary Biology, and Developmental Biology.
-
-\textit{\textbf{Swarm Intelligence}}: From Jason Brownlee's \textit{``Clever Algorithms''} -
-Swarm intelligence is the study of computational systems inspired by
-the ‘collective intelligence’. Collective Intelligence emerges through the
-cooperation of large numbers of homogeneous agents in the environment.
-Examples include schools of fish, flocks of birds, and colonies of ants.
-Such intelligence is decentralized, self-organizing and distributed through
-out an environment. In nature such systems are commonly used to
-solve problems such as effective foraging for food, prey evading, or
-colony re-location. The information is typically stored throughout the
-participating homogeneous agents, or is stored or communicated in
-the environment itself such as through the use of pheromones in ants,
-dancing in bees, and proximity in fish and birds.
-
-\textit{\textbf{Evolutionary Programming:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolutionary Programming is a Global Optimization algorithm and is an instance of an Evolutionary
-Algorithm from the field of Evolutionary Computation. The approach is a sibling of other Evolutionary
-Algorithms such as the Genetic Algorithm, and Learning Classifier Systems. It is sometimes confused with Genetic
-Programming given the similarity in name, and more recently it shows a strong functional similarity to Evolution Strategies.
-Evolutionary Programming is inspired by the theory of evolution by means of natural selection. Specifically, the technique is inspired by
-macro-level or the species-level process of evolution (phenotype, hereditary, variation) and is not concerned with the genetic mechanisms of
-evolution (genome, chromosomes, genes, alleles).
-
-\textit{\textbf{Evolutionary Strategies:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolution Strategies is a global optimization algorithm and is an instance of an Evolutionary Algorithm from the field of Evolutionary
-Computation. Evolution Strategies is a sibling technique to other Evolutionary Algorithms such as Genetic Algorithms (Section 3.2), Genetic
-Programming (Section 3.3), Learning Classifier Systems, and Evolutionary Programming. A popular descendant of
-the Evolution Strategies algorithm is the Covariance Matrix Adaptation Evolution Strategies (CMA-ES).
-
-\textit{\textbf{Genetic Algorithms:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-The Genetic Algorithm is an Adaptive Strategy and a Global Optimization technique. It is an Evolutionary Algorithm and belongs to the
-broader study of Evolutionary Computation. The Genetic Algorithm is a sibling of other Evolutionary Algorithms such as Genetic Programming,
- Evolution Strategies, Evolutionary Programming, and Learning Classifier Systems. The Genetic Algorithm is a parent of a large number of variant techniques
-and sub-fields too numerous to list. The Genetic Algorithm is inspired by population genetics (including heredity and gene frequencies),
-and evolution at the population level, as well as the Mendelian understanding of the structure (such as chromosomes, genes, alleles) and mechanisms
-(such as recombination and mutation). This is the so-called new or modern synthesis of evolutionary biology.
-
-\textit{\textbf{Particle Swarm Optimization:}} From Jason Brownlee's \textit{``Clever Algorithms''} - Particle Swarm Optimization belongs to the field of
-Swarm Intelligence and Collective Intelligence and is a sub-field of Computational Intelligence. Particle Swarm Optimization is related to other Swarm Intelligence
-algorithms such as Ant Colony Optimization and it is a baseline algorithm for many variations, too numerous to list. It is inspired by the social foraging behavior
-of some animals such as flocking behavior of birds and the schooling behavior of fish.
-
-\textit{\textbf{Firefly Algorithm:}} From Xin-She Yang \textit{``Nature-Inspired Metaheuristic Algorithms''} -
-The flashing light of fireflies is an amazing sight in the summer sky in the tropical and temperate regions. There are about two thousand firefly
-species, and most fireflies produce short and rhythmic flashes. The pattern of flashes is often unique for a particular species. The flashing light is
-produced by a process of bioluminescence, and the true functions of suchsignaling systems are still being debated. However, two fundamental functions
-of such flashes are to attract mating partners (communication), and to attract potential prey. In addition, flashing may also serve as a protective warning
-mechanism to remind potential predators of the bitter taste of fireflies. The firefly algorithm tries to mimic the attractiveness of Fireflies and has three
-basic rules:
-
-\begin{itemize}
-    \item All fireflies are unisex so that one firefly will be attracted to other
-          fireflies regardless of their sex;
-    \item Attractiveness is proportional to the their brightness, thus for any two
-          flashing fireflies, the less brighter one will move towards the brighter
-          one. The attractiveness is proportional to the brightness and they
-          both decrease as their distance increases. If there is no brighter one
-          than a particular firefly, it will move randomly;
-    \item The brightness of a firefly is affected or determined by the landscape
-          of the objective function.
-\end{itemize}
-
-\textit{\textbf{Bees Algorithm:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-The Bees Algorithm beings to Bee Inspired Algorithms and the field of Swarm Intelligence, and more broadly the fields of Computational
-Intelligence and Metaheuristics. The Bees Algorithm is related to other Bee Inspired Algorithms, such as Bee Colony Optimization, and other
-Swarm Intelligence algorithms such as Ant Colony Optimization and Particle Swarm Optimization.
-It is inspired by the foraging behavior of honey bees. Honey bees collect nectar from vast areas around their hive (more than
-10 kilometers). Bee Colonies have been observed to send bees to collect nectar from flower patches relative to the amount of food available at
-each patch. Bees communicate with each other at the hive via a waggle dance that informs other bees in the hive as to the direction, distance,
-and quality rating of food sources.
-
-\section{Methodology}
-\label{sec:methodology}
-
-\subsection{Optimization Problem Selection}
-\label{subsec:optimization-problem-selection}
-The two problems selected for this paper were \textit{Spring Tension Design} and \textit{Pressure Vessel Design}. Although it was simple
-to choose the first two problems from the computational work statements, the choice was more than justified because these aroblems are well
-known in the literature.
-Thus, the problem selection was driven by which has more than one source to compare results.
-
-\subsubsection{Spring Tension Design}
-\label{subsubsec:methodology-spring-tension-design}
-From \textit{Nature-Inspired Metaheuristic Algorithms - Xin-She Yang} -
-The design of a tension and compression spring is a well-known benchmark
-optimization problem.
-The main aim is to minimize the weight subject
-to constraints on deflection, stress, surge frequency and geometry. It involves
-three design variables: the wire diameter $x_1$ , coil diameter $x_2$ and
-number/length of the coil $x_3$.
-This problem can be summarized as:
-
-\begin{equation}
-    f (x) = x_1^2 x_2 (2 + x_3)
-\end{equation}
-
-subject to
-
-\begin{equation}
-    \begin{split}
-        g_1(x) = \frac{x_2^3 x_3}{71785 x_1^4} \leq 0\\
-        g_2(x) = \frac{4 x_2^2 - x_1 x_2}{12566 \left( x_1^3 x_2 - x_1^4\right)}\\
-        + \frac{1}{5108 x_1^2} -1 \leq 0\\
-        g_3(x) = 1 - \frac{140.45 x_1}{x_2^2 x_3} \leq 0\\
-        g_4 = \frac{x_1 + x_2}{1.5} - 1 \leq 0
-    \end{split}
-\end{equation}
-
-The original bounding limits of the variables, extracted from computational work
-statements, are:
-
-\begin{equation}
-    \begin{split}
-        0.05 \leq x_1 \leq 2.0\\
-        0.25 \leq x_2 \leq 1.3\\
-        2.0 \leq x_3 \leq 15.0
-    \end{split}
-\end{equation}
-
-\subsubsection{Pressure Vessel Design}
-\label{subsubsec:methodology-pressure-vessel-design}
-From \textit{Solving Design of Pressure Vessel Engineering
-Problem Using a Fruit Fly Optimization Algorithm - XIANTING KE et al} -
-A pressure vessel design model involves four decision variables: $x_1$ is defined
-thickness of the pressure vessel $T_s$ , $x_2$ stands for
-thickness of the head $T_H$ , $x_3$ represents inner radius of the
-vessel $R$ , and $x_4$ is on behalf of length of the vessel
-barring head $L$ , the total variables described as $( x_1 , x_2 , x_3 , x_4 )$.
-The objective function of the problem is to minimize the total cost, including
-the cost of material, forming, and welding.
-The general pressure vessel design optimization model is expressed as:
-
-\begin{equation}
-	\begin{split}
-        f(x) = 0.6224 x_1 x_3 x_4 + 1.7781 x_2 x_3^2 \\
-        + 3.1661 x_1^2 x_4 + 19.84 x_1^2 x_3
-	\end{split}
-\end{equation}
-
-subject to:
-
-\begin{equation}
-    \begin{split}
-        g_1(x) = - x_1 + 0.0193 x_3 \leq 0\\
-        g_2(x) = - x_2 + 0.00954 x_3 \leq 0\\
-        g_3(x) = - \pi x_3^2 x_4 -\frac{4}{3}\pi x_3^3 + 1296000 \leq 0\\
-        g_4(x) = x_4 -240 \leq 0\\
-    \end{split}
-\end{equation}
-
-The original bounding limits of the variables, extracted from computational work
-statements, are:
-
-\begin{equation}
-    \begin{split}
-        0 \leq x_1 \leq 99\\
-        0 \leq x_2 \leq 99\\
-        10 \leq x_3 \leq 200\\
-        10 \leq x_4 \leq 200\\
-    \end{split}
-\end{equation}
-
-For some reason these settings does not work at all with the selected optimizers, so
-some research in the literature \textit{Solving Design of Pressure Vessel Engineering
-Problem Using a Fruit Fly Optimization Algorithm - XIANTING KE et al} suggest the
-following bounding limits:
-
-\begin{equation}
-    \begin{split}
-        0.0625 \leq x_1 \leq 99 \times 0.0625\\
-        0.0625 \leq x_2 \leq 99 \times 0.0625\\
-        10 \leq x_3 \leq 200\\
-        10 \leq x_4 \leq 200
-    \end{split}
-\end{equation}
-
-But these settings produce many random, bizarre and noisy results in all selected optimizers. Then
-a proud-and-lame-homemade set of variable boundings comes in handy, obtained by tweaking the original
-boundings:
-
-\begin{equation}
-    \begin{split}
-        0.75 \leq x_1 \leq 0.8\\
-        0.35 \leq x_2 \leq 0.4\\
-        39.5 \leq x_3 \leq 41.0\\
-        195.0 \leq x_4 \leq 205.0\\
-    \end{split}
-\end{equation}
-
-It is not intended here to point out modeling errors of any kind, nor point out package
-errors made by the authors or ours, but the homemade bounding limits was necessary to
-reach the literature results.
-
-\subsection{Constraint Implementation}
-\label{subsec:methodology-constraint-implementation}
-The constraints that all problems are subjected were implemented as \textit{penalty functions},
-that is, it adds a high value when the constraint is not satisfied, zero otherwise. It is an optional requirement
-from computational work in question and is the recommended way to put constraints from \textit{MealPy}'s
-Manual.
-
-\subsection{Programming Language}
-\label{subsec:methodology-programming-language}
-
-The chosen programming language for the test code was \textit{Python Language}, version 3.10, because it is an opensource language easy to
-program and has a huge amount of packages regarding artificial intelligence, genetic algorithms and swarm based algorithms.
-From these packages it was selected \textit{MealPy} package, version 2.5.1, because it comprises all the algorithm's classed tested in this paper.
-
-\subsection{Algorithm Selection}
-\label{subsec:methodology-algorithm-selection}
-
-The algorithm selection was made in two steps: first, it was extracted simple version of the two classes (evolutionary and swarm based) and
-then it was used a simple shuffle using Python's \textit{random.shuffle} in a terminal - no script was required.
-
-The chosen algorithms were:
-
-\begin{itemize}
-    \item \textit{\textbf{Evolution Based Algorithms: }} LevyEP (Evolutionary Programming),
-    OriginalES (Evolution Strategy) and BaseGA (Genetic Algorithm)
-    \item \textit{\textbf{Swarm Based Algorithms: }} OriginalBeesA (Bees Algorithm),
-    OriginalFFA (Original Firefly Algorithm) and OriginalPSO (Particle Swarm Optimization)
-\end{itemize}
-
-\subsection{Optimizer Tuning}
-\label{subsec:methodology-optimizer-tuning}
-
-The hyperparameters for each optimizer were tuned using the \textit{MealPy}'s \textit{Tuner} utility.
-It is a recomended procedure to tune hyperparameters for each optimizer and problem, according to
-\textit{MealPy}'s Manual.
-The \textit{Tuner} utility is a very simple grid search metaheuristic search tool
-that test each grid configuration for a specified oprimizer runs.
-Although simple, it is a very expensive procedure that took 2 days to complete. It was defined 10 runs for each
-configuration, with the following set of hyperparameter:
-
-\begin{itemize}
-    \item \textit{\textbf{Evolution Based Algorithms: }}
-        \subitem \textit{LevyEP:}
-            \subsubitem \textit{bout\_size (float)}: percentage of child agents implement tournament selection.
-        \subitem \textit{OriginalES:}
-            \subsubitem \textit{lamda (float)}: Percentage of child agents evolving in the next generation.
-        \subitem \textit{BaseGA:}
-            \subsubitem \textit{pc (float)}: cross-over probability
-            \subsubitem \textit{pm (float)}: mutation probability
-    \item \textit{\textbf{Swarm Based Algorithms: }}
-        \subitem \textit{OriginalBeesA:}
-            \subsubitem \textit{selected\_site\_ratio (float)}
-            \subsubitem \textit{elite\_site\_ratio (float)}
-            \subsubitem \textit{selected\_site\_bee\_ratio (float)}
-            \subsubitem \textit{elite\_site\_bee\_ratio (float)}
-            \subsubitem \textit{dance\_radius (float)}
-            \subsubitem \textit{dance\_reduction (float)}
-        \subitem \textit{OriginalFFA:}
-            \subsubitem \textit{gamma (float)}: Light Absorption Coefficient
-            \subsubitem \textit{beta\_base (float)}: Attraction Coefficient Base Value
-            \subsubitem \textit{alpha (float)}: Mutation Coefficient
-            \subsubitem \textit{alpha\_damp (float)}: Mutation Coefficient Damp Rate
-            \subsubitem \textit{delta (float)}: Mutation Step Size
-            \subsubitem \textit{exponent (int)}: Exponent
-        \subitem \textit{OriginalPSO:}
-            \subsubitem \textit{c1 (float)}: local coefficient
-            \subsubitem \textit{c2 (float)}: global coefficient
-            \subsubitem \textit{w\_min (float)}: Weight min of bird
-            \subsubitem \textit{w\_max (float)}: Weight max of bird
-
-\end{itemize}
-
-\subsection{Optimizer Parameters}
-\label{subsec:methodology-optimizer-parameters}
-
-For all optimizers and problems, were selected the following parameters:
-
-\begin{itemize}
-    \item \textit{Runs}: 100 runs
-    \item \textit{Epochs}: 100 epochs
-    \item \textit{Population}: 100 initial points
-\end{itemize}
-
-The initial solutions were randomly selected using the same seed for all algorithms.
-
-\section{Results}
-\label{sec:results}
-\subsection{Spring Tension Design}
-\label{ssubec:spring_problem}
+Another view of the solutions are presented in Table~\ref{function_values:spring_problem}, where
+are summarized the statistics of all 100 possible solutions for different starting points (populations).
 
@@
 
-\begin{figure}[H]
-\centering
-\caption{Boxplot for Spring Tension Design}
-\label{fig:spring_tension_design_boxplot}
-\includegraphics[scale=0.5]{images/spring_problem_boxplot.png}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\caption{Convergence lines for Spring Tension Design}
-\label{fig:spring_problem_convergence}
-\includegraphics[width= 0.4 \textwidth]{images/spring_problem_convergence.png}
-\end{figure}
-
-\subsection{Pressure Vessel Design (Original)}
-\label{subsec:pressure_vessel_problem_original}
-
-\begin{table}[H]
-\centering
-\caption{Statistical Information about function values for Pressure Vessel Design (Original)}
-\label{function_values:pressure_vessel_problem_original}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrrrrr}
-\toprule
-Algorithm &         Min F &         Mean F &       Median F &          Max F &       StdDev F \\
-\midrule
-       EP &    0.08150806 &     0.15642850 &     0.09093798 &     1.32637552 &     0.16807714 \\
-       ES &    0.08161190 &   718.92910990 &     1.00278859 &  9443.54269260 &  2060.07774212 \\
-       GA &   17.06920868 &   525.00734162 &   361.53879602 &  3112.03503082 &   454.52386703 \\
-    BeesA & 2393.70106213 & 17564.33024022 & 15751.91467117 & 53850.38271384 & 10514.60780411 \\
-      FFA &    0.08306113 &     0.13296127 &     0.13106271 &     0.20084847 &     0.02396876 \\
-      PSO &    0.08149204 &     0.24191732 &     0.08159173 &    10.00611523 &     1.00072349 \\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{figure}[H]
-\centering
-\caption{Boxplot for Pressure Vessel Design (Original)}
-\label{fig:pressure_vessel_design_original_boxplot}
-\includegraphics[scale=0.5]{images/pressure_vessel_problem_original_boxplot.png}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\caption{Convergence lines for Pressure Vessel Design (Original)}
-\label{fig:pressure_vessel_problem_original_convergence}
-\includegraphics[width= 0.4 \textwidth]{images/pressure_vessel_problem_original_convergence.png}
-\end{figure}
-
-\subsection{Pressure Vessel Design}
-\label{subsec:pressure_vessel_problem}
-
-\begin{table}
-\centering
-\caption{Statistical Information about function values for Pressure Vessel Design}
-\label{function_values:pressure_vessel_problem}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrrrrr}
-\toprule
-Algorithm &         Min F &        Mean F &      Median F &         Max F &   StdDev F \\
-\midrule
-       EP & 5534.57345496 & 5534.63426098 & 5534.61416291 & 5534.92993607 & 0.05804548 \\
-       ES & 5534.57917966 & 5535.28165367 & 5535.06149254 & 5538.03003895 & 0.65098467 \\
-       GA & 5534.83662424 & 5538.36788889 & 5536.92932748 & 5550.91639342 & 3.57079951 \\
-    BeesA & 5534.57516657 & 5537.97495231 & 5537.04824684 & 5548.55587234 & 3.28239740 \\
-      FFA & 5534.57401617 & 5534.58849395 & 5534.58435493 & 5534.63296149 & 0.01341777 \\
-      PSO & 5534.57345480 & 5534.57381593 & 5534.57355270 & 5534.57625290 & 0.00053848 \\
-\bottomrule
-\end{tabular}
-}
-\end{table}
-
-\begin{figure}[H]
-\centering
-\caption{Boxplot for Pressure Vessel Design}
-\label{fig:pressure_vessel_design_boxplot}
-\includegraphics[scale=0.5]{images/pressure_vessel_problem_boxplot.png}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\caption{Convergence lines for Pressure Vessel Design}
-\label{fig:pressure_vessel_problem_convergence}
-\includegraphics[width=0.4 \textwidth]{images/pressure_vessel_problem_convergence.png}
-\end{figure}
-
-\subsection{Significance Test}
-\label{subsec:pressure_vessel_problem_significance_test}
-
-\begin{table}[H]
-\centering
-\caption{Significance Test Using Friedman Chi-Squared Test}
-\label{friedman_test}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrr}
-\toprule
-                          Problem &   Statistics &    p-value \\
-\midrule
-            Spring Tension Design & 339.05714286 & 0.00000000 \\
-           Pressure Vessel Design & 436.16000000 & 0.00000000 \\
-Pressure Vessel Design (Original) & 425.07428571 & 0.00000000 \\
-\bottomrule
-\end{tabular}
-}
-\end{table}
-
-\section{Discussion}
-
-The main objective of this work is demonstrate the inner work of a optimization class of algorithms called \textit{Quasi-Newton algorithms}.
-Four of them are presented, along with the results and analysis regarding convergence, function evaluations and function objective values.
-
-For implementation, it was decided to put constraints on search space, because for the original search space of some functions, like Ackley and Rastrigin, there are other minimas that will confuse every algorithm tested for this paper, and there is no sense on test a local minima procedure on these conditions.
-To restrain the initial solution to some region in the search space was a cheap and ready solution to avoid the algorithms to stop because of stumbling upon the wrong minimum.
-
-The \textit{Levenberg-Marquardt Algorithm} implemented for this paper is very sensitive to hyperparameters, namely $\alpha$ and $\lambda$, which was not tunned to every function, so, the conspicuous performance variation is noticeable along the results.
-LMA is known to be fast and reliable, but in our implementation it was found a little tricky to get the hyperparameters right for all the test functions.
-But for Rosenbrock and Rastrigin, it is the best option, even for lame implementations like ours.
-
-The \textit{Broyden–Fletcher–Goldfarb–Shanno} Algorithm was the only one that we decided to use it as is from \textit{SciPy}, because it has features desired for this work, like counting of function evaluations, gradient evaluation and iterations.
-It performed very well for Ackley and Booth Functions, and reasonably well for other functions.
-
-The \textit{Davidon–Fletcher–Powell} Algorithm is not implemented in \textit{SciPy} but its equations shows that it is the dual of BFGS, so, it was easy to implement using some \textit{SciPy} code for BFGS algorithm.
-In the DFP procedure, there is a Hessian inversion to be evaluated every iteration, then, numerical imprecision would be taken into consideration evaluating its results.
-While in some cases it has a superb performance (Like Ackley Function), it has very poor performance in Rosenbrock Function and even in Beale Function.
-The increase of dimensions makes DFP suffer of numerical imprecision due to the Hessian inversion, except for Rastrigin, and it is the loser algorithm in other functions.
-
-Finally, the \textit{Limited memory BFGS} has an average performance among the functions.
-The original algorithm was implemented using code found in the url https://github.com/qkolj/L-BFGS/blob/master/L-BFGS.ipynb.
-
-In fact, there are no Quasi-Newton algorithms that solver the minima problem for an any function.
-From the standpoint of performance and convergence, all the algorithms have an average performance and a reasonable convergence, although we have to restrain the search space to a small area near the optimal solution.
-
-\end{document}
+Looking at standard deviation, EP, ES and BeesA appear to have the same distribution;
+FFA has the lowest function value spread around the mean; GA and PSO have the largest
+function values spread around the mean and particularly GA tend to give discrepant results
+that the rest.

### 2023-01-21 release/code/latex/includes/spring_problem_best_fits.tex
Release Added

--- 2023-01-19 latex/article.tex
@@
-\documentclass[conference]{IEEEtran}
-\IEEEoverridecommandlockouts
-% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-\usepackage{cite}
-\usepackage{amsmath,amssymb,amsfonts}
-\usepackage{mathtools}
-\usepackage{algpseudocode}
-\usepackage{algorithm}
-\usepackage{algorithmicx}
-\usepackage{microtype}
-\usepackage{float}
-\usepackage{adjustbox}
-\usepackage{booktabs,makecell,tabularx}
-\usepackage{graphicx}
-\usepackage{textcomp}
-\usepackage{verbatim}
-\usepackage{xcolor}
-\usepackage{graphics} % for pdf, bitmapped graphics files
-\usepackage{epsfig} % for postscript graphics files
-\usepackage{mathptmx} % assumes new font selection scheme installed
-\usepackage{multicol}
-\usepackage[english]{babel}
-\usepackage[T1]{fontenc}
-\restylefloat{table}
-\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
-    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
-\begin{document}
-\title{Swarm and Evolutionary Based Algorithms used for Optimization}
-\author{
-	\IEEEauthorblockN{Augusto Mathias Adams\IEEEauthorrefmark{1}, Caio Phillipe Mizerkowski\IEEEauthorrefmark{2}, Christian Piltz Araújo\IEEEauthorrefmark{3} and Vinicius Eduardo dos Reis\IEEEauthorrefmark{4}}\\
-	\IEEEauthorblockA{\IEEEauthorrefmark{1}GRR20172143, augusto.adams@ufpr.br, \IEEEauthorrefmark{2}GRR20166403, caiomizerkowski@gmail.com,\\ \IEEEauthorrefmark{3}GRR20172197, christian0294@yahoo.com.br, \IEEEauthorrefmark{4}GRR20175957, eduardo.reis02@gmail.com}
-}
+In this section are presented the results of Spring Tension Design optimization,
+as exposed in Section~\ref{subsubsec:methodology-spring-tension-design}.
 
-\maketitle
-
-\begin{abstract}
-    In this paper, a study of evolution and swarm based algorithms is presented,
-    using two classical engineering problems: \textit{Spring Tension} and \textit{Pressure Vessel
-    Designs}. The test code for the problems was made using the \textit{Python Language},
-    version 3.10 and uses \textit{MealPy} package, version 2.5.1,  to provide the algorithms.
-    The algorithms were randomly chosen from a vast list of \textit{MealPy}'s algorithms:
-    \textit{Evolutionary Programming (LevyEP)}, \textit{Evolution Strategies (OriginalES)} and
-    \textit{Genetic Algorithm (BaseGA)} from \textit{evolutionary\_based} subpackage;
-    \textit{Bees Algorithm (OriginalBeesA)}, \textit{Firefly Algorithm (OriginalFFA)} and
-    \textit{Particle Swarm Optimization (OriginalPSO)} from \textit{swarm\_based} subpackage.
-    Each problem was modeled using \textit{SciPy} package, with constraints implemented as
-    \textit{penalty functions}. Each algorithm were optimized separately to extract the best
-    solutions from each problem using the \textit{MealPy}'s \textit{Tuner} utility.
-    The results, however, are dependant of algorithm and/or problem solved and the Friedman's chi
-    squared test for similarity make it noticeable because, although the values for best fits are
-    similar, running the same algorithm with different initial conditions does not converge to similar
-    values.
-\end{abstract}
-
-\begin{IEEEkeywords}
-	Optimization Methods, Evolutionary Programming, Evolutionary and Swarm Based Strategies.
-\end{IEEEkeywords}
-
-\section{Definitions}
-\label{sec:definitions}
-
-The main objective of this paper is study evolutionary and swarm intelligence algorithms.
-We present the main concepts of these two algorithm's classes, along with the chosen algorithms
-definitions in this section. All citations made in this document are due to Swarm Intelligence classes
-and to \textit{MealPy}'s documentation, which points out the theoretical documentation for each
-implemented algorithm.
-
-\textit{\textbf{Evolution}}: From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolutionary Algorithms belong to the Evolutionary Computation
-field of study concerned with computational methods inspired by the process
-and mechanisms of biological evolution. The process of evolution by
-means of natural selection (descent with modification) was proposed by
-Darwin to account for the variety of life and its suitability (adaptive
-fit) for its environment. The mechanisms of evolution describe how
-evolution actually takes place through the modification and propagation
-of genetic material (proteins). Evolutionary Algorithms are concerned
-with investigating computational systems that resemble simplified ver-
-sions of the processes and mechanisms of evolution toward achieving
-the effects of these processes and mechanisms, namely the development
-of adaptive systems. Additional subject areas that fall within the realm
-of Evolutionary Computation are algorithms that seek to exploit the
-properties from the related fields of Population Genetics, Population
-Ecology, Coevolutionary Biology, and Developmental Biology.
-
-\textit{\textbf{Swarm Intelligence}}: From Jason Brownlee's \textit{``Clever Algorithms''} -
-Swarm intelligence is the study of computational systems inspired by
-the ‘collective intelligence’. Collective Intelligence emerges through the
-cooperation of large numbers of homogeneous agents in the environment.
-Examples include schools of fish, flocks of birds, and colonies of ants.
-Such intelligence is decentralized, self-organizing and distributed through
-out an environment. In nature such systems are commonly used to
-solve problems such as effective foraging for food, prey evading, or
-colony re-location. The information is typically stored throughout the
-participating homogeneous agents, or is stored or communicated in
-the environment itself such as through the use of pheromones in ants,
-dancing in bees, and proximity in fish and birds.
-
-\textit{\textbf{Evolutionary Programming:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolutionary Programming is a Global Optimization algorithm and is an instance of an Evolutionary
-Algorithm from the field of Evolutionary Computation. The approach is a sibling of other Evolutionary
-Algorithms such as the Genetic Algorithm, and Learning Classifier Systems. It is sometimes confused with Genetic
-Programming given the similarity in name, and more recently it shows a strong functional similarity to Evolution Strategies.
-Evolutionary Programming is inspired by the theory of evolution by means of natural selection. Specifically, the technique is inspired by
-macro-level or the species-level process of evolution (phenotype, hereditary, variation) and is not concerned with the genetic mechanisms of
-evolution (genome, chromosomes, genes, alleles).
-
-\textit{\textbf{Evolutionary Strategies:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolution Strategies is a global optimization algorithm and is an instance of an Evolutionary Algorithm from the field of Evolutionary
-Computation. Evolution Strategies is a sibling technique to other Evolutionary Algorithms such as Genetic Algorithms (Section 3.2), Genetic
-Programming (Section 3.3), Learning Classifier Systems, and Evolutionary Programming. A popular descendant of
-the Evolution Strategies algorithm is the Covariance Matrix Adaptation Evolution Strategies (CMA-ES).
-
-\textit{\textbf{Genetic Algorithms:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-The Genetic Algorithm is an Adaptive Strategy and a Global Optimization technique. It is an Evolutionary Algorithm and belongs to the
-broader study of Evolutionary Computation. The Genetic Algorithm is a sibling of other Evolutionary Algorithms such as Genetic Programming,
- Evolution Strategies, Evolutionary Programming, and Learning Classifier Systems. The Genetic Algorithm is a parent of a large number of variant techniques
-and sub-fields too numerous to list. The Genetic Algorithm is inspired by population genetics (including heredity and gene frequencies),
-and evolution at the population level, as well as the Mendelian understanding of the structure (such as chromosomes, genes, alleles) and mechanisms
-(such as recombination and mutation). This is the so-called new or modern synthesis of evolutionary biology.
-
-\textit{\textbf{Particle Swarm Optimization:}} From Jason Brownlee's \textit{``Clever Algorithms''} - Particle Swarm Optimization belongs to the field of
-Swarm Intelligence and Collective Intelligence and is a sub-field of Computational Intelligence. Particle Swarm Optimization is related to other Swarm Intelligence
-algorithms such as Ant Colony Optimization and it is a baseline algorithm for many variations, too numerous to list. It is inspired by the social foraging behavior
-of some animals such as flocking behavior of birds and the schooling behavior of fish.
-
-\textit{\textbf{Firefly Algorithm:}} From Xin-She Yang \textit{``Nature-Inspired Metaheuristic Algorithms''} -
-The flashing light of fireflies is an amazing sight in the summer sky in the tropical and temperate regions. There are about two thousand firefly
-species, and most fireflies produce short and rhythmic flashes. The pattern of flashes is often unique for a particular species. The flashing light is
-produced by a process of bioluminescence, and the true functions of suchsignaling systems are still being debated. However, two fundamental functions
-of such flashes are to attract mating partners (communication), and to attract potential prey. In addition, flashing may also serve as a protective warning
-mechanism to remind potential predators of the bitter taste of fireflies. The firefly algorithm tries to mimic the attractiveness of Fireflies and has three
-basic rules:
-
-\begin{itemize}
-    \item All fireflies are unisex so that one firefly will be attracted to other
-          fireflies regardless of their sex;
-    \item Attractiveness is proportional to the their brightness, thus for any two
-          flashing fireflies, the less brighter one will move towards the brighter
-          one. The attractiveness is proportional to the brightness and they
-          both decrease as their distance increases. If there is no brighter one
-          than a particular firefly, it will move randomly;
-    \item The brightness of a firefly is affected or determined by the landscape
-          of the objective function.
-\end{itemize}
-
-\textit{\textbf{Bees Algorithm:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-The Bees Algorithm beings to Bee Inspired Algorithms and the field of Swarm Intelligence, and more broadly the fields of Computational
-Intelligence and Metaheuristics. The Bees Algorithm is related to other Bee Inspired Algorithms, such as Bee Colony Optimization, and other
-Swarm Intelligence algorithms such as Ant Colony Optimization and Particle Swarm Optimization.
-It is inspired by the foraging behavior of honey bees. Honey bees collect nectar from vast areas around their hive (more than
-10 kilometers). Bee Colonies have been observed to send bees to collect nectar from flower patches relative to the amount of food available at
-each patch. Bees communicate with each other at the hive via a waggle dance that informs other bees in the hive as to the direction, distance,
-and quality rating of food sources.
-
-\section{Methodology}
-\label{sec:methodology}
-
-\subsection{Optimization Problem Selection}
-\label{subsec:optimization-problem-selection}
-The two problems selected for this paper were \textit{Spring Tension Design} and \textit{Pressure Vessel Design}. Although it was simple
-to choose the first two problems from the computational work statements, the choice was more than justified because these aroblems are well
-known in the literature.
-Thus, the problem selection was driven by which has more than one source to compare results.
-
-\subsubsection{Spring Tension Design}
-\label{subsubsec:methodology-spring-tension-design}
-From \textit{Nature-Inspired Metaheuristic Algorithms - Xin-She Yang} -
-The design of a tension and compression spring is a well-known benchmark
-optimization problem.
-The main aim is to minimize the weight subject
-to constraints on deflection, stress, surge frequency and geometry. It involves
-three design variables: the wire diameter $x_1$ , coil diameter $x_2$ and
-number/length of the coil $x_3$.
-This problem can be summarized as:
-
-\begin{equation}
-    f (x) = x_1^2 x_2 (2 + x_3)
-\end{equation}
-
-subject to
-
-\begin{equation}
-    \begin{split}
-        g_1(x) = \frac{x_2^3 x_3}{71785 x_1^4} \leq 0\\
-        g_2(x) = \frac{4 x_2^2 - x_1 x_2}{12566 \left( x_1^3 x_2 - x_1^4\right)}\\
-        + \frac{1}{5108 x_1^2} -1 \leq 0\\
-        g_3(x) = 1 - \frac{140.45 x_1}{x_2^2 x_3} \leq 0\\
-        g_4 = \frac{x_1 + x_2}{1.5} - 1 \leq 0
-    \end{split}
-\end{equation}
-
-The original bounding limits of the variables, extracted from computational work
-statements, are:
-
-\begin{equation}
-    \begin{split}
-        0.05 \leq x_1 \leq 2.0\\
-        0.25 \leq x_2 \leq 1.3\\
-        2.0 \leq x_3 \leq 15.0
-    \end{split}
-\end{equation}
-
-\subsubsection{Pressure Vessel Design}
-\label{subsubsec:methodology-pressure-vessel-design}
-From \textit{Solving Design of Pressure Vessel Engineering
-Problem Using a Fruit Fly Optimization Algorithm - XIANTING KE et al} -
-A pressure vessel design model involves four decision variables: $x_1$ is defined
-thickness of the pressure vessel $T_s$ , $x_2$ stands for
-thickness of the head $T_H$ , $x_3$ represents inner radius of the
-vessel $R$ , and $x_4$ is on behalf of length of the vessel
-barring head $L$ , the total variables described as $( x_1 , x_2 , x_3 , x_4 )$.
-The objective function of the problem is to minimize the total cost, including
-the cost of material, forming, and welding.
-The general pressure vessel design optimization model is expressed as:
-
-\begin{equation}
-	\begin{split}
-        f(x) = 0.6224 x_1 x_3 x_4 + 1.7781 x_2 x_3^2 \\
-        + 3.1661 x_1^2 x_4 + 19.84 x_1^2 x_3
-	\end{split}
-\end{equation}
-
-subject to:
-
-\begin{equation}
-    \begin{split}
-        g_1(x) = - x_1 + 0.0193 x_3 \leq 0\\
-        g_2(x) = - x_2 + 0.00954 x_3 \leq 0\\
-        g_3(x) = - \pi x_3^2 x_4 -\frac{4}{3}\pi x_3^3 + 1296000 \leq 0\\
-        g_4(x) = x_4 -240 \leq 0\\
-    \end{split}
-\end{equation}
-
-The original bounding limits of the variables, extracted from computational work
-statements, are:
-
-\begin{equation}
-    \begin{split}
-        0 \leq x_1 \leq 99\\
-        0 \leq x_2 \leq 99\\
-        10 \leq x_3 \leq 200\\
-        10 \leq x_4 \leq 200\\
-    \end{split}
-\end{equation}
-
-For some reason these settings does not work at all with the selected optimizers, so
-some research in the literature \textit{Solving Design of Pressure Vessel Engineering
-Problem Using a Fruit Fly Optimization Algorithm - XIANTING KE et al} suggest the
-following bounding limits:
-
-\begin{equation}
-    \begin{split}
-        0.0625 \leq x_1 \leq 99 \times 0.0625\\
-        0.0625 \leq x_2 \leq 99 \times 0.0625\\
-        10 \leq x_3 \leq 200\\
-        10 \leq x_4 \leq 200
-    \end{split}
-\end{equation}
-
-But these settings produce many random, bizarre and noisy results in all selected optimizers. Then
-a proud-and-lame-homemade set of variable boundings comes in handy, obtained by tweaking the original
-boundings:
-
-\begin{equation}
-    \begin{split}
-        0.75 \leq x_1 \leq 0.8\\
-        0.35 \leq x_2 \leq 0.4\\
-        39.5 \leq x_3 \leq 41.0\\
-        195.0 \leq x_4 \leq 205.0\\
-    \end{split}
-\end{equation}
-
-It is not intended here to point out modeling errors of any kind, nor point out package
-errors made by the authors or ours, but the homemade bounding limits was necessary to
-reach the literature results.
-
-\subsection{Constraint Implementation}
-\label{subsec:methodology-constraint-implementation}
-The constraints that all problems are subjected were implemented as \textit{penalty functions},
-that is, it adds a high value when the constraint is not satisfied, zero otherwise. It is an optional requirement
-from computational work in question and is the recommended way to put constraints from \textit{MealPy}'s
-Manual.
-
-\subsection{Programming Language}
-\label{subsec:methodology-programming-language}
-
-The chosen programming language for the test code was \textit{Python Language}, version 3.10, because it is an opensource language easy to
-program and has a huge amount of packages regarding artificial intelligence, genetic algorithms and swarm based algorithms.
-From these packages it was selected \textit{MealPy} package, version 2.5.1, because it comprises all the algorithm's classed tested in this paper.
-
-\subsection{Algorithm Selection}
-\label{subsec:methodology-algorithm-selection}
-
-The algorithm selection was made in two steps: first, it was extracted simple version of the two classes (evolutionary and swarm based) and
-then it was used a simple shuffle using Python's \textit{random.shuffle} in a terminal - no script was required.
-
-The chosen algorithms were:
-
-\begin{itemize}
-    \item \textit{\textbf{Evolution Based Algorithms: }} LevyEP (Evolutionary Programming),
-    OriginalES (Evolution Strategy) and BaseGA (Genetic Algorithm)
-    \item \textit{\textbf{Swarm Based Algorithms: }} OriginalBeesA (Bees Algorithm),
-    OriginalFFA (Original Firefly Algorithm) and OriginalPSO (Particle Swarm Optimization)
-\end{itemize}
-
-\subsection{Optimizer Tuning}
-\label{subsec:methodology-optimizer-tuning}
-
-The hyperparameters for each optimizer were tuned using the \textit{MealPy}'s \textit{Tuner} utility.
-It is a recomended procedure to tune hyperparameters for each optimizer and problem, according to
-\textit{MealPy}'s Manual.
-The \textit{Tuner} utility is a very simple grid search metaheuristic search tool
-that test each grid configuration for a specified oprimizer runs.
-Although simple, it is a very expensive procedure that took 2 days to complete. It was defined 10 runs for each
-configuration, with the following set of hyperparameter:
-
-\begin{itemize}
-    \item \textit{\textbf{Evolution Based Algorithms: }}
-        \subitem \textit{LevyEP:}
-            \subsubitem \textit{bout\_size (float)}: percentage of child agents implement tournament selection.
-        \subitem \textit{OriginalES:}
-            \subsubitem \textit{lamda (float)}: Percentage of child agents evolving in the next generation.
-        \subitem \textit{BaseGA:}
-            \subsubitem \textit{pc (float)}: cross-over probability
-            \subsubitem \textit{pm (float)}: mutation probability
-    \item \textit{\textbf{Swarm Based Algorithms: }}
-        \subitem \textit{OriginalBeesA:}
-            \subsubitem \textit{selected\_site\_ratio (float)}
-            \subsubitem \textit{elite\_site\_ratio (float)}
-            \subsubitem \textit{selected\_site\_bee\_ratio (float)}
-            \subsubitem \textit{elite\_site\_bee\_ratio (float)}
-            \subsubitem \textit{dance\_radius (float)}
-            \subsubitem \textit{dance\_reduction (float)}
-        \subitem \textit{OriginalFFA:}
-            \subsubitem \textit{gamma (float)}: Light Absorption Coefficient
-            \subsubitem \textit{beta\_base (float)}: Attraction Coefficient Base Value
-            \subsubitem \textit{alpha (float)}: Mutation Coefficient
-            \subsubitem \textit{alpha\_damp (float)}: Mutation Coefficient Damp Rate
-            \subsubitem \textit{delta (float)}: Mutation Step Size
-            \subsubitem \textit{exponent (int)}: Exponent
-        \subitem \textit{OriginalPSO:}
-            \subsubitem \textit{c1 (float)}: local coefficient
-            \subsubitem \textit{c2 (float)}: global coefficient
-            \subsubitem \textit{w\_min (float)}: Weight min of bird
-            \subsubitem \textit{w\_max (float)}: Weight max of bird
-
-\end{itemize}
-
-\subsection{Optimizer Parameters}
-\label{subsec:methodology-optimizer-parameters}
-
-For all optimizers and problems, were selected the following parameters:
-
-\begin{itemize}
-    \item \textit{Runs}: 100 runs
-    \item \textit{Epochs}: 100 epochs
-    \item \textit{Population}: 100 initial points
-\end{itemize}
-
-The initial solutions were randomly selected using the same seed for all algorithms.
-
-\section{Results}
-\label{sec:results}
-\subsection{Spring Tension Design}
-\label{ssubec:spring_problem}
+The best results for all algorithms are presented in Table~\ref{best_fits:spring_problem}:
 
@@
 \centering
-\caption{Statistical Information about function values for Spring Tension Design}
-\label{function_values:spring_problem}
+\caption{Best Fits for Spring Tension Design}
+\label{best_fits:spring_problem}
 \resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrrrrr}
+\begin{tabular}{lrrrr}
 \toprule
-Algorithm &      Min F &     Mean F &   Median F &      Max F &   StdDev F \\
+Algorithm &      $x_1$ &      $x_2$ &       $x_3$ &      $f_x$ \\
 \midrule
-       EP & 0.01250534 & 0.01255960 & 0.01253156 & 0.01453933 & 0.00020190 \\
-       ES & 0.01252956 & 0.01281857 & 0.01274283 & 0.01346214 & 0.00024181 \\
-       GA & 0.01252305 & 0.01628575 & 0.01616768 & 0.02561808 & 0.00273276 \\
-    BeesA & 0.01250200 & 0.01268010 & 0.01261691 & 0.01406679 & 0.00021629 \\
-      FFA & 0.01249803 & 0.01254780 & 0.01253499 & 0.01268116 & 0.00003152 \\
-      PSO & 0.01252626 & 0.01390866 & 0.01318774 & 0.03036537 & 0.00342240 \\
+       EP & 0.05078716 & 0.34120356 & 11.93931414 & 0.01250534 \\
+       ES & 0.05000000 & 0.32292194 & 13.26929635 & 0.01252956 \\
+       GA & 0.05260626 & 0.38419911 &  9.63922108 & 0.01252305 \\
+    BeesA & 0.05141008 & 0.35564113 & 11.06109433 & 0.01250200 \\
+      FFA & 0.05148403 & 0.35770175 & 10.95787946 & 0.01249803 \\
+      PSO & 0.05000000 & 0.32241990 & 13.31368880 & 0.01252626 \\
 \bottomrule
@@
 
-\begin{figure}[H]
-\centering
-\caption{Boxplot for Spring Tension Design}
-\label{fig:spring_tension_design_boxplot}
-\includegraphics[scale=0.5]{images/spring_problem_boxplot.png}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\caption{Convergence lines for Spring Tension Design}
-\label{fig:spring_problem_convergence}
-\includegraphics[width= 0.4 \textwidth]{images/spring_problem_convergence.png}
-\end{figure}
-
-\subsection{Pressure Vessel Design (Original)}
-\label{subsec:pressure_vessel_problem_original}
-
-\begin{table}[H]
-\centering
-\caption{Statistical Information about function values for Pressure Vessel Design (Original)}
-\label{function_values:pressure_vessel_problem_original}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrrrrr}
-\toprule
-Algorithm &         Min F &         Mean F &       Median F &          Max F &       StdDev F \\
-\midrule
-       EP &    0.08150806 &     0.15642850 &     0.09093798 &     1.32637552 &     0.16807714 \\
-       ES &    0.08161190 &   718.92910990 &     1.00278859 &  9443.54269260 &  2060.07774212 \\
-       GA &   17.06920868 &   525.00734162 &   361.53879602 &  3112.03503082 &   454.52386703 \\
-    BeesA & 2393.70106213 & 17564.33024022 & 15751.91467117 & 53850.38271384 & 10514.60780411 \\
-      FFA &    0.08306113 &     0.13296127 &     0.13106271 &     0.20084847 &     0.02396876 \\
-      PSO &    0.08149204 &     0.24191732 &     0.08159173 &    10.00611523 &     1.00072349 \\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{figure}[H]
-\centering
-\caption{Boxplot for Pressure Vessel Design (Original)}
-\label{fig:pressure_vessel_design_original_boxplot}
-\includegraphics[scale=0.5]{images/pressure_vessel_problem_original_boxplot.png}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\caption{Convergence lines for Pressure Vessel Design (Original)}
-\label{fig:pressure_vessel_problem_original_convergence}
-\includegraphics[width= 0.4 \textwidth]{images/pressure_vessel_problem_original_convergence.png}
-\end{figure}
-
-\subsection{Pressure Vessel Design}
-\label{subsec:pressure_vessel_problem}
-
-\begin{table}
-\centering
-\caption{Statistical Information about function values for Pressure Vessel Design}
-\label{function_values:pressure_vessel_problem}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrrrrr}
-\toprule
-Algorithm &         Min F &        Mean F &      Median F &         Max F &   StdDev F \\
-\midrule
-       EP & 5534.57345496 & 5534.63426098 & 5534.61416291 & 5534.92993607 & 0.05804548 \\
-       ES & 5534.57917966 & 5535.28165367 & 5535.06149254 & 5538.03003895 & 0.65098467 \\
-       GA & 5534.83662424 & 5538.36788889 & 5536.92932748 & 5550.91639342 & 3.57079951 \\
-    BeesA & 5534.57516657 & 5537.97495231 & 5537.04824684 & 5548.55587234 & 3.28239740 \\
-      FFA & 5534.57401617 & 5534.58849395 & 5534.58435493 & 5534.63296149 & 0.01341777 \\
-      PSO & 5534.57345480 & 5534.57381593 & 5534.57355270 & 5534.57625290 & 0.00053848 \\
-\bottomrule
-\end{tabular}
-}
-\end{table}
-
-\begin{figure}[H]
-\centering
-\caption{Boxplot for Pressure Vessel Design}
-\label{fig:pressure_vessel_design_boxplot}
-\includegraphics[scale=0.5]{images/pressure_vessel_problem_boxplot.png}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\caption{Convergence lines for Pressure Vessel Design}
-\label{fig:pressure_vessel_problem_convergence}
-\includegraphics[width=0.4 \textwidth]{images/pressure_vessel_problem_convergence.png}
-\end{figure}
-
-\subsection{Significance Test}
-\label{subsec:pressure_vessel_problem_significance_test}
-
-\begin{table}[H]
-\centering
-\caption{Significance Test Using Friedman Chi-Squared Test}
-\label{friedman_test}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrr}
-\toprule
-                          Problem &   Statistics &    p-value \\
-\midrule
-            Spring Tension Design & 339.05714286 & 0.00000000 \\
-           Pressure Vessel Design & 436.16000000 & 0.00000000 \\
-Pressure Vessel Design (Original) & 425.07428571 & 0.00000000 \\
-\bottomrule
-\end{tabular}
-}
-\end{table}
-
-\section{Discussion}
-
-The main objective of this work is demonstrate the inner work of a optimization class of algorithms called \textit{Quasi-Newton algorithms}.
-Four of them are presented, along with the results and analysis regarding convergence, function evaluations and function objective values.
-
-For implementation, it was decided to put constraints on search space, because for the original search space of some functions, like Ackley and Rastrigin, there are other minimas that will confuse every algorithm tested for this paper, and there is no sense on test a local minima procedure on these conditions.
-To restrain the initial solution to some region in the search space was a cheap and ready solution to avoid the algorithms to stop because of stumbling upon the wrong minimum.
-
-The \textit{Levenberg-Marquardt Algorithm} implemented for this paper is very sensitive to hyperparameters, namely $\alpha$ and $\lambda$, which was not tunned to every function, so, the conspicuous performance variation is noticeable along the results.
-LMA is known to be fast and reliable, but in our implementation it was found a little tricky to get the hyperparameters right for all the test functions.
-But for Rosenbrock and Rastrigin, it is the best option, even for lame implementations like ours.
-
-The \textit{Broyden–Fletcher–Goldfarb–Shanno} Algorithm was the only one that we decided to use it as is from \textit{SciPy}, because it has features desired for this work, like counting of function evaluations, gradient evaluation and iterations.
-It performed very well for Ackley and Booth Functions, and reasonably well for other functions.
-
-The \textit{Davidon–Fletcher–Powell} Algorithm is not implemented in \textit{SciPy} but its equations shows that it is the dual of BFGS, so, it was easy to implement using some \textit{SciPy} code for BFGS algorithm.
-In the DFP procedure, there is a Hessian inversion to be evaluated every iteration, then, numerical imprecision would be taken into consideration evaluating its results.
-While in some cases it has a superb performance (Like Ackley Function), it has very poor performance in Rosenbrock Function and even in Beale Function.
-The increase of dimensions makes DFP suffer of numerical imprecision due to the Hessian inversion, except for Rastrigin, and it is the loser algorithm in other functions.
-
-Finally, the \textit{Limited memory BFGS} has an average performance among the functions.
-The original algorithm was implemented using code found in the url https://github.com/qkolj/L-BFGS/blob/master/L-BFGS.ipynb.
-
-In fact, there are no Quasi-Newton algorithms that solver the minima problem for an any function.
-From the standpoint of performance and convergence, all the algorithms have an average performance and a reasonable convergence, although we have to restrain the search space to a small area near the optimal solution.
-
-\end{document}
+Although the best fit points have noticeable differences, the cost function $f_x$ have similar results, that is, the
+function $f_x$ seems to have weak minimal points.

### 2023-01-21 release/code/latex/includes/spring_problem_boxplot.tex
Release Added

--- 2023-01-19 latex/article.tex
@@
-\documentclass[conference]{IEEEtran}
-\IEEEoverridecommandlockouts
-% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-\usepackage{cite}
-\usepackage{amsmath,amssymb,amsfonts}
-\usepackage{mathtools}
-\usepackage{algpseudocode}
-\usepackage{algorithm}
-\usepackage{algorithmicx}
-\usepackage{microtype}
-\usepackage{float}
-\usepackage{adjustbox}
-\usepackage{booktabs,makecell,tabularx}
-\usepackage{graphicx}
-\usepackage{textcomp}
-\usepackage{verbatim}
-\usepackage{xcolor}
-\usepackage{graphics} % for pdf, bitmapped graphics files
-\usepackage{epsfig} % for postscript graphics files
-\usepackage{mathptmx} % assumes new font selection scheme installed
-\usepackage{multicol}
-\usepackage[english]{babel}
-\usepackage[T1]{fontenc}
-\restylefloat{table}
-\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
-    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
-\begin{document}
-\title{Swarm and Evolutionary Based Algorithms used for Optimization}
-\author{
-	\IEEEauthorblockN{Augusto Mathias Adams\IEEEauthorrefmark{1}, Caio Phillipe Mizerkowski\IEEEauthorrefmark{2}, Christian Piltz Araújo\IEEEauthorrefmark{3} and Vinicius Eduardo dos Reis\IEEEauthorrefmark{4}}\\
-	\IEEEauthorblockA{\IEEEauthorrefmark{1}GRR20172143, augusto.adams@ufpr.br, \IEEEauthorrefmark{2}GRR20166403, caiomizerkowski@gmail.com,\\ \IEEEauthorrefmark{3}GRR20172197, christian0294@yahoo.com.br, \IEEEauthorrefmark{4}GRR20175957, eduardo.reis02@gmail.com}
-}
-
-\maketitle
-
-\begin{abstract}
-    In this paper, a study of evolution and swarm based algorithms is presented,
-    using two classical engineering problems: \textit{Spring Tension} and \textit{Pressure Vessel
-    Designs}. The test code for the problems was made using the \textit{Python Language},
-    version 3.10 and uses \textit{MealPy} package, version 2.5.1,  to provide the algorithms.
-    The algorithms were randomly chosen from a vast list of \textit{MealPy}'s algorithms:
-    \textit{Evolutionary Programming (LevyEP)}, \textit{Evolution Strategies (OriginalES)} and
-    \textit{Genetic Algorithm (BaseGA)} from \textit{evolutionary\_based} subpackage;
-    \textit{Bees Algorithm (OriginalBeesA)}, \textit{Firefly Algorithm (OriginalFFA)} and
-    \textit{Particle Swarm Optimization (OriginalPSO)} from \textit{swarm\_based} subpackage.
-    Each problem was modeled using \textit{SciPy} package, with constraints implemented as
-    \textit{penalty functions}. Each algorithm were optimized separately to extract the best
-    solutions from each problem using the \textit{MealPy}'s \textit{Tuner} utility.
-    The results, however, are dependant of algorithm and/or problem solved and the Friedman's chi
-    squared test for similarity make it noticeable because, although the values for best fits are
-    similar, running the same algorithm with different initial conditions does not converge to similar
-    values.
-\end{abstract}
-
-\begin{IEEEkeywords}
-	Optimization Methods, Evolutionary Programming, Evolutionary and Swarm Based Strategies.
-\end{IEEEkeywords}
-
-\section{Definitions}
-\label{sec:definitions}
-
-The main objective of this paper is study evolutionary and swarm intelligence algorithms.
-We present the main concepts of these two algorithm's classes, along with the chosen algorithms
-definitions in this section. All citations made in this document are due to Swarm Intelligence classes
-and to \textit{MealPy}'s documentation, which points out the theoretical documentation for each
-implemented algorithm.
-
-\textit{\textbf{Evolution}}: From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolutionary Algorithms belong to the Evolutionary Computation
-field of study concerned with computational methods inspired by the process
-and mechanisms of biological evolution. The process of evolution by
-means of natural selection (descent with modification) was proposed by
-Darwin to account for the variety of life and its suitability (adaptive
-fit) for its environment. The mechanisms of evolution describe how
-evolution actually takes place through the modification and propagation
-of genetic material (proteins). Evolutionary Algorithms are concerned
-with investigating computational systems that resemble simplified ver-
-sions of the processes and mechanisms of evolution toward achieving
-the effects of these processes and mechanisms, namely the development
-of adaptive systems. Additional subject areas that fall within the realm
-of Evolutionary Computation are algorithms that seek to exploit the
-properties from the related fields of Population Genetics, Population
-Ecology, Coevolutionary Biology, and Developmental Biology.
-
-\textit{\textbf{Swarm Intelligence}}: From Jason Brownlee's \textit{``Clever Algorithms''} -
-Swarm intelligence is the study of computational systems inspired by
-the ‘collective intelligence’. Collective Intelligence emerges through the
-cooperation of large numbers of homogeneous agents in the environment.
-Examples include schools of fish, flocks of birds, and colonies of ants.
-Such intelligence is decentralized, self-organizing and distributed through
-out an environment. In nature such systems are commonly used to
-solve problems such as effective foraging for food, prey evading, or
-colony re-location. The information is typically stored throughout the
-participating homogeneous agents, or is stored or communicated in
-the environment itself such as through the use of pheromones in ants,
-dancing in bees, and proximity in fish and birds.
-
-\textit{\textbf{Evolutionary Programming:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolutionary Programming is a Global Optimization algorithm and is an instance of an Evolutionary
-Algorithm from the field of Evolutionary Computation. The approach is a sibling of other Evolutionary
-Algorithms such as the Genetic Algorithm, and Learning Classifier Systems. It is sometimes confused with Genetic
-Programming given the similarity in name, and more recently it shows a strong functional similarity to Evolution Strategies.
-Evolutionary Programming is inspired by the theory of evolution by means of natural selection. Specifically, the technique is inspired by
-macro-level or the species-level process of evolution (phenotype, hereditary, variation) and is not concerned with the genetic mechanisms of
-evolution (genome, chromosomes, genes, alleles).
-
-\textit{\textbf{Evolutionary Strategies:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolution Strategies is a global optimization algorithm and is an instance of an Evolutionary Algorithm from the field of Evolutionary
-Computation. Evolution Strategies is a sibling technique to other Evolutionary Algorithms such as Genetic Algorithms (Section 3.2), Genetic
-Programming (Section 3.3), Learning Classifier Systems, and Evolutionary Programming. A popular descendant of
-the Evolution Strategies algorithm is the Covariance Matrix Adaptation Evolution Strategies (CMA-ES).
-
-\textit{\textbf{Genetic Algorithms:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-The Genetic Algorithm is an Adaptive Strategy and a Global Optimization technique. It is an Evolutionary Algorithm and belongs to the
-broader study of Evolutionary Computation. The Genetic Algorithm is a sibling of other Evolutionary Algorithms such as Genetic Programming,
- Evolution Strategies, Evolutionary Programming, and Learning Classifier Systems. The Genetic Algorithm is a parent of a large number of variant techniques
-and sub-fields too numerous to list. The Genetic Algorithm is inspired by population genetics (including heredity and gene frequencies),
-and evolution at the population level, as well as the Mendelian understanding of the structure (such as chromosomes, genes, alleles) and mechanisms
-(such as recombination and mutation). This is the so-called new or modern synthesis of evolutionary biology.
-
-\textit{\textbf{Particle Swarm Optimization:}} From Jason Brownlee's \textit{``Clever Algorithms''} - Particle Swarm Optimization belongs to the field of
-Swarm Intelligence and Collective Intelligence and is a sub-field of Computational Intelligence. Particle Swarm Optimization is related to other Swarm Intelligence
-algorithms such as Ant Colony Optimization and it is a baseline algorithm for many variations, too numerous to list. It is inspired by the social foraging behavior
-of some animals such as flocking behavior of birds and the schooling behavior of fish.
-
-\textit{\textbf{Firefly Algorithm:}} From Xin-She Yang \textit{``Nature-Inspired Metaheuristic Algorithms''} -
-The flashing light of fireflies is an amazing sight in the summer sky in the tropical and temperate regions. There are about two thousand firefly
-species, and most fireflies produce short and rhythmic flashes. The pattern of flashes is often unique for a particular species. The flashing light is
-produced by a process of bioluminescence, and the true functions of suchsignaling systems are still being debated. However, two fundamental functions
-of such flashes are to attract mating partners (communication), and to attract potential prey. In addition, flashing may also serve as a protective warning
-mechanism to remind potential predators of the bitter taste of fireflies. The firefly algorithm tries to mimic the attractiveness of Fireflies and has three
-basic rules:
-
-\begin{itemize}
-    \item All fireflies are unisex so that one firefly will be attracted to other
-          fireflies regardless of their sex;
-    \item Attractiveness is proportional to the their brightness, thus for any two
-          flashing fireflies, the less brighter one will move towards the brighter
-          one. The attractiveness is proportional to the brightness and they
-          both decrease as their distance increases. If there is no brighter one
-          than a particular firefly, it will move randomly;
-    \item The brightness of a firefly is affected or determined by the landscape
-          of the objective function.
-\end{itemize}
-
-\textit{\textbf{Bees Algorithm:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-The Bees Algorithm beings to Bee Inspired Algorithms and the field of Swarm Intelligence, and more broadly the fields of Computational
-Intelligence and Metaheuristics. The Bees Algorithm is related to other Bee Inspired Algorithms, such as Bee Colony Optimization, and other
-Swarm Intelligence algorithms such as Ant Colony Optimization and Particle Swarm Optimization.
-It is inspired by the foraging behavior of honey bees. Honey bees collect nectar from vast areas around their hive (more than
-10 kilometers). Bee Colonies have been observed to send bees to collect nectar from flower patches relative to the amount of food available at
-each patch. Bees communicate with each other at the hive via a waggle dance that informs other bees in the hive as to the direction, distance,
-and quality rating of food sources.
-
-\section{Methodology}
-\label{sec:methodology}
-
-\subsection{Optimization Problem Selection}
-\label{subsec:optimization-problem-selection}
-The two problems selected for this paper were \textit{Spring Tension Design} and \textit{Pressure Vessel Design}. Although it was simple
-to choose the first two problems from the computational work statements, the choice was more than justified because these aroblems are well
-known in the literature.
-Thus, the problem selection was driven by which has more than one source to compare results.
-
-\subsubsection{Spring Tension Design}
-\label{subsubsec:methodology-spring-tension-design}
-From \textit{Nature-Inspired Metaheuristic Algorithms - Xin-She Yang} -
-The design of a tension and compression spring is a well-known benchmark
-optimization problem.
-The main aim is to minimize the weight subject
-to constraints on deflection, stress, surge frequency and geometry. It involves
-three design variables: the wire diameter $x_1$ , coil diameter $x_2$ and
-number/length of the coil $x_3$.
-This problem can be summarized as:
-
-\begin{equation}
-    f (x) = x_1^2 x_2 (2 + x_3)
-\end{equation}
-
-subject to
-
-\begin{equation}
-    \begin{split}
-        g_1(x) = \frac{x_2^3 x_3}{71785 x_1^4} \leq 0\\
-        g_2(x) = \frac{4 x_2^2 - x_1 x_2}{12566 \left( x_1^3 x_2 - x_1^4\right)}\\
-        + \frac{1}{5108 x_1^2} -1 \leq 0\\
-        g_3(x) = 1 - \frac{140.45 x_1}{x_2^2 x_3} \leq 0\\
-        g_4 = \frac{x_1 + x_2}{1.5} - 1 \leq 0
-    \end{split}
-\end{equation}
-
-The original bounding limits of the variables, extracted from computational work
-statements, are:
-
-\begin{equation}
-    \begin{split}
-        0.05 \leq x_1 \leq 2.0\\
-        0.25 \leq x_2 \leq 1.3\\
-        2.0 \leq x_3 \leq 15.0
-    \end{split}
-\end{equation}
-
-\subsubsection{Pressure Vessel Design}
-\label{subsubsec:methodology-pressure-vessel-design}
-From \textit{Solving Design of Pressure Vessel Engineering
-Problem Using a Fruit Fly Optimization Algorithm - XIANTING KE et al} -
-A pressure vessel design model involves four decision variables: $x_1$ is defined
-thickness of the pressure vessel $T_s$ , $x_2$ stands for
-thickness of the head $T_H$ , $x_3$ represents inner radius of the
-vessel $R$ , and $x_4$ is on behalf of length of the vessel
-barring head $L$ , the total variables described as $( x_1 , x_2 , x_3 , x_4 )$.
-The objective function of the problem is to minimize the total cost, including
-the cost of material, forming, and welding.
-The general pressure vessel design optimization model is expressed as:
-
-\begin{equation}
-	\begin{split}
-        f(x) = 0.6224 x_1 x_3 x_4 + 1.7781 x_2 x_3^2 \\
-        + 3.1661 x_1^2 x_4 + 19.84 x_1^2 x_3
-	\end{split}
-\end{equation}
-
-subject to:
-
-\begin{equation}
-    \begin{split}
-        g_1(x) = - x_1 + 0.0193 x_3 \leq 0\\
-        g_2(x) = - x_2 + 0.00954 x_3 \leq 0\\
-        g_3(x) = - \pi x_3^2 x_4 -\frac{4}{3}\pi x_3^3 + 1296000 \leq 0\\
-        g_4(x) = x_4 -240 \leq 0\\
-    \end{split}
-\end{equation}
-
-The original bounding limits of the variables, extracted from computational work
-statements, are:
-
-\begin{equation}
-    \begin{split}
-        0 \leq x_1 \leq 99\\
-        0 \leq x_2 \leq 99\\
-        10 \leq x_3 \leq 200\\
-        10 \leq x_4 \leq 200\\
-    \end{split}
-\end{equation}
-
-For some reason these settings does not work at all with the selected optimizers, so
-some research in the literature \textit{Solving Design of Pressure Vessel Engineering
-Problem Using a Fruit Fly Optimization Algorithm - XIANTING KE et al} suggest the
-following bounding limits:
-
-\begin{equation}
-    \begin{split}
-        0.0625 \leq x_1 \leq 99 \times 0.0625\\
-        0.0625 \leq x_2 \leq 99 \times 0.0625\\
-        10 \leq x_3 \leq 200\\
-        10 \leq x_4 \leq 200
-    \end{split}
-\end{equation}
-
-But these settings produce many random, bizarre and noisy results in all selected optimizers. Then
-a proud-and-lame-homemade set of variable boundings comes in handy, obtained by tweaking the original
-boundings:
-
-\begin{equation}
-    \begin{split}
-        0.75 \leq x_1 \leq 0.8\\
-        0.35 \leq x_2 \leq 0.4\\
-        39.5 \leq x_3 \leq 41.0\\
-        195.0 \leq x_4 \leq 205.0\\
-    \end{split}
-\end{equation}
-
-It is not intended here to point out modeling errors of any kind, nor point out package
-errors made by the authors or ours, but the homemade bounding limits was necessary to
-reach the literature results.
-
-\subsection{Constraint Implementation}
-\label{subsec:methodology-constraint-implementation}
-The constraints that all problems are subjected were implemented as \textit{penalty functions},
-that is, it adds a high value when the constraint is not satisfied, zero otherwise. It is an optional requirement
-from computational work in question and is the recommended way to put constraints from \textit{MealPy}'s
-Manual.
-
-\subsection{Programming Language}
-\label{subsec:methodology-programming-language}
-
-The chosen programming language for the test code was \textit{Python Language}, version 3.10, because it is an opensource language easy to
-program and has a huge amount of packages regarding artificial intelligence, genetic algorithms and swarm based algorithms.
-From these packages it was selected \textit{MealPy} package, version 2.5.1, because it comprises all the algorithm's classed tested in this paper.
-
-\subsection{Algorithm Selection}
-\label{subsec:methodology-algorithm-selection}
-
-The algorithm selection was made in two steps: first, it was extracted simple version of the two classes (evolutionary and swarm based) and
-then it was used a simple shuffle using Python's \textit{random.shuffle} in a terminal - no script was required.
-
-The chosen algorithms were:
-
-\begin{itemize}
-    \item \textit{\textbf{Evolution Based Algorithms: }} LevyEP (Evolutionary Programming),
-    OriginalES (Evolution Strategy) and BaseGA (Genetic Algorithm)
-    \item \textit{\textbf{Swarm Based Algorithms: }} OriginalBeesA (Bees Algorithm),
-    OriginalFFA (Original Firefly Algorithm) and OriginalPSO (Particle Swarm Optimization)
-\end{itemize}
-
-\subsection{Optimizer Tuning}
-\label{subsec:methodology-optimizer-tuning}
-
-The hyperparameters for each optimizer were tuned using the \textit{MealPy}'s \textit{Tuner} utility.
-It is a recomended procedure to tune hyperparameters for each optimizer and problem, according to
-\textit{MealPy}'s Manual.
-The \textit{Tuner} utility is a very simple grid search metaheuristic search tool
-that test each grid configuration for a specified oprimizer runs.
-Although simple, it is a very expensive procedure that took 2 days to complete. It was defined 10 runs for each
-configuration, with the following set of hyperparameter:
-
-\begin{itemize}
-    \item \textit{\textbf{Evolution Based Algorithms: }}
-        \subitem \textit{LevyEP:}
-            \subsubitem \textit{bout\_size (float)}: percentage of child agents implement tournament selection.
-        \subitem \textit{OriginalES:}
-            \subsubitem \textit{lamda (float)}: Percentage of child agents evolving in the next generation.
-        \subitem \textit{BaseGA:}
-            \subsubitem \textit{pc (float)}: cross-over probability
-            \subsubitem \textit{pm (float)}: mutation probability
-    \item \textit{\textbf{Swarm Based Algorithms: }}
-        \subitem \textit{OriginalBeesA:}
-            \subsubitem \textit{selected\_site\_ratio (float)}
-            \subsubitem \textit{elite\_site\_ratio (float)}
-            \subsubitem \textit{selected\_site\_bee\_ratio (float)}
-            \subsubitem \textit{elite\_site\_bee\_ratio (float)}
-            \subsubitem \textit{dance\_radius (float)}
-            \subsubitem \textit{dance\_reduction (float)}
-        \subitem \textit{OriginalFFA:}
-            \subsubitem \textit{gamma (float)}: Light Absorption Coefficient
-            \subsubitem \textit{beta\_base (float)}: Attraction Coefficient Base Value
-            \subsubitem \textit{alpha (float)}: Mutation Coefficient
-            \subsubitem \textit{alpha\_damp (float)}: Mutation Coefficient Damp Rate
-            \subsubitem \textit{delta (float)}: Mutation Step Size
-            \subsubitem \textit{exponent (int)}: Exponent
-        \subitem \textit{OriginalPSO:}
-            \subsubitem \textit{c1 (float)}: local coefficient
-            \subsubitem \textit{c2 (float)}: global coefficient
-            \subsubitem \textit{w\_min (float)}: Weight min of bird
-            \subsubitem \textit{w\_max (float)}: Weight max of bird
-
-\end{itemize}
-
-\subsection{Optimizer Parameters}
-\label{subsec:methodology-optimizer-parameters}
-
-For all optimizers and problems, were selected the following parameters:
-
-\begin{itemize}
-    \item \textit{Runs}: 100 runs
-    \item \textit{Epochs}: 100 epochs
-    \item \textit{Population}: 100 initial points
-\end{itemize}
-
-The initial solutions were randomly selected using the same seed for all algorithms.
-
-\section{Results}
-\label{sec:results}
-\subsection{Spring Tension Design}
-\label{ssubec:spring_problem}
-
-\begin{table}[H]
-\centering
-\caption{Statistical Information about function values for Spring Tension Design}
-\label{function_values:spring_problem}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrrrrr}
-\toprule
-Algorithm &      Min F &     Mean F &   Median F &      Max F &   StdDev F \\
-\midrule
-       EP & 0.01250534 & 0.01255960 & 0.01253156 & 0.01453933 & 0.00020190 \\
-       ES & 0.01252956 & 0.01281857 & 0.01274283 & 0.01346214 & 0.00024181 \\
-       GA & 0.01252305 & 0.01628575 & 0.01616768 & 0.02561808 & 0.00273276 \\
-    BeesA & 0.01250200 & 0.01268010 & 0.01261691 & 0.01406679 & 0.00021629 \\
-      FFA & 0.01249803 & 0.01254780 & 0.01253499 & 0.01268116 & 0.00003152 \\
-      PSO & 0.01252626 & 0.01390866 & 0.01318774 & 0.03036537 & 0.00342240 \\
-\bottomrule
-\end{tabular}}
-\end{table}
+A quick way to access the Table~\ref{function_values:spring_problem} is
+shown on Figure~\ref{fig:spring_tension_design_boxplot}.
 
@@
 
-\begin{figure}[H]
-\centering
-\caption{Convergence lines for Spring Tension Design}
-\label{fig:spring_problem_convergence}
-\includegraphics[width= 0.4 \textwidth]{images/spring_problem_convergence.png}
-\end{figure}
-
-\subsection{Pressure Vessel Design (Original)}
-\label{subsec:pressure_vessel_problem_original}
-
-\begin{table}[H]
-\centering
-\caption{Statistical Information about function values for Pressure Vessel Design (Original)}
-\label{function_values:pressure_vessel_problem_original}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrrrrr}
-\toprule
-Algorithm &         Min F &         Mean F &       Median F &          Max F &       StdDev F \\
-\midrule
-       EP &    0.08150806 &     0.15642850 &     0.09093798 &     1.32637552 &     0.16807714 \\
-       ES &    0.08161190 &   718.92910990 &     1.00278859 &  9443.54269260 &  2060.07774212 \\
-       GA &   17.06920868 &   525.00734162 &   361.53879602 &  3112.03503082 &   454.52386703 \\
-    BeesA & 2393.70106213 & 17564.33024022 & 15751.91467117 & 53850.38271384 & 10514.60780411 \\
-      FFA &    0.08306113 &     0.13296127 &     0.13106271 &     0.20084847 &     0.02396876 \\
-      PSO &    0.08149204 &     0.24191732 &     0.08159173 &    10.00611523 &     1.00072349 \\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{figure}[H]
-\centering
-\caption{Boxplot for Pressure Vessel Design (Original)}
-\label{fig:pressure_vessel_design_original_boxplot}
-\includegraphics[scale=0.5]{images/pressure_vessel_problem_original_boxplot.png}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\caption{Convergence lines for Pressure Vessel Design (Original)}
-\label{fig:pressure_vessel_problem_original_convergence}
-\includegraphics[width= 0.4 \textwidth]{images/pressure_vessel_problem_original_convergence.png}
-\end{figure}
-
-\subsection{Pressure Vessel Design}
-\label{subsec:pressure_vessel_problem}
-
-\begin{table}
-\centering
-\caption{Statistical Information about function values for Pressure Vessel Design}
-\label{function_values:pressure_vessel_problem}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrrrrr}
-\toprule
-Algorithm &         Min F &        Mean F &      Median F &         Max F &   StdDev F \\
-\midrule
-       EP & 5534.57345496 & 5534.63426098 & 5534.61416291 & 5534.92993607 & 0.05804548 \\
-       ES & 5534.57917966 & 5535.28165367 & 5535.06149254 & 5538.03003895 & 0.65098467 \\
-       GA & 5534.83662424 & 5538.36788889 & 5536.92932748 & 5550.91639342 & 3.57079951 \\
-    BeesA & 5534.57516657 & 5537.97495231 & 5537.04824684 & 5548.55587234 & 3.28239740 \\
-      FFA & 5534.57401617 & 5534.58849395 & 5534.58435493 & 5534.63296149 & 0.01341777 \\
-      PSO & 5534.57345480 & 5534.57381593 & 5534.57355270 & 5534.57625290 & 0.00053848 \\
-\bottomrule
-\end{tabular}
-}
-\end{table}
-
-\begin{figure}[H]
-\centering
-\caption{Boxplot for Pressure Vessel Design}
-\label{fig:pressure_vessel_design_boxplot}
-\includegraphics[scale=0.5]{images/pressure_vessel_problem_boxplot.png}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\caption{Convergence lines for Pressure Vessel Design}
-\label{fig:pressure_vessel_problem_convergence}
-\includegraphics[width=0.4 \textwidth]{images/pressure_vessel_problem_convergence.png}
-\end{figure}
-
-\subsection{Significance Test}
-\label{subsec:pressure_vessel_problem_significance_test}
-
-\begin{table}[H]
-\centering
-\caption{Significance Test Using Friedman Chi-Squared Test}
-\label{friedman_test}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrr}
-\toprule
-                          Problem &   Statistics &    p-value \\
-\midrule
-            Spring Tension Design & 339.05714286 & 0.00000000 \\
-           Pressure Vessel Design & 436.16000000 & 0.00000000 \\
-Pressure Vessel Design (Original) & 425.07428571 & 0.00000000 \\
-\bottomrule
-\end{tabular}
-}
-\end{table}
-
-\section{Discussion}
-
-The main objective of this work is demonstrate the inner work of a optimization class of algorithms called \textit{Quasi-Newton algorithms}.
-Four of them are presented, along with the results and analysis regarding convergence, function evaluations and function objective values.
-
-For implementation, it was decided to put constraints on search space, because for the original search space of some functions, like Ackley and Rastrigin, there are other minimas that will confuse every algorithm tested for this paper, and there is no sense on test a local minima procedure on these conditions.
-To restrain the initial solution to some region in the search space was a cheap and ready solution to avoid the algorithms to stop because of stumbling upon the wrong minimum.
-
-The \textit{Levenberg-Marquardt Algorithm} implemented for this paper is very sensitive to hyperparameters, namely $\alpha$ and $\lambda$, which was not tunned to every function, so, the conspicuous performance variation is noticeable along the results.
-LMA is known to be fast and reliable, but in our implementation it was found a little tricky to get the hyperparameters right for all the test functions.
-But for Rosenbrock and Rastrigin, it is the best option, even for lame implementations like ours.
-
-The \textit{Broyden–Fletcher–Goldfarb–Shanno} Algorithm was the only one that we decided to use it as is from \textit{SciPy}, because it has features desired for this work, like counting of function evaluations, gradient evaluation and iterations.
-It performed very well for Ackley and Booth Functions, and reasonably well for other functions.
-
-The \textit{Davidon–Fletcher–Powell} Algorithm is not implemented in \textit{SciPy} but its equations shows that it is the dual of BFGS, so, it was easy to implement using some \textit{SciPy} code for BFGS algorithm.
-In the DFP procedure, there is a Hessian inversion to be evaluated every iteration, then, numerical imprecision would be taken into consideration evaluating its results.
-While in some cases it has a superb performance (Like Ackley Function), it has very poor performance in Rosenbrock Function and even in Beale Function.
-The increase of dimensions makes DFP suffer of numerical imprecision due to the Hessian inversion, except for Rastrigin, and it is the loser algorithm in other functions.
-
-Finally, the \textit{Limited memory BFGS} has an average performance among the functions.
-The original algorithm was implemented using code found in the url https://github.com/qkolj/L-BFGS/blob/master/L-BFGS.ipynb.
-
-In fact, there are no Quasi-Newton algorithms that solver the minima problem for an any function.
-From the standpoint of performance and convergence, all the algorithms have an average performance and a reasonable convergence, although we have to restrain the search space to a small area near the optimal solution.
-
-\end{document}
+It shows the same information as the Table~\ref{function_values:spring_problem}
+and it evidences that not all algorithms have the same mean, so it is a clear evidence
+that not all algorithm give similar results from an arbitrary starting point (population).

### 2023-01-21 release/code/latex/includes/spring_problem_convergence.tex
Release Added

--- 2023-01-19 latex/article.tex
@@
-\documentclass[conference]{IEEEtran}
-\IEEEoverridecommandlockouts
-% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-\usepackage{cite}
-\usepackage{amsmath,amssymb,amsfonts}
-\usepackage{mathtools}
-\usepackage{algpseudocode}
-\usepackage{algorithm}
-\usepackage{algorithmicx}
-\usepackage{microtype}
-\usepackage{float}
-\usepackage{adjustbox}
-\usepackage{booktabs,makecell,tabularx}
-\usepackage{graphicx}
-\usepackage{textcomp}
-\usepackage{verbatim}
-\usepackage{xcolor}
-\usepackage{graphics} % for pdf, bitmapped graphics files
-\usepackage{epsfig} % for postscript graphics files
-\usepackage{mathptmx} % assumes new font selection scheme installed
-\usepackage{multicol}
-\usepackage[english]{babel}
-\usepackage[T1]{fontenc}
-\restylefloat{table}
-\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
-    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
-\begin{document}
-\title{Swarm and Evolutionary Based Algorithms used for Optimization}
-\author{
-	\IEEEauthorblockN{Augusto Mathias Adams\IEEEauthorrefmark{1}, Caio Phillipe Mizerkowski\IEEEauthorrefmark{2}, Christian Piltz Araújo\IEEEauthorrefmark{3} and Vinicius Eduardo dos Reis\IEEEauthorrefmark{4}}\\
-	\IEEEauthorblockA{\IEEEauthorrefmark{1}GRR20172143, augusto.adams@ufpr.br, \IEEEauthorrefmark{2}GRR20166403, caiomizerkowski@gmail.com,\\ \IEEEauthorrefmark{3}GRR20172197, christian0294@yahoo.com.br, \IEEEauthorrefmark{4}GRR20175957, eduardo.reis02@gmail.com}
-}
-
-\maketitle
-
-\begin{abstract}
-    In this paper, a study of evolution and swarm based algorithms is presented,
-    using two classical engineering problems: \textit{Spring Tension} and \textit{Pressure Vessel
-    Designs}. The test code for the problems was made using the \textit{Python Language},
-    version 3.10 and uses \textit{MealPy} package, version 2.5.1,  to provide the algorithms.
-    The algorithms were randomly chosen from a vast list of \textit{MealPy}'s algorithms:
-    \textit{Evolutionary Programming (LevyEP)}, \textit{Evolution Strategies (OriginalES)} and
-    \textit{Genetic Algorithm (BaseGA)} from \textit{evolutionary\_based} subpackage;
-    \textit{Bees Algorithm (OriginalBeesA)}, \textit{Firefly Algorithm (OriginalFFA)} and
-    \textit{Particle Swarm Optimization (OriginalPSO)} from \textit{swarm\_based} subpackage.
-    Each problem was modeled using \textit{SciPy} package, with constraints implemented as
-    \textit{penalty functions}. Each algorithm were optimized separately to extract the best
-    solutions from each problem using the \textit{MealPy}'s \textit{Tuner} utility.
-    The results, however, are dependant of algorithm and/or problem solved and the Friedman's chi
-    squared test for similarity make it noticeable because, although the values for best fits are
-    similar, running the same algorithm with different initial conditions does not converge to similar
-    values.
-\end{abstract}
-
-\begin{IEEEkeywords}
-	Optimization Methods, Evolutionary Programming, Evolutionary and Swarm Based Strategies.
-\end{IEEEkeywords}
-
-\section{Definitions}
-\label{sec:definitions}
-
-The main objective of this paper is study evolutionary and swarm intelligence algorithms.
-We present the main concepts of these two algorithm's classes, along with the chosen algorithms
-definitions in this section. All citations made in this document are due to Swarm Intelligence classes
-and to \textit{MealPy}'s documentation, which points out the theoretical documentation for each
-implemented algorithm.
-
-\textit{\textbf{Evolution}}: From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolutionary Algorithms belong to the Evolutionary Computation
-field of study concerned with computational methods inspired by the process
-and mechanisms of biological evolution. The process of evolution by
-means of natural selection (descent with modification) was proposed by
-Darwin to account for the variety of life and its suitability (adaptive
-fit) for its environment. The mechanisms of evolution describe how
-evolution actually takes place through the modification and propagation
-of genetic material (proteins). Evolutionary Algorithms are concerned
-with investigating computational systems that resemble simplified ver-
-sions of the processes and mechanisms of evolution toward achieving
-the effects of these processes and mechanisms, namely the development
-of adaptive systems. Additional subject areas that fall within the realm
-of Evolutionary Computation are algorithms that seek to exploit the
-properties from the related fields of Population Genetics, Population
-Ecology, Coevolutionary Biology, and Developmental Biology.
-
-\textit{\textbf{Swarm Intelligence}}: From Jason Brownlee's \textit{``Clever Algorithms''} -
-Swarm intelligence is the study of computational systems inspired by
-the ‘collective intelligence’. Collective Intelligence emerges through the
-cooperation of large numbers of homogeneous agents in the environment.
-Examples include schools of fish, flocks of birds, and colonies of ants.
-Such intelligence is decentralized, self-organizing and distributed through
-out an environment. In nature such systems are commonly used to
-solve problems such as effective foraging for food, prey evading, or
-colony re-location. The information is typically stored throughout the
-participating homogeneous agents, or is stored or communicated in
-the environment itself such as through the use of pheromones in ants,
-dancing in bees, and proximity in fish and birds.
-
-\textit{\textbf{Evolutionary Programming:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolutionary Programming is a Global Optimization algorithm and is an instance of an Evolutionary
-Algorithm from the field of Evolutionary Computation. The approach is a sibling of other Evolutionary
-Algorithms such as the Genetic Algorithm, and Learning Classifier Systems. It is sometimes confused with Genetic
-Programming given the similarity in name, and more recently it shows a strong functional similarity to Evolution Strategies.
-Evolutionary Programming is inspired by the theory of evolution by means of natural selection. Specifically, the technique is inspired by
-macro-level or the species-level process of evolution (phenotype, hereditary, variation) and is not concerned with the genetic mechanisms of
-evolution (genome, chromosomes, genes, alleles).
-
-\textit{\textbf{Evolutionary Strategies:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolution Strategies is a global optimization algorithm and is an instance of an Evolutionary Algorithm from the field of Evolutionary
-Computation. Evolution Strategies is a sibling technique to other Evolutionary Algorithms such as Genetic Algorithms (Section 3.2), Genetic
-Programming (Section 3.3), Learning Classifier Systems, and Evolutionary Programming. A popular descendant of
-the Evolution Strategies algorithm is the Covariance Matrix Adaptation Evolution Strategies (CMA-ES).
-
-\textit{\textbf{Genetic Algorithms:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-The Genetic Algorithm is an Adaptive Strategy and a Global Optimization technique. It is an Evolutionary Algorithm and belongs to the
-broader study of Evolutionary Computation. The Genetic Algorithm is a sibling of other Evolutionary Algorithms such as Genetic Programming,
- Evolution Strategies, Evolutionary Programming, and Learning Classifier Systems. The Genetic Algorithm is a parent of a large number of variant techniques
-and sub-fields too numerous to list. The Genetic Algorithm is inspired by population genetics (including heredity and gene frequencies),
-and evolution at the population level, as well as the Mendelian understanding of the structure (such as chromosomes, genes, alleles) and mechanisms
-(such as recombination and mutation). This is the so-called new or modern synthesis of evolutionary biology.
-
-\textit{\textbf{Particle Swarm Optimization:}} From Jason Brownlee's \textit{``Clever Algorithms''} - Particle Swarm Optimization belongs to the field of
-Swarm Intelligence and Collective Intelligence and is a sub-field of Computational Intelligence. Particle Swarm Optimization is related to other Swarm Intelligence
-algorithms such as Ant Colony Optimization and it is a baseline algorithm for many variations, too numerous to list. It is inspired by the social foraging behavior
-of some animals such as flocking behavior of birds and the schooling behavior of fish.
-
-\textit{\textbf{Firefly Algorithm:}} From Xin-She Yang \textit{``Nature-Inspired Metaheuristic Algorithms''} -
-The flashing light of fireflies is an amazing sight in the summer sky in the tropical and temperate regions. There are about two thousand firefly
-species, and most fireflies produce short and rhythmic flashes. The pattern of flashes is often unique for a particular species. The flashing light is
-produced by a process of bioluminescence, and the true functions of suchsignaling systems are still being debated. However, two fundamental functions
-of such flashes are to attract mating partners (communication), and to attract potential prey. In addition, flashing may also serve as a protective warning
-mechanism to remind potential predators of the bitter taste of fireflies. The firefly algorithm tries to mimic the attractiveness of Fireflies and has three
-basic rules:
-
-\begin{itemize}
-    \item All fireflies are unisex so that one firefly will be attracted to other
-          fireflies regardless of their sex;
-    \item Attractiveness is proportional to the their brightness, thus for any two
-          flashing fireflies, the less brighter one will move towards the brighter
-          one. The attractiveness is proportional to the brightness and they
-          both decrease as their distance increases. If there is no brighter one
-          than a particular firefly, it will move randomly;
-    \item The brightness of a firefly is affected or determined by the landscape
-          of the objective function.
-\end{itemize}
-
-\textit{\textbf{Bees Algorithm:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-The Bees Algorithm beings to Bee Inspired Algorithms and the field of Swarm Intelligence, and more broadly the fields of Computational
-Intelligence and Metaheuristics. The Bees Algorithm is related to other Bee Inspired Algorithms, such as Bee Colony Optimization, and other
-Swarm Intelligence algorithms such as Ant Colony Optimization and Particle Swarm Optimization.
-It is inspired by the foraging behavior of honey bees. Honey bees collect nectar from vast areas around their hive (more than
-10 kilometers). Bee Colonies have been observed to send bees to collect nectar from flower patches relative to the amount of food available at
-each patch. Bees communicate with each other at the hive via a waggle dance that informs other bees in the hive as to the direction, distance,
-and quality rating of food sources.
-
-\section{Methodology}
-\label{sec:methodology}
-
-\subsection{Optimization Problem Selection}
-\label{subsec:optimization-problem-selection}
-The two problems selected for this paper were \textit{Spring Tension Design} and \textit{Pressure Vessel Design}. Although it was simple
-to choose the first two problems from the computational work statements, the choice was more than justified because these aroblems are well
-known in the literature.
-Thus, the problem selection was driven by which has more than one source to compare results.
-
-\subsubsection{Spring Tension Design}
-\label{subsubsec:methodology-spring-tension-design}
-From \textit{Nature-Inspired Metaheuristic Algorithms - Xin-She Yang} -
-The design of a tension and compression spring is a well-known benchmark
-optimization problem.
-The main aim is to minimize the weight subject
-to constraints on deflection, stress, surge frequency and geometry. It involves
-three design variables: the wire diameter $x_1$ , coil diameter $x_2$ and
-number/length of the coil $x_3$.
-This problem can be summarized as:
-
-\begin{equation}
-    f (x) = x_1^2 x_2 (2 + x_3)
-\end{equation}
-
-subject to
-
-\begin{equation}
-    \begin{split}
-        g_1(x) = \frac{x_2^3 x_3}{71785 x_1^4} \leq 0\\
-        g_2(x) = \frac{4 x_2^2 - x_1 x_2}{12566 \left( x_1^3 x_2 - x_1^4\right)}\\
-        + \frac{1}{5108 x_1^2} -1 \leq 0\\
-        g_3(x) = 1 - \frac{140.45 x_1}{x_2^2 x_3} \leq 0\\
-        g_4 = \frac{x_1 + x_2}{1.5} - 1 \leq 0
-    \end{split}
-\end{equation}
-
-The original bounding limits of the variables, extracted from computational work
-statements, are:
-
-\begin{equation}
-    \begin{split}
-        0.05 \leq x_1 \leq 2.0\\
-        0.25 \leq x_2 \leq 1.3\\
-        2.0 \leq x_3 \leq 15.0
-    \end{split}
-\end{equation}
-
-\subsubsection{Pressure Vessel Design}
-\label{subsubsec:methodology-pressure-vessel-design}
-From \textit{Solving Design of Pressure Vessel Engineering
-Problem Using a Fruit Fly Optimization Algorithm - XIANTING KE et al} -
-A pressure vessel design model involves four decision variables: $x_1$ is defined
-thickness of the pressure vessel $T_s$ , $x_2$ stands for
-thickness of the head $T_H$ , $x_3$ represents inner radius of the
-vessel $R$ , and $x_4$ is on behalf of length of the vessel
-barring head $L$ , the total variables described as $( x_1 , x_2 , x_3 , x_4 )$.
-The objective function of the problem is to minimize the total cost, including
-the cost of material, forming, and welding.
-The general pressure vessel design optimization model is expressed as:
-
-\begin{equation}
-	\begin{split}
-        f(x) = 0.6224 x_1 x_3 x_4 + 1.7781 x_2 x_3^2 \\
-        + 3.1661 x_1^2 x_4 + 19.84 x_1^2 x_3
-	\end{split}
-\end{equation}
-
-subject to:
-
-\begin{equation}
-    \begin{split}
-        g_1(x) = - x_1 + 0.0193 x_3 \leq 0\\
-        g_2(x) = - x_2 + 0.00954 x_3 \leq 0\\
-        g_3(x) = - \pi x_3^2 x_4 -\frac{4}{3}\pi x_3^3 + 1296000 \leq 0\\
-        g_4(x) = x_4 -240 \leq 0\\
-    \end{split}
-\end{equation}
-
-The original bounding limits of the variables, extracted from computational work
-statements, are:
-
-\begin{equation}
-    \begin{split}
-        0 \leq x_1 \leq 99\\
-        0 \leq x_2 \leq 99\\
-        10 \leq x_3 \leq 200\\
-        10 \leq x_4 \leq 200\\
-    \end{split}
-\end{equation}
-
-For some reason these settings does not work at all with the selected optimizers, so
-some research in the literature \textit{Solving Design of Pressure Vessel Engineering
-Problem Using a Fruit Fly Optimization Algorithm - XIANTING KE et al} suggest the
-following bounding limits:
-
-\begin{equation}
-    \begin{split}
-        0.0625 \leq x_1 \leq 99 \times 0.0625\\
-        0.0625 \leq x_2 \leq 99 \times 0.0625\\
-        10 \leq x_3 \leq 200\\
-        10 \leq x_4 \leq 200
-    \end{split}
-\end{equation}
-
-But these settings produce many random, bizarre and noisy results in all selected optimizers. Then
-a proud-and-lame-homemade set of variable boundings comes in handy, obtained by tweaking the original
-boundings:
-
-\begin{equation}
-    \begin{split}
-        0.75 \leq x_1 \leq 0.8\\
-        0.35 \leq x_2 \leq 0.4\\
-        39.5 \leq x_3 \leq 41.0\\
-        195.0 \leq x_4 \leq 205.0\\
-    \end{split}
-\end{equation}
-
-It is not intended here to point out modeling errors of any kind, nor point out package
-errors made by the authors or ours, but the homemade bounding limits was necessary to
-reach the literature results.
-
-\subsection{Constraint Implementation}
-\label{subsec:methodology-constraint-implementation}
-The constraints that all problems are subjected were implemented as \textit{penalty functions},
-that is, it adds a high value when the constraint is not satisfied, zero otherwise. It is an optional requirement
-from computational work in question and is the recommended way to put constraints from \textit{MealPy}'s
-Manual.
-
-\subsection{Programming Language}
-\label{subsec:methodology-programming-language}
-
-The chosen programming language for the test code was \textit{Python Language}, version 3.10, because it is an opensource language easy to
-program and has a huge amount of packages regarding artificial intelligence, genetic algorithms and swarm based algorithms.
-From these packages it was selected \textit{MealPy} package, version 2.5.1, because it comprises all the algorithm's classed tested in this paper.
-
-\subsection{Algorithm Selection}
-\label{subsec:methodology-algorithm-selection}
-
-The algorithm selection was made in two steps: first, it was extracted simple version of the two classes (evolutionary and swarm based) and
-then it was used a simple shuffle using Python's \textit{random.shuffle} in a terminal - no script was required.
-
-The chosen algorithms were:
-
-\begin{itemize}
-    \item \textit{\textbf{Evolution Based Algorithms: }} LevyEP (Evolutionary Programming),
-    OriginalES (Evolution Strategy) and BaseGA (Genetic Algorithm)
-    \item \textit{\textbf{Swarm Based Algorithms: }} OriginalBeesA (Bees Algorithm),
-    OriginalFFA (Original Firefly Algorithm) and OriginalPSO (Particle Swarm Optimization)
-\end{itemize}
-
-\subsection{Optimizer Tuning}
-\label{subsec:methodology-optimizer-tuning}
-
-The hyperparameters for each optimizer were tuned using the \textit{MealPy}'s \textit{Tuner} utility.
-It is a recomended procedure to tune hyperparameters for each optimizer and problem, according to
-\textit{MealPy}'s Manual.
-The \textit{Tuner} utility is a very simple grid search metaheuristic search tool
-that test each grid configuration for a specified oprimizer runs.
-Although simple, it is a very expensive procedure that took 2 days to complete. It was defined 10 runs for each
-configuration, with the following set of hyperparameter:
-
-\begin{itemize}
-    \item \textit{\textbf{Evolution Based Algorithms: }}
-        \subitem \textit{LevyEP:}
-            \subsubitem \textit{bout\_size (float)}: percentage of child agents implement tournament selection.
-        \subitem \textit{OriginalES:}
-            \subsubitem \textit{lamda (float)}: Percentage of child agents evolving in the next generation.
-        \subitem \textit{BaseGA:}
-            \subsubitem \textit{pc (float)}: cross-over probability
-            \subsubitem \textit{pm (float)}: mutation probability
-    \item \textit{\textbf{Swarm Based Algorithms: }}
-        \subitem \textit{OriginalBeesA:}
-            \subsubitem \textit{selected\_site\_ratio (float)}
-            \subsubitem \textit{elite\_site\_ratio (float)}
-            \subsubitem \textit{selected\_site\_bee\_ratio (float)}
-            \subsubitem \textit{elite\_site\_bee\_ratio (float)}
-            \subsubitem \textit{dance\_radius (float)}
-            \subsubitem \textit{dance\_reduction (float)}
-        \subitem \textit{OriginalFFA:}
-            \subsubitem \textit{gamma (float)}: Light Absorption Coefficient
-            \subsubitem \textit{beta\_base (float)}: Attraction Coefficient Base Value
-            \subsubitem \textit{alpha (float)}: Mutation Coefficient
-            \subsubitem \textit{alpha\_damp (float)}: Mutation Coefficient Damp Rate
-            \subsubitem \textit{delta (float)}: Mutation Step Size
-            \subsubitem \textit{exponent (int)}: Exponent
-        \subitem \textit{OriginalPSO:}
-            \subsubitem \textit{c1 (float)}: local coefficient
-            \subsubitem \textit{c2 (float)}: global coefficient
-            \subsubitem \textit{w\_min (float)}: Weight min of bird
-            \subsubitem \textit{w\_max (float)}: Weight max of bird
-
-\end{itemize}
-
-\subsection{Optimizer Parameters}
-\label{subsec:methodology-optimizer-parameters}
-
-For all optimizers and problems, were selected the following parameters:
-
-\begin{itemize}
-    \item \textit{Runs}: 100 runs
-    \item \textit{Epochs}: 100 epochs
-    \item \textit{Population}: 100 initial points
-\end{itemize}
-
-The initial solutions were randomly selected using the same seed for all algorithms.
-
-\section{Results}
-\label{sec:results}
-\subsection{Spring Tension Design}
-\label{ssubec:spring_problem}
-
-\begin{table}[H]
-\centering
-\caption{Statistical Information about function values for Spring Tension Design}
-\label{function_values:spring_problem}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrrrrr}
-\toprule
-Algorithm &      Min F &     Mean F &   Median F &      Max F &   StdDev F \\
-\midrule
-       EP & 0.01250534 & 0.01255960 & 0.01253156 & 0.01453933 & 0.00020190 \\
-       ES & 0.01252956 & 0.01281857 & 0.01274283 & 0.01346214 & 0.00024181 \\
-       GA & 0.01252305 & 0.01628575 & 0.01616768 & 0.02561808 & 0.00273276 \\
-    BeesA & 0.01250200 & 0.01268010 & 0.01261691 & 0.01406679 & 0.00021629 \\
-      FFA & 0.01249803 & 0.01254780 & 0.01253499 & 0.01268116 & 0.00003152 \\
-      PSO & 0.01252626 & 0.01390866 & 0.01318774 & 0.03036537 & 0.00342240 \\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{figure}[H]
-\centering
-\caption{Boxplot for Spring Tension Design}
-\label{fig:spring_tension_design_boxplot}
-\includegraphics[scale=0.5]{images/spring_problem_boxplot.png}
-\end{figure}
+Figure~\ref{fig:spring_problem_convergence} shows the
+function maximum, minimum and mean function of algorithm's evolution:
 
@@
 \label{fig:spring_problem_convergence}
-\includegraphics[width= 0.4 \textwidth]{images/spring_problem_convergence.png}
+\includegraphics[width=0.4 \textwidth]{images/spring_problem_convergence.png}
 \end{figure}
 
-\subsection{Pressure Vessel Design (Original)}
-\label{subsec:pressure_vessel_problem_original}
-
-\begin{table}[H]
-\centering
-\caption{Statistical Information about function values for Pressure Vessel Design (Original)}
-\label{function_values:pressure_vessel_problem_original}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrrrrr}
-\toprule
-Algorithm &         Min F &         Mean F &       Median F &          Max F &       StdDev F \\
-\midrule
-       EP &    0.08150806 &     0.15642850 &     0.09093798 &     1.32637552 &     0.16807714 \\
-       ES &    0.08161190 &   718.92910990 &     1.00278859 &  9443.54269260 &  2060.07774212 \\
-       GA &   17.06920868 &   525.00734162 &   361.53879602 &  3112.03503082 &   454.52386703 \\
-    BeesA & 2393.70106213 & 17564.33024022 & 15751.91467117 & 53850.38271384 & 10514.60780411 \\
-      FFA &    0.08306113 &     0.13296127 &     0.13106271 &     0.20084847 &     0.02396876 \\
-      PSO &    0.08149204 &     0.24191732 &     0.08159173 &    10.00611523 &     1.00072349 \\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{figure}[H]
-\centering
-\caption{Boxplot for Pressure Vessel Design (Original)}
-\label{fig:pressure_vessel_design_original_boxplot}
-\includegraphics[scale=0.5]{images/pressure_vessel_problem_original_boxplot.png}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\caption{Convergence lines for Pressure Vessel Design (Original)}
-\label{fig:pressure_vessel_problem_original_convergence}
-\includegraphics[width= 0.4 \textwidth]{images/pressure_vessel_problem_original_convergence.png}
-\end{figure}
-
-\subsection{Pressure Vessel Design}
-\label{subsec:pressure_vessel_problem}
-
-\begin{table}
-\centering
-\caption{Statistical Information about function values for Pressure Vessel Design}
-\label{function_values:pressure_vessel_problem}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrrrrr}
-\toprule
-Algorithm &         Min F &        Mean F &      Median F &         Max F &   StdDev F \\
-\midrule
-       EP & 5534.57345496 & 5534.63426098 & 5534.61416291 & 5534.92993607 & 0.05804548 \\
-       ES & 5534.57917966 & 5535.28165367 & 5535.06149254 & 5538.03003895 & 0.65098467 \\
-       GA & 5534.83662424 & 5538.36788889 & 5536.92932748 & 5550.91639342 & 3.57079951 \\
-    BeesA & 5534.57516657 & 5537.97495231 & 5537.04824684 & 5548.55587234 & 3.28239740 \\
-      FFA & 5534.57401617 & 5534.58849395 & 5534.58435493 & 5534.63296149 & 0.01341777 \\
-      PSO & 5534.57345480 & 5534.57381593 & 5534.57355270 & 5534.57625290 & 0.00053848 \\
-\bottomrule
-\end{tabular}
-}
-\end{table}
-
-\begin{figure}[H]
-\centering
-\caption{Boxplot for Pressure Vessel Design}
-\label{fig:pressure_vessel_design_boxplot}
-\includegraphics[scale=0.5]{images/pressure_vessel_problem_boxplot.png}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\caption{Convergence lines for Pressure Vessel Design}
-\label{fig:pressure_vessel_problem_convergence}
-\includegraphics[width=0.4 \textwidth]{images/pressure_vessel_problem_convergence.png}
-\end{figure}
-
-\subsection{Significance Test}
-\label{subsec:pressure_vessel_problem_significance_test}
-
-\begin{table}[H]
-\centering
-\caption{Significance Test Using Friedman Chi-Squared Test}
-\label{friedman_test}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrr}
-\toprule
-                          Problem &   Statistics &    p-value \\
-\midrule
-            Spring Tension Design & 339.05714286 & 0.00000000 \\
-           Pressure Vessel Design & 436.16000000 & 0.00000000 \\
-Pressure Vessel Design (Original) & 425.07428571 & 0.00000000 \\
-\bottomrule
-\end{tabular}
-}
-\end{table}
-
-\section{Discussion}
-
-The main objective of this work is demonstrate the inner work of a optimization class of algorithms called \textit{Quasi-Newton algorithms}.
-Four of them are presented, along with the results and analysis regarding convergence, function evaluations and function objective values.
-
-For implementation, it was decided to put constraints on search space, because for the original search space of some functions, like Ackley and Rastrigin, there are other minimas that will confuse every algorithm tested for this paper, and there is no sense on test a local minima procedure on these conditions.
-To restrain the initial solution to some region in the search space was a cheap and ready solution to avoid the algorithms to stop because of stumbling upon the wrong minimum.
-
-The \textit{Levenberg-Marquardt Algorithm} implemented for this paper is very sensitive to hyperparameters, namely $\alpha$ and $\lambda$, which was not tunned to every function, so, the conspicuous performance variation is noticeable along the results.
-LMA is known to be fast and reliable, but in our implementation it was found a little tricky to get the hyperparameters right for all the test functions.
-But for Rosenbrock and Rastrigin, it is the best option, even for lame implementations like ours.
-
-The \textit{Broyden–Fletcher–Goldfarb–Shanno} Algorithm was the only one that we decided to use it as is from \textit{SciPy}, because it has features desired for this work, like counting of function evaluations, gradient evaluation and iterations.
-It performed very well for Ackley and Booth Functions, and reasonably well for other functions.
-
-The \textit{Davidon–Fletcher–Powell} Algorithm is not implemented in \textit{SciPy} but its equations shows that it is the dual of BFGS, so, it was easy to implement using some \textit{SciPy} code for BFGS algorithm.
-In the DFP procedure, there is a Hessian inversion to be evaluated every iteration, then, numerical imprecision would be taken into consideration evaluating its results.
-While in some cases it has a superb performance (Like Ackley Function), it has very poor performance in Rosenbrock Function and even in Beale Function.
-The increase of dimensions makes DFP suffer of numerical imprecision due to the Hessian inversion, except for Rastrigin, and it is the loser algorithm in other functions.
-
-Finally, the \textit{Limited memory BFGS} has an average performance among the functions.
-The original algorithm was implemented using code found in the url https://github.com/qkolj/L-BFGS/blob/master/L-BFGS.ipynb.
-
-In fact, there are no Quasi-Newton algorithms that solver the minima problem for an any function.
-From the standpoint of performance and convergence, all the algorithms have an average performance and a reasonable convergence, although we have to restrain the search space to a small area near the optimal solution.
-
-\end{document}
+EP, ES and FFA have the best fitness.
+All algorithms seems to converge the minimum line very quickly when
+the algorithm find a minimal point.
+Apart from EP and ES, the algorithms seems to maintain exploration and exploitation
+until the time runs out.

### 2023-01-21 release/code/latex/includes/spring_problem_wilcoxon_test.tex
Release Added

--- 2023-01-19 latex/article.tex
@@
-\documentclass[conference]{IEEEtran}
-\IEEEoverridecommandlockouts
-% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-\usepackage{cite}
-\usepackage{amsmath,amssymb,amsfonts}
-\usepackage{mathtools}
-\usepackage{algpseudocode}
-\usepackage{algorithm}
-\usepackage{algorithmicx}
-\usepackage{microtype}
-\usepackage{float}
-\usepackage{adjustbox}
-\usepackage{booktabs,makecell,tabularx}
-\usepackage{graphicx}
-\usepackage{textcomp}
-\usepackage{verbatim}
-\usepackage{xcolor}
-\usepackage{graphics} % for pdf, bitmapped graphics files
-\usepackage{epsfig} % for postscript graphics files
-\usepackage{mathptmx} % assumes new font selection scheme installed
-\usepackage{multicol}
-\usepackage[english]{babel}
-\usepackage[T1]{fontenc}
-\restylefloat{table}
-\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
-    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
-\begin{document}
-\title{Swarm and Evolutionary Based Algorithms used for Optimization}
-\author{
-	\IEEEauthorblockN{Augusto Mathias Adams\IEEEauthorrefmark{1}, Caio Phillipe Mizerkowski\IEEEauthorrefmark{2}, Christian Piltz Araújo\IEEEauthorrefmark{3} and Vinicius Eduardo dos Reis\IEEEauthorrefmark{4}}\\
-	\IEEEauthorblockA{\IEEEauthorrefmark{1}GRR20172143, augusto.adams@ufpr.br, \IEEEauthorrefmark{2}GRR20166403, caiomizerkowski@gmail.com,\\ \IEEEauthorrefmark{3}GRR20172197, christian0294@yahoo.com.br, \IEEEauthorrefmark{4}GRR20175957, eduardo.reis02@gmail.com}
-}
-
-\maketitle
-
-\begin{abstract}
-    In this paper, a study of evolution and swarm based algorithms is presented,
-    using two classical engineering problems: \textit{Spring Tension} and \textit{Pressure Vessel
-    Designs}. The test code for the problems was made using the \textit{Python Language},
-    version 3.10 and uses \textit{MealPy} package, version 2.5.1,  to provide the algorithms.
-    The algorithms were randomly chosen from a vast list of \textit{MealPy}'s algorithms:
-    \textit{Evolutionary Programming (LevyEP)}, \textit{Evolution Strategies (OriginalES)} and
-    \textit{Genetic Algorithm (BaseGA)} from \textit{evolutionary\_based} subpackage;
-    \textit{Bees Algorithm (OriginalBeesA)}, \textit{Firefly Algorithm (OriginalFFA)} and
-    \textit{Particle Swarm Optimization (OriginalPSO)} from \textit{swarm\_based} subpackage.
-    Each problem was modeled using \textit{SciPy} package, with constraints implemented as
-    \textit{penalty functions}. Each algorithm were optimized separately to extract the best
-    solutions from each problem using the \textit{MealPy}'s \textit{Tuner} utility.
-    The results, however, are dependant of algorithm and/or problem solved and the Friedman's chi
-    squared test for similarity make it noticeable because, although the values for best fits are
-    similar, running the same algorithm with different initial conditions does not converge to similar
-    values.
-\end{abstract}
-
-\begin{IEEEkeywords}
-	Optimization Methods, Evolutionary Programming, Evolutionary and Swarm Based Strategies.
-\end{IEEEkeywords}
-
-\section{Definitions}
-\label{sec:definitions}
-
-The main objective of this paper is study evolutionary and swarm intelligence algorithms.
-We present the main concepts of these two algorithm's classes, along with the chosen algorithms
-definitions in this section. All citations made in this document are due to Swarm Intelligence classes
-and to \textit{MealPy}'s documentation, which points out the theoretical documentation for each
-implemented algorithm.
-
-\textit{\textbf{Evolution}}: From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolutionary Algorithms belong to the Evolutionary Computation
-field of study concerned with computational methods inspired by the process
-and mechanisms of biological evolution. The process of evolution by
-means of natural selection (descent with modification) was proposed by
-Darwin to account for the variety of life and its suitability (adaptive
-fit) for its environment. The mechanisms of evolution describe how
-evolution actually takes place through the modification and propagation
-of genetic material (proteins). Evolutionary Algorithms are concerned
-with investigating computational systems that resemble simplified ver-
-sions of the processes and mechanisms of evolution toward achieving
-the effects of these processes and mechanisms, namely the development
-of adaptive systems. Additional subject areas that fall within the realm
-of Evolutionary Computation are algorithms that seek to exploit the
-properties from the related fields of Population Genetics, Population
-Ecology, Coevolutionary Biology, and Developmental Biology.
-
-\textit{\textbf{Swarm Intelligence}}: From Jason Brownlee's \textit{``Clever Algorithms''} -
-Swarm intelligence is the study of computational systems inspired by
-the ‘collective intelligence’. Collective Intelligence emerges through the
-cooperation of large numbers of homogeneous agents in the environment.
-Examples include schools of fish, flocks of birds, and colonies of ants.
-Such intelligence is decentralized, self-organizing and distributed through
-out an environment. In nature such systems are commonly used to
-solve problems such as effective foraging for food, prey evading, or
-colony re-location. The information is typically stored throughout the
-participating homogeneous agents, or is stored or communicated in
-the environment itself such as through the use of pheromones in ants,
-dancing in bees, and proximity in fish and birds.
-
-\textit{\textbf{Evolutionary Programming:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolutionary Programming is a Global Optimization algorithm and is an instance of an Evolutionary
-Algorithm from the field of Evolutionary Computation. The approach is a sibling of other Evolutionary
-Algorithms such as the Genetic Algorithm, and Learning Classifier Systems. It is sometimes confused with Genetic
-Programming given the similarity in name, and more recently it shows a strong functional similarity to Evolution Strategies.
-Evolutionary Programming is inspired by the theory of evolution by means of natural selection. Specifically, the technique is inspired by
-macro-level or the species-level process of evolution (phenotype, hereditary, variation) and is not concerned with the genetic mechanisms of
-evolution (genome, chromosomes, genes, alleles).
-
-\textit{\textbf{Evolutionary Strategies:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-Evolution Strategies is a global optimization algorithm and is an instance of an Evolutionary Algorithm from the field of Evolutionary
-Computation. Evolution Strategies is a sibling technique to other Evolutionary Algorithms such as Genetic Algorithms (Section 3.2), Genetic
-Programming (Section 3.3), Learning Classifier Systems, and Evolutionary Programming. A popular descendant of
-the Evolution Strategies algorithm is the Covariance Matrix Adaptation Evolution Strategies (CMA-ES).
-
-\textit{\textbf{Genetic Algorithms:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-The Genetic Algorithm is an Adaptive Strategy and a Global Optimization technique. It is an Evolutionary Algorithm and belongs to the
-broader study of Evolutionary Computation. The Genetic Algorithm is a sibling of other Evolutionary Algorithms such as Genetic Programming,
- Evolution Strategies, Evolutionary Programming, and Learning Classifier Systems. The Genetic Algorithm is a parent of a large number of variant techniques
-and sub-fields too numerous to list. The Genetic Algorithm is inspired by population genetics (including heredity and gene frequencies),
-and evolution at the population level, as well as the Mendelian understanding of the structure (such as chromosomes, genes, alleles) and mechanisms
-(such as recombination and mutation). This is the so-called new or modern synthesis of evolutionary biology.
-
-\textit{\textbf{Particle Swarm Optimization:}} From Jason Brownlee's \textit{``Clever Algorithms''} - Particle Swarm Optimization belongs to the field of
-Swarm Intelligence and Collective Intelligence and is a sub-field of Computational Intelligence. Particle Swarm Optimization is related to other Swarm Intelligence
-algorithms such as Ant Colony Optimization and it is a baseline algorithm for many variations, too numerous to list. It is inspired by the social foraging behavior
-of some animals such as flocking behavior of birds and the schooling behavior of fish.
-
-\textit{\textbf{Firefly Algorithm:}} From Xin-She Yang \textit{``Nature-Inspired Metaheuristic Algorithms''} -
-The flashing light of fireflies is an amazing sight in the summer sky in the tropical and temperate regions. There are about two thousand firefly
-species, and most fireflies produce short and rhythmic flashes. The pattern of flashes is often unique for a particular species. The flashing light is
-produced by a process of bioluminescence, and the true functions of suchsignaling systems are still being debated. However, two fundamental functions
-of such flashes are to attract mating partners (communication), and to attract potential prey. In addition, flashing may also serve as a protective warning
-mechanism to remind potential predators of the bitter taste of fireflies. The firefly algorithm tries to mimic the attractiveness of Fireflies and has three
-basic rules:
-
-\begin{itemize}
-    \item All fireflies are unisex so that one firefly will be attracted to other
-          fireflies regardless of their sex;
-    \item Attractiveness is proportional to the their brightness, thus for any two
-          flashing fireflies, the less brighter one will move towards the brighter
-          one. The attractiveness is proportional to the brightness and they
-          both decrease as their distance increases. If there is no brighter one
-          than a particular firefly, it will move randomly;
-    \item The brightness of a firefly is affected or determined by the landscape
-          of the objective function.
-\end{itemize}
-
-\textit{\textbf{Bees Algorithm:}} From Jason Brownlee's \textit{``Clever Algorithms''} -
-The Bees Algorithm beings to Bee Inspired Algorithms and the field of Swarm Intelligence, and more broadly the fields of Computational
-Intelligence and Metaheuristics. The Bees Algorithm is related to other Bee Inspired Algorithms, such as Bee Colony Optimization, and other
-Swarm Intelligence algorithms such as Ant Colony Optimization and Particle Swarm Optimization.
-It is inspired by the foraging behavior of honey bees. Honey bees collect nectar from vast areas around their hive (more than
-10 kilometers). Bee Colonies have been observed to send bees to collect nectar from flower patches relative to the amount of food available at
-each patch. Bees communicate with each other at the hive via a waggle dance that informs other bees in the hive as to the direction, distance,
-and quality rating of food sources.
-
-\section{Methodology}
-\label{sec:methodology}
-
-\subsection{Optimization Problem Selection}
-\label{subsec:optimization-problem-selection}
-The two problems selected for this paper were \textit{Spring Tension Design} and \textit{Pressure Vessel Design}. Although it was simple
-to choose the first two problems from the computational work statements, the choice was more than justified because these aroblems are well
-known in the literature.
-Thus, the problem selection was driven by which has more than one source to compare results.
-
-\subsubsection{Spring Tension Design}
-\label{subsubsec:methodology-spring-tension-design}
-From \textit{Nature-Inspired Metaheuristic Algorithms - Xin-She Yang} -
-The design of a tension and compression spring is a well-known benchmark
-optimization problem.
-The main aim is to minimize the weight subject
-to constraints on deflection, stress, surge frequency and geometry. It involves
-three design variables: the wire diameter $x_1$ , coil diameter $x_2$ and
-number/length of the coil $x_3$.
-This problem can be summarized as:
-
-\begin{equation}
-    f (x) = x_1^2 x_2 (2 + x_3)
-\end{equation}
-
-subject to
-
-\begin{equation}
-    \begin{split}
-        g_1(x) = \frac{x_2^3 x_3}{71785 x_1^4} \leq 0\\
-        g_2(x) = \frac{4 x_2^2 - x_1 x_2}{12566 \left( x_1^3 x_2 - x_1^4\right)}\\
-        + \frac{1}{5108 x_1^2} -1 \leq 0\\
-        g_3(x) = 1 - \frac{140.45 x_1}{x_2^2 x_3} \leq 0\\
-        g_4 = \frac{x_1 + x_2}{1.5} - 1 \leq 0
-    \end{split}
-\end{equation}
-
-The original bounding limits of the variables, extracted from computational work
-statements, are:
-
-\begin{equation}
-    \begin{split}
-        0.05 \leq x_1 \leq 2.0\\
-        0.25 \leq x_2 \leq 1.3\\
-        2.0 \leq x_3 \leq 15.0
-    \end{split}
-\end{equation}
-
-\subsubsection{Pressure Vessel Design}
-\label{subsubsec:methodology-pressure-vessel-design}
-From \textit{Solving Design of Pressure Vessel Engineering
-Problem Using a Fruit Fly Optimization Algorithm - XIANTING KE et al} -
-A pressure vessel design model involves four decision variables: $x_1$ is defined
-thickness of the pressure vessel $T_s$ , $x_2$ stands for
-thickness of the head $T_H$ , $x_3$ represents inner radius of the
-vessel $R$ , and $x_4$ is on behalf of length of the vessel
-barring head $L$ , the total variables described as $( x_1 , x_2 , x_3 , x_4 )$.
-The objective function of the problem is to minimize the total cost, including
-the cost of material, forming, and welding.
-The general pressure vessel design optimization model is expressed as:
-
-\begin{equation}
-	\begin{split}
-        f(x) = 0.6224 x_1 x_3 x_4 + 1.7781 x_2 x_3^2 \\
-        + 3.1661 x_1^2 x_4 + 19.84 x_1^2 x_3
-	\end{split}
-\end{equation}
-
-subject to:
-
-\begin{equation}
-    \begin{split}
-        g_1(x) = - x_1 + 0.0193 x_3 \leq 0\\
-        g_2(x) = - x_2 + 0.00954 x_3 \leq 0\\
-        g_3(x) = - \pi x_3^2 x_4 -\frac{4}{3}\pi x_3^3 + 1296000 \leq 0\\
-        g_4(x) = x_4 -240 \leq 0\\
-    \end{split}
-\end{equation}
-
-The original bounding limits of the variables, extracted from computational work
-statements, are:
-
-\begin{equation}
-    \begin{split}
-        0 \leq x_1 \leq 99\\
-        0 \leq x_2 \leq 99\\
-        10 \leq x_3 \leq 200\\
-        10 \leq x_4 \leq 200\\
-    \end{split}
-\end{equation}
-
-For some reason these settings does not work at all with the selected optimizers, so
-some research in the literature \textit{Solving Design of Pressure Vessel Engineering
-Problem Using a Fruit Fly Optimization Algorithm - XIANTING KE et al} suggest the
-following bounding limits:
-
-\begin{equation}
-    \begin{split}
-        0.0625 \leq x_1 \leq 99 \times 0.0625\\
-        0.0625 \leq x_2 \leq 99 \times 0.0625\\
-        10 \leq x_3 \leq 200\\
-        10 \leq x_4 \leq 200
-    \end{split}
-\end{equation}
-
-But these settings produce many random, bizarre and noisy results in all selected optimizers. Then
-a proud-and-lame-homemade set of variable boundings comes in handy, obtained by tweaking the original
-boundings:
-
-\begin{equation}
-    \begin{split}
-        0.75 \leq x_1 \leq 0.8\\
-        0.35 \leq x_2 \leq 0.4\\
-        39.5 \leq x_3 \leq 41.0\\
-        195.0 \leq x_4 \leq 205.0\\
-    \end{split}
-\end{equation}
-
-It is not intended here to point out modeling errors of any kind, nor point out package
-errors made by the authors or ours, but the homemade bounding limits was necessary to
-reach the literature results.
-
-\subsection{Constraint Implementation}
-\label{subsec:methodology-constraint-implementation}
-The constraints that all problems are subjected were implemented as \textit{penalty functions},
-that is, it adds a high value when the constraint is not satisfied, zero otherwise. It is an optional requirement
-from computational work in question and is the recommended way to put constraints from \textit{MealPy}'s
-Manual.
-
-\subsection{Programming Language}
-\label{subsec:methodology-programming-language}
-
-The chosen programming language for the test code was \textit{Python Language}, version 3.10, because it is an opensource language easy to
-program and has a huge amount of packages regarding artificial intelligence, genetic algorithms and swarm based algorithms.
-From these packages it was selected \textit{MealPy} package, version 2.5.1, because it comprises all the algorithm's classed tested in this paper.
-
-\subsection{Algorithm Selection}
-\label{subsec:methodology-algorithm-selection}
-
-The algorithm selection was made in two steps: first, it was extracted simple version of the two classes (evolutionary and swarm based) and
-then it was used a simple shuffle using Python's \textit{random.shuffle} in a terminal - no script was required.
-
-The chosen algorithms were:
-
-\begin{itemize}
-    \item \textit{\textbf{Evolution Based Algorithms: }} LevyEP (Evolutionary Programming),
-    OriginalES (Evolution Strategy) and BaseGA (Genetic Algorithm)
-    \item \textit{\textbf{Swarm Based Algorithms: }} OriginalBeesA (Bees Algorithm),
-    OriginalFFA (Original Firefly Algorithm) and OriginalPSO (Particle Swarm Optimization)
-\end{itemize}
-
-\subsection{Optimizer Tuning}
-\label{subsec:methodology-optimizer-tuning}
-
-The hyperparameters for each optimizer were tuned using the \textit{MealPy}'s \textit{Tuner} utility.
-It is a recomended procedure to tune hyperparameters for each optimizer and problem, according to
-\textit{MealPy}'s Manual.
-The \textit{Tuner} utility is a very simple grid search metaheuristic search tool
-that test each grid configuration for a specified oprimizer runs.
-Although simple, it is a very expensive procedure that took 2 days to complete. It was defined 10 runs for each
-configuration, with the following set of hyperparameter:
-
-\begin{itemize}
-    \item \textit{\textbf{Evolution Based Algorithms: }}
-        \subitem \textit{LevyEP:}
-            \subsubitem \textit{bout\_size (float)}: percentage of child agents implement tournament selection.
-        \subitem \textit{OriginalES:}
-            \subsubitem \textit{lamda (float)}: Percentage of child agents evolving in the next generation.
-        \subitem \textit{BaseGA:}
-            \subsubitem \textit{pc (float)}: cross-over probability
-            \subsubitem \textit{pm (float)}: mutation probability
-    \item \textit{\textbf{Swarm Based Algorithms: }}
-        \subitem \textit{OriginalBeesA:}
-            \subsubitem \textit{selected\_site\_ratio (float)}
-            \subsubitem \textit{elite\_site\_ratio (float)}
-            \subsubitem \textit{selected\_site\_bee\_ratio (float)}
-            \subsubitem \textit{elite\_site\_bee\_ratio (float)}
-            \subsubitem \textit{dance\_radius (float)}
-            \subsubitem \textit{dance\_reduction (float)}
-        \subitem \textit{OriginalFFA:}
-            \subsubitem \textit{gamma (float)}: Light Absorption Coefficient
-            \subsubitem \textit{beta\_base (float)}: Attraction Coefficient Base Value
-            \subsubitem \textit{alpha (float)}: Mutation Coefficient
-            \subsubitem \textit{alpha\_damp (float)}: Mutation Coefficient Damp Rate
-            \subsubitem \textit{delta (float)}: Mutation Step Size
-            \subsubitem \textit{exponent (int)}: Exponent
-        \subitem \textit{OriginalPSO:}
-            \subsubitem \textit{c1 (float)}: local coefficient
-            \subsubitem \textit{c2 (float)}: global coefficient
-            \subsubitem \textit{w\_min (float)}: Weight min of bird
-            \subsubitem \textit{w\_max (float)}: Weight max of bird
-
-\end{itemize}
-
-\subsection{Optimizer Parameters}
-\label{subsec:methodology-optimizer-parameters}
-
-For all optimizers and problems, were selected the following parameters:
-
-\begin{itemize}
-    \item \textit{Runs}: 100 runs
-    \item \textit{Epochs}: 100 epochs
-    \item \textit{Population}: 100 initial points
-\end{itemize}
-
-The initial solutions were randomly selected using the same seed for all algorithms.
-
-\section{Results}
-\label{sec:results}
-\subsection{Spring Tension Design}
-\label{ssubec:spring_problem}
+The Table~\ref{wilcoxon_test:spring_problem} gives the Wilcoxon test results
+for \textit{Spring Tension Design} as exposed in Section~\ref{subsubsec:methodology-spring-tension-design}.
 
@@
 \centering
-\caption{Statistical Information about function values for Spring Tension Design}
-\label{function_values:spring_problem}
+\caption{Significance Test Using Wilcoxon Test for Spring Tension Design}
+\label{wilcoxon_test:spring_problem}
 \resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrrrrr}
+\begin{tabular}{lllllll}
 \toprule
-Algorithm &      Min F &     Mean F &   Median F &      Max F &   StdDev F \\
+  --- & EP & ES & GA & BeesA & FFA & PSO \\
 \midrule
-       EP & 0.01250534 & 0.01255960 & 0.01253156 & 0.01453933 & 0.00020190 \\
-       ES & 0.01252956 & 0.01281857 & 0.01274283 & 0.01346214 & 0.00024181 \\
-       GA & 0.01252305 & 0.01628575 & 0.01616768 & 0.02561808 & 0.00273276 \\
-    BeesA & 0.01250200 & 0.01268010 & 0.01261691 & 0.01406679 & 0.00021629 \\
-      FFA & 0.01249803 & 0.01254780 & 0.01253499 & 0.01268116 & 0.00003152 \\
-      PSO & 0.01252626 & 0.01390866 & 0.01318774 & 0.03036537 & 0.00342240 \\
+   EP & 0.0 & 1.47e-16 & 4.01e-18 & 4.37e-12 & 0.01 & 2.33e-16 \\
+   ES & 1.47e-16 & 0.0 &  1.90e-17 & 2.12e-06 & 3.24e-17 & 7.98e-12 \\
+   GA & 4.01e-18 &  1.90e-17 & 0.0 & 8.02e-18 & 4.27e-18 & 1.29e-11 \\
+BeesA & 4.36e-12 & 2.12e-06 & 8.02e-18 & 0.0 & 3.01e-11 & 6.82e-15 \\
+  FFA & 0.01 & 3.23e-17 & 4.27e-18 & 3.01e-11 & 0.0 & 9.32e-18 \\
+  PSO & 2.33e-16 & 7.98e-12 & 1.29e-11 & 6.82e-15 & 9.32e-18 & 0.0 \\
 \bottomrule
@@
 
-\begin{figure}[H]
-\centering
-\caption{Boxplot for Spring Tension Design}
-\label{fig:spring_tension_design_boxplot}
-\includegraphics[scale=0.5]{images/spring_problem_boxplot.png}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\caption{Convergence lines for Spring Tension Design}
-\label{fig:spring_problem_convergence}
-\includegraphics[width= 0.4 \textwidth]{images/spring_problem_convergence.png}
-\end{figure}
-
-\subsection{Pressure Vessel Design (Original)}
-\label{subsec:pressure_vessel_problem_original}
-
-\begin{table}[H]
-\centering
-\caption{Statistical Information about function values for Pressure Vessel Design (Original)}
-\label{function_values:pressure_vessel_problem_original}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrrrrr}
-\toprule
-Algorithm &         Min F &         Mean F &       Median F &          Max F &       StdDev F \\
-\midrule
-       EP &    0.08150806 &     0.15642850 &     0.09093798 &     1.32637552 &     0.16807714 \\
-       ES &    0.08161190 &   718.92910990 &     1.00278859 &  9443.54269260 &  2060.07774212 \\
-       GA &   17.06920868 &   525.00734162 &   361.53879602 &  3112.03503082 &   454.52386703 \\
-    BeesA & 2393.70106213 & 17564.33024022 & 15751.91467117 & 53850.38271384 & 10514.60780411 \\
-      FFA &    0.08306113 &     0.13296127 &     0.13106271 &     0.20084847 &     0.02396876 \\
-      PSO &    0.08149204 &     0.24191732 &     0.08159173 &    10.00611523 &     1.00072349 \\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\begin{figure}[H]
-\centering
-\caption{Boxplot for Pressure Vessel Design (Original)}
-\label{fig:pressure_vessel_design_original_boxplot}
-\includegraphics[scale=0.5]{images/pressure_vessel_problem_original_boxplot.png}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\caption{Convergence lines for Pressure Vessel Design (Original)}
-\label{fig:pressure_vessel_problem_original_convergence}
-\includegraphics[width= 0.4 \textwidth]{images/pressure_vessel_problem_original_convergence.png}
-\end{figure}
-
-\subsection{Pressure Vessel Design}
-\label{subsec:pressure_vessel_problem}
-
-\begin{table}
-\centering
-\caption{Statistical Information about function values for Pressure Vessel Design}
-\label{function_values:pressure_vessel_problem}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrrrrr}
-\toprule
-Algorithm &         Min F &        Mean F &      Median F &         Max F &   StdDev F \\
-\midrule
-       EP & 5534.57345496 & 5534.63426098 & 5534.61416291 & 5534.92993607 & 0.05804548 \\
-       ES & 5534.57917966 & 5535.28165367 & 5535.06149254 & 5538.03003895 & 0.65098467 \\
-       GA & 5534.83662424 & 5538.36788889 & 5536.92932748 & 5550.91639342 & 3.57079951 \\
-    BeesA & 5534.57516657 & 5537.97495231 & 5537.04824684 & 5548.55587234 & 3.28239740 \\
-      FFA & 5534.57401617 & 5534.58849395 & 5534.58435493 & 5534.63296149 & 0.01341777 \\
-      PSO & 5534.57345480 & 5534.57381593 & 5534.57355270 & 5534.57625290 & 0.00053848 \\
-\bottomrule
-\end{tabular}
-}
-\end{table}
-
-\begin{figure}[H]
-\centering
-\caption{Boxplot for Pressure Vessel Design}
-\label{fig:pressure_vessel_design_boxplot}
-\includegraphics[scale=0.5]{images/pressure_vessel_problem_boxplot.png}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\caption{Convergence lines for Pressure Vessel Design}
-\label{fig:pressure_vessel_problem_convergence}
-\includegraphics[width=0.4 \textwidth]{images/pressure_vessel_problem_convergence.png}
-\end{figure}
-
-\subsection{Significance Test}
-\label{subsec:pressure_vessel_problem_significance_test}
-
-\begin{table}[H]
-\centering
-\caption{Significance Test Using Friedman Chi-Squared Test}
-\label{friedman_test}
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{lrr}
-\toprule
-                          Problem &   Statistics &    p-value \\
-\midrule
-            Spring Tension Design & 339.05714286 & 0.00000000 \\
-           Pressure Vessel Design & 436.16000000 & 0.00000000 \\
-Pressure Vessel Design (Original) & 425.07428571 & 0.00000000 \\
-\bottomrule
-\end{tabular}
-}
-\end{table}
-
-\section{Discussion}
-
-The main objective of this work is demonstrate the inner work of a optimization class of algorithms called \textit{Quasi-Newton algorithms}.
-Four of them are presented, along with the results and analysis regarding convergence, function evaluations and function objective values.
-
-For implementation, it was decided to put constraints on search space, because for the original search space of some functions, like Ackley and Rastrigin, there are other minimas that will confuse every algorithm tested for this paper, and there is no sense on test a local minima procedure on these conditions.
-To restrain the initial solution to some region in the search space was a cheap and ready solution to avoid the algorithms to stop because of stumbling upon the wrong minimum.
-
-The \textit{Levenberg-Marquardt Algorithm} implemented for this paper is very sensitive to hyperparameters, namely $\alpha$ and $\lambda$, which was not tunned to every function, so, the conspicuous performance variation is noticeable along the results.
-LMA is known to be fast and reliable, but in our implementation it was found a little tricky to get the hyperparameters right for all the test functions.
-But for Rosenbrock and Rastrigin, it is the best option, even for lame implementations like ours.
-
-The \textit{Broyden–Fletcher–Goldfarb–Shanno} Algorithm was the only one that we decided to use it as is from \textit{SciPy}, because it has features desired for this work, like counting of function evaluations, gradient evaluation and iterations.
-It performed very well for Ackley and Booth Functions, and reasonably well for other functions.
-
-The \textit{Davidon–Fletcher–Powell} Algorithm is not implemented in \textit{SciPy} but its equations shows that it is the dual of BFGS, so, it was easy to implement using some \textit{SciPy} code for BFGS algorithm.
-In the DFP procedure, there is a Hessian inversion to be evaluated every iteration, then, numerical imprecision would be taken into consideration evaluating its results.
-While in some cases it has a superb performance (Like Ackley Function), it has very poor performance in Rosenbrock Function and even in Beale Function.
-The increase of dimensions makes DFP suffer of numerical imprecision due to the Hessian inversion, except for Rastrigin, and it is the loser algorithm in other functions.
-
-Finally, the \textit{Limited memory BFGS} has an average performance among the functions.
-The original algorithm was implemented using code found in the url https://github.com/qkolj/L-BFGS/blob/master/L-BFGS.ipynb.
-
-In fact, there are no Quasi-Newton algorithms that solver the minima problem for an any function.
-From the standpoint of performance and convergence, all the algorithms have an average performance and a reasonable convergence, although we have to restrain the search space to a small area near the optimal solution.
-
-\end{document}
+From Wilcoxon Test, the are no difference between all algorithms since p-value
+is less than $0.05$.

### 2023-01-21 release/code/Functions/PressureVessel.py

@@ -1,0 +1,96 @@
+"""
+Computational Work 02 - Evolutionary Computation
+Authors: Augusto Mathias Adams - augusto.adams@ufpr.br - GRR20172143
+         Caio Phillipe Mizerkowski - caiomizerkowski@gmail.com - GRR20166403
+         Christian Piltz Araújo - christian0294@yahoo.com.br - GRR20172197
+         Vinícius Eduardo dos Reis - eduardo.reis02@gmail.com - GRR20175957
+
+Pressure Vessel Design Problem
+optimal value: 5896.94890
+x* = (0.780956, 0.386318, 40.433956, 198.504889)
+"""
+
+import numpy as np
+
+
+def pressure_vessel_get_literature_solution():
+    return [0.780956, 0.386318, 40.433956, 198.504889]
+
+
+def pressure_vessel_function(x):
+    """
+    Function to minimize
+    :return: float
+    """
+    return 0.6224 * x[0] * x[2] * x[3] + \
+        1.7781 * x[1] * (x[2] ** 2) + \
+        3.1661 * (x[0] ** 2) * x[3] + \
+        19.84 * (x[0] ** 2) * x[2]
+
+
+def p_constraint_g1(x):
+    """
+    Constraing g1
+    :return: float
+    """
+    return -x[0] + 0.0193 * x[2]
+
+
+def p_constraint_g2(x):
+    """
+    Constraint g2
+    :return: float
+    """
+    return -x[1] + 0.00954 * x[2]
+
+
+def p_constraint_g3(x):
+    """
+    Constraint g3
+    :return: float
+    """
+    return -np.pi * (x[2] ** 2) * x[3] - (4 / 3) * np.pi * (x[2] ** 3) + 1296000
+
+
+def p_constraint_g4(x):
+    """
+    Constraint g4
+    :return: float
+    """
+    return x[3] - 240
+
+
+def violate(value):
+    """
+    Constraint Violation
+    :param value: constraint function value
+    :return: penalty value
+    """
+    return 0 if value <= 0 else value ** 10
+
+
+def pressure_vessel_get_lb():
+    return [0.75, 0.35, 39.5, 195.0]
+
+
+def pressure_vessel_get_ub():
+    return [0.8, 0.40, 41.0, 205.0]
+
+
+def pressure_vessel_get_lb_original():
+    return [0.0, 0.0, 10.0, 10.0]
+
+
+def pressure_vessel_get_ub_original():
+    return [99.0, 99.0, 200.0, 200.0]
+
+
[…]

### 2023-01-21 release/code/Functions/Spring.py

@@ -1,0 +1,93 @@
+"""
+Computational Work 02 - Evolutionary Computation
+Authors: Augusto Mathias Adams - augusto.adams@ufpr.br - GRR20172143
+         Caio Phillipe Mizerkowski - caiomizerkowski@gmail.com - GRR20166403
+         Christian Piltz Araújo - christian0294@yahoo.com.br - GRR20172197
+         Vinícius Eduardo dos Reis - eduardo.reis02@gmail.com - GRR20175957
+
+Spring Design Problem
+optimal value: 0.012665
+x∗ = (0.051690, 0.356750, 11.287126)
+"""
+
+
+def spring_get_literature_solution():
+    return [0.051690, 0.356750, 11.287126]
+
+
+def spring_function(x):
+    """
+    Function to minimize
+    :return: float
+    """
+    return (x[0] ** 2) * x[1] * (2 + x[2])
+
+
+def s_constraint_g1(x):
+    """
+    Constraing g1
+    :return: float
+    """
+    return 1 - (((x[1] ** 3) * x[2]) / (71785.0 * (x[0] ** 4)))
+
+
+def s_constraint_g2(x):
+    """
+    Constraint g2
+    :return: float
+    """
+    return ((4 * (x[1] ** 2) - x[0] * x[1]) / (12566.0 * ((x[0] ** 3) * x[1] - x[0] ** 4))) + \
+        (1 / (5108.0 * (x[0] ** 2))) - 1.0
+
+
+def s_constraint_g3(x):
+    """
+    Constraint g3
+    :return: float
+    """
+    return 1 - ((140.45 * x[0]) / ((x[1] ** 2) * x[2]))
+
+
+def s_constraint_g4(x):
+    """
+    Constraint g4
+    :return: python function
+    """
+    value = ((x[0] + x[1]) / 1.5) - 1
+    return value
+
+
+def violate(value):
+    """
+    Constraint Violation
+    :param value: constraint function value
+    :return: penalty value
+    """
+    return 0 if value <= 0 else value ** 2
+
+
+def spring_get_lb():
+    """
+    Lower bound
+    :return: array
+    """
+    return [0.05, 0.25, 2.0]
+
+
+def spring_get_ub():
+    """
+    Upper bound
+    :return: array
+    """
+    return [2.0, 1.3, 15.0]
+
+
+def spring_fitness_function(solution):
+    fx = spring_function(solution)
+
+    fx += violate(s_constraint_g1(solution)) + \
[…]

### 2023-01-21 release/code/Functions/__init__.py

@@ -1,0 +1,20 @@
+from .Spring import spring_fitness_function, \
+    spring_get_lb, \
+    spring_get_ub, \
+    spring_get_literature_solution, \
+    spring_function, \
+    s_constraint_g1, \
+    s_constraint_g2, \
+    s_constraint_g3, \
+    s_constraint_g4
+from .PressureVessel import pressure_fitness_function, \
+    pressure_vessel_get_lb, \
+    pressure_vessel_get_ub, \
+    pressure_vessel_get_lb_original, \
+    pressure_vessel_get_ub_original, \
+    pressure_vessel_get_literature_solution, \
+    pressure_vessel_function, \
+    p_constraint_g1, \
+    p_constraint_g2, \
+    p_constraint_g3, \
+    p_constraint_g4

### 2023-01-21 release/code/runner.py

@@ -1,0 +1,243 @@
+"""
+Computational Work 02 - Evolutionary Computation
+Authors: Augusto Mathias Adams - augusto.adams@ufpr.br - GRR20172143
+         Caio Phillipe Mizerkowski - caiomizerkowski@gmail.com - GRR20166403
+         Christian Piltz Araújo - christian0294@yahoo.com.br - GRR20172197
+         Vinícius Eduardo dos Reis - eduardo.reis02@gmail.com - GRR20175957
+
+Optimization Runner
+"""
+
+import json
+import numpy as np
+
+from mealpy.evolutionary_based import ES, EP, GA
+from mealpy.swarm_based import BeesA, FFA, PSO
+from mealpy.utils import io
+
+from Functions import spring_fitness_function, \
+    pressure_fitness_function, \
+    spring_get_lb, \
+    spring_get_ub, \
+    pressure_vessel_get_lb, \
+    pressure_vessel_get_ub, \
+    pressure_vessel_get_lb_original, \
+    pressure_vessel_get_ub_original, \
+    spring_function, \
+    spring_get_literature_solution, \
+    pressure_vessel_function, \
+    pressure_vessel_get_literature_solution
+
+
+def create_starting_positions(rseed,
+                              n_dims,
+                              pop_size,
+                              lb,
+                              ub):
+    """
+    Initial population
+    :param rseed: random seed
+    :param n_dims: problem dimention
+    :param pop_size: population size
+    :param lb: lower bound
+    :param ub: upper bound
+    :return: initial population
+    """
+    rng = np.random.default_rng(rseed)
+    random_extractions = rng.random((pop_size, n_dims))
+    for i in range(0, n_dims):
+        random_extractions[:, i] = (ub[i] - lb[i]) * random_extractions[:, i] + lb[i]
+    return random_extractions
+
+
+# common
+epochs = 100
+
+pop_size = 100
+
+runs = 100
+
+spring_default_solution = spring_get_literature_solution()
+
+print(spring_function(spring_default_solution))
+
+print(spring_fitness_function(spring_default_solution))
+
+pressure_vessel_default_solution = pressure_vessel_get_literature_solution()
+
+print(pressure_vessel_function(pressure_vessel_default_solution))
+
+print(pressure_fitness_function(pressure_vessel_default_solution))
+
+# problems
+
+problems = {"spring_problem": {"lb": spring_get_lb(),
+                               "ub": spring_get_ub(),
+                               "minmax": "min",
[…]

### 2023-01-21 release/code/tuning.py

@@ -1,0 +1,135 @@
+"""
+Computational Work 02 - Evolutionary Computation
+Authors: Augusto Mathias Adams - augusto.adams@ufpr.br - GRR20172143
+         Caio Phillipe Mizerkowski - caiomizerkowski@gmail.com - GRR20166403
+         Christian Piltz Araújo - christian0294@yahoo.com.br - GRR20172197
+         Vinícius Eduardo dos Reis - eduardo.reis02@gmail.com - GRR20175957
+
+Algorithm Tuner
+"""
+
+import numpy as np
+import json
+from mealpy.tuner import Tuner
+from mealpy.evolutionary_based import ES, EP, GA
+from mealpy.swarm_based import BeesA, FFA, PSO
+from Functions import spring_fitness_function, \
+    pressure_fitness_function, \
+    spring_get_lb, \
+    spring_get_ub, \
+    pressure_vessel_get_lb, \
+    pressure_vessel_get_ub
+
+#: common
+
+epochs = 100
+
+pop_size = 100
+
+#: problems
+
+problems = {"spring_problem": {"lb": spring_get_lb(),
+                               "ub": spring_get_ub(),
+                               "minmax": "min",
+                               "fit_func": spring_fitness_function,
+                               "verbose": False,
+                               "name": "Spring Tension Design",
+                               "log_to": None},
+            "pressure_vessel_problem": {"lb": pressure_vessel_get_lb(),
+                                        "ub": pressure_vessel_get_ub(),
+                                        "minmax": "min",
+                                        "verbose": False,
+                                        "fit_func": pressure_fitness_function,
+                                        "name": "Pressure Vessel Design",
+                                        "log_to": None}}
+
+# algorithms
+
+algorithms = {"solve_ep": EP.LevyEP,
+              "solve_es": ES.OriginalES,
+              "solve_ga": GA.BaseGA,
+              "solve_beesa": BeesA.OriginalBeesA,
+              "solve_ffa": FFA.OriginalFFA,
+              "solve_pso": PSO.OriginalPSO}
+
+alg_params = {"solve_ep": {"epoch": [epochs],
+                           "pop_size": [pop_size],
+                           "bout_size": [0.05, 0.06, 0.07, 0.08,
+                                         0.09, 0.1, 0.11, 0.12,
+                                         0.13, 0.14, 0.15, 0.16,
+                                         0.17, 0.18, 0.19, 0.2]},
+              "solve_es" :{"epoch": [epochs],
[…]
